\documentclass[a4paper]{amsart}
\usepackage[margin=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\title[PA\textsuperscript{2}IN]{PDE, Analysis, Artificial Intelligence and Numerics}

\begin{document}
\maketitle

\section*{Event Overview}

\begin{description}
  \item[Event title] PDE, Analysis, Artificial Intelligence and Numerics.
  \item[Dates] January 25 - January 29, with flexibility if the institute requires adjustments.
  \item[Estimated number of participants] 50--100 participants.
\end{description}

\section*{Organizers}

\begin{itemize}
  \item Jo\~ao Pedro Ramos (IMPA)
  \item Jaume de Dios (NYU)
  \item Mitchell Taylor (Oxford/Toronto)
  \item Javier G\'omez-Serrano (Brown University) 
\end{itemize}

\section*{Requested Resources}

\begin{description}
  \item[Financial] R\$30,000.
  \item[Administrative] Assistance with local issues and logistical support.
  \item[Space] One large auditorium (likely Audit\'orio 2) and shared usage of the main hall for a poster session, necessitating only the use of digital screens for poster projection.
\end{description}

\section*{Brief Description}

Historically, the use of computers to prove mathematical theorems has been restricted mainly to brute-force computations. Recently, however, there has been a surge in the use of artificial intelligence - in particular large language models - to prove, disprove, and formally verify the correctness of mathematical statements.

This conference aims to bring together communities from different areas of analysis where large language models and artificial intelligence have recently had an impact. The goal is to exchange methods, expand the scope of current techniques, and foster collaboration and further improvements in the use of large language models for mathematics.

\section*{Examples of Speakers to be invited}

\begin{itemize}
  \item Scott Armstrong (NYU)
  \item Joaquim Serra (ETH Zurich)
  \item Christoph Thiele (Bonn)
  \item Jorge Poco (FGV)
  \item Terence Tao (UCLA)
  \item Felipe Gonçalves (IMPA) 
  \item Danylo Radchenko (CNRS/IHÉS)
  \item Henry Cohn (MIT/Microsoft Research)
  \item Amaury Hayat (ENPC)
\end{itemize}

\end{document}
