\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\Om}{\Omega}
\newcommand{\R}{\mathbb R}
\newcommand{\dT}{\delta_T}
\newcommand{\A}{\mathcal A}
\newcommand{\Et}{E_{\hat t}}
\newcommand{\eps}{\varepsilon}

\title{Brandolini and the Plan 3 Entry Theorem}
\author{}
\date{May 2026}

\begin{document}
\maketitle

\section{Purpose}

This note rechecks whether the remaining entry theorem in the planar hybrid
route can be supplied by Brandolini--Nitsch--Salani--Trombetti together with
the other Plan 3 ingredients.

The answer is:

\begin{quote}
\emph{Brandolini supplies the correct Serrin-to-near-ball input, and the
corrected \(\sqrt{\dT}\)-stopping scale makes this input usable.  However,
Brandolini does not by itself give the radial graph/radialization theorem
needed for the sharp conclusion with constants independent of the stopped
level.  One planar no-fjord/radialization lemma is still missing.}
\end{quote}

This is a positive recheck, not a negative one: the missing lemma is now much
narrower than the previous graph-entry statement.

\section{The stopped level}

Let \(n=2\), normalize \(|U|=\pi\), and set
\[
   \delta=\dT(U),\qquad a=\alpha(U).
\]
In the bad alternative for the desired estimate, \(a>M\sqrt\delta\).  Choose
\[
   \lambda=K\sqrt\delta.
\]
The volume-variable Chebyshev extraction, applied to the joint integrand
\(D_H+D_I\), gives a regular level \(\Et=\{u>\hat t\}\) with
\[
   |U\setminus \Et|\le \lambda,\qquad
   D_H(\hat t)+D_I(\hat t)\le C\frac{\delta}{\lambda}
      =\frac{C}{K}\sqrt\delta .
   \tag{2.1}\label{eq:good-level}
\]
The exact profile transfer gives
\[
   \dT(\Et)\le \frac{1}{1-\lambda/\pi}\,\dT(U)\le 2\delta
   \tag{2.2}\label{eq:def-transfer}
\]
for small \(\delta\).  This is the \(u-\hat t=u_{\Et}\) identity, not a
monotonicity principle.

On the selected class, the \(D_H\)-to-\(L^\infty\) interpolation estimate
from the companion note gives
\[
   \bigl\||\nabla u|-\bar f\bigr\|_{L^\infty(\partial\Et)}
      \le
   C\left(\frac{\delta}{\lambda^2}\right)^{1/3}
      = C K^{-2/3}.
   \tag{2.3}\label{eq:linfty-serrin}
\]
Thus \(K\) fixed and large makes \(\Et\) an approximate Serrin domain in the
pointwise sense.

\section{What Brandolini Gives}

Let \(v=u-\hat t\), so \(v=u_{\Et}\).  After scaling \(v\) by the harmless
dimensional factor that turns \(-\Delta v=1\) into Brandolini's
\(\Delta w=2\) normalization, \eqref{eq:linfty-serrin} implies
\[
   \bigl||Dw|-1\bigr|\le \eps_K
   \quad\hbox{on }\partial\Et,
   \qquad
   \eps_K\to0\quad(K\to\infty),
   \tag{3.1}\label{eq:B-hyp}
\]
up to the harmless adjustment of the target constant coming from
\(|\Et|=\pi+O(\sqrt\delta)\).

Brandolini et al. give two different outputs.

\subsection{Theorem 1: measure closeness to a union of balls}

Their Theorem 1 needs smoothness, bounded diameter, the upper bound
\(|Dw|\le1+\eps_K\), and \(L^1(\partial\Et)\)-closeness of \(|Dw|\) to \(1\).
Our \(L^\infty\) bound gives both boundary assumptions.  The constant depends
only on the diameter in this theorem.  Hence \(\Et\) is close in measure to a
finite union of almost unit balls:
\[
   \left|\Et\Delta\bigcup_{i=1}^m B_i\right|
      \le C\,\eps_K^\beta.
   \tag{3.2}\label{eq:B-measure}
\]
For \(K\) large, and after removing the satellite components controlled by
\(D_I\) below, the volume normalization forces \(m=1\).  Thus Brandolini gives
a robust near-ball location and a center without importing BDV.

\subsection{Theorem 2: annular containment}

Their Theorem 2 says that if the domain is connected and \(C^{2,\alpha}\),
then
\[
   R_{\rm out}-R_{\rm in}\le C\,\eps_K^\mu.
   \tag{3.3}\label{eq:B-annulus}
\]
But here \(C\) depends on the \(C^{2,\alpha}\) regularity constants of the
boundary.  For a stopped torsion level those constants are not uniform from
the information currently proved.  At depth \(\lambda=K\sqrt\delta\), interior
estimates only give schematically
\[
   \|D^2u\|_{L^\infty}\lesssim \lambda^{-1},\qquad
   \|D^3u\|_{L^\infty}\lesssim \lambda^{-2},
   \tag{3.4}
\]
while \(|\nabla u|\) is bounded below on the level.  Thus a direct
implicit-function \(C^{2,\alpha}\) norm for \(\partial\Et\) can blow like a
negative power of \(\lambda\).  Since \(K\) is fixed in the contradiction
argument, \(\eps_K\) is fixed; it cannot compensate for a constant blowing as
\(\delta\downarrow0\).

Therefore Brandolini's Theorem 2 cannot be used as a black box with uniform
constants unless one proves a new uniform regularity estimate for the stopped
levels.  That estimate would essentially be a graph-entry theorem in another
form.

\section{What Plan 3 Adds}

The Plan 3 and Plan 2 files contain several ingredients that partly replace
the regularity-dependent part of Brandolini.

\subsection{Satellites}

Let \(E_0\) be the largest indecomposable component of \(\Et\).  Since
\(D_I(\hat t)\le \eta\), where
\[
   \eta:=C K^{-1}\sqrt\delta,
\]
the planar component estimate in
\texttt{PLANAR\_GRAPH\_REDUCTION\_PUSH.tex} gives
\[
   |\Et\setminus E_0|\le C\eta^2\le C_K\delta.
   \tag{4.1}\label{eq:satellites}
\]
The Saint--Venant bound on each small component gives a negligible torsion
contribution.  Thus satellites are not an obstruction.

\subsection{Closed holes}

The same planar perimeter bookkeeping gives that bounded holes whose total
boundary perimeter is \(p_h\) have total area at most \(p_h^2/(4\pi)\).  Since
their perimeter is part of the isoperimetric excess at the good level,
\[
   |H_{\rm holes}|\le C\eta^2\le C_K\delta.
   \tag{4.2}\label{eq:holes}
\]
Filling closed holes is compatible with the torsion deficit by the monotone
filling lemma in \texttt{PLANAR\_RADIALIZATION\_PROOF\_ATTEMPT.tex}.

\subsection{Outer annular control}

Brandolini Theorem 1 gives small measure distance to one ball once \(K\) is
large.  Together with \(D_I(\hat t)\to0\), the planar Lemma 10 mechanism in
Brandolini gives a small outer excursion.  In dimension two the final step of
that argument is purely length-theoretic: a connected set reaching a distance
\(s\) outside the selected ball pays perimeter outside the ball at least
comparable to \(s\).  Thus the outer radius can be made smaller than the
fixed graph-entry threshold by choosing \(K\) large and then \(\delta\) small.

This part does not require a uniform \(C^{2,\alpha}\) constant in dimension
two.

\subsection{Outward fingers and bad rays}

The \(n=2\) tentacle computation in the repo is favorable.  A surviving tube
of width \(w\) and length \(L\) has active-level cost
\[
   D_H\simeq L/w.
\]
Thus a \(D_H\)-good level cannot carry an arbitrary long thin active finger.
Plan 2's radial slicing gives a separate bad-ray multiplicity absorption once
an annular bracket is known.  These are genuine ingredients for converting
annular near-ball information into radialization.

\section{The Point Still Not Proved}

The remaining issue is the inner and multiple-crossing geometry.  Brandolini's
Theorem 1 allows thin tentacles and gives only measure closeness.  Brandolini's
Theorem 2 would give inner and outer radii, but its constant depends on
boundary regularity.  Planar perimeter estimates rule out deep fjords at a
fixed scale, and capacity rules out missing sets at positive torsion height,
but the repo does not yet contain the arbitrary-geometry theorem that combines
these facts at the sharp torsion scale.

The exact missing lemma is the following.

\begin{conjecture}[Planar Brandolini--Plan 3 radialization lemma]
\label{conj:entry}
Let \(E=\Et\subset\R^2\) be a regular \(\sqrt\delta\)-stopped level satisfying
\eqref{eq:good-level}, \eqref{eq:def-transfer}, and
\eqref{eq:linfty-serrin}, with \(K\) fixed sufficiently large.  Then, after
translation and area normalization, there is a radial graph
\[
   G=\{re^{i\theta}:0<r<1+\varphi(\theta)\},
   \qquad
   \|\varphi\|_{L^\infty}\le \eta_0,
\]
such that
\[
   |E\Delta G|\le C_K\sqrt\delta,
   \qquad
   \dT(G)\le C_K\delta .
   \tag{5.1}\label{eq:radialization}
\]
\end{conjecture}

This lemma is weaker than literal graph entry for \(E\).  It permits filling
shallow fjords and holes and pruning outward debris.  It is also exactly what
the hybrid proof needs: the direct radial-graph theorem gives
\[
   \A(G)^2\le C\,\dT(G)\le C_K\delta,
\]
and then
\[
   \A(E)\le \A(G)+C|E\Delta G|\le C_K\sqrt\delta.
\]
The transfer from \(E\) to \(U\) costs another \(O(K\sqrt\delta)\), so the
desired estimate follows.

\section{Verdict}

The user's instinct is correct in the following precise sense.  The repo
contains the right ingredients around Brandolini:
\[
   \begin{gathered}
   \hbox{pointwise Serrin level}
   +\hbox{Brandolini measure near-ball}\\
   +\,D_I\hbox{ satellite/hole cleanup}
   +D_H\hbox{ thin-finger control}
   +\hbox{Plan 2 bad-ray slicing}.
   \end{gathered}
\]
These reduce the missing entry theorem to
Conjecture~\ref{conj:entry}.

But Conjecture~\ref{conj:entry} is not yet proved in the repo.  The tempting
shortcut through Brandolini's annulus theorem is not uniform, because its
constant depends on \(C^{2,\alpha}\) boundary regularity of the stopped level.
The remaining work is therefore not another Serrin theorem.  It is a planar
geometric radialization theorem showing that the pieces not already handled by
Brandolini measure closeness, \(D_I\), \(D_H\), and bad-ray slicing can be
filled or pruned with \(O(\sqrt\delta)\) measure loss and \(O(\delta)\)
torsion-deficit cost.

\end{document}
