\documentclass[11pt]{article}

\usepackage[a4paper,margin=2.6cm]{geometry}
\usepackage{fontspec}
\setmainfont{Comic Neue}
\setsansfont{Comic Neue}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\R}{\mathbb R}
\newcommand{\dd}{\,d}
\newcommand{\1}{\mathbf 1}
\newcommand{\calD}{\mathcal D}
\newcommand{\calL}{\mathcal L}
\newcommand{\LambdaU}{\Lambda_U}

\title{The \(h_1\) Boundary Equation from the DtN Strategy}
\author{}
\date{}

\begin{document}
\maketitle

\section{From localization to a real free-boundary problem}

Let \(U\subset\C\simeq\R^2\) be bounded.  In the Bargmann model, the condition that
\(h_1\) be an eigenfunction for the \(h_1\)-window localization operator gives
\begin{equation}\label{eq:h1-localization}
  \int_U (1-\pi |z|^2)e^{-\pi |z|^2}(w-z)e^{\pi w\bar z}\dd A(z)
  =
  \lambda w ,
  \qquad w\in\C .
\end{equation}
Set
\[
  a(r):=(1-\pi r^2)e^{-\pi r^2},
  \qquad
  \rho(r):=(1-4\pi r^2+\pi^2r^4)e^{-\pi r^2}.
\]
Differentiating \eqref{eq:h1-localization} in \(w\) gives
\begin{equation}\label{eq:differentiated-identity}
  \int_U a(|z|)
  \bigl(1-\pi |z|^2+\pi w\bar z\bigr)e^{\pi w\bar z}\dd A(z)
  =
  \lambda .
\end{equation}

Let \(x=(x_1,x_2)\in\R^2\) denote the point \(z=x_1+ix_2\), and define the compactly
supported real distribution
\begin{equation}\label{eq:Omega-def}
  \Omega
  :=
  \rho(|x|)\1_U
  -a(|x|)(x\cdot\nu)\,\delta_{\partial U}
  +\lambda\delta_0 ,
\end{equation}
where \(\nu\) is the outward unit normal.  Equivalently, since
\(\nabla\1_U=-\nu\delta_{\partial U}\),
\[
  \Omega
  =
  \rho(|x|)\1_U+a(|x|)\,x\cdot\nabla\1_U+\lambda\delta_0 .
\]

\begin{lemma}\label{lem:annihilation}
For every \(w\in\C\),
\[
  \bigl\langle \Omega,e^{\pi w\bar z}\bigr\rangle=0.
\]
Since \(\Omega\) is real-valued, also
\[
  \bigl\langle \Omega,e^{\pi \bar w z}\bigr\rangle=0.
\]
\end{lemma}

\begin{proof}
Let \(\phi_w(z)=e^{\pi w\bar z}\).  The radial vector field \(a(|x|)x\) satisfies
\[
  \operatorname{div}(a(|x|)x)
  =
  2(1-3\pi |x|^2+\pi^2|x|^4)e^{-\pi |x|^2},
\]
and therefore
\begin{equation}\label{eq:rho-div-identity}
  \rho(|x|)-\operatorname{div}(a(|x|)x)
  =
  -a(|x|)(1-\pi |x|^2).
\end{equation}
Moreover,
\[
  x\cdot\nabla\phi_w=\pi w\bar z\,\phi_w .
\]
Using the divergence theorem in the distributional form encoded by
\eqref{eq:Omega-def}, we get
\begin{align*}
  \langle\Omega,\phi_w\rangle
  &=
  \int_U \rho(|x|)\phi_w\,\dd A
  -
  \int_{\partial U}a(|x|)(x\cdot\nu)\phi_w\,\dd s
  +\lambda \\
  &=
  \int_U
  \bigl(\rho(|x|)-\operatorname{div}(a(|x|)x)\bigr)\phi_w\,\dd A
  -
  \int_U a(|x|)\,x\cdot\nabla\phi_w\,\dd A
  +\lambda \\
  &=
  -\int_U a(|z|)
  \bigl(1-\pi |z|^2+\pi w\bar z\bigr)e^{\pi w\bar z}\dd A(z)
  +\lambda .
\end{align*}
This vanishes by \eqref{eq:differentiated-identity}.  Taking complex conjugates gives
the second assertion.
\end{proof}

By the same Paley--Wiener/Ehrenpreis--Malgrange divisibility input used in the
Section~4 argument, Lemma~\ref{lem:annihilation} yields a compactly supported real
distribution \(u\) such that
\begin{equation}\label{eq:global-poisson}
  \Delta u=\Omega .
\end{equation}
Thus, away from the origin and in the classical regime where \(u\) is represented by a
function in \(U\) and is extended by zero outside \(U\), \eqref{eq:global-poisson}
means
\begin{equation}\label{eq:BVP}
  \Delta u=\rho(|x|)
  \quad\text{in }U,\qquad
  u=0,\quad
  \partial_\nu u=a(|x|)(x\cdot\nu)
  \quad\text{on }\partial U .
\end{equation}
The point mass \(\lambda\delta_0\) is radial and is irrelevant for the boundary
calculation below as long as \(0\notin\partial U\).

\section{Subtracting a radial particular solution}

There is a simpler way to turn \eqref{eq:BVP} into a DtN equation.  Let \(V=V(r)\)
be radial and satisfy
\[
  \Delta V=\rho(r)
  \qquad\text{in }U
\]
away from the source point.  Set
\[
  h:=u-V .
\]
Then
\[
  \Delta h=0
  \qquad\text{in }U
\]
away from the source point.  If \(V\) is chosen with the same logarithmic source as
the distributional solution \(u\), then this harmonicity is distributional in all of
\(U\).

The boundary data are explicit.  Since \(u=0\) on \(\partial U\),
\begin{equation}\label{eq:radial-sub-dirichlet}
  h=-V(r)
  \qquad\text{on }\partial U .
\end{equation}
Moreover,
\[
  \nabla V=V'(r)\frac{x}{r},
  \qquad
  \partial_\nu V=\frac{V'(r)}{r}(x\cdot\nu).
\]
Using the Neumann condition in \eqref{eq:BVP}, we get
\begin{equation}\label{eq:radial-sub-neumann}
  \partial_\nu h
  =
  \left(a(r)-\frac{V'(r)}{r}\right)(x\cdot\nu)
  \qquad\text{on }\partial U .
\end{equation}
Consequently the same information is the DtN equation
\begin{equation}\label{eq:radial-sub-dtn}
  \boxed{
  \Lambda_U\bigl(-V(r)\bigr)
  =
  \left(a(r)-\frac{V'(r)}{r}\right)(x\cdot\nu)
  \qquad\text{on }\partial U .
  }
\end{equation}
This is the cleaner DtN formulation: after subtracting a radial particular solution,
one applies the DtN map to a radial boundary function.

For the regular radial particular solution at the origin,
\[
  \frac{V'(r)}{r}
  =
  P(r^2),
  \qquad
  P(t):=\frac{1}{2t}\int_0^t\rho(\sqrt\sigma)\,\dd\sigma .
\]
For the \(h_1\) density this is
\begin{equation}\label{eq:P-explicit}
  P(t)
  =
  \frac{e^{-\pi t}(1+2\pi t-\pi^2t^2)-1}{2\pi t},
  \qquad
  P(0)=\frac12 .
\end{equation}
Thus
\begin{equation}\label{eq:regular-radial-sub-dtn}
  \boxed{
  \Lambda_U\bigl(-V(r)\bigr)
  =
  \bigl(a(r)-P(r^2)\bigr)(x\cdot\nu)
  \qquad\text{on }\partial U .
  }
\end{equation}
If the source \(\lambda\delta_0\) is included in the radial particular solution, replace
\[
  V(r)
  \quad\text{by}\quad
  V(r)+\frac{\lambda}{2\pi}\log r .
\]
Then the right-hand coefficient in \eqref{eq:regular-radial-sub-dtn} becomes
\[
  a(r)-P(r^2)-\frac{\lambda}{2\pi r^2}.
\]

\section{The DtN boundary equation}

Let
\[
  X(x):=(-x_2,x_1),\qquad L:=X\cdot\nabla ,
\]
and set
\[
  v:=Lu .
\]
Since \(L\) commutes with \(\Delta\) and annihilates radial distributions,
\[
  \Delta v=0
  \qquad\text{in }U .
\]
Thus \(v\) is the harmonic function in \(U\) with the boundary trace computed from
\eqref{eq:BVP}.  On \(\partial U\), the zero Dirichlet trace implies
\[
  \nabla u=(\partial_\nu u)\nu=q\nu,
  \qquad
  q:=a(|x|)(x\cdot\nu).
\]
Therefore
\begin{equation}\label{eq:v-boundary-trace}
  v|_{\partial U}
  =
  q(X\cdot\nu).
\end{equation}
If \(\Lambda_U\) denotes the Dirichlet-to-Neumann map for harmonic functions in \(U\),
then
\begin{equation}\label{eq:dtn-side}
  \partial_\nu v
  =
  \Lambda_U\bigl(q(X\cdot\nu)\bigr)
  \qquad\text{on }\partial U .
\end{equation}

\subsection{Parametrized form of the DtN term}

The term in \eqref{eq:dtn-side} can be written explicitly from a boundary
parametrization.  Since \(U\) is simply connected, write
\[
  \partial U=\Gamma,\qquad
  \gamma:\R/L\mathbb Z\to\Gamma
\]
for an arclength parametrization, with outward normal \(\nu(s)\).  Let
\[
  G_0(x,y):=\frac{1}{2\pi}\log|x-y|
\]
be the planar fundamental solution for \(\Delta\).  For a boundary density \(\mu\),
define the double-layer operator
\[
  (D\mu)(x):=
  \int_0^{L}
  \partial_{\nu(t)}G_0(x,\gamma(t))\,\mu(t)\,\dd t .
\]
Its interior trace is
\[
  (D\mu)|_{\partial U}^{\mathrm{int}}
  =
  \Bigl(\frac12 I+K\Bigr)\mu,
\]
where, for \(s\in\R/L\mathbb Z\),
\begin{equation}\label{eq:K-operator}
  (K\mu)(s)
  =
  \operatorname{p.v.}\int_0^{L}
  \frac{(\gamma(t)-\gamma(s))\cdot\nu(t)}
       {2\pi|\gamma(s)-\gamma(t)|^2}
  \,\mu(t)\,\dd t .
\end{equation}
Consequently, for boundary data \(f\), the double-layer density
\(\mu_f\) of the harmonic solution with trace \(f\) is determined by
\begin{equation}\label{eq:mu-equation}
  \Bigl(\frac12 I+K\Bigr)\mu_f=f .
\end{equation}
The normal derivative of the same harmonic function is the hypersingular
operator
\[
  \Lambda_U f=W\mu_f,
\]
where \(W\) may be written in weakly singular form as
\begin{equation}\label{eq:W-operator}
  (W\mu)(s)
  =
  \partial_s
  \operatorname{p.v.}\int_0^{L}
  G_0(\gamma(s),\gamma(t))\,\partial_t\mu(t)\,\dd t .
\end{equation}
Equivalently,
\begin{equation}\label{eq:param-dtn}
  \Lambda_U f
  =
  W\Bigl(\frac12 I+K\Bigr)^{-1}f .
\end{equation}
For the present problem the relevant boundary datum is
\begin{equation}\label{eq:f-def}
  f(s)
  =
  q(s)\,X(\gamma(s))\cdot\nu(s),
  \qquad
  q(s):=
  a(|\gamma(s)|)\,\gamma(s)\cdot\nu(s).
\end{equation}
Thus the DtN term in \eqref{eq:dtn-side} is the explicit nonlocal quantity
\[
  W\Bigl(\frac12 I+K\Bigr)^{-1}
  \bigl(q\,X\cdot\nu\bigr).
\]

We now compute the same normal derivative directly from the boundary jets.  Let
\(T\) be the arclength unit tangent, and use the signed curvature convention
\[
  T'=\kappa\nu .
\]

\begin{lemma}\label{lem:boundary-jets}
On \(\Gamma\),
\[
  D^2u(T,T)=-\kappa q,\qquad
  D^2u(T,\nu)=\partial_s q,\qquad
  D^2u(\nu,\nu)=\rho(|x|)+\kappa q .
\]
\end{lemma}

\begin{proof}
Since \(u=0\) on \(\Gamma\), differentiating twice along arclength gives
\[
  D^2u(T,T)+\nabla u\cdot T'=0.
\]
Using \(T'=\kappa\nu\) and \(\nabla u=q\nu\), this gives
\[
  D^2u(T,T)=-\kappa q.
\]
Tangentially differentiating \(\partial_\nu u=q\) gives
\[
  D^2u(T,\nu)+\nabla u\cdot\nu'=\partial_s q.
\]
Since \(\nu'\) is tangent and \(\nabla u=q\nu\), the second term vanishes.  Finally,
\[
  \rho(|x|)
  =
  \Delta u
  =
  D^2u(T,T)+D^2u(\nu,\nu),
\]
which gives the claimed normal-normal component.
\end{proof}

\begin{proposition}[DtN boundary equation]\label{prop:dtn-equation}
On \(\Gamma=\partial U\),
\begin{equation}\label{eq:dtn-boundary-equation}
  \boxed{
  W\Bigl(\frac12 I+K\Bigr)^{-1}\bigl(q(X\cdot\nu)\bigr)
  =
  (X\cdot T)\,\partial_s q
  +(X\cdot\nu)\bigl(\rho(|x|)+\kappa q\bigr)
  }
\end{equation}
where
\[
  q=a(|x|)(x\cdot\nu).
\]
In arclength coordinates this says the following.  Let \(\mu\) be the solution of
\begin{equation}\label{eq:explicit-mu}
  \frac12\mu(s)
  +
  \operatorname{p.v.}\int_0^L
  \frac{(\gamma(t)-\gamma(s))\cdot\nu(t)}
       {2\pi|\gamma(s)-\gamma(t)|^2}
  \mu(t)\,\dd t
  =
  q(s)\,X(\gamma(s))\cdot\nu(s).
\end{equation}
Then \eqref{eq:dtn-boundary-equation} is exactly
\begin{align}\label{eq:explicit-param-equation}
  \partial_s
  \operatorname{p.v.}\int_0^L
  \frac{1}{2\pi}\log|\gamma(s)-\gamma(t)|\,\partial_t\mu(t)\,\dd t
  &=
  (X(\gamma(s))\cdot T(s))\,\partial_s q(s) \notag\\
  &\quad+
  (X(\gamma(s))\cdot\nu(s))
  \bigl(\rho(|\gamma(s)|)+\kappa(s)q(s)\bigr).
\end{align}
\end{proposition}

\begin{proof}
Directly,
\[
  \partial_\nu v
  =
  \nabla(X\cdot\nabla u)\cdot\nu
  =
  D^2u(\nu,X)+(DX\,\nu)\cdot\nabla u .
\]
The matrix \(DX\) is rotation by \(\pi/2\), so \((DX\,\nu)\cdot\nu=0\).  Since
\(\nabla u=q\nu\), the last term vanishes.  Decomposing
\[
  X=(X\cdot T)T+(X\cdot\nu)\nu
\]
and using Lemma~\ref{lem:boundary-jets}, we obtain
\[
  \partial_\nu v
  =
  (X\cdot T)\,\partial_s q
  +(X\cdot\nu)\bigl(\rho(|x|)+\kappa q\bigr).
\]
Equating this expression with the DtN expression \eqref{eq:dtn-side} proves
\eqref{eq:dtn-boundary-equation}.
\end{proof}

\subsection{The cleaner scalar form}

The equation above looks worse than its actual geometric content.  Write
\[
  \alpha(s):=\gamma(s)\cdot\nu(s),
  \qquad
  \beta(s):=\gamma(s)\cdot T(s),
  \qquad
  r(s):=|\gamma(s)|.
\]
For the standard boundary orientation compatible with the outward normal,
\[
  X(\gamma)\cdot T=\alpha,\qquad X(\gamma)\cdot\nu=-\beta.
\]
Moreover,
\[
  r_s=\frac{\beta}{r},
  \qquad
  \alpha_s=-\kappa\beta.
\]
Since \(q=a(r)\alpha\),
\[
  \partial_s q
  =
  \beta\left(\frac{a'(r)}{r}\alpha-a(r)\kappa\right).
\]
Substituting these identities into
\eqref{eq:dtn-boundary-equation} gives the scalar form
\begin{equation}\label{eq:clean-dtn-equation}
  \boxed{
  \Lambda_U\bigl(-a(r)\alpha\beta\bigr)
  =
  \beta\left(
  \frac{a'(r)}{r}\alpha^2-\rho(r)-2a(r)\kappa\alpha
  \right).
  }
\end{equation}
Thus the layer-potential formula is not the main point; it is only one explicit
realization of the nonlocal operator \(\Lambda_U\).  The boundary equation itself is
the scalar pseudodifferential condition \eqref{eq:clean-dtn-equation}.

\subsection{The fully expanded curve equation}

Here is the same equation with no geometric shorthand left.  Assume that
\(\gamma:\R/L\mathbb Z\to\partial U\) is arclength-parametrized and oriented so that
\[
  \nu(s)=-X\gamma'(s),
  \qquad
  X(y):=(-y_2,y_1).
\]
This is the counterclockwise orientation for a positively oriented boundary.  Define
\[
  A(s):=\gamma(s)\cdot X\gamma'(s),
  \qquad
  B(s):=\gamma(s)\cdot\gamma'(s),
  \qquad
  C(s):=\gamma''(s)\cdot X\gamma'(s),
  \qquad
  r(s):=|\gamma(s)|.
\]
Then
\[
  \alpha=-A,\qquad
  \beta=B,\qquad
  \kappa=-C.
\]
The boundary datum for \(Lu\) is therefore
\[
  -a(r)\alpha\beta=a(r)A B.
\]
The completely expanded equation is:
\begin{equation}\label{eq:gamma-only-equation}
  \boxed{\begin{aligned}
  &\partial_s\,\operatorname{p.v.}\int_0^L
  \frac{1}{2\pi}\log|\gamma(s)-\gamma(t)|\,\partial_t\mu(t)\,\dd t \\
  &\qquad =
  B(s)\left[
  \frac{a'(r(s))}{r(s)}A(s)^2
  -\rho(r(s))
  -2a(r(s))A(s)C(s)
  \right].
  \end{aligned}}
\end{equation}
where the auxiliary density \(\mu\) is determined only from the curve by
\begin{equation}\label{eq:gamma-only-density}
  \boxed{
  \frac12\mu(s)
  -
  \operatorname{p.v.}\int_0^L
  \frac{(\gamma(t)-\gamma(s))\cdot X\gamma'(t)}
       {2\pi|\gamma(s)-\gamma(t)|^2}
  \,\mu(t)\,\dd t
  =
  a(r(s))A(s)B(s).
  }
\end{equation}
Equivalently, eliminating \(\mu\) from the notation, let
\[
  F_\gamma(s):=a(|\gamma(s)|)
  \bigl(\gamma(s)\cdot X\gamma'(s)\bigr)
  \bigl(\gamma(s)\cdot\gamma'(s)\bigr),
\]
and define
\[
  (K_\gamma m)(s):=
  -\operatorname{p.v.}\int_0^L
  \frac{(\gamma(t)-\gamma(s))\cdot X\gamma'(t)}
       {2\pi|\gamma(s)-\gamma(t)|^2}
  \,m(t)\,\dd t .
\]
Then the same condition is the single nonlocal equation
\begin{align}\label{eq:single-gamma-only-equation}
  &\partial_s\,\operatorname{p.v.}\int_0^L
  \frac{1}{2\pi}\log|\gamma(s)-\gamma(t)|
  \,\partial_t\left[
  \Bigl(\frac12 I+K_\gamma\Bigr)^{-1}F_\gamma
  \right](t)\,\dd t
  \notag\\
  &\qquad =
  \bigl(\gamma(s)\cdot\gamma'(s)\bigr)
  \left[
  \frac{a'(|\gamma(s)|)}{|\gamma(s)|}
  \bigl(\gamma(s)\cdot X\gamma'(s)\bigr)^2
  -\rho(|\gamma(s)|)
  \right. \notag\\
  &\hspace{7.8cm}\left.
  -2a(|\gamma(s)|)
  \bigl(\gamma(s)\cdot X\gamma'(s)\bigr)
  \bigl(\gamma''(s)\cdot X\gamma'(s)\bigr)
  \right].
\end{align}
All occurrences of \(a\) and \(\rho\) are the explicit radial functions
\[
  a(r)=(1-\pi r^2)e^{-\pi r^2},
  \qquad
  \rho(r)=(1-4\pi r^2+\pi^2r^4)e^{-\pi r^2},
\]
and
\[
  a'(r)=2\pi r(\pi r^2-2)e^{-\pi r^2}.
\]

Because \(U\) is simply connected, there is also a conformal way to write the same
operator.  If \(\phi:\mathbb D\to U\) is conformal and
\[
  \gamma(\theta):=\phi(e^{i\theta}),
  \qquad
  J(\theta):=|\gamma_\theta(\theta)|,
\]
then, for any boundary datum \(F\),
\begin{equation}\label{eq:conformal-dtn}
  \Lambda_U F(\gamma(\theta))
  =
  \frac{1}{J(\theta)}
  |D_\theta|\bigl(F\circ\gamma\bigr)(\theta)
  =
  \frac{1}{J(\theta)}
  H\partial_\theta\bigl(F\circ\gamma\bigr)(\theta),
\end{equation}
where \(H\) is the periodic Hilbert transform.  Hence
\eqref{eq:clean-dtn-equation} may equivalently be written as
\begin{equation}\label{eq:conformal-clean-dtn}
  \frac{1}{J}|D_\theta|\bigl(-a(r)\alpha\beta\bigr)
  =
  \beta\left(
  \frac{a'(r)}{r}\alpha^2-\rho(r)-2a(r)\kappa\alpha
  \right),
\end{equation}
with all quantities evaluated on \(\gamma(\theta)\).

\begin{remark}[What this does and does not give]
For the Gaussian zero-Neumann problem, applying \(L\) produces a harmonic function
with zero boundary trace, so one gets a pointwise radius equation.  Here the boundary
trace is
\[
  Lu|_{\partial U}=-a(r)\alpha\beta,
\]
which is generally nonzero.  Thus the method does not give an immediate local
rigidity theorem.  What it gives is the closed nonlocal boundary equation
\eqref{eq:clean-dtn-equation}.
\end{remark}

\begin{remark}[Linearized information near centered disks]
The nonlocal equation still has useful content.  Centered disks satisfy it
identically, since \(\beta=0\).  Linearizing around a centered disk of radius \(R\),
with
\[
  r(\theta)=R+\varepsilon h(\theta),
\]
one obtains, for a nonzero Fourier mode \(h_n e^{in\theta}\),
\[
  (1-\pi R^2)(|n|+1-\pi R^2)n\,h_n=0.
\]
Consequently, away from the resonant radii
\[
  \pi R^2=1
  \qquad\text{or}\qquad
  \pi R^2=1+|n|,
\]
the DtN equation is linearly rigid against nonradial perturbations of centered
disks.  At the resonant radii this first-order test leaves the corresponding angular
modes open; higher-order information or an additional identity would be needed there.
\end{remark}

\section{Plan A: Schwarz-function reduction}

The expanded DtN equation is a poor object to manipulate directly.  A more natural
analytic object appears if the boundary is already known to be real analytic.  This
section records exactly what the \(h_1\) BVP gives in terms of the local Schwarz
function.

Assume that \(\Gamma=\partial U\) is a real-analytic Jordan curve, with local Schwarz
function \(S\) in a collar of \(\Gamma\):
\[
  S(z)=\bar z
  \qquad (z\in\Gamma).
\]
For this section it is cleaner to use the squared-radius variable \(t=r^2\).  Write
\[
  \widetilde a(t):=(1-\pi t)e^{-\pi t}=a(\sqrt t).
\]
Let \(n=\nu_1+i\nu_2\) be the outward unit normal and let \(\tau\) be the positively
oriented unit tangent.  Then \(n=-i\tau\), and differentiating \(S(z)=\bar z\) along
\(\Gamma\) gives
\[
  S'(z)=\frac{\bar\tau}{\tau}=\bar\tau^2,
  \qquad
  \bar n^2=-S'(z).
\]
Set
\[
  G:=2\partial_z u.
\]
Since \(u=0\) on \(\Gamma\), we have \(\nabla u=(\partial_\nu u)\nu\), hence
\[
  G=(\partial_\nu u)\bar n
  \qquad\text{on }\Gamma.
\]
Using
\[
  z\cdot\nu=\frac12(z\bar n+\bar z n),
  \qquad
  \bar z=S(z),
\]
the Neumann condition in \eqref{eq:BVP} becomes the complex boundary identity
\begin{equation}\label{eq:complex-gradient-boundary}
  G
  =
  \frac{\widetilde a(zS(z))}{2}\bigl(S(z)-zS'(z)\bigr)
  \qquad (z\in\Gamma).
\end{equation}

Now remove the radial inhomogeneity in the equation for \(G\).  Define
\[
  P(t):=\frac{1}{2t}\int_0^t \rho(\sqrt\sigma)\,\dd\sigma
  =
  \frac{e^{-\pi t}(1+2\pi t-\pi^2t^2)-1}{2\pi t},
\]
with the removable value \(P(0)=1/2\).  Then
\[
  \partial_{\bar z}\bigl(P(z\bar z)\bar z\bigr)=\frac12\rho(|z|).
\]
Therefore, away from the source point,
\[
  G(z)=H(z)+P(z\bar z)\bar z+\frac{\lambda}{2\pi z},
\]
where \(H\) is holomorphic in \(U\) after removing the prescribed source pole at
the origin.  Combining this with \eqref{eq:complex-gradient-boundary} gives the
following continuation statement.

\begin{proposition}[Weighted Schwarz expression]\label{prop:weighted-schwarz}
In a collar of \(\Gamma\), define
\begin{equation}\label{eq:weighted-schwarz-expression}
  \mathcal A_S(z)
  :=
  \frac{\widetilde a(zS(z))}{2}\bigl(S(z)-zS'(z)\bigr)
  -
  P(zS(z))S(z).
\end{equation}
Then \(\mathcal A_S\) extends meromorphically into \(U\).  The only allowed
singularity is the source pole at \(0\), with principal part
\[
  \frac{\lambda}{2\pi z}.
\]
Equivalently,
\[
  \mathcal A_S(z)-\frac{\lambda}{2\pi z}
\]
extends holomorphically through \(U\), with the source term omitted if \(0\notin U\).
\end{proposition}

\begin{proof}
On the boundary, \eqref{eq:complex-gradient-boundary} and \(S=\bar z\) give
\[
  G-P(z\bar z)\bar z
  =
  \mathcal A_S .
\]
But \(G-P(z\bar z)\bar z\) is holomorphic in \(U\) except for the prescribed
contribution \(\lambda/(2\pi z)\) coming from \(\lambda\delta_0\).  Hence the collar
function \(\mathcal A_S\) is the boundary germ of that meromorphic function.
\end{proof}

The expression can be made slightly more compact.  Since
\[
  \frac{\widetilde a(t)}{2}-P(t)
  =
  \frac{1-(1+\pi t)e^{-\pi t}}{2\pi t}
  =:b(t),
\]
we may rewrite \eqref{eq:weighted-schwarz-expression} as
\begin{equation}\label{eq:weighted-schwarz-compact}
  \mathcal A_S(z)
  =
  b(zS(z))S(z)
  -
  \frac12 \widetilde a(zS(z))zS'(z).
\end{equation}
Thus Plan A does not naturally produce an ordinary meromorphic Schwarz function.
It produces a meromorphic continuation condition for the weighted differential
expression
\[
  b(zS)S-\frac12\widetilde a(zS)zS'.
\]

\begin{remark}[What this buys]
This is substantially cleaner than the DtN equation.  It is local near the boundary,
complex analytic, and has a direct quadrature-domain flavour: a nonlinear expression
in the Schwarz function has only the prescribed source singularity in \(U\).

For a centered disk \(S(z)=R^2/z\), the quantity \(zS=R^2\) is constant and
\[
  \mathcal A_S(z)
  =
  \bigl(\widetilde a(R^2)-P(R^2)\bigr)\frac{R^2}{z},
\]
so the continuation property holds with a single pole at the origin.
\end{remark}

\begin{remark}[What is still missing]
The statement above is not yet a rigidity theorem.  The unknown holomorphic part of
\(\mathcal A_S\) is still free.  If that meromorphic function were known explicitly,
then \eqref{eq:weighted-schwarz-compact} would become a first-order nonlinear ODE for
\(S\):
\[
  zS'
  =
  \frac{2b(zS)}{\widetilde a(zS)}S
  -
  \frac{2}{\widetilde a(zS)}\mathcal A_S .
\]
But the BVP by itself only gives the continuation property of \(\mathcal A_S\), not
its full value.  So the next useful question is whether the original localization
identity gives enough information to identify this meromorphic function, or at least
to control its singularities.  That is much closer to a weighted quadrature-domain
problem than to the raw DtN boundary equation.
\end{remark}

\end{document}
