\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{enumitem}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\Om}{\Omega}
\newcommand{\dT}{\delta_T}
\newcommand{\al}{\alpha}
\newcommand{\Et}{E_{\hat t}}
\newcommand{\dH}{\,d\mathcal H^1}

\title{Pushing the Selection--Plan 3 Hybrid}
\author{}
\date{May 2026}

\begin{document}
\maketitle

\section{Purpose}

This note tries to prove the hybrid replacement for Plan 1 graph entry:
use selection to get a controlled class, go to a Plan 3 good level, upgrade
\(D_H\) to \(L^2\)-Serrin and then to \(L^\infty\)-Serrin, apply a
Brandolini-type annulus theorem, and conclude graph entry.

The positive result is a rigorous quantitative interpolation lemma in
dimension two.  The scale tradeoff is:
the layer depth needed to get \(L^\infty\)-Serrin smallness is generally too
large to preserve the selected asymmetry unless one knows the stronger
relation
\[
   \dT(U)\ll \al(U)^2.
\]
This first looked like an obstruction.  But in a contradiction proof of
\(\al(U)\lesssim \dT(U)^{1/2}\), the bad alternative is exactly
\(\al(U)\gg \dT(U)^{1/2}\), hence exactly \(\dT(U)\ll\al(U)^2\).  Thus the
scale tradeoff is not the remaining obstruction.  The remaining obstruction
is the geometric entry theorem: \(L^\infty\)-Serrin smallness on the chosen
level must put that level into the small radial-graph class, without using
BDV as a black box.

\section{Standing Optimistic Hypotheses}

Let \(U\subset B_R\subset\mathbb R^2\) be a selected minimizer, normalized
near the unit disk, and let \(u\) be its torsion function.  Write
\[
   \delta:=\dT(U),\qquad a:=\al(U),\qquad q:=\delta/a.
\]

To give the hybrid the best possible chance, assume the following uniform
geometric estimates, all with constants depending only on the selected class:

\begin{enumerate}[label=(H\arabic*)]
\item \textbf{Lipschitz potential and linear boundary growth.}
There are \(0<c_0<L_0<\infty\) such that near \(\partial U\),
\[
   c_0\,{\rm dist}(x,\partial U)\le u(x)\le
   L_0\,{\rm dist}(x,\partial U),
   \qquad
   |\nabla u(x)|\le L_0.
   \tag{2.1}\label{eq:growth}
\]
\item \textbf{Tubular layer bound.}
\[
   |\{x\in U:{\rm dist}(x,\partial U)\le r\}|
      \le P_0 r
   \quad\hbox{for }0<r<r_0.
   \tag{2.2}\label{eq:tube}
\]
\item \textbf{Level-set lower density.}
For every regular level \(\Sigma_t=\{u=t\}\) considered below, every
\(x\in\Sigma_t\), and every \(0<r<r_0\),
\[
   \mathcal H^1(\Sigma_t\cap B_r(x))\ge c_1 r.
   \tag{2.3}\label{eq:ahlfors}
\]
\end{enumerate}

\begin{remark}
These hypotheses are stronger than what the selection step alone currently
proves before graph entry.  They are included to isolate the numerical
obstruction even under favorable assumptions.
\end{remark}

\begin{theorem}[Conditional hybrid estimate]\label{thm:conditional-hybrid}
Assume (H1)--(H3) and the Plan 3 volume-variable identity
\[
   \int_0^{|U|}D_H(v(s))\,ds\le C\delta.
\]
Then, for every \(0<\lambda<\lambda_0\), there is a regular level
\(\Sigma_{\hat t}=\partial E_{\hat t}\) such that
\[
   \lambda/2\le |U\setminus E_{\hat t}|\le \lambda,
   \qquad
   D_H(\hat t)\le C\delta/\lambda,
\]
and
\[
   {\rm dist}(\Sigma_{\hat t},\partial U)\ge c\lambda.
\]
Writing \(f=|\nabla u|\) on \(\Sigma_{\hat t}\) and
\(\bar f=|E_{\hat t}|/P(E_{\hat t})\), one has
\[
   \int_{\Sigma_{\hat t}}(f-\bar f)^2\,d\mathcal H^1
      \le C\frac{\delta}{\lambda}
\]
and
\[
   \|f-\bar f\|_{L^\infty(\Sigma_{\hat t})}
      \le
      C\left[
        \left(\frac{\delta}{\lambda^2}\right)^{1/3}
        +\left(\frac{\delta}{\lambda}\right)^{1/2}
      \right].
\]
In particular, for \(\delta,\lambda\le1\),
\[
   \|f-\bar f\|_{L^\infty(\Sigma_{\hat t})}
      \le C\left(\frac{\delta}{\lambda^2}\right)^{1/3}.
\]
Consequently, this mechanism can simultaneously give fixed small
\(L^\infty\)-Serrin oscillation and preserve a fixed fraction of the
selected asymmetry only in the stronger regime
\[
   \delta\le C\alpha(U)^2.
\]
This stronger regime is automatically available in the bad alternative of
the desired estimate \(\alpha(U)\le C\sqrt\delta\).
\end{theorem}

The proof is the chain of estimates in Sections 3--7.

\section{A Good Level in a Prescribed Layer}

Let
\[
   \mu(t):=|U\setminus E_t|,\qquad E_t:=\{u>t\}.
\]
The Plan 3 volume-variable identity gives
\[
   \int_0^{|U|} D_H(v(s))\,ds \le C\delta
\]
in the normalized two-dimensional regime, up to harmless constants.  Hence,
for any layer depth \(0<\lambda<\lambda_0\), there is a regular level
\(\hat t\) with
\[
   \lambda/2\le \mu(\hat t)\le\lambda,
   \qquad
   D_H(\hat t)\le C\frac{\delta}{\lambda}.
   \tag{3.1}\label{eq:good-level-lambda}
\]
Indeed, average over the volume slab
\(\{s: |U|-\lambda\le s\le |U|-\lambda/2\}\), whose length is \(\lambda/2\),
and intersect with regular values.

The layer bound \eqref{eq:tube} and the lower growth in \eqref{eq:growth}
give
\[
   \mu(t)
      =
      |\{0<u\le t\}|
      \le
      |\{{\rm dist}(x,\partial U)\le t/c_0\}|
      \le
      C t.
\]
Thus \(\mu(\hat t)\ge\lambda/2\) implies
\[
   \hat t\ge c\lambda.
   \tag{3.2}\label{eq:t-lower}
\]
The upper Lipschitz bound in \eqref{eq:growth} then implies every point of
\(\Sigma_{\hat t}\) lies at distance at least
\[
   d_\lambda:=c\lambda
   \tag{3.3}\label{eq:dist-lower}
\]
from \(\partial U\).

\section{\(D_H\) Gives \(L^2\)-Serrin}

On \(\Sigma_{\hat t}\), set \(f=|\nabla u|\) and
\(\bar f=|E_{\hat t}|/P(E_{\hat t})\).  The exact identity gives
\[
   \int_{\Sigma_{\hat t}}\frac{(f-\bar f)^2}{f}\,\dH
      =
      \frac{|E_{\hat t}|}{P(E_{\hat t})^2}D_H(\hat t).
\]
Using \(|\nabla u|\le L_0\) and the uniform perimeter/area bounds in the
selected class,
\[
   \int_{\Sigma_{\hat t}}(f-\bar f)^2\,\dH
      \le C D_H(\hat t)
      \le C\frac{\delta}{\lambda}.
   \tag{4.1}\label{eq:l2-lambda}
\]

\section{Interior Regularity Gives a Lipschitz Modulus on the Level}

Since \(\Sigma_{\hat t}\) is at distance \(d_\lambda\ge c\lambda\) from
\(\partial U\), interior estimates apply.  Moreover, by the upper growth in
\eqref{eq:growth}, in balls of radius comparable to \(d_\lambda\) around
\(\Sigma_{\hat t}\) one has \(\sup u\le C d_\lambda\).  Standard interior
estimates for \(-\Delta u=1\) therefore give
\[
   \|D^2u\|_{L^\infty(\hbox{a }c\lambda\hbox{-collar of }\Sigma_{\hat t})}
      \le \frac{C}{\lambda}.
   \tag{5.1}\label{eq:hessian}
\]
Consequently
\[
   {\rm Lip}_{\Sigma_{\hat t}}(|\nabla u|)
      \le \frac{C}{\lambda}.
   \tag{5.2}\label{eq:f-lip}
\]

\section{The \(L^2\to L^\infty\) Upgrade in Dimension Two}

\begin{lemma}[Level interpolation]\label{lem:interp}
Let \(\Sigma\) be a regular level satisfying the lower density
\eqref{eq:ahlfors}.  If \(g\) is Lipschitz on \(\Sigma\), with
\[
   \int_\Sigma g^2\,d\mathcal H^1\le B,
   \qquad
   {\rm Lip}_\Sigma(g)\le M,
\]
then
\[
   \|g\|_{L^\infty(\Sigma)}
      \le C(c_1,r_0)\left((BM)^{1/3}+B^{1/2}\right).
\]
In particular, if \(0<B\le B_0\), \(0<M\), and \(BM\ge B^{3/2}\), then
\[
   \|g\|_{L^\infty(\Sigma)}
      \le C(c_1,r_0,B_0)\,(BM)^{1/3}.
\]
\end{lemma}

\begin{proof}
Let \(A=\|g\|_{L^\infty(\Sigma)}\), attained up to approximation at a point
\(x\in\Sigma\).  If \(M=0\), then \(g\) is constant on each connected
component of \(\Sigma\), and the lower density at one point gives
\(B\ge c_1r_0 A^2\) after replacing \(r_0\) by a smaller dimensional radius
if necessary.  Hence \(A\le C B^{1/2}\).

Assume now \(M>0\), and set \(r=A/(2M)\).  If \(r\le r_0\), then
\(|g|\ge A/2\) on \(\Sigma\cap B_r(x)\), and \eqref{eq:ahlfors} gives
\[
   B\ge \int_{\Sigma\cap B_r(x)}g^2\,d\mathcal H^1
      \ge \frac{A^2}{4}\,c_1 r
      =
      c\,\frac{A^3}{M}.
\]
Hence \(A\le C(BM)^{1/3}\).  If \(r>r_0\), then the same argument with
\(r_0\) gives \(B\ge cA^2r_0\), hence \(A\le C B^{1/2}\).
\end{proof}

Apply Lemma~\ref{lem:interp} to
\[
   g=f-\bar f.
\]
By \eqref{eq:l2-lambda} and \eqref{eq:f-lip},
\[
   B\le C\frac{\delta}{\lambda},
   \qquad
   M\le C\frac1\lambda.
\]
Therefore
\[
   \|\,|\nabla u|-\bar f\,\|_{L^\infty(\Sigma_{\hat t})}
      \le
      C\left[
        \left(\frac{\delta}{\lambda^2}\right)^{1/3}
        +\left(\frac{\delta}{\lambda}\right)^{1/2}
      \right].
   \tag{6.1a}\label{eq:linfty-lambda-full}
\]
In the regime relevant to near-balls, \(\delta,\lambda\le1\), the second
term is dominated by the first:
\[
   \left(\frac{\delta}{\lambda}\right)^{1/2}
      \le
   \left(\frac{\delta}{\lambda^2}\right)^{1/3}.
\]
Thus
\[
   \|\,|\nabla u|-\bar f\,\|_{L^\infty(\Sigma_{\hat t})}
      \le
      C\left(\frac{\delta}{\lambda^2}\right)^{1/3}.
   \tag{6.1b}\label{eq:linfty-lambda}
\]
This is the strongest rigorous estimate obtainable from the proposed
mechanism, even under the optimistic hypotheses above.

\section{The Layer-Depth Tradeoff}

To make the \(L^\infty\)-Serrin oscillation smaller than a prescribed
\(\varepsilon_B\), \eqref{eq:linfty-lambda} requires
\[
   \lambda
      \ge
      C\varepsilon_B^{-3/2}\sqrt{\delta}.
   \tag{7.1}\label{eq:lambda-linf}
\]
This is exactly the \(\sqrt\delta\)-scale found in the Plan 3 push.

But preserving the selected asymmetry requires a much smaller layer.  Since
\(\alpha\) is \(L^1\)-Lipschitz on bounded sets,
\[
   \alpha(E_{\hat t}^{\sharp})
      \ge
      \alpha(U)-C|U\setminus E_{\hat t}|
      \ge
      a-C\lambda.
   \tag{7.2}\label{eq:alpha-layer}
\]
Thus to keep, say,
\[
   \alpha(E_{\hat t}^{\sharp})\ge\frac12\alpha(U),
\]
one needs
\[
   \lambda\le c a.
   \tag{7.3}\label{eq:lambda-alpha}
\]

Combining \eqref{eq:lambda-linf} and \eqref{eq:lambda-alpha}, the route can
simultaneously produce \(L^\infty\)-Serrin smallness and preserve asymmetry
only if
\[
   \sqrt{\delta}\le C a,
   \qquad\hbox{equivalently}\qquad
   \delta\le C a^2.
   \tag{7.4}\label{eq:delta-alpha2}
\]
In terms of \(q=\delta/a\), this is
\[
   q\le C a.
   \tag{7.5}
\]

\section{The Correct Contradiction Split}

The desired conclusion is
\[
   a=\alpha(U)\le C_*\sqrt\delta.
\]
Fix a large constant \(M\), to be chosen from the constants below.  If
\[
   a\le M\sqrt\delta,
\]
there is nothing to prove.  Otherwise assume
\[
   a>M\sqrt\delta.
   \tag{8.1}\label{eq:bad-alt}
\]
Choose
\[
   \lambda=K\sqrt\delta,
   \tag{8.2}\label{eq:lambda-sqrt}
\]
with \(K\) large enough that \eqref{eq:linfty-lambda} gives
\[
   \|\,|\nabla u|-\bar f\,\|_{L^\infty(\partial E_{\hat t})}
      \le \varepsilon_B.
   \tag{8.3}\label{eq:linfty-small}
\]
Indeed
\[
   \left(\frac{\delta}{\lambda^2}\right)^{1/3}
      =
   K^{-2/3}.
\]
Thus \(K\ge C\varepsilon_B^{-3/2}\) suffices.

The same choice is still small relative to the selected asymmetry in the bad
alternative: if \(M\ge 4CK\), then
\[
   \lambda=K\sqrt\delta\le \frac{K}{M}a\le \frac{a}{4C},
\]
and therefore
\[
   \alpha(E_{\hat t}^{\sharp})
      \ge a-C\lambda
      \ge \frac34 a.
   \tag{8.4}\label{eq:alpha-preserved-bad}
\]
This lower bound is not actually needed for the final transfer, but it shows
that the selected badness has not been destroyed by the inset.

The Plan 3 profile transfer for superlevel sets gives, for every small
\(\lambda\) and not only for \(\lambda=O(\delta)\),
\[
   \dT(E_{\hat t})
      \le
   \frac{1}{1-\lambda/|U|}\,\dT(U)
      \le
   2\delta
   \tag{8.5}\label{eq:deficit-transfer-sqrt}
\]
after taking \(\delta\) small enough that \(\lambda\le |U|/2\).  This is the
exact profile computation using \(u-\hat t=u_{E_{\hat t}}\); it is not a
monotonicity assertion.

Now assume the remaining geometric entry statement:

\begin{quote}
\emph{If a regular superlevel set \(E_{\hat t}\) in the selected planar
class satisfies \eqref{eq:linfty-small}, then after translation and volume
normalization it belongs to the small-amplitude radial graph class to which
the direct graph theorem applies.}
\end{quote}

Then the direct radial-graph theorem gives
\[
   \alpha(E_{\hat t})^2
      \le
   C_G\,\dT(E_{\hat t})
      \le
   C_G'\delta.
   \tag{8.6}\label{eq:graph-final}
\]
Finally the elementary superlevel transfer gives
\[
   \alpha(U)
      \le
   \alpha(E_{\hat t})+C|U\setminus E_{\hat t}|
      \le
   C\sqrt\delta + CK\sqrt\delta
      \le
   C_*\sqrt\delta.
   \tag{8.7}\label{eq:transfer-final}
\]
Choosing \(M>C_*\) contradicts the bad alternative
\eqref{eq:bad-alt}.  Therefore \(a\le M\sqrt\delta\).

\section{Checking the Selected-Regularity Route to Brandolini}

The geometric entry statement in the previous section is supplied if the
selection step is used with its full regularity output, not merely with the
coarse Lipschitz/density bounds (H1)--(H3).  The needed input is:

\begin{quote}
\textbf{(SR)} The selected planar minimizer \(U\) has a uniformly controlled
\(C^{2,\alpha}\) boundary in a fixed atlas, the torsion function has a
uniform \(C^{2,\alpha}\) norm up to the boundary, and
\[
   0<q_-\le |\nabla u|\le q_+
   \quad\hbox{on }\partial U,
   \tag{9.1}\label{eq:sr-hopf}
\]
with all constants depending only on the selected class.
\end{quote}

This is exactly the kind of output provided by the Plan~1 graph-entry plus
Schauder bootstrap package: after the selected set is known to be a
\(C^{1,\gamma}\) graph, the selected Bernoulli law and the uniform Schauder
bootstrap give \(C^{m,\gamma}\) bounds, in particular \(C^{2,\alpha}\), with
constants depending only on the selected class.

\begin{lemma}[Inset regularity inherited from the selected boundary]
\label{lem:inset-regularity}
Assume \emph{(SR)}.  Then there are \(t_0>0\) and constants
\(\rho_0,K_0,d_0\), depending only on \emph{(SR)}, such that every regular
level \(E_t=\{u>t\}\), \(0<t<t_0\), is connected and has \(C^{2,\alpha}\)
boundary in the sense of Brandolini's Definition~6, with atlas constants
\((\rho_0,K_0)\) and diameter at most \(d_0\).
\end{lemma}

\begin{proof}
By \eqref{eq:sr-hopf} and the \(C^{1}\)-continuity of \(\nabla u\) up to
\(\partial U\), after shrinking a fixed tubular collar one has
\[
   |\nabla u|\ge q_-/2.
   \tag{9.2}
\]
In normal coordinates \(x=y-s\nu_U(y)\), \(y\in\partial U\), the map
\((y,s)\mapsto u(y-s\nu_U(y))\) is \(C^{2,\alpha}\), has
\(\partial_s u\le -q_-/2\), and has uniformly bounded \(C^{2,\alpha}\) norm.
The quantitative implicit function theorem therefore gives, for
\(0<t<t_0\), a \(C^{2,\alpha}\) function \(s_t(y)\) with uniformly bounded
\(C^{2,\alpha}\) norm such that
\[
   \partial E_t=\{y-s_t(y)\nu_U(y):y\in\partial U\}.
   \tag{9.3}
\]
The uniform atlas constants follow from the corresponding constants for
\(\partial U\), the tubular radius, and the implicit-function constants.
The small selected graph class contains a fixed inner ball, and the linear
boundary growth gives \(E_t\) a slightly smaller fixed inner ball for
\(t<t_0\); hence these near-boundary levels are connected.  The diameter
bound is inherited from \(U\subset B_R\).
\end{proof}

\begin{lemma}[Brandolini annulus for the stopped level]
\label{lem:brandolini-annulus-selected}
Assume \emph{(SR)} and choose the stopped level in the bad alternative with
\(\lambda=K\sqrt\delta\).  After volume normalization of \(E_{\hat t}\), there
are a center \(z\) and a modulus \(\eta(K,\delta)\) such that
\[
   B_{1-\eta(K,\delta)}(z)
      \subset E_{\hat t}^{\sharp}
      \subset B_{1+\eta(K,\delta)}(z),
   \tag{9.4}\label{eq:selected-annulus}
\]
where
\[
   \eta(K,\delta)
      \le
      C_{\rm Br}\left(K^{-2/3}+C_K\sqrt\delta\right)^\mu
      +C_K\sqrt\delta.
   \tag{9.5}\label{eq:eta-K}
\]
Here \(\mu>0\) is Brandolini's dimensional exponent and
\(C_{\rm Br}\) depends only on the selected regularity constants from
\emph{(SR)}.
\end{lemma}

\begin{proof}
Set \(v=u-\hat t=u_{E_{\hat t}}\).  In dimension two, \(w=-2v\) satisfies
\(\Delta w=2\) in \(E_{\hat t}\) and \(w=0\) on \(\partial E_{\hat t}\).
By \eqref{eq:linfty-small},
\[
   \bigl\||\nabla v|-\bar f\bigr\|_{L^\infty(\partial E_{\hat t})}
      \le C K^{-2/3}.
   \tag{9.6}\label{eq:level-linf}
\]
The flux identity gives
\[
   \bar f=\frac{|E_{\hat t}|}{P(E_{\hat t})}.
   \tag{9.7}
\]
Since the good level has \(|E_{\hat t}|=\pi+O_K(\sqrt\delta)\) and
\(P(E_{\hat t})=2\pi+O_K(\sqrt\delta)\), we have
\[
   \left|\bar f-\frac12\right|\le C_K\sqrt\delta.
   \tag{9.8}\label{eq:fbar-half}
\]
Since \(|Dw|=2|\nabla v|\), \eqref{eq:level-linf} and
\eqref{eq:fbar-half} give
\[
   \bigl\||Dw|-1\bigr\|_{L^\infty(\partial E_{\hat t})}
      \le C\left(K^{-2/3}+C_K\sqrt\delta\right).
   \tag{9.9}
\]
Lemma~\ref{lem:inset-regularity} supplies connectedness, diameter control,
and the uniform \(C^{2,\alpha}\) atlas constants required in Brandolini's
Theorem~2.  Therefore Brandolini gives concentric inner and outer balls for
\(E_{\hat t}\) with gap bounded by the first term in \eqref{eq:eta-K}.  The
final area normalization changes all radii by \(1+O_K(\sqrt\delta)\), which
adds the last term in \eqref{eq:eta-K}.
\end{proof}

Thus the annular core needed by the Plan~3 radial-hull pocket lemma is indeed
available from the selection regularity route: first choose \(K\) so large
that the \(K^{-2/3}\) contribution is below the Brandolini/graph threshold,
and then choose \(\delta\) so small that the \(C_K\sqrt\delta\) errors are
smaller than the same threshold.

\begin{remark}
This check does not use BDV's final stability theorem as a black box.  It uses
only the selected-minimizer regularity package and Brandolini's Serrin
stability theorem.  If the available selection output were only Lipschitz
boundary, density, and bounded \(|\nabla u|\), then the argument would fail
exactly at Lemma~\ref{lem:inset-regularity}: Brandolini's Theorem~2 has a
constant depending on the \(C^{2,\alpha}\) atlas of the domain.
\end{remark}

\section{Verdict}

The user's split patches the scale objection.  The estimate
\[
   \|\,|\nabla u|-\bar f\,\|_{L^\infty(\partial E_{\hat t})}
      \le
      C\left(\frac{\delta}{\lambda^2}\right)^{1/3}
\]
forces the \(\sqrt\delta\)-inset scale, but this is compatible with the
proof by contradiction because the only nontrivial case has
\(\alpha(U)\gg\sqrt\delta\).

Thus the remaining issue is not a scale theorem.  If the selected regularity
input \emph{(SR)} is available, Brandolini supplies the same-center annular
core for the stopped level.  Combined with the Plan~3 radial-hull pocket
lemma, this gives the required radialization at \(O(\delta)\) fill cost and
closes the planar hybrid route.

If \emph{(SR)} is weakened to only Lipschitz boundary, density, and bounded
\(|\nabla u|\), then the proof stops exactly at Brandolini's regularity
constant: one has no uniform \(C^{2,\alpha}\) atlas for the stopped level.

\end{document}
