\section{The trapping annulus}\label{sec:annulus}

In this section we prove that the connected inset $\Etil$ produced in
\cref{sec:inset} is trapped between two concentric circles whose radii
differ by an \emph{absolutely small} amount, controlled by the perimeter
excess and the $L^1$ distance to a ball. The decisive point is that the
width of the trapping annulus is bounded \emph{without any second-order
information} on $\partial\Etil$: no interior or exterior ball condition, no
$C^2$ regularity, no Magnanini--Poggesi oscillation estimate. The only
inputs are the connectedness and the no-hole structure of the inset, the
planar isoperimetric deficit, and the closeness to a ball furnished by
\cref{thm:fmp}.

\begin{remark}[The inset is hole-filled from here on]\label{conv:fill}
From this section onward \emph{$\Etil$ denotes the hole-filled inset $E^h$ of
\cref{lem:fill}}: the saturation of the largest super-level component, with
all bounded complementary components filled in. By \cref{lem:fill}\ref{it:fill-top}
this set is bounded, open and connected, and globally hole-free
---$\R^2\setminus\overline\Etil$ is connected with
$\partial(\R^2\setminus\overline\Etil)=\partial\Etil$--- \emph{unconditionally},
with no hypothesis on $\partial\Om$. By \cref{lem:fill}\ref{it:fill-per} its
boundary is contained in that of the super-level component, $\partial\Etil
\subset\set{u=\hat v}\subset\Om$, so it remains an $\HH^1$-rectifiable curve
in the open set $\Om$, and by \cref{lem:fill}\ref{it:fill-scales} it inherits
\emph{every} inset scale ($\mu_E$, $\hat r$, $\diso$, $\Exc$, $a$, $\dstar$)
of \cref{prop:insetcontrols} with the same rates, the filled mass $H\le C\dT$
being of the same higher order as the spillover. All estimates below depend on
$\Etil$ only through these scales and through its connectedness and global
hole-freeness, so they hold verbatim for the hole-filled inset. We keep the
symbol $\Etil$ to avoid notational clutter; nothing in the geometric reduction
of \cref{sec:annulus,sec:fold,sec:cut} is sensitive to the replacement.
\end{remark}

The mechanism is purely geometric: the boundary of a connected, hole-free
set must cross every circle of intermediate radius at least twice; summed
against the radial coordinate through the coarea formula, this forces a
lower bound on the \emph{angular} part of the perimeter, which a single
Cauchy--Schwarz inequality converts into the deficit. We work throughout
with the \emph{measure-theoretic representative} of $\Etil$ described in
\cref{thm:torsion-reg,lem:regular-values,lem:containment,lem:fill}, in
accordance with the standing convention of \cref{ss:containment}: $\hat v$ is
a regular value of the (real-analytic, in $\Om$) torsion function $u$, and by
\cref{conv:fill} $\Etil$ is the hole-filled inset, a bounded open connected
subset of $\Om$ whose boundary lies in the level set $\set{u=\hat v}$ along
which $\nabla u\neq0$. Its topological boundary
\[
   \partial\Etil\subset\set{u=\hat v}\subset\Om
\]
\emph{lies in the open set $\Om$} and is an $\HH^1$-rectifiable curve along
which $\nabla u\neq0$; by \cref{lem:containment}\ref{it:cont-far} the closure
$\overline\Etil\cap\Om$ taken in $\Om$ is a compact subset of $\Om$, and the
only way $\overline\Etil$ (closure in $\R^2$) could meet $\partial\Om$ is on
a set carrying no perimeter of $\Etil$. We therefore use $\overline\Etil
\subset\subset\Om$ as shorthand for this compactness \emph{in $\Om$} of the
representative, which is all the arguments below require; no regularity of
$\partial\Om$ is assumed, and for the punctured disc
(\cref{ss:containment}) the apparent accumulation of $\overline\Etil$ at the
polar puncture is invisible to every quantity used. With this reading
$\partial\Etil$ coincides $\HH^1$-a.e.\ with the reduced and the essential
boundary, and $\HH^1(\partial\Etil)=P(\Etil)$. The plane decomposes
as the disjoint union
\begin{equation}\label{eq:trichotomy}
   \R^2=\Etil\ \sqcup\ \partial\Etil\ \sqcup\ \bigl(\R^2\setminus\overline\Etil\bigr),
\end{equation}
the first and last sets being open. We record the precise topological
consequence of the no-hole property that we shall use.

\begin{lemma}[Exterior connectedness convention]\label{lem:ext-conn}
In the geometric annulus theorem below, the phrase ``$E$ has no holes'' means
that $U:=\R^2\setminus\overline E$ is connected and
$\partial U=\partial E$ for the chosen representative.  Under this convention
the set $U$ used in \cref{lem:Ncross} is connected by hypothesis.
\end{lemma}

\begin{proof}
This is the convention used in the purely geometric part of the section.  The
identity $\partial U=\partial E$ is automatic for representatives satisfying
the trichotomy \eqref{eq:trichotomy} and $E=\operatorname{int}\overline E$.
\end{proof}

\begin{remark}[Global exterior connectedness is supplied by hole-filling]
\label{rem:noholes-resolved}
\Cref{lem:noholes} proves only that a super-level component of the torsion
function has no complementary component compactly contained in $\Om$, which is
weaker than the global exterior-connectedness convention above: a bounded hole
might in principle touch $\partial\Om$ and so evade the interior
minimum-principle argument. This is exactly why we pass to the hole-filled
inset of \cref{conv:fill}: by \cref{lem:fill}\ref{it:fill-top} the saturation
$\Etil=E^h$ has $\R^2\setminus\overline\Etil$ connected with
$\partial(\R^2\setminus\overline\Etil)=\partial\Etil$ \emph{unconditionally},
so it satisfies \cref{lem:ext-conn} with no hypothesis on $\partial\Om$ and no
appeal to the minimum principle. The annulus theorem \cref{thm:annulus} and
the inscribed-ball lemma \cref{lem:zinterior} below therefore apply to the
hole-filled inset directly, and \cref{lem:fill}\ref{it:fill-scales} guarantees
that the deficit and closeness controls are preserved at the sharp scale (the
filled mass being quadratic in the isoperimetric deficit). All statements of
this section are accordingly \emph{unconditional}.
\end{remark}

Throughout, $z\in\R^2$ denotes the centre of an optimal ball realising the
Fraenkel asymmetry of $\Etil$ --- the \emph{exact} $L^1$-optimal centre.
This $z$ is an interior point of $\Etil$, $z\in\Etil$, with a definite
inscribed ball; this is \emph{proved} for the inset, with the sharp rate and
an absolute constant, in \cref{lem:zinterior} below. (The proof is deferred
to the end of the section because it reuses the trapping mechanism, but it
removes any hypothesis on the location of $z$.) With
$\hat r:=\sqrt{|\Etil|/\pi}\in[\tfrac12,1]$ (the bounds follow from
$\pi/4\le|\Etil|\le\pi$, \cref{lem:spill})
\begin{equation}\label{eq:a-def}
   a:=|\Etil\triangle B_{\hat r}(z)|
   =\min_{x_0\in\R^2}|\Etil\triangle B_{\hat r}(x_0)|
   =\AF(\Etil)\,|\Etil| .
\end{equation}
We write $e_r:=(x-z)/|x-z|$ for the radial unit field (defined on
$\R^2\setminus\set z$), $e_\theta:=e_r^{\perp}$ for the orthogonal angular
field, $\nu$ for the outward unit normal on the rectifiable boundary, and
\[
   \nu_r:=\nu\cdot e_r,\qquad
   \nu_\theta:=\nu\cdot e_\theta,\qquad
   \nu_r^2+\nu_\theta^2=1 \quad(\HH^1\text{-a.e.\ on }\partial\Etil),
\]
\[
   P_r:=\int_{\partial\Etil}|\nu_r|\,\d\HH^1,
   \qquad
   P_\theta:=\int_{\partial\Etil}|\nu_\theta|\,\d\HH^1,
   \qquad
   0\le P_r,\,P_\theta\le P(\Etil).
\]
Finally we record the standing scaling assumption of the construction,
$\dT\le\delta_\star$, together with the deficit scales carried in from
\cref{sec:inset} (here $\tau$ is the level-selection parameter of that
section, kept symbolic until the optimisation in \cref{sec:main}):
\begin{equation}\label{eq:ann-scales}
   \Exc:=P(\Etil)-2\pi\hat r=2\pi\hat r\,\diso(\Etil)\le C\,\frac{\dT}{\tau},
   \qquad
   a\le C_{\mathrm F}\sqrt{\diso(\Etil)}\;|\Etil|\le C\Bigl(\frac{\dT}{\tau}\Bigr)^{1/2},
\end{equation}
the first from \cref{lem:spill}, the second from the planar quantitative
isoperimetric inequality \cref{thm:fmp}. In particular $\Exc+a\le C(\dT/\tau)
^{1/2}$ for $\dT/\tau\le1$, so the trapping width produced below will scale
like $(\dT/\tau)^{1/4}$.

\subsection{The inner and outer radii}

\begin{definition}[Inner and outer radius]\label{def:radii}
For the optimal centre $z\in\Etil$ set
\begin{equation}\label{eq:radii-def}
   \rho_i:=\sup\set{r>0:\ B_r(z)\subseteq\Etil},
   \qquad
   \rho_e:=\inf\set{r>0:\ \Etil\subseteq B_r(z)} .
\end{equation}
\end{definition}

We will use Definition~\ref{def:radii} under the hypothesis $z\in\Etil$,
which guarantees $\rho_i>0$; that $z\in\Etil$ holds in the application is
proved by \cref{lem:zinterior} \textup{(}using the global hole-freeness of
the hole-filled inset, \cref{lem:fill}\ref{it:fill-top}\textup{)}. The next
lemma collects the
elementary properties of these radii; they are the rigorous substitute for
the (here unavailable) minimum and maximum of $|x-z|$ over a smooth boundary.

\begin{lemma}[Basic properties of $\rho_i,\rho_e$]\label{lem:radii}
Assume $z\in\Etil$. Then $0<\rho_i\le\rho_e<\infty$ and
\begin{equation}\label{eq:inclusions}
   B_{\rho_i}(z)\subseteq\Etil\subseteq \overline{B_{\rho_e}(z)} .
\end{equation}
Moreover $\rho_i=\min_{x\in\partial\Etil}|x-z|$ and
$\rho_e=\max_{x\in\partial\Etil}|x-z|=\max_{x\in\overline\Etil}|x-z|$; both
extrema are attained, and
\begin{equation}\label{eq:rhat-between}
   \rho_i\le\hat r\le\rho_e .
\end{equation}
\end{lemma}

\begin{proof}
Since $z\in\Etil$ and $\Etil$ is open, some $B_r(z)\subseteq\Etil$, so
$\rho_i>0$; since $\Etil$ is bounded, $\rho_e<\infty$, and $B_r(z)\subseteq
\Etil\subseteq B_{r'}(z)$ forces $r\le r'$, whence $\rho_i\le\rho_e$. For the
left inclusion in \eqref{eq:inclusions}, $B_{\rho_i}(z)=\bigcup_{r<\rho_i}
B_r(z)\subseteq\Etil$. For the right inclusion, $\overline\Etil
\subseteq\overline{B_{\rho_e}(z)}$ because $\Etil\subseteq B_{r}(z)$ for
every $r>\rho_e$.

Set $\rho_i':=\min\set{|x-z|:x\in\partial\Etil}$ and $\rho_e':=\max\set{|x-z|:
x\in\partial\Etil}$, both attained since $\partial\Etil$ is compact and
nonempty.

\emph{The outer radius.} First, $\rho_e=\sup_{x\in\Etil}|x-z|$: indeed
$\Etil\subseteq B_r(z)$ holds iff $r>\sup_{x\in\Etil}|x-z|$, so the infimum
defining $\rho_e$ equals this supremum. We claim this supremum equals
$\rho_e'$, the maximal boundary radius. On one hand $\rho_e'\le\sup_{\Etil}
|x-z|$: a boundary point $w$ of radius $\rho_e'$ is a limit of points of
$\Etil$, whose radii approach $\rho_e'$. On the other hand $\sup_{\Etil}|x-z|
\le\rho_e'$: suppose some $x\in\Etil$ had $|x-z|>\rho_e'$. Extend the ray
from $z$ through $x$ to a far point $y$ with $y\notin\overline\Etil$
(possible, $\Etil$ being bounded). The set $\set{t\in[0,1]:(1-t)x+ty\in
\overline\Etil}$ is closed, contains $0$ but not $1$; its supremum $t^*$
gives a point $p=(1-t^*)x+t^*y\in\overline\Etil$ with all nearby points
further out on the ray outside $\overline\Etil$, so $p\in\partial\Etil$.
As $p$ lies on the outward ray beyond $x$, $|p-z|\ge|x-z|>\rho_e'$,
contradicting the maximality of $\rho_e'$. Hence $\rho_e=\sup_{\Etil}|x-z|
=\rho_e'$ is attained on $\partial\Etil$, and \eqref{eq:inclusions} gives
$\Etil\subseteq\overline{B_{\rho_e}(z)}$.

\emph{The inner radius.} No boundary point has radius $<\rho_i$, because the
open ball $B_{\rho_i}(z)\subseteq\Etil$ contains no point of $\partial\Etil$;
thus $\rho_i'\ge\rho_i$. Conversely $\rho_i'\le\rho_i$: the open ball
$B_{\rho_i'}(z)$ contains no boundary point (all of $\partial\Etil$ has
radius $\ge\rho_i'$), so by \eqref{eq:trichotomy} it is partitioned by the
two disjoint open sets $\Etil$ and $\R^2\setminus\overline\Etil$; being
connected and containing $z\in\Etil$, it lies entirely in $\Etil$, whence
$\rho_i\ge\rho_i'$ by definition of $\rho_i$. Hence $\rho_i=\rho_i'$,
attained at some $w_i\in\partial\Etil$ with $|w_i-z|=\rho_i$.

\emph{Position of $\hat r$.} Finally $B_{\rho_i}(z)\subseteq\Etil$ gives
$\pi\rho_i^2\le|\Etil|=\pi\hat r^2$, and $\Etil\subseteq\overline{B_{\rho_e}
(z)}$ gives $\pi\hat r^2=|\Etil|\le\pi\rho_e^2$, which is
\eqref{eq:rhat-between}.
\end{proof}

\subsection{The angular coarea identity}

For $\rho>0$ let
\begin{equation}\label{eq:Ndef}
   N(\rho):=\HH^0\bigl(\partial\Etil\cap\partial B_\rho(z)\bigr)
   \in\set{0,1,2,\dots,\infty}
\end{equation}
be the number of boundary points on the circle of radius $\rho$ about $z$.

\begin{lemma}[Angular coarea identity]\label{lem:angular-coarea}
With $P_\theta$ and $N$ as above,
\begin{equation}\label{eq:angular-coarea}
   P_\theta=\int_{\partial\Etil}|\nu_\theta|\,\d\HH^1
   =\int_0^\infty N(\rho)\,\d\rho .
\end{equation}
\end{lemma}

\begin{proof}
The radial function $f(x):=|x-z|$ is $1$-Lipschitz on $\R^2$, with
$\nabla f=e_r$ on $\R^2\setminus\set z$. Let $\nabla^{\partial\Etil}f$ denote
its tangential gradient along the rectifiable curve $\partial\Etil$, i.e.\
the orthogonal projection of $\nabla f$ onto the (approximate) tangent line,
which $\HH^1$-a.e.\ is the line $\R\,\nu^\perp$. Writing $\nu=\nu_r e_r
+\nu_\theta e_\theta$ and decomposing $e_r=(e_r\cdot\nu)\nu+(e_r\cdot
\nu^\perp)\nu^\perp$,
\[
   |\nabla^{\partial\Etil}f|=|e_r\cdot\nu^\perp|
   =\sqrt{1-(e_r\cdot\nu)^2}=\sqrt{1-\nu_r^2}=|\nu_\theta|
   \qquad(\HH^1\text{-a.e.}).
\]
The coarea formula for Lipschitz functions on $\HH^1$-rectifiable sets
\textup{(}\cref{thm:coarea}; see also \cite[Theorem~2.93]{AFP2000} and
\cite[\S3.4.2]{EvansGariepy2015}\textup{)} gives
\[
   \int_{\partial\Etil}|\nabla^{\partial\Etil}f|\,\d\HH^1
   =\int_0^\infty\HH^0\bigl(\partial\Etil\cap f^{-1}(\rho)\bigr)\,\d\rho
   =\int_0^\infty N(\rho)\,\d\rho,
\]
which is \eqref{eq:angular-coarea}.
\end{proof}

We record the companion \emph{weighted} identity, used once below. Let
$\Theta:\R^2\setminus\set z\to S^1$, $\Theta(x)=(x-z)/|x-z|$, be the angular
projection (well defined on $\partial\Etil$ since $z\in\Etil$ is interior).
A computation identical to the one above, now for $\Theta$, gives
$|\nabla^{\partial\Etil}\Theta|=|\nu_r|/|x-z|$, so the coarea formula with
the weight $g(x)=|x-z|$ yields
\begin{equation}\label{eq:radial-weighted}
   P_r=\int_{\partial\Etil}|\nu_r|\,\d\HH^1
     =\int_{\partial\Etil}|x-z|\,|\nabla^{\partial\Etil}\Theta|\,\d\HH^1
     =\int_{S^1}\Bigl(\sum_{x\in\partial\Etil\cap\,\mathrm{ray}(\theta)}|x-z|\Bigr)\d\theta,
\end{equation}
where $\mathrm{ray}(\theta):=\set{z+\rho e^{i\theta}:\rho>0}$. (We only use
the elementary consequence \eqref{eq:Pr-lower} below.)

\subsection{Two crossings at every intermediate radius}

\begin{lemma}[$N\ge2$ on the trapping interval]\label{lem:Ncross}
Assume $z\in\Etil$, and recall $U:=\R^2\setminus\overline\Etil$ is connected
with $\partial U=\partial\Etil$ \textup{(}\cref{lem:ext-conn}, from the global
hole-freeness of the hole-filled inset \cref{lem:fill}\ref{it:fill-top}\textup{)}.
Then
\begin{equation}\label{eq:Ngeq2}
   N(\rho)\ge2\qquad\text{for every }\rho\in(\rho_i,\rho_e).
\end{equation}
\end{lemma}

\begin{proof}
Fix $\rho\in(\rho_i,\rho_e)$ and let $C_\rho:=\partial B_\rho(z)$, a circle
(homeomorphic to $S^1$, hence connected). By \eqref{eq:trichotomy} every
point of $C_\rho$ lies in exactly one of the open sets $\Etil$,
$U:=\R^2\setminus\overline\Etil$, or in $\partial\Etil$. We show that
$C_\rho$ meets both $\Etil$ and $U$; the conclusion then follows from a
connectedness count.

\emph{Step 1: $C_\rho$ meets $\Etil$.} The function $f(x)=|x-z|$ is
continuous on the connected open set $\Etil$ (open connected subsets of
$\R^2$ are path-connected), so $f(\Etil)$ is an interval. It contains $0$
(as $z\in\Etil$, take $f(z)=0$) and, by \cref{lem:radii}, values
arbitrarily close to $\rho_e$ from below (points of $\Etil$ of radius
$\to\rho_e$). Hence $f(\Etil)\supseteq[0,\rho_e)\ni\rho$, so some point of
$\Etil$ has radius $\rho$, i.e.\ $C_\rho\cap\Etil\neq\varnothing$.

\emph{Step 2: $C_\rho$ meets $U$.} By \cref{lem:radii} there is a boundary
point $w_i\in\partial\Etil$ with $|w_i-z|=\rho_i$. For the good
representative the topological boundaries coincide, $\partial U=\partial
\overline\Etil=\partial\Etil$, so $w_i\in\overline U$, and every
neighbourhood of $w_i$ meets the open set $U$; thus $U$ contains points of
radius arbitrarily close to $\rho_i$, all of radius $\ge\rho_i$ since
$B_{\rho_i}(z)\subseteq\Etil$. Hence $\inf_{U}f=\rho_i$ (not necessarily
attained). On the
other hand $U$ is unbounded (it is the complement of the bounded set
$\overline\Etil$), so $\sup_U f=\infty$. Since $U$ is connected and open,
hence path-connected, $f(U)$ is an interval with infimum $\rho_i$ and
supremum $\infty$, so $f(U)\supseteq(\rho_i,\infty)\ni\rho$. Therefore some
point of $U$ has radius $\rho$, i.e.\ $C_\rho\cap U\neq\varnothing$.

\emph{Step 3: at least two boundary crossings.} Suppose, for contradiction,
that $\HH^0(C_\rho\cap\partial\Etil)\le1$. Then $C_\rho\setminus\partial\Etil$
is $C_\rho$ with at most one point removed, hence connected. By
\eqref{eq:trichotomy}, $C_\rho\setminus\partial\Etil=(C_\rho\cap\Etil)\sqcup
(C_\rho\cap U)$ is a partition into two disjoint sets that are open in
$C_\rho$ and, by Steps 1--2, both nonempty. A connected topological space
admits no such partition---a contradiction. Hence
$N(\rho)=\HH^0(C_\rho\cap\partial\Etil)\ge2$.
\end{proof}

\begin{remark}[Where connectedness and no-holes enter]\label{rem:why}
Connectedness of $\Etil$ is used in Step~1 to drive the radius continuously
from $0$ to near $\rho_e$; the no-hole hypothesis (connectedness of
$U=\R^2\setminus\overline\Etil$) is used in Step~2 to drive the
\emph{exterior} radius continuously from near $\rho_i$ out to $\infty$. If
$\Etil$ had a hole, the bounded complementary component could sit inside a
circle $C_\rho$ without forcing a second crossing, and the argument would
fail. The bound \eqref{eq:Ngeq2} holds for \emph{every}
$\rho\in(\rho_i,\rho_e)$, not merely almost every $\rho$; the a.e.\ caveat
enters only through the coarea formula \eqref{eq:angular-coarea}, where
$N(\rho)$ is finite for a.e.\ $\rho$ because $P_\theta\le P(\Etil)<\infty$.
\end{remark}

\subsection{The radial-profile bound}

We now bound the angular defect $P-P_r$ of the perimeter by the geometric
quantities $\Exc$ and $a$. Define the \emph{outer radial profile}
\begin{equation}\label{eq:Rdef}
   R(\theta):=\sup\set{\rho>0:\ z+\rho e^{i\theta}\in\Etil}\in[0,\rho_e]
   \qquad(\theta\in S^1).
\end{equation}
The function $R$ is measurable: for each $t>0$,
\[
   \{\theta:R(\theta)>t\}
   =\bigcup_{\substack{q\in\mathbb Q\\ q>t}}
      \{\theta:z+q e^{i\theta}\in\Etil\},
\]
and the sets in the union are open because $\Etil$ is open and
$\theta\mapsto z+q e^{i\theta}$ is continuous.
Because $z\in\Etil$ and $\Etil$ is bounded and open, the ray
$\mathrm{ray}(\theta)$ starts inside $\Etil$ and leaves it, so it meets
$\partial\Etil$; for a.e.\ $\theta$ the meeting set is finite with
outermost radius equal to $R(\theta)$, and
\begin{equation}\label{eq:Pr-lower}
   P_r=\int_{S^1}\Bigl(\sum_{x\in\partial\Etil\cap\,\mathrm{ray}(\theta)}|x-z|\Bigr)\d\theta
   \ \ge\ \int_{S^1}R(\theta)\,\d\theta,
\end{equation}
the equality being \eqref{eq:radial-weighted} and the inequality holding
because the inner sum is at least its largest term $R(\theta)$.

\begin{lemma}[Radial-profile bound]\label{lem:radial-profile}
Assume $z\in\Etil$. Then
\begin{equation}\label{eq:radial-profile}
   P(\Etil)-P_r\ \le\ \Exc+\frac{2a}{\hat r}\ \le\ \Exc+4a .
\end{equation}
\end{lemma}

\begin{proof}
For each $\theta$ with $R(\theta)<\hat r$, every point $z+\rho e^{i\theta}$
with $R(\theta)<\rho<\hat r$ has radius exceeding $R(\theta)$, hence lies
\emph{outside} $\Etil$ (by definition of $R$), while having radius $<\hat r$,
hence inside $B_{\hat r}(z)$; thus the radial segment $\set{R(\theta)<\rho
<\hat r}$ along direction $\theta$ lies in $B_{\hat r}(z)\setminus\Etil$.
Integrating in polar coordinates and using
$\int_{R}^{\hat r}\rho\,\d\rho=\tfrac12(\hat r^2-R^2)
=\tfrac12(\hat r-R)(\hat r+R)\ge\tfrac{\hat r}{2}(\hat r-R)$ (valid as
$R\ge0$),
\[
   a\ \ge\ |B_{\hat r}(z)\setminus\Etil|
   \ \ge\ \int_{\set{R<\hat r}}\!\int_{R(\theta)}^{\hat r}\rho\,\d\rho\,\d\theta
   \ \ge\ \frac{\hat r}{2}\int_{S^1}(\hat r-R(\theta))_+\,\d\theta,
\]
where $|B_{\hat r}(z)\setminus\Etil|\le|\Etil\triangle B_{\hat r}(z)|=a$ by
\eqref{eq:a-def}. Hence $\int_{S^1}(\hat r-R)_+\,\d\theta\le 2a/\hat r$, and
since $R\ge\hat r-(\hat r-R)_+$,
\[
   \int_{S^1}R(\theta)\,\d\theta\ \ge\ 2\pi\hat r-\int_{S^1}(\hat r-R)_+\,\d\theta
   \ \ge\ 2\pi\hat r-\frac{2a}{\hat r}.
\]
Combining with \eqref{eq:Pr-lower} and $P(\Etil)=2\pi\hat r+\Exc$,
\[
   P(\Etil)-P_r\ \le\ P(\Etil)-\int_{S^1}R\,\d\theta
   \ \le\ (2\pi\hat r+\Exc)-\Bigl(2\pi\hat r-\frac{2a}{\hat r}\Bigr)
   =\Exc+\frac{2a}{\hat r}.
\]
The final inequality in \eqref{eq:radial-profile} uses $\hat r\ge\tfrac12$.
\end{proof}

\subsection{The trapping theorem}

\begin{theorem}[Trapping annulus]\label{thm:annulus}
Let $E\subseteq\R^2$ be a bounded, open, connected set, equal to the good
representative described above \textup{(}so $\partial E$ is the topological
boundary, $\HH^1$-rectifiable with $\HH^1(\partial E)=P(E)$, and the
trichotomy \eqref{eq:trichotomy} holds\textup{)}, with no holes
\textup{(}$\R^2\setminus\overline E$ connected\textup{)}, area
$|E|=\pi\hat r^2$, isoperimetric deficit $\diso(E)$, perimeter excess
$\Exc=P(E)-2\pi\hat r=2\pi\hat r\,\diso(E)$, and ball distance
$a=|E\triangle B_{\hat r}(z)|$ at the optimal centre $z$. Assume $z\in E$,
and let $\rho_i,\rho_e$ be as in \eqref{eq:radii-def}. Then
\begin{equation}\label{eq:annulus}
   B_{\rho_i}(z)\subseteq E\subseteq \overline{B_{\rho_e}(z)},
   \qquad
   \rho_i\le\hat r\le\rho_e,
   \qquad
   4\eta^2\le 2(2\pi\hat r+\Exc)\Bigl(\Exc+\frac{2a}{\hat r}\Bigr),
\end{equation}
where $\eta:=\rho_e-\rho_i$.  In particular, if
$\hat r\in[\tfrac12,1]$ and $\Exc\le C_0$, then
$\eta\le C(C_0)(\Exc+a)^{1/2}$.  For the hole-filled inset $\Etil=E^h$ of
\cref{sec:inset} \textup{(}\cref{conv:fill}; $\dT\le\delta_\star$,
$\hat r\in[\tfrac12,1]$, and the scales \eqref{eq:ann-scales}\textup{)}, which
is connected and globally hole-free by \cref{lem:fill}\ref{it:fill-top} and
where the hypothesis $z\in\Etil$ at the \emph{exact} $L^1$-optimal centre $z$
holds by \cref{lem:zinterior} below,
\begin{equation}\label{eq:annulus-rate}
   \eta=\rho_e-\rho_i\ \le\ C\,(\Exc+a)^{1/2}\ \le\ C\,\Bigl(\frac{\dT}{\tau}
   \Bigr)^{1/4},
\end{equation}
which at the optimal choice $\tau=\sqrt{\dT}$ of \cref{sec:main} reads
$\eta\le C\,\dT^{1/8}$. This rate uses the ball distance $a$ at the exact
optimal centre, with no recentring penalty, the exterior-connectedness
hypothesis being available unconditionally
\textup{(}\cref{lem:fill}, \cref{lem:zinterior}\textup{)}.
\end{theorem}

\begin{proof}
The inclusions and $\rho_i\le\hat r\le\rho_e$ are \cref{lem:radii}; it
remains to prove the width bound. We give the estimate in three steps and
assemble.

\emph{Step 1 \textup{(}geometry $\Rightarrow$ angular perimeter\textup{)}.}
By \cref{lem:Ncross}, $N(\rho)\ge2$ for every $\rho\in(\rho_i,\rho_e)$, so
\cref{lem:angular-coarea} gives
\begin{equation}\label{eq:step1}
   P_\theta=\int_0^\infty N(\rho)\,\d\rho
   \ \ge\ \int_{\rho_i}^{\rho_e}2\,\d\rho
   =2(\rho_e-\rho_i)=2\eta .
\end{equation}

\emph{Step 2 \textup{(}Cauchy--Schwarz\textup{)}.} Write $P:=P(E)$. By the
Cauchy--Schwarz inequality on $\partial E$ (with the constant function $1$),
\[
   P_\theta^2=\Bigl(\int_{\partial E}|\nu_\theta|\,\d\HH^1\Bigr)^2
   \le P\int_{\partial E}\nu_\theta^2\,\d\HH^1
   = P\int_{\partial E}\bigl(1-\nu_r^2\bigr)\,\d\HH^1
   = P\Bigl(P-\int_{\partial E}\nu_r^2\,\d\HH^1\Bigr),
\]
using $\nu_r^2+\nu_\theta^2=1$. A second application of Cauchy--Schwarz gives
$\int_{\partial E}\nu_r^2\,\d\HH^1\ge\bigl(\int_{\partial E}|\nu_r|\,\d\HH^1
\bigr)^2/P=P_r^2/P$, hence
\begin{equation}\label{eq:step2}
   P_\theta^2\ \le\ P\Bigl(P-\frac{P_r^2}{P}\Bigr)=P^2-P_r^2
   =(P-P_r)(P+P_r)\ \le\ 2P\,(P-P_r),
\end{equation}
the last step using $0\le P_r\le P$.

\emph{Step 3 \textup{(}radial-profile bound\textup{)}.} By
\cref{lem:radial-profile}, $P-P_r\le\Exc+2a/\hat r$.

\emph{Assembly.} Combining \eqref{eq:step1}, \eqref{eq:step2}, Step 3 and
$P=2\pi\hat r+\Exc$,
\[
   4\eta^2\ \le\ P_\theta^2\ \le\ 2P\,(P-P_r)
   \ \le\ 2\,(2\pi\hat r+\Exc)\Bigl(\Exc+\frac{2a}{\hat r}\Bigr).
\]
This is the scale-correct width bound in \eqref{eq:annulus}. If
$\hat r\in[\tfrac12,1]$ and $\Exc\le C_0$, then
$2\pi\hat r+\Exc\le2\pi+C_0$ and $2a/\hat r\le4a$, so
$\eta\le C(C_0)(\Exc+a)^{1/2}$. Finally, for the inset, inserting
\eqref{eq:ann-scales}, $\Exc+a\le C(\dT/\tau)+C(\dT/\tau)^{1/2}\le
C(\dT/\tau)^{1/2}$ for $\dT/\tau\le1$, so $\eta\le C(\dT/\tau)^{1/4}$, which
is \eqref{eq:annulus-rate}; at $\tau=\sqrt\dT$ this is $C\dT^{1/8}$.
\end{proof}

\begin{remark}[A posteriori: the annulus is centred near the unit circle]
\label{rem:posterior}
The bound \eqref{eq:annulus-rate} together with $\rho_i\le\hat r\le\rho_e$
yields
\[
   \hat r-\rho_i\le\eta\le C\,(\dT/\tau)^{1/4},
   \qquad
   \rho_e-\hat r\le\eta\le C\,(\dT/\tau)^{1/4},
\]
so $\rho_i\ge\hat r-C(\dT/\tau)^{1/4}\ge\tfrac12$ and $\rho_e\le\hat
r+C(\dT/\tau)^{1/4}\le 2$ once $\dT\le\delta_\star$ is small enough (recall
$\hat r\in[\tfrac12,1]$ and $\dT/\tau\to0$). These bounds (in particular
$\rho_i\ge\tfrac12$) are exactly the inputs used in \cref{sec:fold,sec:cut};
they are \emph{outputs} of the trapping, not assumptions of it.
\end{remark}

\subsection{The exact optimal centre is interior: the inscribed-ball lemma}
\label{ss:zinterior}

It remains to discharge the sole structural hypothesis of \cref{thm:annulus}:
that the \emph{exact} $L^1$-optimal centre $z$ (the one realising
$a=|\Etil\triangle B_{\hat r}(z)|=\AF(\Etil)|\Etil|$) is an interior point of
$\Etil$, with a definite inscribed ball. Using the global
exterior-connectedness of the hole-filled inset (\cref{lem:fill}\ref{it:fill-top},
\cref{conv:fill}), we prove this
at the sharp scale, so that the rate \eqref{eq:annulus-rate} holds with the
ball distance $a$ measured at the exact optimum --- no recentring, hence no
square-root loss. The mechanism is the trapping mechanism itself, run
about $z$ before knowing $z\in\Etil$: the angular-coarea bound forces the
angular perimeter $P_\theta$ to be \emph{large} (a definite constant) whenever
$z$ fails to be interior, contradicting the smallness $P_\theta\le
C(\Exc+a)^{1/2}$ that the very same Cauchy--Schwarz/radial-profile chain
delivers.

We first isolate the two ingredients of the trapping chain that are valid for
\emph{any} centre $w\notin\partial\Etil$, not only for $w\in\Etil$. Recall
$\partial\Etil$ is a compact $\HH^1$-rectifiable curve in the open set $\Om$
with $\HH^1(\partial\Etil)=P:=P(\Etil)$.

\begin{lemma}[Centre-free Cauchy--Schwarz and radial-profile bounds]
\label{lem:centrefree}
Fix any $w\in\R^2\setminus\partial\Etil$ and define, with $e_r^w:=(x-w)/|x-w|$,
$\nu_r^w:=\nu\cdot e_r^w$, $\nu_\theta^w:=\nu\cdot(e_r^w)^\perp$,
\[
   P_r^w:=\int_{\partial\Etil}|\nu_r^w|\,\d\HH^1,
   \qquad
   P_\theta^w:=\int_{\partial\Etil}|\nu_\theta^w|\,\d\HH^1,
   \qquad
   N^w(\rho):=\HH^0\bigl(\partial\Etil\cap\partial B_\rho(w)\bigr).
\]
Then $P_\theta^w=\int_0^\infty N^w(\rho)\,\d\rho$, and
\begin{equation}\label{eq:cf-cs}
   (P_\theta^w)^2\ \le\ 2P\,(P-P_r^w).
\end{equation}
If moreover $a_w:=|\Etil\triangle B_{\hat r}(w)|$ denotes the ball distance at
$w$, then
\begin{equation}\label{eq:cf-radial}
   P-P_r^w\ \le\ \Exc+\frac{2a_w}{\hat r}.
\end{equation}
\end{lemma}

\begin{proof}
The coarea identity $P_\theta^w=\int_0^\infty N^w\,\d\rho$ is
\cref{lem:angular-coarea} verbatim with $z$ replaced by $w$: its proof uses
only that $f_w(x):=|x-w|$ is $1$-Lipschitz with $|\nabla^{\partial\Etil}f_w|
=|\nu_\theta^w|$ $\HH^1$-a.e.\ on $\partial\Etil$ (true since $w\notin
\partial\Etil$, so $e_r^w$ is defined and smooth along $\partial\Etil$), and
the coarea formula on the rectifiable curve. The chain \eqref{eq:cf-cs} is
Step~2 of the proof of \cref{thm:annulus} (eq.~\eqref{eq:step2}) verbatim:
it is two Cauchy--Schwarz inequalities on $\partial\Etil$ using
$(\nu_r^w)^2+(\nu_\theta^w)^2=1$ and $0\le P_r^w\le P$, with no reference to
the position of $w$. For \eqref{eq:cf-radial}, the proof of
\cref{lem:radial-profile} applies with $w$ in place of $z$: define the outer
radial profile $R_w(\theta):=\sup\set{\rho>0:w+\rho e^{i\theta}\in\Etil}\in
[0,\rho_e^w]$, where $\rho_e^w:=\sup_{x\in\Etil}|x-w|<\infty$; for each
$\theta$ with $R_w(\theta)<\hat r$ the segment $\set{R_w(\theta)<\rho<\hat r}$
on the ray from $w$ lies in $B_{\hat r}(w)\setminus\Etil$ (its points have
radius $>R_w(\theta)$, hence are outside $\Etil$ by definition of the
supremum, and radius $<\hat r$), so by polar integration and
$\int_R^{\hat r}\rho\,\d\rho\ge\tfrac{\hat r}{2}(\hat r-R)$ (valid as
$R\ge0$),
\[
   a_w\ \ge\ |B_{\hat r}(w)\setminus\Etil|\ \ge\
   \tfrac{\hat r}{2}\int_{S^1}(\hat r-R_w)_+\,\d\theta,
\]
whence $\int_{S^1}R_w\,\d\theta\ge2\pi\hat r-2a_w/\hat r$. Finally $P_r^w\ge
\int_{S^1}R_w\,\d\theta$ by the weighted coarea identity
\eqref{eq:radial-weighted} with $w$ in place of $z$ (again valid because
$w\notin\partial\Etil$, so $\Theta_w(x)=(x-w)/|x-w|$ is defined on
$\partial\Etil$), the inner sum there being at least its outermost term
$R_w(\theta)$. Combining with $P=2\pi\hat r+\Exc$ gives \eqref{eq:cf-radial}.
\end{proof}

\begin{lemma}[The exact optimal centre is interior; inscribed ball]
\label{lem:zinterior}
Let $\Etil=E^h$ be the hole-filled inset \textup{(}\cref{conv:fill};
$\dT\le\delta_\star$, connected, globally hole-free by
\cref{lem:fill}\ref{it:fill-top}, $\hat r\in[\tfrac12,1]$, scales
\eqref{eq:ann-scales}\textup{)}, and let $z$ be an \emph{exact} $L^1$-optimal
centre, $a=|\Etil\triangle B_{\hat r}(z)|=\AF(\Etil)|\Etil|$. There is an
absolute constant $C_0$ such that, after possibly shrinking the absolute
threshold $\delta_\star$,
\begin{equation}\label{eq:zinterior}
   z\in\Etil,
   \qquad
   \rho_i=\dist(z,\partial\Etil)\ \ge\ \hat r-C_0\,(\Exc+a)^{1/2}\ \ge\
   \tfrac12 .
\end{equation}
In particular $B_{\rho_i}(z)\subseteq\Etil$ with $\rho_i\ge\tfrac12>0$, so the
hypothesis $z\in\Etil$ of \cref{thm:annulus} holds at the exact optimum,
unconditionally.
\end{lemma}

\begin{proof}
Set $\beta:=2P\,(\Exc+2a/\hat r)$, an absolute small quantity: by
\eqref{eq:ann-scales} and $\hat r\in[\tfrac12,1]$ one has $P=2\pi\hat r+\Exc
\le2\pi+C$ and $\Exc+2a/\hat r\le\Exc+4a\le C(\Exc+a)\le C(\dT/\tau)^{1/2}$,
so
\begin{equation}\label{eq:beta-small}
   \beta\ \le\ C_1\,(\Exc+a)\ \le\ C_1\,C\,(\dT/\tau)^{1/2}
   \ \xrightarrow[\ \dT/\tau\to0\ ]{}\ 0,
\end{equation}
with $C_1$ absolute. We show that if $z$ is \emph{not} an interior point with
$\rho_i\ge\tfrac12$, then $\beta\ge\tfrac1{4}$, which is impossible once
$\delta_\star$ is small enough that the right side of \eqref{eq:beta-small} is
$<\tfrac14$; this proves \eqref{eq:zinterior}.

\emph{Step 0: trichotomy for $z$.} By \eqref{eq:trichotomy}, exactly one of
$z\in\Etil$, $z\in\partial\Etil$, $z\in U:=\R^2\setminus\overline\Etil$ holds.
We treat the two non-interior cases and show each forces $\beta\ge\tfrac14$;
we also show that in the interior case the inscribed radius is large.

\emph{Step 1: $z\in U$ is impossible.} Suppose $z\in U$. Put
$d:=\dist(z,\overline\Etil)>0$ (positive since $U$ is open). First, the
trivial area bound: $B_{\min(d,\hat r)}(z)\cap\Etil=\varnothing$, so
$\pi\min(d,\hat r)^2\le|B_{\hat r}(z)\setminus\Etil|\le a$; since $a\le
C(\dT/\tau)^{1/2}<\pi\hat r^2$ for $\dT/\tau$ small (as $\hat r\ge\tfrac12$),
this forces $d<\hat r$ and
\begin{equation}\label{eq:d-area}
   d\ \le\ \sqrt{a/\pi}\ \le\ C\,(\dT/\tau)^{1/4}\ \le\ \tfrac14
\end{equation}
for $\dT/\tau$ small. Now we lower-bound $P_\theta^z$. Because $z\notin
\partial\Etil$, \cref{lem:centrefree} applies with $w=z$, giving
$P_\theta^z=\int_0^\infty N^z(\rho)\,\d\rho$ and
$(P_\theta^z)^2\le2P(\Exc+2a/\hat r)=\beta$. We claim $N^z(\rho)\ge2$ for
every $\rho\in(d,\rho_e^z)$, where $\rho_e^z:=\sup_{x\in\Etil}|x-z|\ge\hat r$
(the inequality because $\Etil\subset\overline{B_{\rho_e^z}(z)}$ gives
$\pi\hat r^2=|\Etil|\le\pi(\rho_e^z)^2$). Indeed, let $C_\rho:=\partial
B_\rho(z)$ with $\rho\in(d,\rho_e^z)$.
\begin{itemize}[leftmargin=1.6em]
\item $C_\rho$ meets $\Etil$: the radial function $f(x)=|x-z|$ is continuous
on the connected open set $\Etil$, so $f(\Etil)$ is an interval; it has
infimum $d=\inf_{\overline\Etil}f$ (attained in $\overline\Etil$, approached
within $\Etil$) and supremum $\rho_e^z$, so $f(\Etil)\supseteq(d,\rho_e^z)\ni
\rho$.
\item $C_\rho$ meets $U$: by \cref{lem:ext-conn} the set $U$ is connected,
open and unbounded, and $z\in U$, so $f(U)$ is an interval with infimum
$f(z)=0$ and supremum $+\infty$; hence $f(U)\supseteq(0,\infty)\ni\rho$.
\end{itemize}
Thus $C_\rho\setminus\partial\Etil=(C_\rho\cap\Etil)\sqcup(C_\rho\cap U)$ is a
disjoint union of two nonempty relatively open subsets of the connected curve
$C_\rho$; were $N^z(\rho)=\HH^0(C_\rho\cap\partial\Etil)\le1$, removing at most
one point would leave $C_\rho$ connected, contradicting the existence of such a
partition. Hence $N^z(\rho)\ge2$. Therefore, using \eqref{eq:d-area} and
$\rho_e^z\ge\hat r\ge\tfrac12$,
\[
   \sqrt{\beta}\ \ge\ P_\theta^z\ =\ \int_0^\infty N^z\,\d\rho\ \ge\
   \int_{d}^{\rho_e^z}2\,\d\rho\ =\ 2(\rho_e^z-d)\ \ge\ 2\bigl(\tfrac12-
   \tfrac14\bigr)\ =\ \tfrac12,
\]
so $\beta\ge\tfrac14$, the desired contradiction. Hence $z\notin U$.

\emph{Step 2: $z\in\partial\Etil$ is impossible.} Suppose $z\in\partial\Etil$.
We cannot apply \cref{lem:centrefree} directly at $w=z$, but we apply it at a
sequence $w_k\to z$, $w_k\in U$, $w_k\notin\partial\Etil$ (such $w_k$ exist:
$z\in\partial\Etil=\partial U$ by \cref{lem:ext-conn}, so every neighbourhood
of $z$ meets the open set $U$). Set $d_k:=\dist(w_k,\overline\Etil)\ge0$, with
$d_k\to0$ as $w_k\to z\in\partial\Etil$. Exactly as in Step~1
\textup{(}$w_k\in U$\textup{)} we obtain $N^{w_k}(\rho)\ge2$ for $\rho\in
(d_k,\rho_e^{w_k})$, where $\rho_e^{w_k}=\sup_{x\in\Etil}|x-w_k|\ge\hat r$, and
\[
   P_\theta^{w_k}\ \ge\ 2(\rho_e^{w_k}-d_k)\ \ge\ 2(\hat r-d_k)\
   \xrightarrow[k\to\infty]{}\ 2\hat r\ \ge\ 1 .
\]
On the other hand $a_{w_k}=|\Etil\triangle B_{\hat r}(w_k)|\le a+4\pi\hat r\,
|w_k-z|\to a$, since $B_{\hat r}(z)\triangle B_{\hat r}(w_k)\subseteq
B_{\hat r+|w_k-z|}(z)\setminus B_{\hat r-|w_k-z|}(z)$ has measure
$4\pi\hat r|w_k-z|$; so by \eqref{eq:cf-cs}--\eqref{eq:cf-radial},
$(P_\theta^{w_k})^2\le2P(\Exc+2a_{w_k}/\hat r)$, whose right side tends to
$2P(\Exc+2a/\hat r)=\beta$. Fix $\eps>0$. For $k$ large, $d_k<\eps$ and the
right side is $<\beta+\eps$, so $(2\hat r-2\eps)^2\le(P_\theta^{w_k})^2<
\beta+\eps$; as $\hat r\ge\tfrac12$ and $\eps>0$ is arbitrary this gives
$1\le4\hat r^2\le\beta$, so again $\beta\ge1>\tfrac14$, a contradiction.
Hence $z\notin\partial\Etil$.

\emph{Step 3: interior case and inscribed radius.} By Steps~1--2, $z\in\Etil$.
Then \cref{def:radii} gives $\rho_i=\dist(z,\partial\Etil)>0$ and
$B_{\rho_i}(z)\subseteq\Etil$ (\cref{lem:radii}), and \cref{thm:annulus}
applies at this very $z$ with the exact ball distance $a$: it yields
$\eta=\rho_e-\rho_i\le C(\Exc+a)^{1/2}$. Since $\rho_i\le\hat r\le\rho_e$
(\cref{lem:radii}), $\hat r-\rho_i\le\rho_e-\rho_i=\eta$, whence
\[
   \rho_i\ \ge\ \hat r-\eta\ \ge\ \hat r-C(\Exc+a)^{1/2}\ =:\
   \hat r-C_0(\Exc+a)^{1/2}.
\]
By \eqref{eq:ann-scales}, $C_0(\Exc+a)^{1/2}\le C_0C(\dT/\tau)^{1/4}\le
\hat r-\tfrac12$ once $\delta_\star$ is small (recall $\hat r\ge\tfrac12$ and,
in the application $\tau=\sqrt\dT$, $\hat r\to1$ so $\hat r\ge\tfrac34$ and
$\hat r-\tfrac12\ge\tfrac14\ge C_0C\dT^{1/8}$ for $\dT$ small). Hence
$\rho_i\ge\tfrac12$, which is \eqref{eq:zinterior}.
\end{proof}

\begin{remark}[Why this is the sharp, not the recentred, rate]
\label{rem:zinE}
The naive route recenters from the exact optimum $z$ to a nearby interior
point $z_0\in\Etil$ with $|z-z_0|$ possibly as large as $\dist(z,\Etil)\sim
a^{1/2}$, and pays the \emph{linear} symmetric-difference penalty
$a_0\le a+4\pi\hat r|z-z_0|\sim a^{1/2}$, one square root worse than $a$;
fed into \eqref{eq:annulus} this gives only $\eta\le C(\Exc+a_0)^{1/2}\sim
\dT^{1/16}$ at $\tau=\sqrt\dT$. \cref{lem:zinterior} avoids recentring
altogether: it proves the exact optimum is \emph{already} interior with
$\rho_i\ge\tfrac12$, so the trapping is run at $z$ itself and the ball
distance entering \eqref{eq:annulus} is the optimal $a\sim\dT^{1/4}$, giving
the sharp $\eta\le C(\Exc+a)^{1/2}\sim\dT^{1/8}$. The decisive point is that
the obstruction to interiority is charged not to the \emph{area} $a$ (which
only bounds $\dist(z,\Etil)\lesssim a^{1/2}$) but to the \emph{angular
perimeter}: a non-interior centre would force $P_\theta\ge\tfrac12$ a definite
constant, whereas the deficits force $P_\theta\le C(\Exc+a)^{1/2}\to0$. This
is the rigorous form of route~(i) of the program: the cost of the exterior
pocket reaching $z$ is the two crossings it forces at \emph{every}
intermediate radius, summed by the coarea identity, i.e.\ a perimeter cost,
not an area cost.
\end{remark}

\begin{remark}[The a-posteriori check is now a theorem]\label{rem:zinE-gap}
The self-consistency observation of \cref{rem:posterior} --- that the trapping
output $\rho_i\ge\tfrac12$ is compatible with $z$ being interior --- is
\emph{upgraded to a proof} by \cref{lem:zinterior}: interiority is established
\emph{a priori}, by the same angular-coarea mechanism, with no appeal to the
conclusion. Consequently the graph-defect bound \cref{cor:gd}, the closeness
$|\Om\triangle G|$ of \cref{sec:fold,sec:cut}, and the final exponent in
\cref{thm:main} all rest on the \emph{sharp} rate $\eta\sim\dT^{1/8}$
unconditionally, the global hole-freeness being supplied by the hole-filled
inset (\cref{lem:fill}); the degenerate boundary configuration of the optimal
centre does \emph{not} occur.
The inputs of this section remain exactly connectedness, the global hole
property, $\Exc$ and $a$ (the Serrin defect $D_H$ is not used).
\end{remark}

\begin{remark}[What is, and is not, used]\label{rem:summary}
The trapping width $\eta\le C(\Exc+a)^{1/2}$ is proved with an
\emph{absolute} constant and \emph{no} second-order information on
$\partial\Etil$: no interior or exterior ball condition, no curvature bound,
no harmonic oscillation estimate. The ingredients are exactly: the
connectedness and global hole-freeness of $\Etil$
(\cref{lem:noholes,lem:fill}); the
coarea formula on a rectifiable curve (\cref{thm:coarea}); the isoperimetric
excess $\Exc$ and the FMP closeness $a$ (\cref{thm:fmp}, via
\eqref{eq:ann-scales}). Notably, the Cauchy--Schwarz/Serrin defect $D_H$ is
\emph{not} used in this section. The single arithmetic of the proof is the
chain $4\eta^2\le P_\theta^2\le2P(P-P_r)\le2P(\Exc+2a/\hat r)$, in which the
geometric lower bound (two crossings per circle) is converted into the
deficit by one Cauchy--Schwarz and one elementary radial-profile estimate.
The hypothesis $z\in\Etil$ --- the interiority of the exact $L^1$-optimal
centre, used to start the radius at $0$ and to define the angular projection
--- is itself \emph{proved} from the same ingredients in \cref{lem:zinterior}
(the very same chain, run before interiority is known, forces a definite
$P_\theta$ at a non-interior centre, contradicting the deficit smallness).
Consequently the \emph{sharp rate} $\eta\le C(\Exc+a)^{1/2}\sim\dT^{1/8}$ for
the inset's exact FMP centre follows unconditionally, the
exterior-connectedness being supplied by the hole-filled inset
(\cref{lem:fill}, \cref{conv:fill}).
\end{remark}
