\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\setlength{\parskip}{0.3em}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Om}{\Omega}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\eps}{\varepsilon}
\newcommand{\dT}{\delta_T}
\newcommand{\diso}{\delta_{\mathrm{iso}}}
\newcommand{\Etil}{\widetilde E}
\newcommand{\abs}[1]{\left|#1\right|}

\title{The inset of a near-extremal Saint--Venant domain\\
       is a regular set}
\author{}
\date{}

\begin{document}
\maketitle

\begin{abstract}
Let $\Om\subset\R^2$ be a bounded open set of area $\pi$ whose torsional
rigidity is close to that of the disk, i.e.\ with small Saint--Venant
deficit $\dT(\Om)=T(B_1)-T(\Om)$. The boundary $\partial\Om$ may be
arbitrarily irregular. We prove that a suitably chosen super-level set of
the torsion function --- the \emph{inset} --- is nonetheless a regular set,
and we quantify in what sense. Precisely (Theorem~\ref{thm:main}), there is
a regular value $\hat v$ of the torsion function $u$ such that the inset
$\Etil=\{u>\hat v\}$ has: \emph{(i)} an analytic boundary (a finite union of
analytic Jordan curves) lying at positive distance from $\partial\Om$, with
$|\nabla u|>0$ on it; \emph{(ii)} small isoperimetric and Serrin deficits,
both $O(\dT)$; \emph{(iii)} closeness to a disk in measure,
$|\Etil\,\triangle\,B|\lesssim\sqrt\dT$; \emph{(iv)} no interior holes; and
\emph{(v)} containment in a thin annulus between two concentric circles,
$B_{\hat r-\eta}(z)\subset\Etil\subset B_{\hat r+\eta}(z)$. For the width we
give two routes: applying the Magnanini--Poggesi stability theorem to the
\emph{smooth} inset yields $\eta\lesssim\dT^{\tau/2}$ but with a constant
depending on the inset's $C^2$ geometry; replacing the interior/exterior
ball conditions of that proof by the \emph{measure-theoretic} crossing count
of the radial function on $\partial\Etil$ --- the coarea identity
$\int_{\partial\Etil}|\nu_\theta|=\int_0^\infty N(\rho)\,d\rho$, which sums
all inward fjords and outward tentacles at once --- yields instead
$\eta\lesssim\dT^{1/4}$ with an \emph{absolute} constant, free of any $C^2$
dependence and free of the multi-fjord covering bookkeeping, the whole
dependence being on the isoperimetric deficit $D_I$. Every lemma is proved
in full; standard facts are cited verbatim. The qualitative principle is
that the roughness of $\partial\Om$ never reaches the inset: every feature
of $\Etil$ is controlled by the deficits alone.
\end{abstract}

\tableofcontents

\section{Introduction}\label{sec:intro}

\subsection*{Setup and motivation}
For a bounded open set $\Om\subset\R^2$, the \emph{torsion function} $u$ is
the solution of $-\Delta u=1$ in $\Om$ with $u=0$ on $\partial\Om$, and the
\emph{torsional rigidity} is $T(\Om)=\int_\Om u$. The Saint--Venant
inequality states $T(\Om)\le T(B)$ among sets $B$ of equal area, with
equality only for disks. Normalising $|\Om|=\pi$ (so the optimal disk is the
unit disk $B_1$, $T(B_1)=\pi/8$), the \emph{Saint--Venant deficit} is
\[
   \dT(\Om):=T(B_1)-T(\Om)\ \ge\ 0 .
\]
A central problem is the sharp \emph{quantitative} Saint--Venant
inequality, which would bound the Fraenkel asymmetry of $\Om$ by $\dT$. A
standard difficulty is that $\partial\Om$ carries no a priori regularity:
the only hypothesis is that $\dT$ is small. The contribution of this note is
to show, with complete proofs, that one can extract from $\Om$ a
\emph{regular} subdomain --- a super-level set of $u$ --- that captures the
geometry while being analytic, nearly circular, and trapped (on the outside)
in a thin annulus. This ``inset'' is the object on which the perturbative
machinery of the quantitative theory can be run.

The key principle is that \emph{the interior is always regular}: $u$ solves
an analytic elliptic equation, so it is real-analytic inside $\Om$ no matter
how rough $\partial\Om$ is, and its level sets a definite distance inside are
analytic curves (Section~\ref{sec:smooth}). The roughness of $\partial\Om$
does not propagate inward. What requires work is the \emph{quantitative}
geometry: that the inset is nearly a disk, and how nearly.

\subsection*{Standing assumptions}
Throughout, $\Om\subset\R^2$ is a bounded open set, regular for the
Dirichlet problem (so that the torsion function satisfies $u\in
H^1_0(\Om)\cap C(\overline\Om)$ with $u=0$ on $\partial\Om$; this holds for
instance whenever $\Om$ satisfies an exterior corkscrew or cone condition,
and is no loss for the deficit since $\dT$ is continuous under invasion of
$\Om$ by regular subdomains). We normalise $|\Om|=\pi$. We write $\dT$ for
$\dT(\Om)$ and assume $\dT\le\delta_\star$, where $\delta_\star>0$ is an
absolute constant fixed in the course of the proofs. Constants denoted
$c,C,C_0,\dots$ are absolute unless a dependence is displayed; the only
non-absolute dependence that appears anywhere is in the annulus
\emph{width} of Section~\ref{sec:trapping}, whose constant depends on the
$C^2$ geometry of the (smooth) inset --- see Remark~\ref{rem:nonuniform}.
Every other constant in the paper is absolute.

\subsection*{Main result}
The following theorem collects the conclusions proved in
Sections~\ref{sec:smooth}--\ref{sec:trapping}. Recall the \emph{isoperimetric
deficit} $\diso(E)=P(E)/(2\sqrt{\pi|E|})-1$ and the \emph{Fraenkel
asymmetry} $\mathcal A(E)=\min_x|E\triangle B(x)|/|E|$ (disk $B(x)$ of area
$|E|$).

\begin{theorem}[The inset is a regular set]\label{thm:main}
There is an absolute constant $\delta_\star>0$ with the following property.
Let $\Om\subset\R^2$ be bounded open, regular for the Dirichlet problem,
$|\Om|=\pi$, with torsion function $u$ and $\dT(\Om)\le\delta_\star$. Then
there is a regular value $\hat v\in(0,\tfrac14)$ of $u$ such that the
\emph{inset}
\[
   \Etil:=\{x\in\Om:u(x)>\hat v\},\qquad
   \hat\mu:=|\Etil|\in[\tfrac\pi4,\pi),\qquad
   \hat r:=\sqrt{\hat\mu/\pi}\in[\tfrac12,1),
\]
satisfies all of the following.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
\item \textup{(Analytic boundary, interior.)} $\partial\Etil=\{u=\hat v\}$
is a finite disjoint union of real-analytic Jordan curves, with
$|\nabla u|>0$ everywhere on it, and
$\operatorname{dist}(\overline\Etil,\partial\Om)>0$. Consequently $\Etil$ is
a bounded open set of finite perimeter, $P(\Etil)=\HH^1(\{u=\hat v\})$, with
outward unit normal $-\nabla u/|\nabla u|$.
\item \textup{(Controlled deficits.)} $\diso(\Etil)\le C\,\dT$ and the
weighted Serrin deficit obeys
$\displaystyle\int_{\partial\Etil}\frac{(|\nabla u|-c)^2}{|\nabla u|}\,
d\HH^1\le C\,\dT$, where $c=|\Etil|/P(\Etil)$.
\item \textup{(Near-circular in measure.)} There is $z\in\R^2$ with
$\abs{\Etil\,\triangle\,B_{\hat r}(z)}\le C\,\sqrt\dT$; equivalently
$\mathcal A(\Etil)\le C\sqrt\dT$.
\item \textup{(No interior holes.)} Every connected component of
$\Om\setminus\overline\Etil$ has closure meeting $\partial\Om$; in
particular $\Etil$ has no holes.
\item \textup{(Squeezed between two concentric circles.)} The inset (its
main component) is trapped in a thin annulus
$B_{\hat r-\eta}(z)\subset\Etil\subset B_{\hat r+\eta}(z)$, in either of two
forms:
\begin{itemize}[leftmargin=1.4em]
\item[\textup{(v$_{\mathrm{a}}$)}] \textup{(via Magnanini--Poggesi)}
$\eta\le C_{\mathrm{MP}}\,\dT^{\tau/2}$, $\tau\in(0,1]$ absolute, but
$C_{\mathrm{MP}}$ depending on the $C^2$ geometry of the smooth inset
\textup{(}Theorem~\ref{thm:annulus}\textup{)};
\item[\textup{(v$_{\mathrm{b}}$)}] \textup{(regularity-free)} $\eta\le
C\,\dT^{1/4}$ with $C$ \emph{absolute}, depending only on the deficits;
proved via the angular-perimeter coarea identity
$P_\theta=\int_0^\infty N(\rho)\,d\rho$, which charges all inward fjords and
outward tentacles to $D_I$ at once \textup{(}no $C^2$ data, no covering;
Theorem~\ref{thm:perim-annulus}\textup{)}. The only standing assumption is
connectedness of the main component, which carries area $\hat\mu-O(\dT)$.
\end{itemize}
\end{enumerate}
The constants $C$ in \textup{(i)--(iv)} are \emph{absolute}. Clause
\textup{(v$_{\mathrm a}$)} pays a non-absolute $C^2$ constant;
\textup{(v$_{\mathrm b}$)} removes it with an absolute constant, the entire
dependence then being on the isoperimetric deficit $D_I$
(Remarks~\ref{rem:nonuniform}, \ref{rem:covering-gone}, \ref{rem:loop}).
\end{theorem}

\subsection*{Strategy and organisation}
The proof has three layers. \emph{Interior regularity}
(Sections~\ref{sec:prelim}--\ref{sec:smooth}): $u$ is analytic inside, so
a.e.\ level set is an analytic curve at positive distance from
$\partial\Om$; this is qualitative and uses no smallness. \emph{Energy /
$L^1$ control} (Sections~\ref{sec:identity}--\ref{sec:controlled}): the
level-set deficit identity
$\int_0^m(D_H+D_I)\,dv=4\pi\dT$ (Theorem~\ref{thm:identity}) writes the
deficit as the total of two non-negative level defects; combined with
Talenti's volume comparison (Section~\ref{sec:talenti}) it yields, by
averaging, a single good inset with $O(\dT)$ isoperimetric and Serrin
defects and definite area, hence $\sqrt\dT$-closeness to a disk by the
sharp quantitative isoperimetric inequality. \emph{Geometric control}
(Sections~\ref{sec:topology}--\ref{sec:trapping}): superharmonicity removes
interior holes, and --- crucially using that the inset is \emph{smooth} ---
the Magnanini--Poggesi stability theorem for Serrin's overdetermined problem
traps the inset between two concentric circles. This last step is where the
inset's smoothness pays off: the regularity-dependent stability machinery,
inapplicable to the rough $\Om$, applies to the analytic $\Etil$.

Section~\ref{sec:prelim} collects the cited background; the reader familiar
with finite-perimeter theory, the FMP inequality, interior elliptic
regularity, and Sard's and Talenti's theorems may skip to
Section~\ref{sec:smooth}.

\bigskip
\input{sec_preliminaries}

\bigskip
\input{sec_smoothness}

\bigskip
\input{sec_core}

\bigskip
\input{sec_core2}

\bigskip
\input{sec_density_annulus}

\begin{thebibliography}{99}

\bibitem{AFP2000} L.~Ambrosio, N.~Fusco, D.~Pallara,
\emph{Functions of Bounded Variation and Free Discontinuity Problems},
Oxford Mathematical Monographs, Oxford University Press, 2000.

\bibitem{EvansGariepy2015} L.~C.~Evans, R.~F.~Gariepy,
\emph{Measure Theory and Fine Properties of Functions}, revised edition,
Textbooks in Mathematics, CRC Press, Boca Raton, 2015.

\bibitem{FMP2008} N.~Fusco, F.~Maggi, A.~Pratelli,
\emph{The sharp quantitative isoperimetric inequality},
Annals of Mathematics (2) \textbf{168} (2008), no.~3, 941--980.

\bibitem{GT1983} D.~Gilbarg, N.~S.~Trudinger,
\emph{Elliptic Partial Differential Equations of Second Order},
Grundlehren der mathematischen Wissenschaften 224, Springer-Verlag, Berlin,
2nd ed., 1983 (reprinted 2001).

\bibitem{KrantzParks2002} S.~G.~Krantz, H.~R.~Parks,
\emph{A Primer of Real Analytic Functions}, 2nd ed., Birkh\"auser Advanced
Texts, Boston, 2002.

\bibitem{Maggi2012} F.~Maggi,
\emph{Sets of Finite Perimeter and Geometric Variational Problems. An
Introduction to Geometric Measure Theory}, Cambridge Studies in Advanced
Mathematics 135, Cambridge University Press, 2012.

\bibitem{MagnaniniPoggesi2019} R.~Magnanini, G.~Poggesi,
\emph{On the stability for Alexandrov's Soap Bubble theorem},
Journal d'Analyse Math\'ematique \textbf{139} (2019), no.~1, 179--205.
\textup{(}See also: \emph{Serrin's problem and Alexandrov's Soap Bubble
Theorem: stability via integral identities}, Indiana Univ.\ Math.\ J.\
\textbf{69} (2020), no.~4, 1181--1205.\textup{)}

\bibitem{Milnor1997} J.~W.~Milnor,
\emph{Topology from the Differentiable Viewpoint}, revised reprint,
Princeton Landmarks in Mathematics, Princeton University Press, 1997.

\bibitem{Morrey1966} C.~B.~Morrey, Jr.,
\emph{Multiple Integrals in the Calculus of Variations}, Grundlehren der
mathematischen Wissenschaften 130, Springer-Verlag, New York, 1966.

\bibitem{Sard1942} A.~Sard,
\emph{The measure of the critical values of differentiable maps},
Bulletin of the American Mathematical Society \textbf{48} (1942), 883--890.

\bibitem{Talenti1976} G.~Talenti,
\emph{Elliptic equations and rearrangements},
Annali della Scuola Normale Superiore di Pisa, Classe di Scienze (4)
\textbf{3} (1976), no.~4, 697--718.

\end{thebibliography}

\end{document}
