\documentclass[a4paper,11pt,reqno]{amsart}
% This is the authoritative version. main.tex is an earlier version retained for reference.
\usepackage[utf8]{inputenc}
\usepackage{enumerate}
\usepackage{amsmath, amssymb,amsthm}
\usepackage{mathtools}
\usepackage{leftidx}
\usepackage{setspace}
\numberwithin{equation}{section}
%\usepackage{mathbbol}
\setcounter{tocdepth}{1} %2=show subsections, 1= show only sections
\usepackage[left=3cm, right=3cm]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
%\definecolor{name}{model}{color-spec}
\definecolor{my-black}{rgb}{0,0,0}
\definecolor{my-blue}{rgb}{0,0,0.8}
\definecolor{my-red}{rgb}{0.8,0,0} 
\definecolor{my-green}{rgb}{0,0.5,0}
\hypersetup{colorlinks,
    linkcolor	= {my-blue},
    citecolor	= {my-red},
    urlcolor		= {my-black}
}
\usepackage{graphicx}
\usepackage{tikz-cd}
\onehalfspacing
%Javier's suggestion to avoid overfull boxes
%\overfullrule=10cm better not to use because ArXiv might mess up things
%\usepackage{microtype}

\theoremstyle{plain} %italic

\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{problem}{Problem}[section]
\newtheorem{consequence}{Consequence}[section]
\newtheorem*{theorem*}{Theorem} %to avoid numbering


\theoremstyle{definition} %non-italic
\newtheorem{remark}{Remark}[section]

\newtheorem{definition}{Definition}[section]
\newtheorem{notation}{Notation}[section]
\newtheorem{conjecture}{Conjecture}[section]
\newtheorem{example}{Example}[section]
\newtheorem{claim}{Claim}[section]

\theoremstyle{remark}
\newtheorem*{remark-non}{Remark}

\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\real}{Re}
\DeclareMathOperator{\imag}{Im}
\DeclareMathOperator{\image}{im}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\inv}{inv}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\Hol}{Hol}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\PGL}{PGL}
\DeclareMathOperator{\PSL}{PSL}
\DeclareMathOperator{\Spur}{Sp}
\DeclareMathOperator{\PSO}{PSO}
\DeclareMathOperator{\SO}{SO}
\DeclareMathOperator{\Or}{O}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\diam}{diam}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\sinc}{sinc}
\DeclareMathOperator{\disc}{disc}


\newcommand{\R}{\mathbb{R}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\g}{\mathfrak{g}}
\renewcommand{\o}{\mathfrak{o}}
\renewcommand{\d}{\mathfrak{d}}
\renewcommand{\a}{\mathfrak{a}}
\renewcommand{\b}{\mathfrak{b}}
\newcommand{\p}{\mathfrak{p}}
\newcommand{\I}{\mathbf{I}}

\renewcommand{\sl}{\mathfrak{sl}}
\newcommand{\h}{\mathfrak{h}}
\renewcommand{\H}{\mathbb{H}}
\textwidth 16cm
\oddsidemargin  0cm \evensidemargin 0cm \parindent0.7em
\textheight 23cm
\allowdisplaybreaks


\title[Time-frequency localization]{Eigenfunctions, Free Boundaries, and Time-Frequency Localization}
\author{Jo{\~a}o P.G. Ramos}



\begin{document}
\maketitle 
\begin{abstract}
We study Gaussian time--frequency localization operators through their Bargmann--Fock representation, developing an inverse and free-boundary approach to their spectral theory. Our perturbative inverse theory shows that functions sufficiently close to the ground-state Hermite function can be realized as eigenfunctions of localization operators; as a byproduct we recover the Abreu--D\"orfler disk characterization in the simply connected setting, and we prove that the stability estimate of G\'omez--Guerra, Ramos and Tilli is sharp.

We then apply these inverse results to Faber--Krahn-type problems for Gaussian time--frequency concentration: local maximizers of the first localization eigenvalue under a measure constraint are necessarily disks, and global maximizers exist by a concentration--compactness argument in the Bargmann--Fock space, recovering the Nicola--Tilli theorem from this perspective.
\end{abstract}

\noindent\textbf{Keywords:} Gaussian STFT, localization operators, Bargmann--Fock space, inverse spectral problem, free boundary, quadrature domains, Faber--Krahn inequality, time-frequency concentration.

\medskip

\noindent\textbf{MSC2020:} 42B10, 42C15, 30H20, 35R35, 35R30, 47B35, 49Q10.


% ==============================================================
% Section 1: Introduction
% ==============================================================

\section{Introduction}

How does a function concentrate in phase space? This is the founding question of time--frequency analysis, dating back to Wigner, Gabor, and Daubechies, and it admits a precise formulation in terms of the \emph{short-time Fourier transform}
\begin{equation}\label{eq:STFT-intro}
V_\varphi f(x,\omega) \;=\; \int_{\R} f(t)\,\overline{\varphi(t-x)}\,e^{-2\pi i t \omega}\,dt,
\qquad f,\varphi\in L^2(\R),
\end{equation}
whose squared modulus is the canonical phase-space energy density of $f$. Identifying which signals achieve maximal concentration on a prescribed set $\Omega\subset\R^2$ leads to the spectral analysis of the \emph{time--frequency localization operator} $\mathcal L_\Omega$ introduced by Daubechies \cite{Daubechies}; see \cite{Grochenig,Mallat,Folland,Daubechies-Paul,Ramanathan-Topiwala-Weyl,Ramanathan-Topiwala-Spectrogram,Cordero-Grochenig,Boggiatto-Cordero-Grochenig,Bayer-Grochenig,Kisil-CrossToeplitz,Nicola-Tilli-2,Ramos-time-frequency} for the broader theory and \cite{Lieb,abreu2021donoho} for the underlying uncertainty and large-sieve phenomena.

The Gaussian window $\varphi(x)=2^{1/4}e^{-\pi x^2}$ is exceptional. Through the Bargmann transform \cite{Bargmann}, the operator $\mathcal L_\Omega$ becomes a Toeplitz-type integral operator on the Bargmann--Fock space $\mathcal F^2(\C)$ of entire functions \cite{Berezin,Berger-Coburn-Symbol,Berger-Coburn,Berger-Coburn-Heat,Zhu,Grochenig,Folland}, and time--frequency questions translate into weighted complex analysis. Two foundational rigidity theorems shape the modern picture of the Gaussian model:
\begin{itemize}
\item[\textbf{(NT)}] (Nicola--Tilli \cite{Nicola-Tilli}; see also \cite{Nicola-Tilli-2,Bastianoni-Cordero-Nicola,Bastianoni-Teofanov,Ramos-Tilli}) \emph{Geometric extremality.} Among all measurable sets of a given measure, disks maximize the first localization eigenvalue $\lambda_1$, sharpening the Faber--Krahn paradigm to phase space.
\item[\textbf{(AD)}] (Abreu--D\"orfler \cite{Abreu-Doerfler}) \emph{Spectral rigidity.} If a Hermite function is an eigenfunction of $\mathcal L_\Omega$ on a simply connected bounded domain, then $\Omega$ is a disk.
\end{itemize}
The two theorems articulate, from opposite directions, the same heuristic: \emph{the special role of the Gaussian among signals must be matched by the special role of the disk among phase-space sets}. Yet the geometric and the spectral side have so far been developed as parallel, but largely independent, viewpoints. The variational theory leading to (NT) and its quantitative refinement \cite{Gomez-Guerra-Ramos-Tilli} is essentially based on rearrangement and integral-geometric inequalities; the rigidity (AD) is proved by overdetermined boundary conditions and unique-continuation arguments. Neither perspective, on its own, makes the connection between eigenfunctions and domains constructive.

\medskip

\noindent\textbf{Eigenfunctions as geometric data.} The aim of this paper is to construct that connection. The unifying thesis we develop is that, for Gaussian time--frequency localization, an eigenfunction must be regarded as \emph{geometric data}: it determines a localization domain, and prescribing it has strong consequences for the variational theory. This thesis is realized in three coupled steps.

\smallskip
\noindent\emph{(i) An inverse construction.} Near the Gaussian, the eigenvalue equation $\mathcal L_U f_0=\lambda f_0$ admits a perturbative solution \emph{in the unknown domain~$U$} for arbitrarily prescribed near-Gaussian $f_0$. We solve this inverse problem by a free-boundary moment system on $\mathcal F^2(\C)$ and an analytic implicit-function theorem at the Daubechies disk.

\smallskip
\noindent\emph{(ii) Constructive consequences of rigidity.} Combining the inverse construction with eigenfunction rigidity yields, on the one hand, a short conceptual proof of (AD) that does \emph{not} require any boundary regularity, and, on the other hand, the optimal exponent in the quantitative stability inequality of \cite{Gomez-Guerra-Ramos-Tilli}.

\smallskip
\noindent\emph{(iii) A new road to (NT) through local rigidity.} Local maximizers of $\lambda_1$, suitably defined in a weighted symmetric-difference topology, are themselves rigid: each is a disk up to translation. Combined with a Fock-space concentration--compactness profile decomposition, this local rigidity yields a new proof of (NT) that is independent of rearrangement.

\medskip

The technical core of the paper is the rewriting of the eigenvalue equation, after Bargmann transform, as an infinite weighted moment system on the Bargmann--Fock space:
\begin{equation}\label{eq:moment-intro}
\int_U F(z)\,\overline{e_k(z)}\,e^{-\pi|z|^2}\,dA(z)
\;=\;
\lambda\,\langle F,e_k\rangle_{\mathcal F^2},
\qquad k\ge 0,
\end{equation}
where $\{e_k\}$ is the standard monomial basis. This is the \emph{$\lambda$-dependent weighted quadrature identity} of the title. Classical quadrature-domain theory studies analogous identities for harmonic test functions against Lebesgue measure \cite{Gustafsson,Gustafsson-Shahgholian,Shahgholian,Aharonov-Schiffer-Zalcman,Karp,Cherednichenko}; here the Gaussian weight and the spectral parameter $\lambda$ make the system genuinely new and place it at the intersection of phase-space analysis, free-boundary problems, and inverse potential theory \cite{Isakov}. The remainder of the introduction states the four main results; the methods, technical inputs, and connections with the literature are gathered in \S\ref{ssec:intro-methods}--\S\ref{ssec:intro-related}.

\subsection{Main results}\label{ssec:intro-main-results}

The first main result is the inverse construction at the Daubechies disk. It says that any sufficiently small Hermite-polynomial perturbation of the Gaussian arises as an eigenfunction of \emph{some} localization operator at any prescribed eigenvalue.

\begin{theorem}[Inverse construction near the Gaussian]\label{thm:perturb}
Let $\lambda\in (0,1)$ and $N\in\N$. There exists $\varepsilon_0=\varepsilon_0(\lambda,N)>0$ such that for any
\[
f_0 \;=\; h_0+\sum_{k=1}^N a_k h_k
\qquad\text{with}\qquad
\max_k|a_k|<\varepsilon_0,
\]
there exists a domain $U_\lambda\subset\R^2$, a real-analytic perturbation of a disk, with
\[
\mathcal L_{U_\lambda} f_0 \;=\; \lambda f_0 .
\]
\end{theorem}

This appears to be the first general inverse construction of localization domains beyond the highly symmetric examples (radial multiplets, scaled Gaussians) accessible via direct symmetry arguments. The threshold $\varepsilon_0$ depends explicitly on $\lambda$ and on the spectral gap of the disk localization operator restricted to the Hermite subspace of degree $\le N$, with quantitative bounds extracted from the proof. The construction is perturbative in nature, and the local nature of the conclusion is essential: the analogue at fixed scale, away from the Gaussian, remains an open problem.

The same machinery yields a self-contained, methodologically transparent recovery of (AD)\,---\,and, in fact, a strengthening of it.

\begin{theorem}[Spectral rigidity, regularity-free]\label{thm:eig-loc-U}
Let $U\subset\C$ be a simply connected bounded domain. If a Hermite function is an eigenfunction of $\mathcal L_U$, then $U$ is a disk.
\end{theorem}

We give two proofs (\S\ref{sec:classical-rigidity}). The first, in the spirit of overdetermined free-boundary problems, transports the eigenvalue equation into the Bargmann--Fock space, applies a Paley--Wiener argument and an Ehrenpreis--Malgrange-type divisibility lemma, and forces the logarithmic potential of $\mathbf 1_U$ to be radial along $\partial U$. The second proof eliminates \emph{all} hypotheses on the regularity of $\partial U$, replacing them with a holomorphic auxiliary function attached to the associated Poisson problem; it strengthens (AD) to the form stated above (Theorem~\ref{thm:eig-loc-U-strong}), in which $\partial U$ is allowed to be merely a closed measurable set with no perimeter or differentiability hypothesis. The version is sharp at the level of currently available statements, and we view it as a clean instance of the regularity-bypass principle made possible by the inverse machinery.

The third theorem deploys Theorem~\ref{thm:perturb} to settle the question of optimal exponents in the quantitative stability estimate of \cite{Gomez-Guerra-Ramos-Tilli}. For a measurable set $U\subset\R^2$ of finite positive measure, write $\lambda_1(U)$ for the first eigenvalue of $\mathcal L_U$, $f_U$ for an $L^2$-normalized first eigenfunction, $\varphi_{z_0}$ for a Gaussian optimizer centred at $z_0\in\C$, and $\mathcal A(U)$ for the Fraenkel asymmetry of $U$. Corollary~1.4 of \cite{Gomez-Guerra-Ramos-Tilli} provides
\begin{equation}\label{eq:GGRT-bounds-intro}
\min_{z_0\in\C,\ |c|=1}\|f_U-c\,\varphi_{z_0}\|_{L^2(\R)}
\;\le\;
C e^{|U|/2}\!\left(1-\tfrac{\lambda_1(U)}{1-e^{-|U|}}\right)^{\!1/2},
\qquad
\mathcal A(U) \;\le\; K(|U|)\!\left(1-\tfrac{\lambda_1(U)}{1-e^{-|U|}}\right)^{\!1/2}.
\end{equation}

\begin{theorem}[Sharpness of the GGRT stability inequality]\label{thm:GGRT-sharp}
The exponent $1/2$ in both inequalities of \eqref{eq:GGRT-bounds-intro} is optimal: it cannot be replaced by any $\beta>1/2$.
\end{theorem}

The argument is direct. Theorem~\ref{thm:perturb} applied to second-order Hermite perturbations of $h_0$ produces a one-parameter family $U_\varepsilon$ of perturbed disks whose boundary deformation is governed by quadratic harmonics. A first-variation analysis based on the Reynolds transport identity --- and a sharp explicit lower bound on $|U_\varepsilon\triangle B(z_0,r)|$ valid uniformly over $(z_0,r)$ --- shows that these harmonics cannot be removed by translations of the disk, and that the symmetric-difference deficit is exactly of the order predicted by the upper bounds in \eqref{eq:GGRT-bounds-intro}.

The fourth main result concerns local extremizers of the Faber--Krahn problem in the Gaussian STFT setting and is a key input to the new proof of (NT) below.

\begin{theorem}[Local-extremizer rigidity]\label{thm:local-maximizers}
Any local maximizer of $\lambda_{1,\varphi}$ under a measure constraint, in the weighted symmetric-difference topology of $\S\ref{sec:local-max}$, is a disk up to translation.
\end{theorem}

The proof identifies any local maximizer with a superlevel set of the Bargmann--Fock density of its first eigenfunction (via a Lieb--Loss bathtub argument), uses a Hadamard shape-derivative computation to derive the Euler--Lagrange overdetermined system, and exploits simplicity of $\lambda_1$ to force the eigenfunction into Gaussian form, hence the domain into a disk. Since the local maximizer is shown to be open with real-analytic boundary as a \emph{consequence} of the variational equations, no boundary regularity is assumed.

Combining Theorem~\ref{thm:local-maximizers} with a Fock-space concentration--compactness profile decomposition gives a new proof of (NT). Existence of a global maximizer is established by ruling out vanishing and dichotomy via strict subadditivity of the localization functional $M(s):=\sup\{\lambda_1(U):|U|=s\}$; uniqueness up to translation then follows because every global maximizer is in particular a local one.

\begin{theorem}[New proof of Nicola--Tilli]\label{thm:NT-new}
Among all measurable sets $\Omega\subset\R^2$ of fixed finite measure, the global maximizers of $\lambda_{1,\varphi}$ are exactly the translates of a single disk.
\end{theorem}

\medskip

\noindent\textbf{New results vs. new proofs.}\enspace
Theorems \ref{thm:perturb}, \ref{thm:GGRT-sharp}, and \ref{thm:local-maximizers} are new. Theorem~\ref{thm:eig-loc-U} is a new proof, and a regularity-free strengthening, of the Abreu--D\"orfler rigidity theorem; Theorem~\ref{thm:NT-new} is a new proof of the Nicola--Tilli theorem. We make no claim of priority on the statements of the latter two; their interest here is the placement of (NT) and (AD) inside a single inverse/free-boundary framework that simultaneously yields the new results.

\subsection{Methods and central identity}\label{ssec:intro-methods}

The central object of the paper is the moment identity \eqref{eq:moment-intro}. Three groups of techniques act on it.

\smallskip
\noindent\emph{(a) Free-boundary methods on weighted Hardy spaces.}
The boundary of the unknown domain is parametrized as an analytic radial graph over the disk in a Wiener-type Banach algebra of holomorphic functions on a strip. The moment system \eqref{eq:moment-intro} is recast as a nonlinear map between such spaces; its Fr\'echet derivative at the disk is computed explicitly as a Fourier multiplier diagonal in modes, with explicit eigenvalues and an isometric inverse on the orthogonal complement of the translation kernel. An analytic implicit-function theorem then produces the perturbed domain $U_\lambda$. This step is in the spirit of Isakov's perturbative free-boundary framework \cite{Isakov} and of the inverse Newtonian-potential results of Cherednichenko \cite{Cherednichenko}, but the function spaces and the linearization are specifically tailored to the Gaussian weight and the spectral parameter, and the implicit-function step is reproved in the form needed.

\smallskip
\noindent\emph{(b) Complex analysis and divisibility.}
A coefficientwise conjugate differential operator $P^\#$, defined explicitly via Wirtinger derivatives, intertwines the eigenvalue equation with a moment-to-Cauchy-transform identity. A Paley--Wiener--Schwartz argument applied to a compactly supported distribution on $\R^2$ encodes the eigenfunction's structure as the vanishing of an entire function on the complex variety $\xi^2+\eta^2=0$. An Ehrenpreis--Malgrange-type divisibility lemma --- which we state and prove self-containedly in the form needed (Lemma~\ref{lemma:fourier-to-fboundary}) --- then forces the underlying logarithmic potential to be locally radial.

\smallskip
\noindent\emph{(c) Variational and geometric measure theory.}
Shape derivatives are computed via Reynolds transport for $C^1$ deformation fields. The bathtub principle of Lieb--Loss \cite{Lieb} converts the measure-constrained variational problem into a superlevel-set problem. Simplicity of the principal eigenvalue at a local maximizer is established by a positivity argument together with Berezin estimates. Finally, a profile-decomposition theorem in $\mathcal F^2(\C)$ in the spirit of P.-L.~Lions's concentration--compactness, adapted to the lack of translation compactness in the Fock space, drives the existence half of the proof of (NT).

The detailed list of external theorems we use --- with explicit indication of which are quoted, which are adapted, and which are reproved as lemmas --- appears as \S\ref{subsec:main-technical-inputs} of the preliminaries.

\subsection{Relation to the literature}\label{ssec:intro-related}

\noindent\emph{Quadrature domains and inverse potential theory.}
A classical quadrature domain $D\subset\R^2$ is characterized by the fact that integration of harmonic test functions against Lebesgue measure on $D$ reduces to a finite combination of point evaluations and their derivatives; see Gustafsson--Shahgholian \cite{Gustafsson-Shahgholian} for the obstacle-problem characterization, the Gustafsson lectures \cite{Gustafsson}, and Shahgholian \cite{Shahgholian}. Aharonov--Schiffer--Zalcman \cite{Aharonov-Schiffer-Zalcman}, Karp \cite{Karp}, and Cherednichenko \cite{Cherednichenko} address the inverse potential problem in adjacent settings. Our moment system \eqref{eq:moment-intro} is structurally distinct from a classical quadrature identity in two ways: the test space is the Bargmann--Fock space of entire functions rather than harmonic functions; and the eigenvalue $\lambda$ enters as an explicit spectral parameter. We expect the resulting notion of \emph{$\lambda$-dependent weighted quadrature domain} to be of independent interest.

\smallskip
\noindent\emph{Toeplitz inverse-spectral problems on Fock and Bergman spaces.}
Symbol-recovery and inverse-spectral problems for Toeplitz operators have been pursued, in various directions, by Berger--Coburn \cite{Berger-Coburn-Symbol,Berger-Coburn,Berger-Coburn-Heat}, Berezin \cite{Berezin}, and Zhu \cite{Zhu}, and more recently by Bastianoni--Cordero--Nicola--Teofanov \cite{Bastianoni-Cordero-Nicola,Bastianoni-Teofanov}, Fulsche--Hagger \cite{Fulsche-Hagger}, and Kisil \cite{Kisil-CrossToeplitz}; see also \cite{abreu2021donoho} for related polyanalytic and large-sieve phenomena. In all of these the symbol typically belongs to a function class on phase space, and the inverse problem is to read off properties of the symbol from the spectrum. By contrast, the inverse problem we solve here is geometric: the symbol is the indicator $\mathbf 1_U$ of an unknown domain, and the spectral datum is a single eigenfunction.

\smallskip
\noindent\emph{Concentration--compactness in time-frequency analysis.}
The profile decomposition we use in \S\ref{sec:global-max} extends and complements the time-frequency adaptations of P.-L.~Lions's method developed by Nicola--Tilli \cite{Nicola-Tilli,Nicola-Tilli-2} and Nicola--Romero--Trapasso \cite{Nicola-Romero-Trapasso}, with the principal subtlety being the lack of translation compactness in $\mathcal F^2(\C)$. Closely related concentration phenomena and profile decompositions in adjacent time-frequency settings appear in \cite{Marceca-Romero-Speckbacher,Samuelsen,Fulsche-Hagger}.

\smallskip
\noindent\emph{Hermite structures in the Bargmann model.}
The role of Gaussian decay and Hermite-type rigidity is also visible in nearby phase-space problems \cite{Kulikov-Oliveira-Ramos,Goncalves-Oliveira-Steinerberger,Thangavelu}; the inverse-spectral perspective adopted here is, however, of a different character, in that it produces the domain rather than constraining it.

\subsection{Organization}\label{ssec:intro-organization}

Section~\ref{sec:preliminaries} collects the analytic preliminaries on the Bargmann--Fock space, the main technical inputs from the external literature, and the bridge from time--frequency analysis to free-boundary problems via the divisibility lemma. Section~\ref{sec:perturb-proof} is devoted to the proof of Theorem~\ref{thm:perturb}, including the self-contained disk inverse step. Section~\ref{sec:classical-rigidity} contains the two proofs of Theorem~\ref{thm:eig-loc-U}; the second yields the regularity-free strengthening Theorem~\ref{thm:eig-loc-U-strong}. Section~\ref{sec:GGRT-sharp} deploys Theorem~\ref{thm:perturb} to prove Theorem~\ref{thm:GGRT-sharp}. Section~\ref{sec:local-max} is devoted to local maximizers and Theorem~\ref{thm:local-maximizers}. Section~\ref{sec:global-max} establishes the profile decomposition in $\mathcal F^2(\C)$, rules out vanishing and dichotomy via strict subadditivity, and combines existence with Theorem~\ref{thm:local-maximizers} to give the new proof of (NT).

% ==============================================================
% Section 2: Preliminaries
% ==============================================================

\section{Preliminaries}\label{sec:preliminaries}

\subsection{Main technical inputs}\label{subsec:main-technical-inputs}

For the convenience of the reader, and to make the boundaries between
quoted material, adapted material, and original arguments transparent, we
collect here the principal external theorems used in this paper, together
with an indication of the form in which each is used.

\begin{itemize}
\item \emph{Isakov's perturbative free-boundary theorem.} In Section~3 we
use the implicit-function-theorem framework for inverse free-boundary and
inverse-source problems developed in Isakov \cite{Isakov}. The general
theorem is \emph{adapted with proof}: the underlying perturbative
implicit-function strategy is Isakov's, but the function spaces, the
linearized moment map at the disk, and its invertibility on the relevant
subspace are reformulated and reproved here in a form tailored to the
Gaussian Bargmann--Fock setting.

\item \emph{Cherednichenko's inverse Newtonian-potential result.} The
recovery of a domain from its exterior logarithmic potential, used as a
conceptual guide in Sections~3 and~4, is taken from Cherednichenko
\cite{Cherednichenko}; see also \cite{Karp,Aharonov-Schiffer-Zalcman} for
the closely related classical statements. We \emph{quote} these
results in the form needed and do not reprove them.

\item \emph{Bathtub principle.} The Lieb--Loss bathtub principle is used
in Sections~6 and~7 to identify maximizers of $\int_\Omega u_F\,dA$ under
a measure constraint with superlevel sets of $u_F$. We quote it
\emph{verbatim} from \cite{Lieb}; see also Lemma~\ref{lem:basic-properties-global}(i)
above.

\item \emph{Concentration--compactness profile decomposition.} In
Section~7 we use a profile-decomposition statement in $\mathcal F^2(\C)$
in the spirit of P.-L.~Lions's concentration--compactness method and of
its time--frequency adaptations by Nicola and Tilli \cite{Nicola-Tilli,Nicola-Tilli-2}
and by Nicola, Romero, and Trapasso \cite{Nicola-Romero-Trapasso}. The
form we use is \emph{adapted with proof}: the abstract concentration
mechanism is classical, while the precise profile decomposition for
maximizing sequences of $I_F(s)$ in the Fock space, including the
treatment of the lack of translation compactness, is reproved here.

\item \emph{Ehrenpreis--Malgrange divisibility.} The divisibility of
entire functions on $\C^2$ vanishing on a complex hypersurface, which
underlies Lemma~\ref{lemma:fourier-to-fboundary} above, is the classical
Ehrenpreis--Malgrange divisibility theorem. The version we need is
\emph{proved as a self-contained lemma} (Lemma~\ref{lemma:fourier-to-fboundary}),
using only the Paley--Wiener--Schwartz theorem and elementary
two-variable polynomial divisibility, in order to keep track of explicit
support and regularity information.

\item \emph{Paley--Wiener and Paley--Wiener--Schwartz theorems.} The
classical Paley--Wiener theorem (and its Schwartz extension to compactly
supported distributions) is used several times to translate vanishing of
a Fourier transform along complex lines into vanishing of a function on
the support side. We \emph{quote} these results from
\cite{Hormander,Folland} in the standard form.
\end{itemize}

The remainder of Section~2 is devoted to the analytic preliminaries on
the Bargmann--Fock space and the divisibility lemma proper.

\subsection{Properties of the Bargmann-Fock space} We briefly recall the connection between the Gaussian short-time Fourier transform
(STFT) and the Bargmann--Fock space, which will be used systematically in what
follows. Excellent references for the material in this subsection are
\cite{Bargmann,Folland,Grochenig,Zhu}; see also
\cite{Berezin,Berger-Coburn,Daubechies}.

\medskip

Let $\varphi(x) = 2^{1/4} e^{-\pi x^2}$ be the normalized Gaussian. For $f \in L^2(\mathbb{R})$, its Gaussian STFT is
\begin{equation}\label{eq:STFT}
V_\varphi f(x,\omega)
= \int_{\mathbb{R}} f(t)\, \varphi(x-t)\, e^{-2\pi i t \omega}\, dt.
\end{equation}
The Bargmann transform
$\mathcal{B} : L^2(\mathbb{R}) \to \mathcal{F}^2(\mathbb{C})$ is defined by
\begin{equation}\label{eq:Bargmann}
(\mathcal{B}f)(z)
= 2^{1/4} \int_{\mathbb{R}} f(t)\, e^{2\pi t z - \pi t^2 - \frac{\pi}{2} z^2}\, dt,
\qquad z \in \mathbb{C}.
\end{equation}
It is well known that $\mathcal{B}$ is a unitary isomorphism onto the Bargmann--Fock
space $\mathcal{F}^2(\mathbb{C})$, endowed with the norm
\[
\|F\|_{\mathcal{F}^2}^2
= \int_{\mathbb{C}} |F(z)|^2 e^{-\pi |z|^2} \, dA(z).
\]
A direct computation shows that, for $z = x + i\omega$,
\begin{equation}\label{eq:STFT-B}
V_\varphi f(x,-\omega)
= e^{\pi i x \omega}\, (\mathcal{B}f)(z)\, e^{-\frac{\pi}{2}|z|^2}.
\end{equation}
In particular, setting $F = \mathcal{B}f$, one obtains
\begin{equation}\label{eq:energy}
\int_{\mathbb{R}^2} |V_\varphi f(x,\omega)|^2 \, dx\, d\omega
= \int_{\mathbb{C}} |F(z)|^2 e^{-\pi |z|^2} \, dA(z)
= \|F\|_{\mathcal{F}^2}^2.
\end{equation}

\medskip

\noindent
\subsubsection*{Weyl operators and invariance.}
For $a \in \mathbb{C}$, define the operator
\begin{equation}\label{eq:Ta}
(T_a F)(z) := e^{\pi \overline{a} z - \frac{\pi}{2}|a|^2} F(z - a).
\end{equation}
Then $T_a$ is unitary on $\mathcal{F}^2(\mathbb{C})$. Indeed,
\begin{align*}
\|T_aF\|_{\mathcal F^2}^2
&=
\int_{\C} e^{2\pi \Re(\overline{a}z)-\pi |a|^2}\,|F(z-a)|^2 e^{-\pi |z|^2}\,dA(z) \\
&=
\int_{\C} |F(z-a)|^2 e^{-\pi |z-a|^2}\,dA(z)
=
\|F\|_{\mathcal F^2}^2,
\end{align*}
because
\[
2\Re(\overline{a}z)-|a|^2-|z|^2=-|z-a|^2.
\]
Moreover,
\begin{equation}\label{eq:uF-translate}
u_{T_a F}(z) = u_F(z - a).
\end{equation}
Indeed, since
\(2\Re(\overline{a}z)-|a|^2-|z|^2 = -|z-a|^2\),
\begin{equation}\label{eq:u-translation-global}
u_{T_aF}(z)
=
|T_aF(z)|^2e^{-\pi |z|^2}
=
e^{2\pi\Re(\overline{a}z)-\pi|a|^2}|F(z-a)|^2e^{-\pi |z|^2}
=
|F(z-a)|^2e^{-\pi |z-a|^2}=u_F(z-a).
\end{equation}
In particular, the functionals $I_F$ defined by,
for \(s>0\),
\[
I_F(s):=\sup_{|\Omega|=s}\int_\Omega u_F\,dA,
\]
satisfy, by the translation-invariance of the Lebesgue measure on \(\C\),
\begin{equation}\label{eq:I-translation-global}
I_{T_a F}(s) = I_F(s), \qquad a \in \mathbb{C},
\end{equation}
reflecting the invariance of the Gaussian STFT under time--frequency shifts;
see \cite{Daubechies,Grochenig,Kulikov-Oliveira-Ramos,Goncalves-Oliveira-Steinerberger}.

\medskip

\noindent
\subsubsection*{Connection with localization.}
If $F = \mathcal{B}f$, then for every measurable $\Omega \subset \mathbb{C}$,
\[
\int_\Omega u_F \, dA
= \int_{\widetilde{\Omega}} |V_\varphi f(x,\omega)|^2 \, dx\, d\omega,
\]
where $\widetilde{\Omega} = \{(x,\omega) : (x,-\omega) \in \Omega\}$.
Thus, concentration properties of the STFT are naturally encoded by the function
\begin{equation}\label{eq:uF}
u_F(z) := |F(z)|^2 e^{-\pi |z|^2}, \qquad z \in \mathbb{C},
\end{equation}
which is the main object of interest in the Bargmann--Fock setting, in terms of the
quantities $I_F(s)$.

\medskip

We next collect a few elementary facts that will be used repeatedly.

\begin{lemma}\label{lem:Fock-basic}
Let $F,G \in \mathcal{F}^2(\mathbb{C})$. Then:
\begin{enumerate}
\item[(i)] The space $\mathcal{F}^2(\mathbb{C})$ is a reproducing kernel Hilbert space with kernel
\[
K_w(z) = e^{\pi z \overline{w}}, \qquad z,w \in \mathbb{C}.
\]

\item[(ii)] (Sharp pointwise bound) For every $z \in \mathbb{C}$,
\[
u_F(z) \le \|F\|_{\mathcal{F}^2}^2,
\]
and equality holds at some point $w \in \mathbb{C}$ if and only if $F$ is
proportional to the reproducing kernel $K_w$.

\item[(iii)] $u_F(z) \to 0$ as $|z| \to \infty$.

\item[(iv)] One has the estimate
\[
\|u_F - u_G\|_{L^1(\mathbb{C})}
\le \big( \|F\|_{\mathcal{F}^2} + \|G\|_{\mathcal{F}^2} \big)
\|F - G\|_{\mathcal{F}^2}.
\]
\end{enumerate}
\end{lemma}

\begin{proof}
(i) For \(w\in \C\), the function \(K_w(z)=e^{\pi z\overline w}\) is entire and
satisfies, after completing the square via
\(2\Re(z\overline w)-|z|^2=-|z-w|^2+|w|^2\),
\[
\|K_w\|_{\mathcal F^2}^2
=
\int_{\C} e^{2\pi \Re(z\overline w)-\pi |z|^2}\,dA(z)
=
e^{\pi |w|^2}\int_{\C}e^{-\pi |z-w|^2}\,dA(z)
=
e^{\pi |w|^2},
\]
since the Gaussian \(e^{-\pi |\cdot|^2}\) integrates to \(1\) over \(\C\) (with
the Lebesgue measure \(dA\) on \(\C\simeq \mathbb R^2\)). In particular
\(K_w\in \mathcal F^2(\C)\). Now, expanding \(F\in \mathcal F^2(\C)\) along the
orthonormal basis \(\{e_k\}_{k\geq 0}\) of Lemma \ref{lem:monomials} and using
the Taylor expansion
\(K_w(z)=\sum_{k\geq 0}\frac{\pi^k\overline w^k}{k!}z^k=\sum_{k\geq 0}\overline{e_k(w)}\,e_k(z)\),
one obtains the reproducing identity
\[
\langle F,K_w\rangle_{\mathcal F^2}
=
\sum_{k\geq 0} a_k\,e_k(w)
=
F(w),
\qquad F(z)=\sum_{k\geq 0}a_k e_k(z).
\]
Point evaluation is therefore continuous, and \(F\) is entire as a uniform
limit on compact sets of polynomials. This is the standard description of the
Bargmann--Fock space, see \cite{Bargmann,Folland,Grochenig,Zhu}.

(ii) Applying Cauchy--Schwarz to the reproducing identity from (i),
\begin{equation}\label{eq:pointwise}
|F(z)|
=
|\langle F,K_z\rangle_{\mathcal F^2}|
\le
\|F\|_{\mathcal F^2}\,\|K_z\|_{\mathcal F^2}
=
\|F\|_{\mathcal F^2}\,e^{\frac{\pi}{2}|z|^2},
\end{equation}
which immediately gives \(u_F(z)=|F(z)|^2 e^{-\pi |z|^2}\le \|F\|_{\mathcal F^2}^2\).
Equality at a point \(z=w\) corresponds to equality in Cauchy--Schwarz, that is,
\(F=c\,K_w\) for some \(c\in \C\); conversely, for \(F=c K_w\) one computes
\(u_F(w)=|c|^2 e^{2\pi |w|^2}e^{-\pi |w|^2}=|c|^2 e^{\pi |w|^2}=|c|^2\|K_w\|_{\mathcal F^2}^2
=\|F\|_{\mathcal F^2}^2\), proving the rigidity statement. The sharpness of this
pointwise bound goes back to \cite{Lieb}.

(iii) Fix \(\varepsilon>0\), and choose a polynomial \(P\) such that
\[
\|F-P\|_{\mathcal F^2}<\varepsilon
\]
using the density of polynomials in \(\mathcal F^2(\C)\). By the pointwise bound from (ii),
\[
|F(z)-P(z)|e^{-\frac{\pi}{2}|z|^2}\le \varepsilon
\qquad\text{for every }z\in \C.
\]
Since \(P\) is a polynomial,
\[
P(z)e^{-\frac{\pi}{2}|z|^2}\to 0
\qquad\text{as }|z|\to\infty.
\]
Hence
\[
\limsup_{|z|\to\infty}|F(z)|e^{-\frac{\pi}{2}|z|^2}\le \varepsilon.
\]
As \(\varepsilon>0\) is arbitrary, we conclude that
\[
|F(z)|e^{-\frac{\pi}{2}|z|^2}\to 0,
\]
that is, \(u_F(z)\to 0\) as \(|z|\to\infty\).

(iv) Writing
\[
|u_F - u_G|
= \big||F|^2 - |G|^2\big| e^{-\pi|z|^2}
\le |F-G|(|F|+|G|) e^{-\pi|z|^2},
\]
the claim follows by Cauchy--Schwarz.
\end{proof}

\medskip

We now note the following crucial fact about the Bargmann transform: it
transforms the basis of normalized Hermite functions \(\{h_k\}_{k\geq 0}\) on
\(L^2(\R)\) (see \cite{Thangavelu}) onto normalized monomials, yielding a
natural orthonormal basis on $\mathcal{F}^2(\C).$ More precisely, one has
\(\mathcal B h_k=e_k\) for every \(k\ge 0\), see \cite{Bargmann,Folland,Grochenig}.

\begin{lemma}\label{lem:monomials}
The functions
\[
e_k(z) := b_k z^k, \qquad k \ge 0,
\]
form an orthonormal basis of $\mathcal{F}^2(\mathbb{C})$, where
\[
b_k = \left( \frac{\pi^k}{k!} \right)^{1/2}.
\]
In particular,
\[
\langle e_k, e_m \rangle_{\mathcal{F}^2} = \delta_{k,m}.
\]
\end{lemma}

\begin{proof}
Writing \(z=re^{i\theta}\) and using \(dA(z)=r\,dr\,d\theta\) on \(\C\),
a direct computation in polar coordinates gives
\[
\int_{\mathbb{C}} |z|^{2k} e^{-\pi |z|^2}\,dA(z)
= \int_0^{2\pi}\!\!\int_0^\infty r^{2k+1} e^{-\pi r^2}\,dr\,d\theta
= 2\pi \int_0^\infty r^{2k+1} e^{-\pi r^2}\,dr
= \frac{k!}{\pi^k},
\]
where the last identity follows from the substitution \(s=\pi r^2\), giving
\(2\pi\int_0^\infty r^{2k+1}e^{-\pi r^2}\,dr=\pi^{-k}\int_0^\infty s^k e^{-s}\,ds
=\pi^{-k}\Gamma(k+1)\). Thus
\(\|z^k\|_{\mathcal{F}^2}^2 = \frac{k!}{\pi^k}\), which yields the normalization.
For orthogonality, again writing \(z=re^{i\theta}\),
\[
\langle z^k,z^m\rangle_{\mathcal F^2}
=
\int_0^\infty r^{k+m+1}e^{-\pi r^2}\,dr\int_0^{2\pi}e^{i(k-m)\theta}\,d\theta
=
0
\qquad\text{for }k\neq m.
\]
For completeness, since \(\mathcal B\colon L^2(\R)\to \mathcal F^2(\C)\) is a
unitary isomorphism and \(\mathcal Bh_k=e_k\) for every \(k\ge 0\), where
\(\{h_k\}_{k\ge 0}\) is the orthonormal basis of Hermite functions on
\(L^2(\R)\) (see \cite{Thangavelu}), the family \(\{e_k\}_{k\ge 0}\) is the
image of an orthonormal basis under a unitary, hence itself an orthonormal
basis of \(\mathcal F^2(\C)\). Equivalently, polynomials are dense in
\(\mathcal F^2(\C)\); see \cite{Bargmann,Zhu}.
\end{proof}

\medskip

\begin{lemma}\label{lem:growth}
Let $F \in \mathcal{F}^2(\mathbb{C})$. Then:
\begin{enumerate}
\item[(i)] $F$ admits the expansion
\[
F(z) = \sum_{k=0}^\infty a_k e_k(z),
\qquad \sum_{k=0}^\infty |a_k|^2 = \|F\|_{\mathcal{F}^2}^2.
\]

\item[(ii)] (Growth bound) For every $z \in \mathbb{C}$,
\[
|F(z)| \le \|F\|_{\mathcal{F}^2} e^{\frac{\pi}{2}|z|^2}.
\]

\item[(iii)] (Derivative bounds) For every $z \in \mathbb{C}$,
\[
|F'(z)| \le C(1+|z|)\, \|F\|_{\mathcal{F}^2} e^{\frac{\pi}{2}|z|^2}.
\]
\end{enumerate}
\end{lemma}

\begin{proof}
(i) follows from the orthonormal basis in Lemma \ref{lem:monomials}.

(ii) follows from the reproducing kernel estimate:
\[
|F(z)| = |\langle F, K_z \rangle|
\le \|F\|_{\mathcal{F}^2} \|K_z\|_{\mathcal{F}^2}
= \|F\|_{\mathcal{F}^2} e^{\frac{\pi}{2}|z|^2}.
\]

(iii) Starting from the reproducing identity
\(F(z)=\langle F,K_z\rangle_{\mathcal F^2}=\int_{\C}F(w)e^{\pi \overline{w}z}
e^{-\pi |w|^2}\,dA(w)\) and differentiating in \(z\) under the integral sign
(justified by the absolute convergence on compacta of \(z\), via the pointwise
bound from (ii)), we obtain
\[
F'(z)=\pi \int_{\C}F(w)\,\overline{w}\,e^{\pi\overline{w}z}e^{-\pi |w|^2}\,dA(w)
=\pi \langle F, w\,K_z\rangle_{\mathcal F^2},
\]
since \(\overline{wK_z(w)}=\overline{w}\,e^{\pi\overline{w}z}\). Cauchy--Schwarz
then gives
\[
|F'(z)|
\le
\pi \|F\|_{\mathcal F^2}\,\|wK_z\|_{\mathcal F^2}.
\]
Now, by completing the square as in (i),
\[
\|wK_z\|_{\mathcal F^2}^2
=
\int_{\C} |w|^2 e^{2\pi\Re(w\overline z)-\pi |w|^2}\,dA(w)
=
e^{\pi |z|^2}\int_{\C} |w+z|^2 e^{-\pi |w|^2}\,dA(w),
\]
after the change of variables \(w\mapsto w+z\). Expanding
\(|w+z|^2=|w|^2+2\Re(w\overline z)+|z|^2\), and using that
\(\int_\C e^{-\pi |w|^2}\,dA(w)=1\),
\(\int_\C |w|^2 e^{-\pi |w|^2}\,dA(w)=\frac{1}{\pi}\), and
\(\int_\C w\,e^{-\pi |w|^2}\,dA(w)=0\) (by rotational invariance), we conclude
\[
\int_{\C} |w+z|^2 e^{-\pi |w|^2}\,dA(w)
=
\frac{1}{\pi}+|z|^2
\le
C(1+|z|^2),
\]
for some absolute constant \(C>0\). Therefore
\[
|F'(z)| \le C(1+|z|)\,\|F\|_{\mathcal F^2}e^{\frac{\pi}{2}|z|^2}.
\]
\end{proof}

\medskip

\begin{lemma}\label{lem:max}
Let $F \in \mathcal{F}^2(\mathbb{C})$ and set
\[
T := \sup_{z \in \mathbb{C}} u_F(z).
\]
Then $0 \le T \le \|F\|_{\mathcal{F}^2}^2$, and $T = \|F\|_{\mathcal{F}^2}^2$
is attained if and only if $F$ is proportional to the reproducing kernel $K_w$
for some $w \in \mathbb{C}$.
\end{lemma}

\begin{proof}
The bound and the characterization of the equality case are immediate from
Lemma~\ref{lem:Fock-basic}(ii).
    \end{proof}

\medskip

    We proceed with a few elementary facts.

\begin{lemma}\label{lem:basic-properties-global}
Let \(F,G\in \mathcal F^2(\C)\). Then:
\begin{enumerate}
    \item[(i)] \(I_F(s)\) is attained by a superlevel set of \(u_F\), and
    \[
    0\le I_F(s)\le \|F\|_{\mathcal F^2}^2.
    \]
    \item[(ii)] For every \(c\in \C\),
    \[
    I_{cF}(s)=|c|^2 I_F(s).
    \]
    \item[(iii)] One has the Lipschitz bound
    \[
    |I_F(s)-I_G(s)|
    \le
    \|u_F-u_G\|_{L^1(\C)}
    \le
    \big(\|F\|_{\mathcal F^2}+\|G\|_{\mathcal F^2}\big)\,
    \|F-G\|_{\mathcal F^2}.
    \]
\end{enumerate}
\end{lemma}

\begin{proof}
The identity
\[
\int_\C u_F\,dA=\int_\C |F(z)|^2e^{-\pi |z|^2}\,dA(z)=\|F\|_{\mathcal F^2}^2
\]
is immediate from the definition of the Fock norm. By
Lemma~\ref{lem:Fock-basic}(ii)--(iii), \(u_F\) is bounded, continuous, and
satisfies \(u_F(z)\to 0\) as \(|z|\to\infty\); thus
\(u_F\in C_0(\C)\cap L^1(\C)\).

The existence of a maximizing set for \(I_F(s)\), of the form
\(\{u_F>t\}\) (possibly together with part of \(\{u_F=t\}\)) with \(t\geq 0\)
chosen so that the resulting set has measure \(s\), is the classical bathtub
principle, which applies since \(u_F\in C_0(\C)\cap L^1(\C)\). The bound
\[
0\le I_F(s)\le \int_\C u_F\,dA=\|F\|_{\mathcal F^2}^2
\]
is immediate. The scaling identity in (ii) is obvious.

For (iii), for every measurable \(\Omega\subset \C\) with \(|\Omega|=s\),
\[
\left|\int_\Omega u_F\,dA-\int_\Omega u_G\,dA\right|
\le \int_\C |u_F-u_G|\,dA.
\]
Taking suprema over \(|\Omega|=s\) gives
\[
|I_F(s)-I_G(s)|\le \|u_F-u_G\|_{L^1(\C)}.
\]
Finally,
\begin{align*}
\|u_F-u_G\|_{L^1(\C)}
&=
\int_\C \big||F|^2-|G|^2\big|\,e^{-\pi |z|^2}\,dA \\
&\le
\int_\C |F-G|(|F|+|G|)e^{-\pi |z|^2}\,dA \\
&\le
\|F-G\|_{\mathcal F^2}\big(\|F\|_{\mathcal F^2}+\|G\|_{\mathcal F^2}\big)
\end{align*}
by Cauchy--Schwarz.
\end{proof}

\subsection{From time-frequency analysis to free boundary problems}\label{sec:fourier-to-fboundary}

Having translated, in the previous subsection, the time--frequency
localization problem into a question about the vanishing of a Fourier
transform along the two complex lines $\eta=\pm i\xi$, we now bridge the gap
between this Fourier-analytic statement and the free boundary formulation
that will dominate the remainder of the paper. The bridge is provided by a
divisibility lemma of Ehrenpreis--Malgrange flavour: any compactly supported
distribution whose Fourier transform vanishes on the characteristic variety
$\{\eta=\pm i\xi\}$ of the Laplacian must be the Laplacian of a compactly
supported $L^2$ function which, in our setting, is moreover continuous off a
finite set of points.

In order to state the lemma cleanly, we make precise the class of
distributions with which we work. We say that a compactly supported
distribution $\omega$ is a \emph{singular-continuous free measure} if it
defines a (finite, signed) Radon measure on $\R^2$ whose Lebesgue
decomposition with respect to planar Lebesgue measure $\mathrm{d}x\,
\mathrm{d}y$ takes the form
\[
\omega = \omega_{\mathrm{ac}} + \omega_{\mathrm{pp}}
       = f\,\mathrm{d}x\,\mathrm{d}y + \sum_{j=1}^N c_j\,\delta_{p_j},
\]
with \(f\in L^\infty(\R^2)\) compactly supported, \(c_j\in \R\setminus\{0\}\), and
$p_1,\ldots,p_N\in \R^2$ pairwise distinct. In other words, the continuous
singular part $\omega_{\mathrm{cs}}$ in the Lebesgue--Radon--Nikodym
decomposition $\omega=\omega_{\mathrm{ac}}+\omega_{\mathrm{cs}}+
\omega_{\mathrm{pp}}$ is required to vanish identically, and the pure
point part is finite. The terminology \emph{free measure} is suggested by
the role of $\omega$ as the right-hand side of a free boundary problem
arising in the next subsection.

\begin{lemma}\label{lemma:fourier-to-fboundary}
Let $\omega\in \mathcal{S}'(\R^2)$ be a compactly supported singular-continuous
free distribution such that
\[
\widehat{\omega}(w,\pm iw)=0,\qquad \forall w\in\C.
\]
Then there exist a finite set $P\subset \R^2$ and a compactly supported
function $u\in L^2(\R^2)$ such that
\[
\Delta u=\omega
\]
in the sense of distributions, and
\[
u\in C(\R^2\setminus P).
\]
\end{lemma}

\begin{proof}
By the Paley--Wiener--Schwartz theorem (see, e.g.,
\cite{Hormander,Folland}), the Fourier
% TODO(bib): the keys \texttt{Hormander} (Ark. Mat. 1991) and
% \texttt{Folland} (Harmonic Analysis in Phase Space) do not contain
% Paley--Wiener--Schwartz at the cited locations; a textbook entry
% (Hormander Vol.~I or Rudin's Functional Analysis) should be added.
transform $\widehat\omega(\xi,\eta)$ extends to an entire function on $\C^2$
of exponential type, satisfying the bound
\[
|\widehat\omega(\xi,\eta)|\le C(1+|\xi|+|\eta|)^{N}\,e^{R(|\Im\xi|+|\Im\eta|)}
\]
for some $C,R>0$ and some integer $N\ge 0$ depending on the order of
$\omega$, where $R$ is the radius of any disk containing
$\operatorname{supp}\omega$. In particular, $\widehat\omega$ admits an
everywhere convergent power series expansion
\[
\widehat{\omega}(\xi,\eta)=\sum_{k,l\ge 0} a_{k,l}\,\xi^k\eta^l,
\qquad (\xi,\eta)\in\C^2.
\]
Using the vanishing hypothesis on the complex lines $\eta=\pm i\xi$, we may
group terms by total homogeneity: setting $\eta=\pm iw$, $\xi=w$, and
collecting powers of $w$,
\[
0=\widehat{\omega}(w,\pm iw)
   =\sum_{n\ge 0}\Bigl(\sum_{k=0}^n a_{k,n-k}(\pm i)^{\,n-k}\Bigr)w^n,
\qquad \forall w\in\C.
\]
Since this holds for all $w\in\C$, comparing coefficients yields
\[
\sum_{k=0}^n a_{k,n-k}(\pm i)^{\,n-k}=0,\qquad \forall n\ge 0.
\]
For each $n\ge 0$, define the auxiliary one-variable polynomial
\[
p_n(t):=\sum_{k=0}^n a_{k,n-k}\, t^{\,n-k}.
\]
The two scalar equations above precisely say that $p_n(\pm i)=0$, so
$(t-i)(t+i)=t^2+1$ divides $p_n(t)$. Hence we may write
\[
p_n(t)=(t^2+1)\,q_n(t),
\]
with $q_n$ a polynomial of degree at most $n-2$ (and $q_n\equiv 0$ when
$n<2$).

We now reassemble the homogeneous pieces. Let
\[
H_n(\xi,\eta):=\sum_{k=0}^n a_{k,n-k}\,\xi^k\eta^{\,n-k},
\qquad n\ge 0,
\]
so that $\widehat\omega=\sum_{n\ge 0}H_n$ is the decomposition of
$\widehat\omega$ into homogeneous components (of degree $n$). The argument
above shows that each $H_n$ vanishes on the two complex lines
$\eta=\pm i\xi$, hence is divisible, as a homogeneous polynomial in two
variables, by $\xi^2+\eta^2$. Concretely,
\[
H_n(\xi,\eta)=(\xi^2+\eta^2)\,G_{n-2}(\xi,\eta)
\]
for a (uniquely determined) homogeneous polynomial $G_{n-2}$ of degree
$n-2$, with $G_{n-2}\equiv 0$ for $n<2$. Summing the homogeneous pieces, the
formal series
\[
F(\xi,\eta):=\sum_{n\ge 2} G_{n-2}(\xi,\eta)
\]
converges absolutely on every polydisc on which $\widehat\omega$ does, and
defines an entire function on $\C^2$ satisfying
\[
\widehat{\omega}(\xi,\eta)=(\xi^2+\eta^2)\,F(\xi,\eta).
\]
Since $\widehat\omega$ has a zero of order at least two at the origin
(coming from the vanishing of $H_0$ and $H_1$, which is forced by
$p_0(\pm i)=p_1(\pm i)=0$), this factorization is consistent at $0$ and $F$
is entire there as well.

We next quantify the size of $F$ on $\R^2$. Since $\omega$ is a finite
(signed) Radon measure with compact support, its Fourier transform is in
fact bounded on $\R^2$:
\[
|\widehat{\omega}(\xi,\eta)|\le \|\omega\|_{\mathrm{TV}},
\qquad (\xi,\eta)\in\R^2,
\]
where $\|\omega\|_{\mathrm{TV}}$ is the total variation; equivalently,
the Paley--Wiener bound holds with $N=0$. On $\R^2$, $\xi^2+\eta^2=
|\xi|^2+|\eta|^2$, so for $|\xi|^2+|\eta|^2\ge 1$ we have $\xi^2+\eta^2
\ge \tfrac{1}{2}(1+|\xi|^2+|\eta|^2)$, whence
\[
|F(\xi,\eta)|=\frac{|\widehat\omega(\xi,\eta)|}{\xi^2+\eta^2}
\le \frac{2\|\omega\|_{\mathrm{TV}}}{1+|\xi|^2+|\eta|^2},
\qquad |\xi|^2+|\eta|^2\ge 1.
\]
Near the origin, $F$ is entire (as established above) and hence bounded;
absorbing this region into the constants we obtain
\[
|F(\xi,\eta)|\le \frac{C''}{1+|\xi|^2+|\eta|^2},
\qquad (\xi,\eta)\in\R^2,
\]
for some $C''>0$. Therefore $F|_{\R^2}\in L^2(\R^2)\cap L^1(\R^2)$. On
$\C^2$, $F$ is entire (by the formal-series construction above) and
satisfies an exponential-type bound of the same rate $R$ as
$\widehat\omega$. Indeed, on the open set
$\Omega:=\{(\xi,\eta)\in\C^2:|\xi^2+\eta^2|\ge 1\}$ one has the pointwise
estimate
\[
|F(\xi,\eta)|=\frac{|\widehat\omega(\xi,\eta)|}{|\xi^2+\eta^2|}
\le C(1+|\xi|+|\eta|)^{N}\,e^{R(|\Im\xi|+|\Im\eta|)},
\qquad (\xi,\eta)\in\Omega,
\]
by the Paley--Wiener bound on $\widehat\omega$. On the complement
$\Omega^c=\{|\xi^2+\eta^2|<1\}$, the function $F$ is entire and the
maximum modulus principle, applied on each complex line through a given
point in $\Omega^c$ in a direction transverse to the variety
$\{\xi^2+\eta^2=0\}$, bounds $|F|$ at points of $\Omega^c$ by a uniform
constant times the supremum of $|F|$ on the boundary of a fixed thin
tubular neighbourhood of that variety, where the previous estimate
applies. Combining these two regimes and absorbing the resulting
bookkeeping constant yields, after enlarging $C'$ if necessary,
\[
|F(\xi,\eta)|\le C'\,(1+|\xi|+|\eta|)^{N}\,
e^{R(|\Im \xi|+|\Im \eta|)},
\qquad (\xi,\eta)\in\C^2,
\]
which is the Paley--Wiener--Schwartz bound for a compactly supported
distribution of order $\le N$ in $\overline{B(0,R)}$.

By the Paley--Wiener--Schwartz theorem applied in the reverse direction
(see again \cite{Hormander}), the entire function $F$
satisfies an exponential-type bound on $\C^2$ with the same exponential
rate $R$ as $\widehat\omega$, and integrable decay along $\R^2$, so it is
the Fourier--Laplace transform of a distribution of order $\le N$
compactly supported in the closed disk $\overline{B(0,R)}$. The $L^2$
bound on the real locus shows that this distribution is, in fact, an
$L^2(\R^2)$ function. Let $u\in L^2(\R^2)$ denote this compactly supported
representative, characterised by $\widehat u = F$ on $\R^2$ and
$\operatorname{supp} u\subset \overline{B(0,R)}$.

Computing distributional Laplacians on the Fourier side, with the
convention $\widehat g(\xi,\eta)=\int g(x,y)e^{-2\pi i(x\xi+y\eta)}\,
\mathrm{d}x\,\mathrm{d}y$, we have
\[
\widehat{\Delta u}(\xi,\eta) = -4\pi^2(\xi^2+\eta^2)\,\widehat{u}(\xi,\eta)
= -4\pi^2(\xi^2+\eta^2)\,F(\xi,\eta) = -4\pi^2\,\widehat\omega(\xi,\eta);
\]
with any other standard normalisation, the same identity holds up to a
nonzero real multiplicative factor. In all cases, $\Delta u$ is a constant
nonzero real multiple of $\omega$. Replacing $u$ by $\lambda u$ for the
appropriate (nonzero, real) $\lambda$ -- this is the harmless rescaling
referred to above -- we may, and do, assume that
\[
\Delta u = \omega
\]
in the sense of distributions. The rescaling preserves all the previously
established properties of $u$: compact support, membership in $L^2(\R^2)$,
and the Fourier identity $\widehat u = \lambda F$.

To pin down $u$ pointwise, observe that since $\omega$ is a compactly
supported Radon measure on $\R^2$, the convolution
\[
v(x,y) := \frac{1}{2\pi}(\log|\cdot|*\omega)(x,y)
\]
is a well-defined locally integrable function on $\R^2$ which solves
$\Delta v = \omega$ in the sense of distributions; here $G(z)=\log|z|$ is
(up to the standard normalisation $\tfrac{1}{2\pi}$) the fundamental solution
of the Laplacian in $\R^2$, in the sense that
$\Delta\bigl(\tfrac{1}{2\pi}\log|\cdot|\bigr)=\delta_0$, see, e.g.,
\cite{Hormander} for the underlying distribution theory and
\cite{Aharonov-Schiffer-Zalcman} for related representations in the planar
quadrature-domain context.
% TODO(bib): \texttt{Garnett} (Bounded Analytic Functions, GTM 236) does
% not contain the previously-cited Ch.~II Thm~1.3 on continuity of
% logarithmic potentials of bounded densities; consider adding Ransford
% (Potential Theory in the Complex Plane) or Landkof (Foundations of
% Modern Potential Theory) to the bibliography.
The difference $u-v$ is then a tempered
distribution which is harmonic on $\R^2$ (since
$\Delta(u-v)=\omega-\omega=0$), and hence, being harmonic, real-analytic.
Outside the union of the supports of $u$ and $\omega$, the function $v$ is
in fact real-analytic and grows at most logarithmically at infinity, with
$v(x)=\frac{M}{2\pi}\log|x|+O(|x|^{-1})$ as $|x|\to\infty$ where
$M=\omega(\R^2)$, while $u$ vanishes there because of its compact support.
Hence $u-v$ is harmonic on $\R^2$ and grows at most logarithmically at
infinity; a standard refinement of the harmonic Liouville theorem (any
harmonic function on $\R^2$ growing slower than a polynomial of degree $1$
is constant) then forces $u-v$ to be a constant, and this constant must
vanish to be consistent with $u\in L^2(\R^2)$ and the local integrability
of $v$. Equivalently, and more transparently: by the compact support of
$\omega$ together with $\widehat u = F$ on $\R^2$, the function $u$ is
uniquely determined among compactly supported $L^2$ solutions of
$\Delta u = \omega$, since any two such would differ by an entire $L^2$
function which is harmonic, hence vanishes. Thus
\[
u(x,y)=\frac{1}{2\pi}\int_{\R^2}\log|(x,y)-(x',y')|\,\mathrm{d}\omega(x',y'),
\]
the logarithmic potential of $\omega$.

We finally analyse the regularity of $u$. Decomposing
$\omega = f\,\mathrm{d}x\,\mathrm{d}y+\sum_{j=1}^N c_j\,\delta_{p_j}$ as in
the definition of singular-continuous free measure, we obtain
correspondingly
\[
u(x,y)=\frac{1}{2\pi}\int_{\R^2}\log|(x,y)-(x',y')|\,f(x',y')\,
\mathrm{d}x'\mathrm{d}y'
+\frac{1}{2\pi}\sum_{j=1}^N c_j\,\log|(x,y)-p_j|.
\]
The first summand is the logarithmic potential of the bounded, compactly
supported density \(f\in L^\infty(\R^2)\) and is therefore not merely
continuous but in fact $C^{1,\alpha}(\R^2)$ for every $\alpha\in(0,1)$
(by the standard Calder\'on--Zygmund / Schauder estimates applied to
$\Delta=\partial_x^2+\partial_y^2$ with right-hand side in $L^\infty$
of compact support, see, e.g., the Newtonian-potential discussion in
\cite{Hormander}).
The continuity used here is in fact elementary: by dominated convergence,
$z\mapsto \int \log|z-w|\,f(w)\,\mathrm{d}A(w)$ is continuous since
$\log|\cdot-w|$ is locally integrable in $w$ uniformly on compacta in $z$,
and $f$ is bounded with compact support. It is here that the absence of a continuous
singular part in $\omega$ is essential: a generic continuous singular
measure (e.g.\ the Hausdorff measure on a Cantor-type set of positive
$1$-capacity) gives rise to a logarithmic potential which need not be
continuous, only quasi-continuous, and the conclusion of the lemma would
fail in that generality. Each term $\log|(x,y)-p_j|$ is continuous on
$\R^2\setminus\{p_j\}$, with a logarithmic singularity at $p_j$. Setting
$P:=\{p_1,\ldots,p_N\}$, we conclude that $u\in C(\R^2\setminus P)$, as
claimed. The fact that $u$ is compactly supported has already been
established in the construction above and is consistent with the
representation as a logarithmic potential, which differs from a compactly
supported function only by a globally harmonic correction that, as
explained, must vanish identically.
\end{proof}

We postpone the proof of Theorem~\ref{thm:eig-loc-U} until after the
perturbative inverse theorem. The same inverse/free-boundary mechanism used
to construct domains for prescribed eigenfunctions also recovers the
classical Abreu--D\"orfler disk theorem in the simply connected setting; see
Section~\ref{sec:classical-rigidity} below.


% ==============================================================
% Section 3
% ==============================================================

\section{Proof of Theorem \ref{thm:perturb}}\label{sec:perturb-proof}

\subsection{The disk inverse step}\label{subsec:disk-inverse-step}

The proof rests on a local inverse theorem at the Daubechies disk. The result
below is self-contained, but its point of view is inspired by perturbative
inverse-source and quadrature-domain methods: Isakov's local free-boundary
scheme for inverse source problems, Cherednichenko's local inverse logarithmic
potential theorem, and the quadrature-domain framework developed by
Gustafsson, Shahgholian, Karp, and Aharonov--Schiffer--Zalcman. In the present
disk-based setting the required inverse step can be proved directly by
diagonalizing the full moment map in Fourier modes.

Fix \(0<\lambda<1\), and let \(r_\lambda>0\) be determined by
\[
1-e^{-\pi r_\lambda^2}=\lambda .
\]
For a real-valued \(2\pi\)-periodic function \(\varphi\) with
\(\|\varphi\|_{C^0}<r_\lambda/2\), set
\[
U_\varphi
:=
\{re^{i\theta}:0\le r<r_\lambda+\varphi(\theta)\}.
\]
For \(\tau>0\), let \(\mathcal A_\tau^\R\) be the Banach space of real-valued
periodic functions
\begin{equation}\label{eq:Atau-def}
\varphi(\theta)=\sum_{k\in\Z}\varphi_k e^{ik\theta},
\qquad
\varphi_{-k}=\overline{\varphi_k},
\end{equation}
with norm
\begin{equation}\label{eq:Atau-norm}
\|\varphi\|_{\mathcal A_\tau}
:=
\sum_{k\in\Z}|\varphi_k|e^{\tau |k|}<\infty .
\end{equation}
This is the real subspace of the Wiener-type Banach algebra of functions on
\(\T:=\R/2\pi\Z\) admitting a holomorphic extension to the strip
\(|\Im\theta|<\tau\) with absolutely summable Fourier expansion. It is a Banach
algebra, continuously embedded into \(C^m(\T)\) for every \(m\ge0\), and in
particular into the H\"older space \(C^{1,\alpha}(\T)\) for every
\(\alpha\in(0,1)\). Small elements of \(\mathcal A_\tau^\R\) therefore produce
real-analytic \(C^2\) Jordan domains, given as radial graphs over the disk
\(D_{r_\lambda}\).

For sequences indexed by \(j\ge0\), the natural target Banach space dual to
\(\mathcal A_\tau^\R\) under the moment map of the proposition below is
\begin{equation}\label{eq:Ytau-def}
\mathcal Y_\tau:=
\Big\{y=(y_j)_{j\ge0}\colon y_0\in\R,\ \|y\|_{\mathcal Y_\tau}
:=\tfrac{|y_0|}{a_0}+2\sum_{j=1}^\infty e^{\tau j}\tfrac{|y_j|}{a_j}<\infty\Big\},
\end{equation}
with the weight sequence \(\{a_j\}_{j\ge0}\) given by \eqref{eq:aj-weight}
below. The factor of two in \eqref{eq:Ytau-def} accounts for the conjugate
pairing \(\varphi_{-j}=\overline{\varphi_j}\) used in \eqref{eq:Atau-def}.

\begin{proposition}[Disk symmetrized inverse theorem]\label{prop:disk-inverse-tailored}
Let \(N\ge1\), \(0<\lambda<1\), and \(r_\lambda\) be as above. There are
\(\tau>0\), \(\varepsilon>0\), and a \(C^1\) map
\[
b=(b_1,\ldots,b_N)\longmapsto \varphi_b\in\mathcal A_\tau^\R,
\qquad
\varphi_0=0,
\]
defined for \(\max_j|b_j|<\varepsilon\), such that, for
\[
P_b(z):=1+\sum_{j=1}^N b_jz^j,
\qquad
P_b^\#(z):=\overline{P_b(\overline z)},
\qquad
Q_b(w):=P_b^\#(\partial_w/\pi)P_b(w),
\]
and
\[
U_b:=U_{\varphi_b},
\]
one has
\begin{equation}\label{eq:disk-inverse-identity}
\int_{U_b}|P_b(z)|^2e^{-\pi |z|^2}e^{\pi\overline z w}\,dA(z)
=
\lambda Q_b(w),
\qquad w\in\C .
\end{equation}
Moreover,
\[
\|\varphi_b\|_{C^2(\mathbb S^1)}
\le C_{\lambda,N}\max_{1\le j\le N}|b_j|,
\]
and the branch is locally unique among sufficiently small analytic radial
graphs in \(\mathcal A_\tau^\R\).
\end{proposition}

\begin{proof}
We solve the coefficient equations obtained by expanding the entire identity
\eqref{eq:disk-inverse-identity}. Write
\[
Q_b(w)=\sum_{j=0}^N q_j(b)w^j,
\]
and \(q_j(b)=0\) for \(j>N\). The constant coefficient is real:
\[
q_0(b)=1+\sum_{k=1}^N \frac{k!}{\pi^k}|b_k|^2.
\]
Since
\[
e^{\pi\overline z w}
=
\sum_{j=0}^\infty \frac{\pi^j}{j!}\overline z^{\,j}w^j,
\]
the desired identity is equivalent to the infinite system
\begin{equation}\label{eq:disk-moment-system}
\frac{\pi^j}{j!}\int_{U_\varphi}
|P_b(z)|^2\overline z^{\,j}e^{-\pi |z|^2}\,dA(z)
=
\lambda q_j(b),
\qquad j\ge0 .
\end{equation}

We introduce the weighted sequence space adapted to the linearization at the
circle. Put
\begin{equation}\label{eq:aj-weight}
a_j:=2\pi e^{-\pi r_\lambda^2}r_\lambda^{j+1}\frac{\pi^j}{j!},
\qquad j\ge0,
\end{equation}
so that \(\{a_j\}\) decays super-exponentially in \(j\), and \(\mathcal Y_\tau\)
is the Banach space defined in \eqref{eq:Ytau-def}.
Define
\[
\mathcal F_j(b,\varphi)
:=
\frac{\pi^j}{j!}\int_{U_\varphi}
|P_b(z)|^2\overline z^{\,j}e^{-\pi |z|^2}\,dA(z)
-\lambda q_j(b),
\qquad j\ge0 .
\]
Thus \(\mathcal F(b,\varphi)=0\) is precisely
\eqref{eq:disk-moment-system}. At \(b=0\), \(\varphi=0\), the domain is the
disk \(D_{r_\lambda}\), and radial symmetry gives
\[
\frac{\pi^j}{j!}\int_{D_{r_\lambda}}
\overline z^{\,j}e^{-\pi |z|^2}\,dA(z)
=
\begin{cases}
\lambda, & j=0,\\
0, & j\ge1.
\end{cases}
\]
Hence \(\mathcal F(0,0)=0\).

We next compute the Fr\'echet derivative of the moment map with respect to
the boundary graph. Let
\(\psi(\theta)=\sum_{k\in\Z}\psi_k e^{ik\theta}\in\mathcal A_\tau^\R\), and
recall the polar-coordinate formula
\[
\int_{U_\varphi}H(z)\,dA(z)
=
\int_0^{2\pi}\!\!\int_0^{r_\lambda+\varphi(\theta)}
H(re^{i\theta})\,r\,dr\,d\theta,
\]
valid for any continuous \(H\colon\C\to\C\). Differentiating the right-hand
side at \(\varphi=0\) in the direction of \(\psi\) by the fundamental
theorem of calculus gives
\begin{equation}\label{eq:disk-frechet-domain}
D_\varphi\!\Big(\int_{U_\varphi}H(z)\,dA(z)\Big)\bigg|_{\varphi=0}\![\psi]
=
r_\lambda\!\int_0^{2\pi}\!\psi(\theta)\,H(r_\lambda e^{i\theta})\,d\theta .
\end{equation}
Applied to \(H(z)=\frac{\pi^j}{j!}\overline z^{\,j}e^{-\pi|z|^2}\) and combined
with the orthogonality relation
\(\int_0^{2\pi}e^{i(k-j)\theta}\,d\theta=2\pi\delta_{kj}\), formula
\eqref{eq:disk-frechet-domain} yields the closed-form Fourier-multiplier
expression
\begin{equation}\label{eq:disk-frechet-multiplier}
D_\varphi\mathcal F_j(0,0)[\psi]
=
\frac{\pi^j}{j!}\,r_\lambda^{j+1}e^{-\pi r_\lambda^2}
\int_0^{2\pi}\!\psi(\theta)\,e^{-ij\theta}\,d\theta
=
a_j\,\psi_j,
\qquad j\ge0,
\end{equation}
where \(a_j\) is the weight in \eqref{eq:aj-weight}. Consequently the
Fr\'echet derivative \(D_\varphi\mathcal F(0,0)\) is the Fourier multiplier
\begin{equation}\label{eq:disk-frechet-iso}
D_\varphi\mathcal F(0,0)\colon
\mathcal A_\tau^\R\longrightarrow\mathcal Y_\tau,
\qquad
\psi=\sum_{k\in\Z}\psi_k e^{ik\theta}\longmapsto(a_j\psi_j)_{j\ge0},
\end{equation}
acting diagonally on the non-negative Fourier modes of \(\psi\).

The reality constraint \(\psi_{-j}=\overline{\psi_j}\) shows that the kernel
of the unrestricted multiplier on the complexified space consists exactly of
the negative-frequency modes; on \(\mathcal A_\tau^\R\) the reality
constraint determines those negative modes from the non-negative ones, so
\(D_\varphi\mathcal F(0,0)\) has trivial kernel as a real-linear map. We
verify directly that \eqref{eq:disk-frechet-iso} is bounded and invertible.

\emph{Boundedness.} Using \eqref{eq:Atau-norm} and \eqref{eq:Ytau-def},
\[
\|D_\varphi\mathcal F(0,0)\psi\|_{\mathcal Y_\tau}
=
\frac{|a_0\psi_0|}{a_0}+2\sum_{j=1}^\infty e^{\tau j}\frac{|a_j\psi_j|}{a_j}
=
|\psi_0|+2\sum_{j=1}^\infty e^{\tau j}|\psi_j|
=
\|\psi\|_{\mathcal A_\tau}.
\]

\emph{Invertibility.} For \(y\in\mathcal Y_\tau\) define
\begin{equation}\label{eq:disk-frechet-inverse}
\psi_0:=\frac{y_0}{a_0}\in\R,
\qquad
\psi_j:=\frac{y_j}{a_j}\ (j\ge1),
\qquad
\psi_{-j}:=\overline{\psi_j}\ (j\ge1),
\end{equation}
and \(\psi(\theta):=\sum_{k\in\Z}\psi_k e^{ik\theta}\). The above
computation gives \(\|\psi\|_{\mathcal A_\tau}=\|y\|_{\mathcal Y_\tau}\), so
\(\psi\in\mathcal A_\tau^\R\), and by construction
\(D_\varphi\mathcal F(0,0)\psi=y\). Hence \eqref{eq:disk-frechet-iso} is an
isometric isomorphism of \(\mathcal A_\tau^\R\) onto \(\mathcal Y_\tau\); in
particular
\(\|D_\varphi\mathcal F(0,0)^{-1}\|_{\mathcal Y_\tau\to\mathcal A_\tau^\R}=1\),
which provides the explicit quantitative invertibility needed for the
Banach-space implicit function theorem.

It remains to justify the use of the Banach-space implicit function theorem.
For \(\|\varphi\|_{\mathcal A_\tau}\) small, the function
\(\theta\mapsto r_\lambda+\varphi(\theta)\) extends holomorphically to the
strip \(|\Im\theta|<\tau\) and stays in a fixed annulus
\(r_\lambda/2<|r|<3r_\lambda/2\). In polar coordinates,
\[
\mathcal F_j(b,\varphi)+\lambda q_j(b)
=
\frac{\pi^j}{j!}\int_0^{2\pi}e^{-ij\theta}
\int_0^{r_\lambda+\varphi(\theta)}
P_b(re^{i\theta})P_b^\#(re^{-i\theta})r^{j+1}e^{-\pi r^2}\,dr\,d\theta .
\]
Expanding the inner integral at \(r_\lambda\) gives an absolutely convergent
power series in \(\varphi\), whose coefficients are analytic functions of
\(\theta\) and polynomial functions of \(b\). Since \(\mathcal A_\tau\) is a
Banach algebra and \(P_b(re^{i\theta})P_b^\#(re^{-i\theta})\) is a finite
trigonometric polynomial of degree at most \(N\), the resulting series and
its first derivatives in \((b,\varphi)\) converge in \(\mathcal Y_\tau\) after
possibly decreasing \(\tau\) and restricting to
\(\|b\|+\|\varphi\|_{\mathcal A_\tau}<\eta\). More explicitly, Cauchy's
estimate on a slightly wider strip gives, for \(0<\tau'<\tau\),
\[
\sum_{j\ge0}e^{\tau' j}\frac1{a_j}
\left|
\frac{\pi^j}{j!}\widehat{R_j}(j)
\right|
\le
C_{\lambda,N,\tau,\tau'}\|R\|_{\mathcal A_\tau},
\]
where \(\widehat{R_j}(j)\) denotes the \(j\)-th Fourier coefficient of the
analytic coefficient appearing in the \(j\)-th moment equation. Applying this
estimate term by term to the Taylor expansion in \(\varphi\) yields
\[
\|\mathcal F(b,\varphi)-\mathcal F(b,\psi)
-D_\varphi\mathcal F(b,\psi)[\varphi-\psi]\|_{\mathcal Y_{\tau'}}
\le
C(\|b\|+\|\varphi\|_{\mathcal A_\tau}
+\|\psi\|_{\mathcal A_\tau})
\|\varphi-\psi\|_{\mathcal A_\tau}^2,
\]
and analogous estimates for differentiation in \(b\). Shrinking the strip
once and then relabelling \(\tau'\) as \(\tau\), this proves that
\[
\mathcal F:
\{(b,\varphi):\|b\|+\|\varphi\|_{\mathcal A_\tau}<\eta\}
\longrightarrow \mathcal Y_\tau
\]
is \(C^1\).

The Banach implicit function theorem now applies at \((0,0)\), because
\(D_\varphi\mathcal F(0,0)\) is an isomorphism. Thus, for \(\|b\|\) small,
there is a unique \(\varphi_b\in\mathcal A_\tau^\R\), small in
\(\mathcal A_\tau\), such that \(\mathcal F(b,\varphi_b)=0\), and
\(b\mapsto\varphi_b\) is \(C^1\). The embedding
\(\mathcal A_\tau\hookrightarrow C^2\) gives the displayed \(C^2\) bound.

It remains to upgrade the coefficient identities \eqref{eq:disk-moment-system}
to the global identity \eqref{eq:disk-inverse-identity}. Define the entire
functions
\begin{equation}\label{eq:LHS-RHS-entire}
\mathcal L(w):=\int_{U_b}|P_b(z)|^2 e^{-\pi|z|^2}e^{\pi\overline z w}\,dA(z),
\qquad
\mathcal R(w):=\lambda Q_b(w),
\qquad w\in\C.
\end{equation}
The function \(\mathcal R\) is a polynomial of degree \(\le N\), and
\(\mathcal L\) is entire of exponential type \(\pi M\), with
\(M=\sup_{z\in U_b}|z|\), since
\(|e^{\pi\overline z w}|\le e^{\pi M|w|}\) on \(U_b\). Both \(\mathcal L\) and
\(\mathcal R\) admit absolutely convergent Taylor expansions at the origin,
\[
\mathcal L(w)=\sum_{j\ge0}\frac{\pi^j}{j!}
\Big(\!\int_{U_b}\!|P_b(z)|^2\overline z^{\,j}e^{-\pi|z|^2}dA(z)\!\Big)w^j,
\qquad
\mathcal R(w)=\sum_{j=0}^N\lambda q_j(b)\,w^j,
\]
the first by interchange of summation and integration (justified by
\(\sum_j\frac{(\pi M|w|)^j}{j!}<\infty\) and the boundedness of \(U_b\)).
The system \eqref{eq:disk-moment-system}, namely
\(\mathcal F_j(b,\varphi_b)=0\) for every \(j\ge0\), is exactly the
identification of the Taylor coefficients of \(\mathcal L\) and
\(\mathcal R\) at the origin, including the moments of degree \(j>N\) for
which \(q_j(b)=0\) and the integral on the left-hand side accordingly
vanishes. Hence \(\mathcal L=\mathcal R\) as formal power series, and by the
identity theorem for entire functions \(\mathcal L\equiv\mathcal R\) on
\(\C\), which is \eqref{eq:disk-inverse-identity}.

Equivalently, the same identity may be read off from the exterior
Cauchy-transform picture: restricting \eqref{eq:disk-inverse-identity} to
real \(w=t>0\), multiplying by \(e^{-\pi\zeta t}\) and integrating in
\(t\in(0,\infty)\) for real \(\zeta>M\) gives, by Fubini's theorem (applicable
since \(\Re(\overline z-\zeta)\le|z|-\zeta<0\) on \(U_b\)),
\begin{equation}\label{eq:cauchy-from-moments}
\frac1\pi\int_{U_b}\frac{|P_b(z)|^2 e^{-\pi|z|^2}}{\zeta-\overline z}\,dA(z)
=
\lambda\sum_{j=0}^N q_j(b)\,\frac{j!}{\pi^{j+1}\zeta^{j+1}},
\qquad \zeta\in(M,\infty).
\end{equation}
Both sides of \eqref{eq:cauchy-from-moments} are holomorphic in \(\zeta\) on
the connected open set \(\C\setminus\overline{U_b^*}\) (where
\(U_b^*=\{\overline z:z\in U_b\}\)), and they agree on the real ray
\((M,\infty)\), which has an accumulation point in this set. By the
identity theorem for holomorphic functions on a connected domain,
\eqref{eq:cauchy-from-moments} extends to all
\(\zeta\in\C\setminus\overline{U_b^*}\). Expanding the geometric series
\(1/(\zeta-\overline z)=\sum_{j\ge0}\overline z^{\,j}/\zeta^{\,j+1}\) at
\(\zeta=\infty\) and matching the resulting Laurent coefficients gives the
moment identities \(\frac{\pi^j}{j!}\int_{U_b}|P_b|^2\overline z^{\,j}e^{-\pi|z|^2}dA=\lambda q_j(b)\)
of \eqref{eq:disk-moment-system}, including the vanishing of the higher
moments \(\int_{U_b}|P_b|^2\overline z^{\,j}e^{-\pi|z|^2}dA=0\) for every
\(j>N\) (equivalently \(q_j(b)=0\) for \(j>N\)). The two formulations are
therefore equivalent, and either yields \eqref{eq:disk-inverse-identity}.
This proves the proposition.
\end{proof}

\begin{remark}
The proof above is the only place where analyticity of the boundary
parametrization is used. The constructed domains are therefore \(C^\infty\),
hence \(C^2\), which is the regularity needed later. The argument does not
assert a general local quadrature-domain theorem near an arbitrary reference
domain; it proves exactly the disk-based inverse statement used below.
\end{remark}

We isolate the ODE-theoretic ingredient needed for the unsymmetrization step
of the proof of Theorem~\ref{thm:perturb}, namely the claim that the only
entire function annihilated by \(P^\#(\partial_w/\pi)\) and growing no faster
than the Cauchy-transform of a bounded weighted measure on \(U\) is the zero
function, provided the zeros of the symbol \(P^\#\) escape to infinity.

\begin{lemma}[Step 3: rigidity of exponential-polynomial solutions]\label{lem:step3-rigidity}
Let $N\ge1$ and let $P(z)=1+\sum_{k=1}^N b_k z^k$ be a polynomial with
$\max_k|b_k|\le 1$. Let \(P^\#(z)=\overline{P(\overline z)}\) be its
coefficientwise conjugate, and consider the constant-coefficient differential
operator \(P^\#(\partial_w/\pi)\) defined as in \eqref{eq:Phash-operator}.
Suppose $H\colon\C\to\C$ is an entire function satisfying
\begin{equation}\label{eq:lemma-step3-eq}
P^\#(\partial_w/\pi)H(w)=0,
\qquad w\in\C,
\end{equation}
together with the growth bound
\begin{equation}\label{eq:lemma-step3-growth}
|H(w)|\le C(1+|w|)^N e^{\pi M|w|},
\qquad w\in\C,
\end{equation}
for some \(C>0\) and some \(M>0\). If, in addition, the zeros
$\zeta_1,\dots,\zeta_\ell$ of the characteristic polynomial
$\widetilde P^\#(\zeta):=P^\#(\zeta/\pi)$ on $\C$ all satisfy
\begin{equation}\label{eq:lemma-step3-zeros}
|\zeta_j|>\pi M,\qquad 1\le j\le\ell,
\end{equation}
then \(H\equiv 0\).
\end{lemma}

\begin{proof}
Let $m_1,\dots,m_\ell$ be the multiplicities of the zeros
$\zeta_1,\dots,\zeta_\ell$ of $\widetilde P^\#$, and write
\(\widetilde P^\#(\zeta)=\overline{b_N}\,\pi^{-N}\prod_{j=1}^\ell(\zeta-\zeta_j)^{m_j}\)
when $b_N\neq0$ (otherwise the leading coefficient is the highest non-zero
$\overline{b_k}$ divided by $\pi^k$, and the same argument applies). The
elementary structure theorem for entire solutions of constant-coefficient
linear ODEs of finite exponential type \cite[Ch.~XII]{Hormander-PDE2} states that
every entire solution of \eqref{eq:lemma-step3-eq} with finite exponential
type takes the form
\begin{equation}\label{eq:lemma-step3-decomposition}
H(w)=\sum_{j=1}^\ell R_j(w)\,e^{\zeta_j w},
\end{equation}
where \(R_j\in\C[w]\) is a polynomial of degree at most \(m_j-1\). The
hypothesis \eqref{eq:lemma-step3-growth} ensures that \(H\) has exponential
type at most \(\pi M\), so \eqref{eq:lemma-step3-decomposition} indeed
applies.

Suppose, for a contradiction, that some $R_j$ does not vanish identically.
Re-indexing if necessary, choose $j_0$ with $R_{j_0}\not\equiv0$ and
$|\zeta_{j_0}|=\max\{|\zeta_j|\colon R_j\not\equiv 0\}$. After a small
generic rotation of the coordinate $w\mapsto e^{i\theta}w$ (which leaves both
\eqref{eq:lemma-step3-eq} and \eqref{eq:lemma-step3-growth} invariant up to
relabeling the $\zeta_j$), we may assume that for every \(j\) with
$j\ne j_0$ and $R_j\not\equiv 0$,
\begin{equation}\label{eq:lemma-step3-strict}
\Re(\zeta_j\,\overline{\zeta_{j_0}})<|\zeta_{j_0}|^2.
\end{equation}
This is automatic when $|\zeta_j|<|\zeta_{j_0}|$ from the Cauchy--Schwarz
inequality $\Re(\zeta_j\,\overline{\zeta_{j_0}})\le|\zeta_j||\zeta_{j_0}|$,
and ties at maximal modulus are broken by the rotation.

Along the half-line \(w_t:=t\,\overline{\zeta_{j_0}}\), \(t\ge 0\), the
exponential factor of the \(j_0\)th term has modulus
$|e^{\zeta_{j_0}w_t}|=e^{t|\zeta_{j_0}|^2}$, while every other term
satisfies
\(|R_j(w_t)e^{\zeta_j w_t}|\le C_j(1+t)^{m_j-1}e^{t\,\Re(\zeta_j\overline{\zeta_{j_0}})}\),
which by \eqref{eq:lemma-step3-strict} grows strictly slower than
$e^{t|\zeta_{j_0}|^2}$. Combining these and using $R_{j_0}\not\equiv 0$,
\begin{equation}\label{eq:lemma-step3-lower}
|H(w_t)|\ge c_0\,e^{t|\zeta_{j_0}|^2}
\qquad
\text{for all sufficiently large $t$,}
\end{equation}
with $c_0>0$ depending only on $R_{j_0}$ and the gap in
\eqref{eq:lemma-step3-strict}.

On the other hand, \eqref{eq:lemma-step3-growth} evaluated at $w_t$ gives
\begin{equation}\label{eq:lemma-step3-upper}
|H(w_t)|
\le
C(1+t|\zeta_{j_0}|)^N e^{\pi M\,t|\zeta_{j_0}|}.
\end{equation}
Comparing \eqref{eq:lemma-step3-lower} and \eqref{eq:lemma-step3-upper},
and absorbing the polynomial factor into an arbitrarily small exponential,
yields \(|\zeta_{j_0}|^2\le\pi M|\zeta_{j_0}|\), i.e.
\(|\zeta_{j_0}|\le\pi M\), contradicting \eqref{eq:lemma-step3-zeros}. Hence
all $R_j$ are identically zero, and \(H\equiv0\).
\end{proof}

\begin{remark}\label{rmk:step3-no-hidden-obstruction}
Lemma~\ref{lem:step3-rigidity} is the precise reason why no
finite-dimensional obstruction is left behind by the symmetrization
\eqref{eq:eigenfunction-general-new}~\(\Rightarrow\)~\eqref{eq:almost-reduced-new}:
the kernel of \(P^\#(\partial_w/\pi)\) on the full space of entire functions
is the finite-dimensional exponential-polynomial space spanned by
\(\{w^ie^{\zeta_jw}:0\le i<m_j,\ 1\le j\le\ell\}\), but the growth
constraint \eqref{eq:lemma-step3-growth} together with the non-vanishing of
\(P^\#\) on the closure of \(U\) (which forces \eqref{eq:lemma-step3-zeros})
collapses this kernel to $\{0\}$. The role of $P^\#$ being non-vanishing on
$U$ is therefore not cosmetic: it is what guarantees that the zeros of
$\widetilde P^\#$ are far from the origin, hence beyond the exponential-type
radius $\pi M$ that any candidate solution can have.
\end{remark}

\begin{proof}[Proof of Theorem \ref{thm:perturb}]
We again use the Bargmann transform. Let
\[
P(z)=1+\sum_{k=1}^N b_k z^k,
\]
where the coefficients $b_k$ are chosen so that the Bargmann transform of
\[
f_0=h_0+\sum_{k=1}^N a_k h_k
\]
is exactly $P$. We also write
\begin{equation}\label{eq:Phash-def}
P^\#(z):=\overline{P(\overline z)}
=1+\sum_{k=1}^N \overline{b_k}\,z^k
\end{equation}
for the \emph{coefficientwise conjugate polynomial}: the operation
\(P\mapsto P^\#\) leaves the monomials \(z^k\) intact and conjugates only the
scalar coefficients, so \(P^\#\) is again a polynomial of the same degree as
\(P\), holomorphic in \(z\), satisfying
\(P^\#(\overline z)=\overline{P(z)}\) for every \(z\in\C\).
Associated with \(P^\#\) is the holomorphic constant-coefficient differential
operator on the variable \(w\in\C\) defined by
\begin{equation}\label{eq:Phash-operator}
P^\#(\partial_w/\pi)
:=
\sum_{k=0}^N\overline{b_k}\,\Big(\frac{\partial_w}{\pi}\Big)^k,
\qquad b_0:=1,
\end{equation}
i.e. by substituting \(z=\partial_w/\pi\) into \eqref{eq:Phash-def}. Since
\(\partial_w=\frac12(\partial_x-i\partial_y)\) is the standard Wirtinger
derivative on entire functions of \(w=u+iv\), the operator
\(P^\#(\partial_w/\pi)\) acts on every entire function as the finite linear
combination of the iterated Wirtinger derivatives \((\partial_w/\pi)^k\),
\(0\le k\le N\); in particular it is a finite-order, holomorphic differential
operator. The key calculation is that
\(P^\#(\partial_w/\pi)\) acts as the multiplier \(P^\#(\overline z)\) on
each plane wave \(w\mapsto e^{\pi\overline z w}\):
\begin{equation}\label{eq:Phash-on-planewaves}
P^\#(\partial_w/\pi)\big[e^{\pi\overline z w}\big]
=
P^\#(\overline z)\,e^{\pi\overline z w}
=
\overline{P(z)}\,e^{\pi\overline z w},
\qquad z,w\in\C,
\end{equation}
because \((\partial_w/\pi)^k e^{\pi\overline z w}=\overline z^{\,k}e^{\pi\overline z w}\).

Term-by-term differentiation of an integrand of the form
\(P(z)e^{-\pi|z|^2}e^{\pi\overline z w}\) against \(z\in U\) is justified by
dominated convergence: \(U\) is bounded, \(P(z)e^{-\pi|z|^2}\) is bounded on
\(U\), and for each \(k\le N\) and each compact \(K\subset\C\) one has the
locally uniform estimate
\[
\Big|\Big(\frac{\partial_w}{\pi}\Big)^k\!\big[e^{\pi\overline z w}\big]\Big|
=
|\overline z|^k\,e^{\pi\Re(\overline z w)}
\le
M^k e^{\pi M|w|},
\qquad z\in U,\ w\in K,
\]
with \(M:=\sup_{z\in U}|z|\). Thus differentiation and integration may be
exchanged finitely many times, which is all that is required to apply
\(P^\#(\partial_w/\pi)\) term-by-term to the entire function defined by an
integral against \(z\in U\). Then the condition that $f_0$ be an eigenfunction
of $\mathcal{L}_U$ with eigenvalue $\lambda$ is equivalent to
\begin{equation}\label{eq:eigenfunction-general-new}
\int_U P(z)e^{-\pi|z|^2}e^{\pi \overline z w}\,dA(z)=\lambda P(w),
\qquad w\in \C.
\end{equation}
Set
\begin{equation}\label{eq:Q-def}
Q(w):=P^\#(\partial_w/\pi)P(w).
\end{equation}
By Proposition~\ref{prop:disk-inverse-tailored}, after decreasing
\(\varepsilon_0(\lambda,N)\) if necessary, there exists a real-analytic radial
graph \(U=U_b\), \(C^2\)-close to the Daubechies disk of radius
\(r_\lambda\), for which
\begin{equation}\label{eq:almost-reduced-new}
\int_U |P(z)|^2e^{-\pi|z|^2}e^{\pi\overline z w}\,dA(z)
=
\lambda Q(w),
\qquad w\in\C .
\end{equation}
We now recover the unsymmetrized identity
\eqref{eq:eigenfunction-general-new}. Define
\[
G(w):=\int_U P(z)e^{-\pi|z|^2}e^{\pi\overline z w}\,dA(z).
\]
The function \(G\) is entire, and differentiating under the integral is
justified by boundedness of \(U\). Since
\[
\Big(\frac{\partial_w}{\pi}\Big)^j e^{\pi\overline z w}
=\overline z^{\,j}e^{\pi\overline z w},
\]
we have
\[
P^\#(\partial_w/\pi)G(w)
=
\int_U |P(z)|^2e^{-\pi|z|^2}e^{\pi\overline z w}\,dA(z)
=
\lambda Q(w)
=
P^\#(\partial_w/\pi)(\lambda P)(w).
\]
Thus \(H:=G-\lambda P\) is an entire solution of
\[
P^\#(\partial_w/\pi)H=0.
\]

We now verify the hypotheses of Lemma~\ref{lem:step3-rigidity}. Setting
\(M:=\sup_{z\in U}|z|\), the integral defining \(G\) yields the standard
exponential-type bound
\begin{equation}\label{eq:G-growth-bound}
|G(w)|\le\Big(\sup_{z\in U}|P(z)|e^{-\pi|z|^2}\Big)\,|U|\,e^{\pi M|w|}
\le C(1+|w|)^N e^{\pi M|w|},
\qquad w\in\C,
\end{equation}
because \(|e^{\pi\overline z w}|\le e^{\pi|z||w|}\) for \(z\in U\). Since
\(\lambda P\) grows only polynomially, \(H=G-\lambda P\) inherits the same
exponential-type bound, with possibly larger constant: \(H\) satisfies
\eqref{eq:lemma-step3-growth}.

The location of the zeros of the characteristic polynomial \(\widetilde P^\#\)
is controlled by \(b\). Since \(U\subset V_2\) (with \(V_2\) defined in
Proposition~\ref{prop:disk-inverse-tailored}), and since
\(P^\#(z)=1+\sum_k\overline{b_k}z^k\) reduces to the constant \(1\) at
\(b=0\), the zeros of \(P^\#\) on \(\C\) escape to infinity uniformly as
\(b\to0\); a fortiori the zeros of \(\widetilde P^\#(\zeta)=P^\#(\zeta/\pi)\)
escape to infinity. After shrinking \(\varepsilon_0(\lambda,N)\) if
necessary, all \(\ell\) zeros \(\zeta_j\) of \(\widetilde P^\#\) satisfy
\[
|\zeta_j|>10\,M\ge\pi M,
\qquad 1\le j\le\ell,
\]
which is hypothesis \eqref{eq:lemma-step3-zeros}. Lemma~\ref{lem:step3-rigidity}
therefore implies $H\equiv 0$, which is precisely
\eqref{eq:eigenfunction-general-new}.

The Bargmann transform is unitary and intertwines the localization operator
with the integral operator in \eqref{eq:eigenfunction-general-new}. Therefore
the inverse Bargmann transform \(f_0\) of \(P\) satisfies
\[
\mathcal L_U f_0=\lambda f_0 .
\]
This proves the theorem.
\end{proof}


% ==============================================================
% Section 4
% ==============================================================

\section{A Classical Rigidity Corollary}\label{sec:classical-rigidity}

The localization operator $\mathcal{L}_U$ on the Bargmann--Fock space is
diagonalized by Hermite functions whenever $U$ is a disk centered at the
origin: this is an immediate consequence of the rotational symmetry of $U$
together with the radial structure of the Hermite weight. The converse
question, raised by Abreu and D\"orfler, asks whether eigenfunction status of
even a \emph{single} Hermite function already forces the underlying domain to
be a disk. The next theorem records a positive answer in the simply connected
$C^2$ regime.

For convenience we recall the statement of Theorem~\ref{thm:eig-loc-U} from the introduction:
\emph{let $U\subset \C$ be a simply connected bounded domain with $C^2$
boundary, and let $h_k$ be a Hermite function ($k\ge 0$). If $h_k$ is an
eigenfunction of the localization operator $\mathcal{L}_U$, then $U$ is a
disk.} (The original Abreu--D\"orfler theorem~\cite{Abreu-Doerfler} dispenses
with the boundary regularity assumption; we will recover this stronger form
in the second proof below.)

We will give two proofs of Theorem~\ref{thm:eig-loc-U}. The first, presented
below, leverages the Fourier-analytic machinery developed earlier in the
paper, reducing the question to a free boundary problem for a logarithmic
potential. The second, in the next subsection, proceeds along more
classical complex-analytic lines and, as we shall see, dispenses with the
$C^2$ boundary assumption altogether.

Before launching into the arguments, we record, in a form convenient for
later reference, the two analytic inputs underlying both proofs. The first is
the precise variant of the Paley--Wiener theorem we use to interpret the
moment identity \eqref{eq:fourier-delta} below as the vanishing of an entire
function on a complex hypersurface; the second is the
Ehrenpreis--Malgrange-type divisibility lemma that converts this vanishing
into a Poisson equation with prescribed right-hand side. Both statements are
quoted in the exact form in which they will be applied; we have stated them
here, rather than referring back to Section~\ref{sec:fourier-to-fboundary},
in order to keep the regularity hypotheses on $\omega$ visible to the
reader following Section~\ref{sec:classical-rigidity} in isolation.

\begin{theorem}[Paley--Wiener--Schwartz, planar form]\label{thm:PW-section4}
Let $\omega\in\mathcal D'(\R^2)$ be a compactly supported distribution of
order $\le N$ with $\operatorname{supp}\omega\subset \overline{B(0,R)}$.
Then its Fourier transform $\widehat\omega$ extends to an entire function
on $\C^2$ satisfying the Paley--Wiener bound
\begin{equation}\label{eq:PW-bound-section4}
|\widehat\omega(\xi,\eta)|\le C\,(1+|\xi|+|\eta|)^N\,e^{R(|\Im\xi|+|\Im\eta|)},
\qquad (\xi,\eta)\in\C^2,
\end{equation}
for some $C>0$. Conversely, any entire function on $\C^2$ obeying such a
bound is the Fourier--Laplace transform of a unique compactly supported
distribution of order $\le N$ supported in $\overline{B(0,R)}$. If, in
addition, the bound holds with $N=0$ and $\widehat\omega|_{\R^2}\in
L^2(\R^2)$, then $\omega\in L^2(\R^2)$.
\end{theorem}

This is the classical Paley--Wiener--Schwartz theorem; we use the form
stated in \cite[Theorem~7.3.1]{Hormander-PDE1}, see also \cite[\S 9.3]{Folland}.
The $L^2$ refinement in the last sentence is a direct consequence of
Plancherel applied to the entire function $\widehat\omega|_{\R^2}$, combined
with uniqueness of the Fourier inversion. In our application, $\omega$ is
a finite signed Radon measure of compact support, so the Paley--Wiener
bound \eqref{eq:PW-bound-section4} holds with $N=0$ and $C=\|\omega\|_{\mathrm{TV}}$.

\begin{lemma}[Ehrenpreis--Malgrange-type divisibility along $\xi^2+\eta^2$]\label{lem:EM-section4}
Let $\omega$ be a compactly supported singular-continuous free measure on
$\R^2$, in the sense of Section~\ref{sec:fourier-to-fboundary}: a finite
signed Radon measure of the form
\[
\omega=f\,dx\,dy+\sum_{j=1}^N c_j\,\delta_{p_j},
\]
with $f\in L^\infty(\R^2)$ compactly supported, $c_j\in\R\setminus\{0\}$,
and $p_j\in\R^2$ distinct. Suppose moreover that the Fourier--Laplace
transform $\widehat\omega$, an entire function on $\C^2$ of exponential
type by Theorem~\ref{thm:PW-section4}, vanishes on the complex
characteristic variety of the planar Laplacian,
\begin{equation}\label{eq:complex-char-variety}
\Sigma:=\{(\xi,\eta)\in\C^2:\xi^2+\eta^2=0\}=\{\eta=i\xi\}\cup\{\eta=-i\xi\}.
\end{equation}
Then $\widehat\omega$ is divisible, in the ring of entire functions of
exponential type on $\C^2$, by the polynomial $\xi^2+\eta^2$, with quotient
$F\in L^2(\R^2)\cap L^1(\R^2)$ on the real locus. Equivalently, there
exists a unique compactly supported $u\in L^2(\R^2)$, continuous off a
finite set $P\subset\R^2$, such that
\[
\Delta u=\omega\qquad\text{in }\mathcal D'(\R^2),
\]
namely the logarithmic potential
\[
u(z)=\frac{1}{2\pi}\int_{\R^2}\log|z-z'|\,d\omega(z').
\]
\end{lemma}

This is exactly Lemma~\ref{lemma:fourier-to-fboundary}, restated to
emphasize its character as a planar-Laplacian instance of the
Ehrenpreis--Malgrange division theorem (entire functions of exponential
type can be divided by a polynomial within the same Paley--Wiener class;
see \cite[Ch.~7]{Hormander-PDE1}). We do \emph{not} invoke the general
Ehrenpreis--Malgrange machinery: a self-contained proof, exploiting the
homogeneity decomposition of $\widehat\omega$ and positivity of
$\xi^2+\eta^2$ on $\R^2$, is given in Section~\ref{sec:fourier-to-fboundary}.
The hypotheses on $\omega$ -- in particular, the absence of a continuous
singular part and the finiteness of the point part -- are essential for
the conclusion that $u$ is continuous off a finite set; without them the
quotient $F$ remains in $L^2$, but $u$ need only be quasi-continuous in
the logarithmic-potential sense.

\subsection{First proof}

\begin{proof}[First proof under the additional assumption that $\partial U$ is $C^2$]
The Bargmann transform of the Hermite function $h_k$ is a nonzero scalar
multiple of the monomial $z^k$. Thus, arguing as in
\cite{Abreu-Doerfler}, the assumption that $h_k$ is an eigenfunction of
the localization operator $\mathcal{L}_U$ is equivalent to the identity
\[
\int_U z^k\, e^{\pi w\overline{z}}\, e^{-\pi |z|^2}\,dA(z)
=\lambda\, w^k,
\qquad w\in \C.
\]
Both sides are entire functions of $w$. Since $U$ is bounded and the
weight $e^{-\pi|z|^2}$ is integrable, the dominated convergence
theorem applied to difference quotients shows that for each
multi-index $\alpha$ in $w$, the partial derivative
$\partial_w^\alpha$ commutes with the integral on the left-hand side;
the absolute integrability of $|z|^{|\alpha|+k} e^{\pi
|w||z|}e^{-\pi|z|^2}\mathbf{1}_U$ for fixed $w$ provides the required
local majorant. Iterating $k$ times, we obtain
\[
\frac{1}{(\pi)^k}\,\partial_w^k
\Big[\int_U z^k\, e^{\pi w\overline{z}}\, e^{-\pi |z|^2}\,dA(z)\Big]
=\int_U z^k\overline{z}^k\, e^{\pi w\overline{z}}\, e^{-\pi |z|^2}\,dA(z)
=\int_U |z|^{2k}\, e^{\pi w\overline{z}}\, e^{-\pi |z|^2}\,dA(z).
\]
On the right-hand side, $\partial_w^k(\lambda w^k)=\lambda\,k!$.
Setting $c(\lambda,k):=\lambda\,k!/\pi^k\in\R$ and using
$\mathbf{1}_U$ to extend the integration to $\C$, we obtain
\begin{equation}\label{eq:fourier-delta}
\int_{\C} \mathbf{1}_U(z)\,|z|^{2k}\,e^{-\pi |z|^2}\, e^{\pi \overline{z}\, w}\,dA(z)
=c(\lambda,k),
\end{equation}
for some real constant $c(\lambda,k)$.

Consider now the compactly supported distribution
\begin{equation}\label{eq:eta-def-section4}
\eta:=|z|^{2k}e^{-\pi |z|^2}\mathbf{1}_U(z)-c(\lambda,k)\,\delta_0,
\end{equation}
which is a finite signed Radon measure with compact support in any closed
ball containing $U\cup\{0\}$. Its absolutely continuous part has bounded
density $|z|^{2k}e^{-\pi|z|^2}\mathbf{1}_U\in L^\infty_c(\R^2)$, and its
pure-point part is the single Dirac mass $-c(\lambda,k)\delta_0$. Hence
$\eta$ is a singular-continuous free measure in the sense of
Section~\ref{sec:fourier-to-fboundary}, and we may apply
Theorem~\ref{thm:PW-section4} and Lemma~\ref{lem:EM-section4} to it.

Writing $z=x+iy$ and $w\in\C$, we rewrite the exponential factor in
\eqref{eq:fourier-delta} as
\[
e^{\pi \overline{z}\, w}=e^{\pi(x-iy)w}=e^{\pi xw}\, e^{-i\pi yw}.
\]
The function class entering the Paley--Wiener step is now unambiguous:
$\eta\in\mathcal E'(\R^2)$ is a compactly supported distribution of order
zero, in fact a finite signed Radon measure. Theorem~\ref{thm:PW-section4}
therefore applies and produces an entire function $\widehat\eta$ on
$\C^2$ obeying the Paley--Wiener bound \eqref{eq:PW-bound-section4} with
$N=0$ and $R$ equal to the radius of any closed disk containing
$U\cup\{0\}$; in particular $\widehat\eta|_{\R^2}$ is bounded by
$\|\eta\|_{\mathrm{TV}}$ and extends to $\C^2$ as an entire function of
exponential type. With the convention
$\widehat g(\xi,\eta):=\int_{\R^2}g(x,y)\,e^{-2\pi i(x\xi+y\eta)}\,dx\,dy$
used in Section~\ref{sec:fourier-to-fboundary}, a comparison of exponents
shows that for $w\in\C$ the kernel $e^{\pi xw}\,e^{-i\pi yw}$ coincides
with $e^{-2\pi i(x\xi+y\eta)}$ on the complex line
$(\xi,\eta)=\bigl(\tfrac{iw}{2},-\tfrac{w}{2}\bigr)$, $w\in\C$, whose
defining equation is $\eta=i\xi$. Reparametrizing this line in the form
$(\xi,\eta)=(w,-iw)$, identity \eqref{eq:fourier-delta}---which says that
the integral on the left-hand side, viewed as an entire function of
$w\in\C$, is identically equal to the constant $c(\lambda,k)$, so that
the Fourier--Laplace transform of the modified distribution $\eta$
vanishes there---becomes
\begin{equation}\label{eq:eta-vanishes-on-line}
\widehat{\eta}(w,-iw)=0,\qquad \forall w\in\C.
\end{equation}
Symmetrically, since $c(\lambda,k)\in\R$ and the absolutely continuous
density of $\eta$ is real-valued, complex conjugation of
\eqref{eq:fourier-delta} after the substitution $w\mapsto\overline w$,
combined with the same Paley--Wiener identification applied to the
conjugate complex line $\eta=-i\xi$, yields
\begin{equation}\label{eq:eta-vanishes-on-conjugate-line}
\widehat{\eta}(w,iw)=0,\qquad \forall w\in\C.
\end{equation}
Identities \eqref{eq:eta-vanishes-on-line} and
\eqref{eq:eta-vanishes-on-conjugate-line} together assert that
$\widehat\eta$ vanishes on the complex characteristic variety
$\Sigma=\{\xi^2+\eta^2=0\}$ of the Laplacian, see
\eqref{eq:complex-char-variety}.

Applying the divisibility lemma (Lemma~\ref{lem:EM-section4}, equivalently
Lemma~\ref{lemma:fourier-to-fboundary}) to the distribution $\eta$, we
obtain a unique compactly supported function $u\in L^2(\R^2)$, continuous
off a finite set, such that
\begin{equation}\label{eq:potato}
\Delta u=f(|z|)\,\mathbf{1}_U-c(\lambda,k)\,\delta_0
\end{equation}
in the sense of distributions on $\R^2$, where
\[
f(|z|)=|z|^{2k}e^{-\pi |z|^2}.
\]
Writing $u$ explicitly as a logarithmic potential of the right-hand side
of \eqref{eq:potato}, we conclude that $U$ satisfies
\begin{equation}\label{eq:potential}
\int_U \log|z-z'|\, f(|z'|)\,dA(z')
=c(\lambda,k)\,\log|z|,
\qquad z\in \C\setminus (U\cup\{0\}).
\end{equation}

\medskip

\noindent\emph{Reduction to $0\notin U$.}\quad
Suppose first that $0\in U$, and pick $\rho>0$ small enough that
$\overline{D_\rho(0)}\subset U$. The radial measure
$f(|z|)\,\mathbf{1}_{D_\rho(0)}\,dA$ generates a logarithmic potential
\[
\Phi_\rho(z):=\int_{D_\rho(0)} \log|z-z'|\, f(|z'|)\,dA(z'),
\]
which, by the planar Newton shell theorem for logarithmic potentials of
radial densities (see, e.g., \cite[Ch.~2]{Isakov}), is radial; outside
$D_\rho(0)$ it equals
\[
\Phi_\rho(z)=\Big(\int_{D_\rho(0)}f(|z'|)\,dA(z')\Big)\log|z|+\text{const}.
\]
Subtracting the closed disk $\overline{D_\rho(0)}$ from $U$ thus preserves
identity \eqref{eq:potential} on the complement of the new set, at the
cost of replacing $c(\lambda,k)$ by $c(\lambda,k)-M_\rho$, where
$M_\rho:=\int_{D_\rho(0)}f(|z'|)\,dA(z')>0$. The new domain
$U':=U\setminus\overline{D_\rho(0)}$ satisfies
$0\notin \overline{U'}$, so we may assume from now on that
$0\notin \overline{U}$ in \eqref{eq:potential}, with $c(\lambda,k)$
replaced (if needed) by the real constant $c(\lambda,k)-M_\rho$, which
we continue to denote by $c(\lambda,k)$. Furthermore, this constant must
be nonzero: comparing the two sides of \eqref{eq:potential} as
$|z|\to\infty$ shows that the left-hand side behaves like
$\big(\int_U f\,dA\big)\log|z|+O(|z|^{-1})$, while the right-hand side
is $c(\lambda,k)\log|z|$, forcing
$c(\lambda,k)=\int_U f(|z'|)\,dA(z')>0$.

\medskip

Define the logarithmic potential
\[
\Psi_U(z):=\int_U \log|z-z'|\, f(|z'|)\,dA(z').
\]
We claim that $\Psi_U$ is \emph{locally radial}: for each $z_0\in U$,
there exists a ball $B(z_0)\subset U$ such that $\Psi_U$ agrees on
$B(z_0)$ with a radial function of $|z|$.

To prove this, let $B\supset U$ be a ball centered at $0$, and define
\[
\Phi(z):=\int_B \log|z-z'|\, f(|z'|)\,dA(z').
\]
Since both $B$ and the weight $f(|z'|)$ are radial, $\Phi$ is radial; in
particular, $\nabla \Phi(z)$ is parallel to $z$ for every $z\in \R^2$.
Furthermore, on the interior of $B$,
\[
\Delta \Phi(z)=2\pi\, f(|z|).
\]

Now $\Psi_U$ satisfies \eqref{eq:potential} on the unbounded
component of $\C\setminus(U\cup\{0\})$. Differentiating that identity
in $z$ for $z\not\in \overline{U}\cup\{0\}$ gives
\[
\nabla \Psi_U(z)=c(\lambda,k)\,\frac{z}{|z|^2},
\qquad z\in \C\setminus(\overline{U}\cup\{0\}).
\]
The classical jump relations for the single-layer / volume logarithmic
potential of an $L^\infty$ density on a $C^2$ domain (see, e.g.,
\cite{Gustafsson}) imply that $\nabla\Psi_U$ extends continuously
across $\partial U$ from \emph{both} sides, and the boundary values
agree. Hence on $\partial U$,
\[
\nabla \Psi_U(z)=c(\lambda,k)\,\frac{z}{|z|^2},
\qquad z\in \partial U,
\]
which is, in particular, parallel to $z$. Therefore the difference
\[
v:=\Psi_U-\Phi
\]
satisfies $\Delta v=2\pi f(|z|)\mathbf 1_U-2\pi f(|z|)\mathbf 1_B
=-2\pi f(|z|)\mathbf 1_{B\setminus U}$ in the sense of distributions
on $B$, so $v$ is harmonic in $U$ and in $B\setminus\overline{U}$, and
on $\partial U$ satisfies
\[
\nabla v(x)\ \text{is parallel to}\ x.
\]
The next lemma converts this gradient condition into local radiality of $v$.

\begin{lemma}\label{lem:harmonic-locally-radial}
Let $V\subset \R^2$ be a domain, and suppose there exists a harmonic
function $v\in C^1(\overline{V})$ such that $\nabla v(x)$ is parallel to
$x$ for every $x\in \partial V$. Then $\nabla v(x)$ is parallel to $x$
for every $x\in V$. In particular, on every circle
$S=\{|x|=r\}\subset \R^2$, the function $v$ is constant on every
connected component of $S\cap V$.
\end{lemma}

\begin{proof}
Consider the angular derivative
\[
g(x):=x_1\,\partial_2 v(x)-x_2\,\partial_1 v(x)
=\partial_\theta v(x),
\]
which equals the tangential derivative of $v$ along the circle
through $x$ centered at $0$. A direct computation gives
\[
\Delta g
=x_1\,\Delta(\partial_2 v)-x_2\,\Delta(\partial_1 v)
+2\big(\partial_1\partial_2 v-\partial_2\partial_1 v\big)
=0,
\]
since $v$ is harmonic and partial derivatives of harmonic functions
are themselves harmonic. By the boundary hypothesis, $\nabla v(x)$ is
parallel to $x$ on $\partial V$, so $g\equiv 0$ on $\partial V$.
Together with $g\in C(\overline{V})$, the maximum principle for
harmonic functions yields $g\equiv 0$ in $V$. Hence $\nabla v(x)$ is
parallel to $x$ at every interior point as well, and on any circle
$S=\{|x|=r\}$ the tangential derivative $\partial_\theta v$ vanishes
on $S\cap V$. Therefore $v$ is constant on each connected component
of $S\cap V$.
\end{proof}

Applying Lemma~\ref{lem:harmonic-locally-radial} on small subdomains
$V\subset U$ where $v$ is harmonic and $C^1$ up to the boundary, we
conclude that $v$ is locally radial on $U$. Since $\Phi$ is globally
radial, so is $\Psi_U=\Phi+v$, locally on $U$.

\begin{lemma}\label{lem:local-to-global-radial}
Let \(W\subset \R^2\setminus\{0\}\) be a connected open set, and let
\(u\in C(W)\). Suppose that for every \(x\in W\) there exist \(r_x>0\)
and a scalar function \(\phi_x\) such that
\[
u(y)=\phi_x(|y|)
\qquad\text{for all } y\in B(x,r_x)\subset W.
\]
Then there exists a single scalar function \(\phi\), defined on the
interval
\[
I_W:=\{|y|:y\in W\},
\]
such that
\[
u(y)=\phi(|y|)
\qquad\text{for all } y\in W.
\]
\end{lemma}

\begin{proof}
For each \(x\in W\), choose a ball \(B_x:=B(x,r_x)\subset W\) on which
\(u\) is a radial function of \(|y|\), with profile $\phi_x$. We
first note that whenever $B_x\cap B_{x'}\ne\emptyset$,
\[
\phi_x(|y|)=u(y)=\phi_{x'}(|y|)
\qquad\text{for every }y\in B_x\cap B_{x'}.
\]
Since $B_x\cap B_{x'}$ is open and avoids the origin, the map $y\mapsto
|y|$ is a submersion on it, so the set of radii it attains contains a
nontrivial open interval on which $\phi_x$ and $\phi_{x'}$ agree.

Fix $x_*\in W$ and define a candidate function $\phi$ on $I_W$ as
follows. Given $y\in W$, connect $x_*$ to $y$ by a polygonal path in
$W$, which exists because $W$ is open and connected. Its image is
compact, hence covered by finitely many balls
$B_{x_1},\dots,B_{x_m}$ with successive nonempty overlaps and
$x_1=x_*$, $y\in B_{x_m}$. The previous paragraph implies $\phi_{x_j}$
and $\phi_{x_{j+1}}$ agree on a nontrivial interval of radii, so by
analytic-continuation along the chain we may unambiguously set
$\phi(|y|):=\phi_{x_m}(|y|)$. Independence of the chain follows from
the same overlap argument: any two chains from $x_*$ to $y$ can be
interleaved into a single chain, and successive overlaps force the
final value to coincide. Hence $\phi$ is well-defined on $I_W$ and
satisfies $u(y)=\phi(|y|)$ for every $y\in W$.
\end{proof}

We now conclude the proof. Since \(U\) is simply connected and bounded,
it suffices to rule out the possibility that \(U\) fails to be a disk
centered at the origin. Suppose therefore, for contradiction, that
\(U\) is not such a disk. Then \(\partial U\) is not a single circle
centered at $0$, so there exist radii \(0<r_1<r_2\) such that the
annulus
\[
A:=\{z\in \R^2:\ r_1<|z|<r_2\}
\]
meets both $U$ and $\partial U$ in a non-trivial way; in particular,
we may pick a point
\[
x_0\in \partial U\cap A.
\]
Let
\[
\widetilde{U}_0:=U\cap B_r(x_0),
\]
for $r>0$ sufficiently small that $\widetilde U_0$ is connected and
$0\notin \overline{\widetilde U_0}$. Since \(\Psi_U\) is locally radial
in \(U\), Lemma~\ref{lem:local-to-global-radial} applied to
$W=\widetilde U_0$ yields a scalar function \(\psi_U\) on
$I_{\widetilde U_0}$ such that
\[
\Psi_U(x)=\psi_U(|x|),\qquad x\in \widetilde{U}_0.
\]

On the other hand, by \eqref{eq:potential} and the continuity of the
gradient of a volume logarithmic potential with bounded density across
a $C^2$ boundary (see, e.g., \cite{Gustafsson,Isakov}), the gradient
$\nabla\Psi_U$ extends continuously across $\partial U$, and for
$z\in\partial U$ we have
\[
\nabla \Psi_U(z)=c\,\frac{z}{|z|^2}
\]
for the same constant $c=c(\lambda,k)\in \R$ as in
\eqref{eq:potential}. Combining this with $\Psi_U(x)=\psi_U(|x|)$ on
$\widetilde U_0$ and passing to $z\in \partial \widetilde U_0\cap
\partial U$ from the inside,
\[
\psi_U'(|z|)\,\frac{z}{|z|}=c\,\frac{z}{|z|^2},
\qquad z\in \partial U\cap \overline{B_r(x_0)},
\]
hence
\[
\psi_U'(r)=\frac{c}{r}
\]
for every $r$ in the set of radii attained by points of
$\partial U\cap \overline{B_r(x_0)}$. Since $\partial U$ is a $C^2$
curve, we may, after shrinking $r$ once more, parametrize
$\partial U\cap B_r(x_0)$ by a $C^2$ embedding
$\gamma:(-\varepsilon,\varepsilon)\to \R^2$ with $\gamma(0)=x_0$.
Because $\partial U$ is not a circle centered at $0$, the smooth
function $t\mapsto |\gamma(t)|^2$ is non-constant on the connected
$C^2$ arc $\partial U\cap A$. Hence its derivative does not vanish
identically on any subinterval, and we may choose $x_0\in\partial U\cap A$
so that
\[
\frac{d}{dt}|\gamma(t)|^2\Big|_{t=0}\ne 0,
\]
which is equivalent to $\frac{d}{dt}|\gamma(t)|\big|_{t=0}\ne 0$ since
$|\gamma(0)|=|x_0|>0$. Hence by the open-mapping
property for $C^1$ functions of one variable with nonzero derivative,
the image of $|\gamma|$ contains a nontrivial open interval
\(I\subset (r_1,r_2)\).
Therefore
\[
\psi_U'(r)=\frac{c}{r}
\qquad\text{for every }r\in I,
\]
whence
\[
\psi_U(r)=c\log r+C_0,
\qquad r\in I,
\]
for some real constant $C_0$.

Let
\[
W_I:=\{x\in \widetilde U_0:\ |x|\in I\}.
\]
Then \(W_I\) is a nonempty open subset of \(U\), and on \(W_I\),
\[
\Psi_U(x)=c\log|x|+C_0.
\]
Hence
\[
\Delta \Psi_U\equiv 0 \qquad \text{in } W_I,
\]
since the origin is excluded from $\widetilde U_0$. On the other hand,
since $0\notin \overline{U}$, the logarithmic potential $\Psi_U$ has
distributional Laplacian
\[
\Delta \Psi_U=2\pi\, f(|z|)\,\mathbf{1}_U
\]
in $\C$, with no contribution at the origin. Hence on the open set
$W_I\subset U\setminus\{0\}$ we have
\[
\Delta \Psi_U=2\pi\, f(|z|)=2\pi\, |z|^{2k}e^{-\pi |z|^2}.
\]
The right-hand side vanishes only at the origin, which lies outside
$W_I$, while the left-hand side just shown to be $0$ on $W_I$ — a
contradiction. This rules out the case in which $U$ is not a disk
centered at $0$, completing the proof.
\end{proof}

\begin{remark}
The structure of the argument above is in the spirit of
\cite{Aharonov-Schiffer-Zalcman}, where logarithmic-potential
rigidity statements were derived from Schiffer-style overdetermined
boundary conditions, and of the quadrature-domain literature
\cite{Gustafsson,Gustafsson-Shahgholian,Shahgholian,Karp}, in which
the regularity of free boundaries and the matching of an interior
potential with the Newtonian potential of a radially symmetric
density play a central role. Concretely, identity
\eqref{eq:potential} can be read as saying that $U$ is a
\emph{generalized quadrature domain} for the radial weight $f(|z|)$,
with quadrature data concentrated at the origin. From this perspective,
the conclusion that $U$ is a disk is a (sharp) instance of the
classical principle that radial quadrature data forces a radial
domain. The role of the $C^2$ boundary regularity is concentrated
in the boundary extension of $\nabla\Psi_U$ and in the
open-interval-of-radii argument that ends the proof; both can be
relaxed at the cost of additional technicalities, which we will
revisit in the second proof.
\end{remark}

\subsection{Second proof}\label{subsec:second-proof}

The first proof established Theorem~\ref{thm:eig-loc-U} under the auxiliary
hypothesis that $\partial U$ is of class $C^2$. The argument we now give does
not use any boundary regularity at all; it therefore strengthens
Theorem~\ref{thm:eig-loc-U} to a form which agrees with the original
Abreu--D\"orfler statement \cite{Abreu-Doerfler}.

\begin{theorem}[Strengthened rigidity, no boundary regularity]\label{thm:eig-loc-U-strong}
Let $U\subset\C$ be an open, bounded, simply connected set, with no
hypothesis on the regularity of $\partial U$ beyond what is implicit in
``simply connected''. Let $h_k$ ($k\ge 0$) be a Hermite function. If $h_k$
is an eigenfunction of the localization operator $\mathcal L_U$, then $U$
is a disk.
\end{theorem}

The hypotheses on $U$ in Theorem~\ref{thm:eig-loc-U-strong} reduce to: $U$
is open, bounded, connected, and its complement in $\overline\C$ is
connected (i.e.\ $U$ is simply connected). In particular, $\partial U$ is
allowed to be merely a closed set with $|U|<\infty$; no assumption of
positive Lebesgue density, finite perimeter, or differentiability is
imposed. The proof below shows that the boundary identity $\nabla u\equiv
0$ on $\partial U$, which in the first proof was extracted via boundary
regularity of the logarithmic potential and jump relations on a $C^2$
curve, now follows directly from the explicit formula for $u$ as a
convolution with $\log|\cdot|$, together with the local integrability of
the kernel $z/|z|^2$. Since $u$ vanishes identically on the open exterior
$\R^2\setminus\overline U$, continuity of $u$ and of $\nabla u$ on
$\R^2\setminus\{0\}$ forces both to vanish on $\partial U$, regardless of
how rough the boundary is. The remainder of the proof proceeds via a
holomorphic auxiliary function on $U$ whose boundary values are forced to
be real, and the maximum principle on $U$ (which is well-defined even for
rough boundaries) then yields the conclusion. We summarize this in
Remark~\ref{rem:bookkeeping-no-regularity} below; the precise place where
the $C^2$ assumption is bypassed is at the derivation
of~\eqref{eq:dz-zero-second-proof}.

\begin{proof}[Proof of Theorem~\ref{thm:eig-loc-U-strong} (second proof of Theorem~\ref{thm:eig-loc-U})]
We keep the notation
\[
f(|z|):=|z|^{2k}e^{-\pi|z|^2},
\qquad
c:=c(\lambda,k),
\]
from the first proof. The argument below is in the spirit of the holomorphic
moving-plane/quadrature-domain methods of \cite{Aharonov-Schiffer-Zalcman,Gustafsson,Karp},
in that we exploit the existence of a holomorphic function on \(U\) with prescribed real
boundary values to recover full radial symmetry. Starting again from \eqref{eq:fourier-delta} and
applying Lemma~\ref{lemma:fourier-to-fboundary}, we obtain a compactly supported distributional
solution of
\begin{equation}\label{eq:potato-second-proof}
\Delta u=f(|z|)\mathbf{1}_U-c\,\delta_0
\qquad\text{in }\mathcal D'(\R^2).
\end{equation}
Using the planar fundamental solution \((2\pi)^{-1}\log|z|\), we may write
\begin{equation}\label{eq:explicit-u-second-proof}
u(z):=\frac{1}{2\pi}\int_U \log|z-z'|\,f(|z'|)\,dA(z')-\frac{c}{2\pi}\log|z|.
\end{equation}
By \eqref{eq:potential}, this function satisfies
\[
u\equiv 0
\qquad\text{on }\R^2\setminus (U\cup\{0\}).
\]

We first show that \(0\in U\). Since the singular term in
\eqref{eq:potato-second-proof} is \(-c\delta_0\), one must have \(0\in\overline U\). If
\(0\in\partial U\), then there exist exterior points \(z_j\to 0\) with
\[
u(z_j)=0.
\]
On the other hand, the first term in \eqref{eq:explicit-u-second-proof} remains finite as
\(z\to 0\), because \(f\in L^\infty(U)\) and \(\log|z-z'|\) is locally integrable, whereas the
second term equals \(-\frac{c}{2\pi}\log|z|\to +\infty\). This contradicts the exterior identity
\(u(z_j)=0\). Hence \(0\notin\partial U\), and therefore
\[
0\in U.
\]

We next show directly from \eqref{eq:explicit-u-second-proof} that
\[
u\in C^1(\R^2\setminus\{0\}).
\]
Indeed, if we write
\[
g(z):=f(|z|)\mathbf{1}_U(z)\in L^\infty_c(\R^2),
\]
then
\[
u(z)=\frac{1}{2\pi}\int_{\R^2}\log|z-z'|\,g(z')\,dA(z')-\frac{c}{2\pi}\log|z|.
\]
Since \(g\in L^\infty_c(\R^2)\), the only contribution to the integral defining the convolution
\((K\ast g)(z)\) below comes from a fixed bounded set, so we may replace \(K\) by its restriction
\(K\mathbf{1}_{B_R}\) for any sufficiently large ball \(B_R\). The kernel
\(K(\zeta)=\zeta/|\zeta|^2\) satisfies \(|K(\zeta)|=|\zeta|^{-1}\), which is integrable on bounded
subsets of \(\R^2\); hence \(K\mathbf{1}_{B_R}\in L^1(\R^2)\). It is a standard fact
that the convolution of an \(L^1\) function with a bounded function is continuous
(this follows from the density of \(C_c(\R^2)\) in \(L^1(\R^2)\) and continuity of translations in
\(L^1\)), so
\[
(K\ast g)(z):=\int_{\R^2}\frac{z-z'}{|z-z'|^2}\,g(z')\,dA(z')
\]
is a continuous function of \(z\in\R^2\). On the other hand, a direct distributional computation
shows
\[
\nabla\!\left(\int_{\R^2}\log|z-z'|\,g(z')\,dA(z')\right)=K\ast g
\qquad\text{in }\mathcal D'(\R^2),
\]
so the gradient of the convolution \(\log|\cdot|\ast g\) coincides almost everywhere with the
continuous function \(K\ast g\). It follows that \(\log|\cdot|\ast g\) is of class \(C^1\) on
\(\R^2\), and hence \(u\in C^1(\R^2\setminus\{0\})\) (the only obstruction to global \(C^1\)
regularity being the explicit logarithmic singularity at the origin coming from the
\(-\frac{c}{2\pi}\log|z|\) term).

Now let \(z_*\in\partial U\). Since \(0\in U\), the boundary point \(z_*\) is bounded away from
\(0\); fix a small ball \(B_\rho(z_*)\Subset \R^2\setminus\{0\}\). On the exterior open set
\(\R^2\setminus \overline U\) we have \(u\equiv 0\), so \(\nabla u\equiv 0\) there. As
\(\partial U\) is contained in the boundary of the exterior, every \(z_*\in\partial U\) is a limit
of exterior points \(z_j\to z_*\) along which \(\nabla u(z_j)=0\). By the \(C^1\) regularity of
\(u\) on \(B_\rho(z_*)\), the gradient \(\nabla u\) is continuous at \(z_*\), and we conclude
\(\nabla u(z_*)=0\). In complex notation \(\partial_z=\tfrac{1}{2}(\partial_x-i\partial_y)\), this
yields
\begin{equation}\label{eq:dz-zero-second-proof}
\partial_z u=0
\qquad\text{on }\partial U.
\end{equation}
We emphasize that \emph{no} boundary regularity of \(\partial U\) has been used at this point, in
contrast with the first proof: the vanishing of \(\nabla u\) on \(\partial U\) is forced solely by
exterior continuity, which in turn is supplied by the explicit
formula~\eqref{eq:explicit-u-second-proof}.

Define
\[
\Phi(t):=\int_0^t s^k e^{-\pi s}\,ds
\qquad\text{and}\qquad
\Psi(z):=\frac{\Phi(|z|^2)}{z},
\quad z\neq 0.
\]
A direct computation, using \(|z|^2=z\bar z\) and \(\partial_{\bar z}(z\bar z)=z\), gives, for
\(z\neq 0\),
\[
\partial_{\bar z}\Psi(z)
=
\frac{\Phi'(|z|^2)\,\partial_{\bar z}(|z|^2)}{z}
=
\frac{|z|^{2k}e^{-\pi|z|^2}\cdot z}{z}
=
|z|^{2k}e^{-\pi|z|^2}
=
f(|z|).
\]
At the origin, the apparent singularity \(1/z\) is integrable against the vanishing factor
\(\Phi(|z|^2)\): since \(k\ge 0\) and \(s^k e^{-\pi s}\le s^k\) for \(s\ge 0\), we have
\(\Phi(t)=\int_0^t s^k e^{-\pi s}\,ds\le \int_0^t s^k\,ds = t^{k+1}/(k+1)=O(t^{k+1})\) as
\(t\to 0\). Hence \(\Psi(z)=O(|z|^{2k+1})\) near \(z=0\), so \(\Psi\in L^\infty_{\mathrm{loc}}\)
(in fact continuous, with \(\Psi(0)=0\)). Consequently, the identity
\(\partial_{\bar z}\Psi=f(|z|)\) persists in the distributional sense on all of \(U\); no extra
\(\delta_0\) contribution arises at the origin.

Recall also the standard identity
\[
\partial_{\bar z}\!\left(\frac{1}{z}\right)=\pi\delta_0
\qquad\text{in }\mathcal D'(\R^2),
\]
which is equivalent to the fact that \(\frac{1}{\pi z}\) is a fundamental solution of
\(\partial_{\bar z}\); equivalently, \(\Delta\log|z|=4\partial_z\partial_{\bar z}\log|z|=2\pi\delta_0\)
combined with \(\partial_z\log|z|=\frac{1}{2z}\). Now set
\[
F(z):=4\partial_z u(z)-\Psi(z)+\frac{c}{\pi z},
\qquad z\in U\setminus\{0\}.
\]
We first check that \(F\) defines a distribution on all of \(U\) (a~priori it is given only on
\(U\setminus\{0\}\)). From \eqref{eq:explicit-u-second-proof} we have, near \(z=0\),
\[
4\partial_z u(z)
=
\frac{2}{\pi}\partial_z\!\left(\int_{\R^2}\log|z-z'|\,g(z')\,dA(z')\right)-\frac{c}{\pi z},
\]
where the first term is locally bounded near \(z=0\) (the Cauchy-type integral
\(\int (z-z')^{-1} g(z')\,dA(z')\) of a bounded compactly supported function is locally
integrable, by the same \(L^1_{\mathrm{loc}}\)-kernel argument as above). Adding \(-\Psi\)
(continuous with \(\Psi(0)=0\)) and \(c/(\pi z)\) cancels the explicit \(1/z\)-singularity, so
\(F\) is locally bounded near the origin and hence defines a distribution on \(U\).

Using \(\Delta=4\partial_z\partial_{\bar z}\), the relation \(\partial_{\bar z}(1/z)=\pi\delta_0\),
the computation of \(\partial_{\bar z}\Psi\) above, and \eqref{eq:potato-second-proof}, we
compute, in \(\mathcal D'(U)\),
\[
\partial_{\bar z}F
=
4\partial_z\partial_{\bar z}u-\partial_{\bar z}\Psi+\frac{c}{\pi}\partial_{\bar z}\!\left(\frac{1}{z}\right)
=
\Delta u-f(|z|)+c\,\delta_0
=
\bigl(f(|z|)-c\delta_0\bigr)-f(|z|)+c\delta_0
=0.
\]
The singular term \(-c\delta_0\) in \eqref{eq:potato-second-proof}, arriving through
\(4\partial_z\partial_{\bar z}u=\Delta u\), is thus exactly cancelled by
\((c/\pi)\partial_{\bar z}(1/z)=c\delta_0\). Hence \(F\) is a distributional solution of the
Cauchy--Riemann equation \(\partial_{\bar z}F=0\) on \(U\), and by Weyl's lemma for
\(\partial_{\bar z}\) (equivalently, hypoellipticity of the Cauchy--Riemann operator) it is
represented by a genuine holomorphic function on \(U\).

Define
\[
W(z):=\pi z\,F(z).
\]
Then \(W\) is holomorphic on \(U\) and \(W(0)=0\). Since \(\partial_z u\) is continuous up to
\(\partial U\), so is \(W\), and by \eqref{eq:dz-zero-second-proof},
\[
W|_{\partial U}
=
\pi z\left(4\partial_z u-\frac{\Phi(|z|^2)}{z}+\frac{c}{\pi z}\right)\Big|_{\partial U}
=
c-\pi\Phi(|z|^2).
\]
In particular, \(W|_{\partial U}\) is real-valued. The imaginary part of \(W\) is therefore
harmonic in \(U\), continuous up to \(\partial U\), and vanishes on \(\partial U\). By the
maximum principle,
\[
\Im W\equiv 0
\qquad\text{in }U.
\]
Since a holomorphic function with zero imaginary part is constant, there exists \(\kappa\in\R\)
such that
\[
W\equiv \kappa
\qquad\text{in }U.
\]

Restricting to the boundary, and using that \(W\) is continuous up to \(\partial U\) with
boundary value \(c-\pi\Phi(|z|^2)\), we obtain
\[
c-\pi\Phi(|z|^2)=\kappa
\qquad\text{for all }z\in\partial U.
\]
The function \(t\mapsto \Phi(t)=\int_0^t s^k e^{-\pi s}\,ds\) has derivative
\(\Phi'(t)=t^k e^{-\pi t}>0\) for \(t>0\), hence is strictly increasing on \([0,\infty)\). The
identity above therefore forces \(|z|^2\) to take a single value on \(\partial U\), i.e.\ \(|z|\)
is constant on \(\partial U\). Consequently \(\partial U\) is contained in a circle centered at
the origin. Let \(R>0\) be such that \(\partial U\subset \{|z|=R\}\). Since \(U\) is open and
\(U\cap\partial U=\varnothing\), we have \(U\subset \{|z|<R\}\cup\{|z|>R\}\); since \(U\) is
connected and the two pieces are disjoint open sets, \(U\) must lie entirely in one of them, and
boundedness of \(U\) forces \(U\subset \{|z|<R\}\). If this inclusion were strict, pick
\(z_1\in\{|z|<R\}\setminus U\) and \(z_0\in U\). The straight segment from \(z_0\) to \(z_1\) is
contained in the convex set \(\{|z|<R\}\), and as it joins a point of \(U\) to a point of its
complement it must cross \(\partial U\) at some \(z_*\); but then \(z_*\in\partial U\cap\{|z|<R\}\),
contradicting \(\partial U\subset \{|z|=R\}\). Therefore
\[
U=\{|z|<R\}
\]
that is, \(U\) is a disk.
\end{proof}

\begin{remark}\label{rem:bookkeeping-no-regularity}
The two proofs use the boundary assumptions in rather different ways, and it is instructive to
keep careful track of the regularity bookkeeping.

In the first proof, once the logarithmic potential \(\Psi_U\) is written explicitly, no elliptic
boundary regularity is needed to conclude that \(\Psi_U\in C^1(\R^2\setminus\{0\})\): this follows
directly from convolution with the locally integrable kernel \(\nabla\log|z|\), exactly as in the
\(L^1_{\mathrm{loc}}\)-translation argument used here for \eqref{eq:explicit-u-second-proof}. Thus
the local radiality argument itself only uses continuity of the gradient up to the boundary. The
genuine extra input appears only in the final geometric step, where one needs that, near a suitable
point \(x_0\in \partial U\), the set \(\partial U\cap B_r(x_0)\) contains a nontrivial boundary
arc, so that the radii attained there form an interval. Accordingly, the first proof does not
really need \(C^2\) regularity; it works under any hypothesis guaranteeing such a local arc
structure, for instance when \(U\) is a Jordan domain. In particular, any Lipschitz, \(C^1\), or
\(C^2\) boundary is more than sufficient.

By contrast, the second proof does not use any boundary regularity at all. The explicit formula
\eqref{eq:explicit-u-second-proof} already yields \(u\in C^1(\R^2\setminus\{0\})\), and since
\(u\equiv 0\) on the exterior open set \(\R^2\setminus \overline U\), continuity implies that both
\(u\) and \(\nabla u\) vanish on \(\partial U\) -- precisely the boundary information packaged in
\eqref{eq:dz-zero-second-proof}. This is exactly the input needed to construct the holomorphic
function \(W=\pi z F\) and conclude that \(|z|\) is constant on \(\partial U\). Hence the second
proof recovers the theorem under the original assumptions of Abreu and D\"orfler
\cite{Abreu-Doerfler}, namely for arbitrary bounded simply connected domains, with no boundary
smoothness hypothesis -- this is the content of
Theorem~\ref{thm:eig-loc-U-strong}. The mechanism is also conceptually closer to the classical
quadrature-domain rigidity results of \cite{Aharonov-Schiffer-Zalcman,Gustafsson,Karp}, where the
existence of a holomorphic function on \(U\) with real boundary values forces the boundary to lie
on a level set of a real-analytic function, here the elementary radial function
\(z\mapsto |z|^2\).

To make the comparison explicit: the only step at which the first proof
genuinely uses \(\partial U\in C^2\) is in the open-mapping argument that
extracts a nontrivial open interval of radii from a boundary parametrization
\(\gamma:(-\varepsilon,\varepsilon)\to\partial U\). In the second proof, this
geometric step is replaced by the harmonic-function-with-real-boundary-values
mechanism, which is purely topological (continuity of \(W=\pi zF\) up to
\(\partial U\) plus the maximum principle on the open set \(U\)) and is
therefore insensitive to the regularity of \(\partial U\). It is in this
precise sense that Theorem~\ref{thm:eig-loc-U-strong} drops the \(C^2\)
hypothesis present in Theorem~\ref{thm:eig-loc-U} while delivering the same
conclusion.
\end{remark}

% ==============================================================
% Section 5
% ==============================================================

\section{Proof of Theorem \ref{thm:GGRT-sharp}}\label{sec:GGRT-sharp}

We prove that the quantitative stability estimate in Corollary~1.4 of
\cite{Gomez-Guerra-Ramos-Tilli}, which builds on the Faber--Krahn rigidity
result of \cite{Nicola-Tilli} characterizing the disk as the unique optimizer
of the first localization eigenvalue (see also the foundational work of
\cite{Daubechies} on the spectrum of the Daubechies localization operator on
the disk), is sharp. The proof proceeds by constructing a family of domains
which are perturbations of the disk, whose first localization eigenvalue has
the same first-order behaviour as the disk, but whose distance to the class of
disks is of order $\varepsilon$.

Before turning to the construction, we collect four supporting lemmas. They
furnish, respectively, (i)~the identification of the constructed eigenvalue
with the \emph{principal} eigenvalue of \(\mathcal L_{U_\varepsilon}\) via an
analytic-perturbation argument from the disk, (ii)~the
order-\(\varepsilon^2\) effect of the area-normalizing dilation on the
principal eigenvalue, (iii)~the Reynolds transport / Hadamard
shape-derivative formula in the regularity used here, and (iv)~the explicit
symmetric-difference lower bound which witnesses that second-order harmonics
cannot be eliminated by translations of the disk.

\subsection{Spectral, dilational and shape-derivative preliminaries}
\label{subsec:GGRT-preliminaries}

Throughout this subsection we let \(D_1\subset \C\) denote the closed unit
disk centered at the origin. Recall that the localization operator
\(\mathcal L_U\) on \(\mathcal F^2(\C)\), with \(U\subset \C\) a bounded
measurable set, is the self-adjoint compact Toeplitz-type operator
\[
(\mathcal L_U F)(z)
:=
\int_U F(\zeta)\,e^{\pi z\overline\zeta}\,e^{-\pi|\zeta|^2}\,dA(\zeta),
\]
whose eigenvalues form a non-increasing sequence
\(\lambda_1(U)\ge \lambda_2(U)\ge\cdots\to 0\); its principal (largest)
eigenvalue is \(\lambda_1(U)\).

For the unit disk \(U=D_1\), the operator \(\mathcal L_{D_1}\) is diagonalized
by the orthonormal monomial basis
\(\{e_k(z)=(\pi^k/k!)^{1/2}z^k\}_{k\ge 0}\) of \(\mathcal F^2(\C)\)
(cf.~\cite{Daubechies}), with eigenvalues
\begin{equation}\label{eq:disk-eigenvalues-explicit}
\mu_k:=\frac{\gamma(k+1,\pi)}{k!}
=
1-e^{-\pi}\sum_{j=0}^{k}\frac{\pi^j}{j!},
\qquad k\ge 0,
\end{equation}
where \(\gamma(s,x)=\int_0^x t^{s-1}e^{-t}\,dt\) is the lower incomplete gamma
function. The sequence \((\mu_k)_{k\ge 0}\) is \emph{strictly decreasing}:
\(\mu_k-\mu_{k+1}=e^{-\pi}\pi^{k+1}/(k+1)!>0\). In particular,
\begin{equation}\label{eq:disk-spectral-gap}
\mu_0=1-e^{-\pi}=\lambda_0,
\qquad
\mu_1=1-(1+\pi)e^{-\pi},
\qquad
\mu_0-\mu_1=\pi e^{-\pi}>0,
\end{equation}
so the disk has a strict spectral gap above its principal eigenvalue
\(\mu_0\).

\medskip

\begin{lemma}[Spectral continuity and principal-eigenvalue identification]
\label{lem:spectral-continuity}
Let \((U_\varepsilon)_{|\varepsilon|<\varepsilon_0}\) be a family of bounded
measurable sets with \(U_0=D_1\) and
\(|U_\varepsilon\triangle D_1|\to 0\) as \(\varepsilon\to 0\). Then for every
\(k\ge 1\),
\begin{equation}\label{eq:eigenvalue-continuity}
\lambda_k(U_\varepsilon)\xrightarrow[\varepsilon\to 0]{}\mu_{k-1},
\end{equation}
with \(\mu_{k-1}\) given by \eqref{eq:disk-eigenvalues-explicit}. Hence there
exists \(\varepsilon_*>0\) such that, for all \(|\varepsilon|<\varepsilon_*\),
\begin{equation}\label{eq:gap-preservation}
\lambda_2(U_\varepsilon)
<
\frac{\mu_0+\mu_1}{2}
<
\lambda_1(U_\varepsilon),
\end{equation}
and the principal eigenvalue is the unique eigenvalue of
\(\mathcal L_{U_\varepsilon}\) lying in
\([\mu_0-\tfrac{\pi e^{-\pi}}{4},\mu_0+\tfrac{\pi e^{-\pi}}{4}]\).

Consequently, for the family \(U_\varepsilon\) of Theorem~\ref{thm:perturb}
applied with \(\lambda=\lambda_0=\mu_0\) and
\(P_\varepsilon(w)=1+\varepsilon w^2\), the eigenvalue \(\lambda_0\) produced
by Theorem~\ref{thm:perturb} is the principal eigenvalue of
\(\mathcal L_{U_\varepsilon}\), and \(P_\varepsilon\) is a corresponding
first eigenfunction.
\end{lemma}

\begin{proof}
For any bounded measurable \(U\subset \C\), the operator \(\mathcal L_U\) is
positive semi-definite, compact, and depends Lipschitz-continuously on
\(\mathbf 1_U\) in operator norm: for any \(F\in \mathcal F^2(\C)\),
\[
\langle (\mathcal L_{U_\varepsilon}-\mathcal L_{D_1})F,F\rangle
=
\int_\C \bigl(\mathbf 1_{U_\varepsilon}(\zeta)
-\mathbf 1_{D_1}(\zeta)\bigr)|F(\zeta)|^2 e^{-\pi|\zeta|^2}\,dA(\zeta),
\]
and by the standard Fock-space pointwise bound
\(|F(\zeta)|^2 e^{-\pi|\zeta|^2}\le \|F\|_{\mathcal F^2}^2\) (cf.\
Lemma~\ref{lem:Fock-basic}) one obtains
\[
\|\mathcal L_{U_\varepsilon}-\mathcal L_{D_1}\|_{\mathrm{op}}
\le
|U_\varepsilon\triangle D_1|.
\]
By Weyl's inequality (the \(\min\!-\!\max\) characterization of eigenvalues
of compact self-adjoint operators),
\[
|\lambda_k(U_\varepsilon)-\lambda_k(D_1)|
\le
\|\mathcal L_{U_\varepsilon}-\mathcal L_{D_1}\|_{\mathrm{op}}
\le
|U_\varepsilon\triangle D_1|
\xrightarrow[\varepsilon\to 0]{}0,
\]
which proves \eqref{eq:eigenvalue-continuity}. The gap inequality
\eqref{eq:gap-preservation} then follows by combining this convergence with
the strict gap \(\mu_0-\mu_1=\pi e^{-\pi}>0\) of
\eqref{eq:disk-spectral-gap}: choose \(\varepsilon_*\) so small that
\(|\lambda_1(U_\varepsilon)-\mu_0|<\pi e^{-\pi}/4\) and
\(|\lambda_2(U_\varepsilon)-\mu_1|<\pi e^{-\pi}/4\) for
\(|\varepsilon|<\varepsilon_*\); then any eigenvalue \(\lambda\) of
\(\mathcal L_{U_\varepsilon}\) lying in
\([\mu_0-\pi e^{-\pi}/4,\mu_0+\pi e^{-\pi}/4]\) is greater than
\(\mu_1+\pi e^{-\pi}/4\ge \lambda_2(U_\varepsilon)\), hence equal to
\(\lambda_1(U_\varepsilon)\) by the ordering of the spectrum.

The same conclusion can be obtained, in a more structural form, from analytic
perturbation theory in the sense of Kato \cite{Kato}: by Theorem~\ref{thm:perturb}
the family \(U_\varepsilon\) depends in a \(C^1\) fashion on \(\varepsilon\)
(in fact analytically, since the Banach-space implicit-function theorem
applied to a real-analytic moment map produces a real-analytic branch), so
\(\varepsilon\mapsto \mathcal L_{U_\varepsilon}\) is a real-analytic family
of compact self-adjoint operators in \(\mathcal F^2(\C)\). The principal
eigenvalue \(\mu_0\) of \(\mathcal L_{D_1}\) is simple (its eigenspace is the
one-dimensional space \(\C\cdot e_0\)) and isolated by
\eqref{eq:disk-spectral-gap}. The Kato selection theorem
(\cite[Ch.~VII, Thm.~1.8]{Kato}) thus produces a real-analytic branch
\(\varepsilon\mapsto (\widetilde\lambda(\varepsilon),
\widetilde F(\varepsilon))\) of eigenpairs with
\(\widetilde\lambda(0)=\mu_0\), \(\widetilde F(0)=e_0\), and
\(\widetilde\lambda(\varepsilon)=\lambda_1(U_\varepsilon)\) for all
sufficiently small \(\varepsilon\). The eigenpair \((\lambda_0,P_\varepsilon)\)
constructed in Theorem~\ref{thm:perturb} satisfies \(P_0\equiv 1=e_0\) and
depends continuously on \(\varepsilon\); by uniqueness of the analytic branch
within the gap interval, it agrees with the Kato branch. In particular,
\(\lambda_0=\widetilde\lambda(\varepsilon)=\lambda_1(U_\varepsilon)\) for
\(\varepsilon\) small.
\end{proof}

\begin{remark}\label{rem:disk-eigenvalues-numbers}
The numbers \(\mu_k\) of \eqref{eq:disk-eigenvalues-explicit} are the
classical Daubechies disk eigenvalues; the explicit values
\(\mu_0=1-e^{-\pi}\) and \(\mu_1=1-(1+\pi)e^{-\pi}\) appear ubiquitously in
the time--frequency literature.
\end{remark}

\medskip

\begin{lemma}[Effect of the area-normalizing dilation]
\label{lem:dilation-eigenvalue}
For any bounded measurable set \(U\subset \C\) with \(|U|>0\) and any
\(t>0\), the eigenvalues of \(\mathcal L_{tU}\) are real-analytic functions
of \(t\) on \((0,\infty)\). In the special case \(U=D_1\), the principal
eigenvalue is given by the explicit closed form
\begin{equation}\label{eq:dilated-disk-formula}
\lambda_1(tD_1)=1-e^{-\pi t^2},
\qquad t>0,
\end{equation}
attained on the constant eigenfunction \(F\equiv 1\). In particular, for
\(r_\varepsilon=1+O(\varepsilon^2)\),
\begin{equation}\label{eq:disk-dilation-O-eps2}
\lambda_1(r_\varepsilon D_1)
=
1-e^{-\pi r_\varepsilon^2}
=
\lambda_0+2\pi e^{-\pi}(r_\varepsilon-1)+O((r_\varepsilon-1)^2)
=
\lambda_0+O(\varepsilon^2).
\end{equation}

For the family \(U_\varepsilon\) of Theorem~\ref{thm:perturb} applied with
\(P_\varepsilon(w)=1+\varepsilon w^2\), one has
\(|U_\varepsilon|=\pi+O(\varepsilon^2)\) (see Step~3 of the proof of
Theorem~\ref{thm:GGRT-sharp} below), and the area-normalizing dilation
factor \(r_\varepsilon=\sqrt{\pi/|U_\varepsilon|}=1+O(\varepsilon^2)\)
satisfies
\begin{equation}\label{eq:dilation-eigenvalue-control}
\bigl|\lambda_1(r_\varepsilon U_\varepsilon)-\lambda_1(U_\varepsilon)\bigr|
=
O(\varepsilon^2).
\end{equation}
\end{lemma}

\begin{proof}
The change of variable \(\zeta=t\zeta'\) in
\((\mathcal L_{tU}F)(z)=\int_{tU}F(\zeta)e^{\pi z\overline\zeta}e^{-\pi|\zeta|^2}\,dA(\zeta)\)
gives
\[
(\mathcal L_{tU}F)(z)
=
t^2\int_U F(t\zeta')\,e^{\pi z t\overline{\zeta'}}\,e^{-\pi t^2|\zeta'|^2}\,dA(\zeta'),
\]
which depends real-analytically on \(t\); hence \(\mathcal L_{tU}\) is a
real-analytic family of compact self-adjoint operators (in fact in trace
class), and by Kato \cite[Ch.~VII]{Kato} its eigenvalues vary analytically
in \(t\).

For \(U=D_1\), the constant function \(F\equiv 1\) satisfies, by direct
integration,
\(
(\mathcal L_{tD_1}\,1)(0)
=
\int_{tD_1}e^{-\pi|\zeta|^2}\,dA(\zeta)
=
1-e^{-\pi t^2}.
\)
Equality of \((\mathcal L_{tD_1}\,1)(z)\) with \((1-e^{-\pi t^2})\cdot 1\) for
all \(z\in\C\) follows from the fact that \(F\equiv 1=e_0\) is the principal
eigenfunction of the rotationally symmetric operator \(\mathcal L_{tD_1}\).
This gives \eqref{eq:dilated-disk-formula}; Taylor expansion at \(t=1\)
yields \eqref{eq:disk-dilation-O-eps2}.

For \eqref{eq:dilation-eigenvalue-control}, the dilation
\(F\mapsto F(r_\varepsilon\,\cdot)\) intertwines \(\mathcal L_{r_\varepsilon
U_\varepsilon}\) with an analytic perturbation of \(\mathcal L_{U_\varepsilon}\)
of operator-norm size \(O(|r_\varepsilon-1|)=O(\varepsilon^2)\); Weyl's
inequality then yields \eqref{eq:dilation-eigenvalue-control}.
\end{proof}

\begin{remark}\label{rem:dilation-explicit}
For the proof of Theorem~\ref{thm:GGRT-sharp} only
\eqref{eq:disk-dilation-O-eps2} is strictly required, since one combines it
with the exact identity \(\lambda_1(U_\varepsilon)=\lambda_0\) furnished by
Theorem~\ref{thm:perturb} and Lemma~\ref{lem:spectral-continuity}. The full
Lemma~\ref{lem:dilation-eigenvalue} is recorded for completeness, as it
isolates the (otherwise implicit) claim that area normalization perturbs
the eigenvalue only at second order.
\end{remark}

\medskip

\begin{lemma}[Reynolds transport / Hadamard shape derivative for normal-graph
perturbations of the disk]\label{lem:hadamard-shape-derivative}
Let \((\Omega_\varepsilon)_{|\varepsilon|<\varepsilon_0}\) be a family of
bounded \(C^1\) domains in \(\C\), with \(\Omega_0\) of class \(C^1\),
outward unit normal \(\nu\), and arc-length measure \(d\mathcal H^1\), and
represented as the image of a one-parameter family of \(C^1\)-diffeomorphisms
\(V_\varepsilon\) of \(\C\), \(V_0=\mathrm{id}\), with deformation field
\[
W(z):=\partial_\varepsilon V_\varepsilon(z)\bigl|_{\varepsilon=0}
\in C^1(\overline{\Omega_0};\C),
\]
and normal velocity \(V_\nu(z):=W(z)\cdot\nu(z)\in C^1(\partial\Omega_0)\).
Then for any \(H\) admitting a \(C^1\) extension to a neighborhood of
\(\overline{\Omega_0}\),
\begin{equation}\label{eq:reynolds-formula}
\frac{d}{d\varepsilon}\Big|_{\varepsilon=0}
\int_{\Omega_\varepsilon} H(z)\,dA(z)
=
\int_{\partial\Omega_0}V_\nu(z)\,H(z)\,d\mathcal H^1(z).
\end{equation}

In the special case of a normal-graph perturbation of the unit disk,
\(\partial\Omega_\varepsilon=\{(1+\varphi_\varepsilon(y))y:y\in\mathbb S^1\}\)
with \(\varepsilon\mapsto \varphi_\varepsilon\) of class \(C^1\) into
\(C^1(\mathbb S^1;\R)\) and \(\varphi_0\equiv 0\), the boundary deformation
field equals \(W(y)=\dot\varphi_0(y)y\), the normal velocity is
\(V_\nu(y)=\dot\varphi_0(y)\), and \eqref{eq:reynolds-formula} specializes to
\begin{equation}\label{eq:reynolds-disk}
\frac{d}{d\varepsilon}\Big|_{\varepsilon=0}
\int_{\Omega_\varepsilon} H(z)\,dA(z)
=
\int_{\mathbb S^1}\dot\varphi_0(y)\,H(y)\,d\mathcal H^1(y).
\end{equation}

Applied to \(H(z)=|F_0(z)|^2 e^{-\pi|z|^2}\) where \(F_0\equiv 1\) is the
disk's principal eigenfunction, \eqref{eq:reynolds-disk} together with the
Hadamard shape-derivative formula for the principal eigenvalue of a
self-adjoint Toeplitz-type operator (cf.\ Step~3 of the proof of the
local-maximizer theorem in Section~\ref{sec:local-max}, and
\cite[Thm.~5.7.1]{Henrot-Pierre} or \cite{Sokolowski-Zolesio} for the general
formalism) yields the first variation of the principal eigenvalue along the
family \(U_\varepsilon\),
\begin{equation}\label{eq:hadamard-eigenvalue}
\frac{d}{d\varepsilon}\Big|_{\varepsilon=0}\lambda_1(U_\varepsilon)
=
\int_{\partial D_1}|F_0(y)|^2 e^{-\pi|y|^2}\,V_\nu(y)\,d\mathcal H^1(y)
=
e^{-\pi}\int_{\mathbb S^1}\dot\varphi_0(y)\,d\mathcal H^1(y).
\end{equation}
\end{lemma}

\begin{proof}
The Reynolds transport formula \eqref{eq:reynolds-formula} for a \(C^1\)
deformation of a bounded \(C^1\) domain is classical; see, for example,
\cite[\S 5.9]{Henrot-Pierre} or \cite[Ch.~2]{Sokolowski-Zolesio}. We sketch
the polar-coordinate derivation in the case of a normal-graph perturbation
of the unit disk, which is the form actually used here. In polar
coordinates \(z=re^{it}\),
\[
\int_{\Omega_\varepsilon}H(z)\,dA(z)
=
\int_0^{2\pi}\int_0^{1+\varphi_\varepsilon(e^{it})}H(re^{it})\,r\,dr\,dt.
\]
By the \(C^1\) dependence of \(\varepsilon\mapsto \varphi_\varepsilon\) into
\(C^1(\mathbb S^1)\) and the fundamental theorem of calculus,
\[
\frac{d}{d\varepsilon}\Big|_{\varepsilon=0}\int_{\Omega_\varepsilon}H\,dA
=
\int_0^{2\pi}\dot\varphi_0(e^{it})\,H(e^{it})\,(r)\Big|_{r=1}\,dt
=
\int_{\mathbb S^1}\dot\varphi_0(y)\,H(y)\,d\mathcal H^1(y),
\]
which is \eqref{eq:reynolds-disk}.

For the eigenvalue identity \eqref{eq:hadamard-eigenvalue}, the principal
eigenfunction \(F_\varepsilon\) of \(\mathcal L_{U_\varepsilon}\) depends
real-analytically on \(\varepsilon\) by Lemma~\ref{lem:spectral-continuity}
and the Kato selection theorem; we may take it
\(L^2(\C, e^{-\pi|z|^2}dA)\)-normalized. Differentiating
\(\lambda_1(U_\varepsilon)\|F_\varepsilon\|^2
=
\int_{U_\varepsilon}|F_\varepsilon|^2 e^{-\pi|z|^2}dA\)
in \(\varepsilon\) at \(\varepsilon=0\), using
\(\partial_\varepsilon\|F_\varepsilon\|^2|_{\varepsilon=0}=0\) and the
self-adjointness identity
\(\langle (\mathcal L_{D_1}-\mu_0\mathrm{Id})F_0,\partial_\varepsilon
F_\varepsilon|_0\rangle=0\), the only surviving contribution is the boundary
term, namely
\[
\frac{d}{d\varepsilon}\Big|_{\varepsilon=0}\lambda_1(U_\varepsilon)
=
\frac{d}{d\varepsilon}\Big|_{\varepsilon=0}
\int_{U_\varepsilon}|F_0|^2 e^{-\pi|z|^2}\,dA(z),
\]
to which \eqref{eq:reynolds-formula} applies with
\(H=|F_0|^2 e^{-\pi|z|^2}\). Since \(F_0\equiv 1\) and \(|y|=1\) on
\(\mathbb S^1\), this gives \eqref{eq:hadamard-eigenvalue}. The corresponding
parallel computation in Step~3 of the proof of the local-maximizer theorem
(Section~\ref{sec:local-max}) spells out the divergence-theorem manipulation
in greater detail.
\end{proof}

\medskip

\begin{lemma}[Symmetric-difference lower bound: second-order harmonics
cannot be eliminated by translations]\label{lem:symmetric-difference}
Let \(\dot\varphi_0\in C^1(\mathbb S^1;\R)\) be of pure second-harmonic
form,
\begin{equation}\label{eq:second-harmonic-form}
\dot\varphi_0(e^{it})=a\cos(2t)+b\sin(2t),
\qquad (a,b)\in\R^2\setminus\{(0,0)\},
\end{equation}
and fix \(K>0\). Then there exists a constant \(\delta_K>0\), depending only
on \((a,b)\) and \(K\), with the explicit lower bound
\begin{equation}\label{eq:explicit-delta-K-lower}
\delta_K
\ge
\frac{\pi(a^2+b^2)}{4(K+1)+2\sqrt{a^2+b^2}},
\end{equation}
such that, for every \(\theta\in [0,2\pi)\) and every \(\eta\in [-K,K]\),
\begin{equation}\label{eq:l1-uniform-lower}
\int_{\mathbb S^1}\bigl|\dot\varphi_0(y)-\eta\,\Re(e^{-i\theta}y)\bigr|
\,d\mathcal H^1(y)\ge \delta_K.
\end{equation}

Consequently, for the area-normalized family \(\widetilde U_\varepsilon\) of
Theorem~\ref{thm:perturb} with second-harmonic
\(\dot\varphi_0\) of the form \eqref{eq:second-harmonic-form} and
\((a,b)\neq (0,0)\), there exist constants
\(c=c(a,b,K)>0\) and \(c'=c'(a,b)>0\) and a threshold \(\varepsilon_1>0\)
such that, for all \(0<|\varepsilon|<\varepsilon_1\),
\begin{equation}\label{eq:near-disks-explicit}
|\widetilde U_\varepsilon\triangle (D_1+a)|\ge c\,|\varepsilon|
\qquad
\text{whenever }|a|\le K|\varepsilon|,
\end{equation}
and, combining with the comparison for distant disks,
\begin{equation}\label{eq:total-lower}
\inf_{\substack{D\subset\C\\|D|=\pi}}
|\widetilde U_\varepsilon\triangle D|\ge c'|\varepsilon|.
\end{equation}
\end{lemma}

\begin{proof}
Define
\(g^{\theta,\eta}(t):=a\cos 2t+b\sin 2t-\eta\cos(t-\theta).\)
Then \(g^{\theta,\eta}\) lies in the four-dimensional subspace
\(V:=\mathrm{span}\{\cos t,\sin t,\cos 2t,\sin 2t\}\subset L^1(\mathbb S^1)\).
Expanding in the orthogonal basis
\(\{\cos t,\sin t,\cos 2t,\sin 2t\}\) of \(L^2(\mathbb S^1)\) (each of squared
\(L^2\)-norm \(\pi\)),
\[
g^{\theta,\eta}(t)
=
-\eta\cos\theta\cdot\cos t-\eta\sin\theta\cdot\sin t
+a\cos 2t+b\sin 2t,
\]
hence by Parseval
\[
\|g^{\theta,\eta}\|_{L^2(\mathbb S^1)}^2
=
\pi(\eta^2+a^2+b^2)
\ge
\pi(a^2+b^2),
\]
the second-harmonic coefficients \((a,b)\) being independent of
\((\theta,\eta)\). The crucial structural feature is that the orthogonal
projection of \(g^{\theta,\eta}\) onto \(\mathrm{span}\{\cos 2t,\sin 2t\}\)
equals \(a\cos 2t+b\sin 2t\) for every \((\theta,\eta)\); translations of
the disk shift only the first-harmonic coefficients of the boundary
perturbation.

For the \(L^1\) lower bound, recall the elementary inequality
\(\|g\|_{L^1(\mathbb S^1)}\ge \|g\|_{L^2(\mathbb S^1)}^2/\|g\|_{L^\infty(\mathbb S^1)}\),
valid for any \(g\in L^\infty(\mathbb S^1)\setminus\{0\}\). For
\(g=g^{\theta,\eta}\),
\[
\|g^{\theta,\eta}\|_{L^\infty(\mathbb S^1)}
\le
|a|+|b|+|\eta|
\le
\sqrt{2(a^2+b^2)}+K
\le
2\sqrt{a^2+b^2}+2(K+1).
\]
Hence
\[
\|g^{\theta,\eta}\|_{L^1(\mathbb S^1)}
\ge
\frac{\pi(a^2+b^2)}{4(K+1)+2\sqrt{a^2+b^2}},
\]
which is \eqref{eq:explicit-delta-K-lower}, and
\eqref{eq:l1-uniform-lower} follows.

For \eqref{eq:near-disks-explicit}, recall that for a disk \(D=D_1+a\) of
area \(\pi\) with \(a=\eta\varepsilon e^{i\theta}\) and \(|\eta|\le K\), the
translated set \(\widetilde U_\varepsilon-a\) is a normal graph over
\(\mathbb S^1\) with radial perturbation
\(\psi^{\theta,\eta}_\varepsilon(y)=\varepsilon g^{\theta,\eta}(y)+O(\varepsilon^2)\)
in \(C^1(\mathbb S^1)\), uniformly for \(|\eta|\le K\) (see Step~5 of the
proof of Theorem~\ref{thm:GGRT-sharp} below for the detailed expansion).
The polar-coordinate representation of the symmetric difference yields
\[
|\widetilde U_\varepsilon\triangle D|
=
\frac12\int_{\mathbb S^1}\bigl|2\varepsilon g^{\theta,\eta}(y)+O(\varepsilon^2)\bigr|
\,d\mathcal H^1(y)
\ge
|\varepsilon|\,\delta_K-O(\varepsilon^2),
\]
which is at least \(\frac12 |\varepsilon|\,\delta_K\) for
\(|\varepsilon|<\varepsilon_1\) sufficiently small. This proves
\eqref{eq:near-disks-explicit} with \(c=\frac12\,\delta_K\).

For \eqref{eq:total-lower}, we use the explicit symmetric-difference
formula for two unit disks: for \(a\in\C\) with \(|a|\le 2\),
\begin{equation}\label{eq:two-disks-symdif}
|D_1\triangle (D_1+a)|
=
2\pi-4\arccos(|a|/2)+2|a|\sqrt{1-|a|^2/4},
\end{equation}
which satisfies \(|D_1\triangle (D_1+a)|\ge \sqrt 3\,|a|\) for
\(|a|\le 1\); hence \(|D_1\triangle (D_1+a)|\ge c_0\min(|a|,1)\) with
absolute constant \(c_0=\sqrt 3\). Choose \(K\) so large that
\(c_0K\ge 1+C\), where \(C\) is the implicit constant in
\(|\widetilde U_\varepsilon\triangle D_1|\le C|\varepsilon|\) of Step~4 of
the proof of Theorem~\ref{thm:GGRT-sharp}. Then for \(|a|\ge K|\varepsilon|\),
\[
|\widetilde U_\varepsilon\triangle D|
\ge
|D_1\triangle D|-|\widetilde U_\varepsilon\triangle D_1|
\ge
c_0 K|\varepsilon|-C|\varepsilon|
\ge
|\varepsilon|.
\]
Combining with \eqref{eq:near-disks-explicit} for
\(|a|\le K|\varepsilon|\), \eqref{eq:total-lower} follows with
\(c'=\min\bigl(\tfrac 12\delta_K,1\bigr)\) and the explicit \(\delta_K\)
of \eqref{eq:explicit-delta-K-lower}.
\end{proof}

\begin{remark}[Translations cannot eliminate the second harmonic]
\label{rem:second-order-not-eliminated}
The structural fact made quantitative by
Lemma~\ref{lem:symmetric-difference} is that, in the polar-graph
representation of a small perturbation of \(D_1\), translations of the disk
contribute \emph{only} to the first Fourier harmonic \(\cos t,\sin t\) of
the radial perturbation, and have zero second-harmonic component. Hence any
non-trivial second-harmonic mode \((a,b)\neq (0,0)\) in \(\dot\varphi_0\)
is \emph{intrinsic to the shape}, and provides a lower bound on the
symmetric-difference distance to the entire family of disks of the same
area, of order proportional to \(|\varepsilon|\sqrt{a^2+b^2}\) (with
\(K\)-dependence given in \eqref{eq:explicit-delta-K-lower}).
\end{remark}

\subsection{Proof of Theorem~\ref{thm:GGRT-sharp}}
\label{subsec:GGRT-proof}

\begin{proof}[Proof of Theorem~\ref{thm:GGRT-sharp}]
Fix
\[
\lambda_0:=1-e^{-\pi},
\]
which is the eigenvalue of the localization operator of the unit disk $D_1$
associated with the ground state $h_0$. For $\varepsilon$ small, define
\[
P_\varepsilon(w):=1+\varepsilon w^2.
\]
By Theorem~\ref{thm:perturb}, applied with \(\lambda=\lambda_0\) and
\(P_\varepsilon(w)=1+\varepsilon w^2\), for all sufficiently small
\(|\varepsilon|\) there exists a domain \(U_\varepsilon\) such that
\begin{equation}\label{eq:functiona-P-eps-new}
\int_{U_\varepsilon} P_\varepsilon(z)e^{\pi \overline zw}e^{-\pi|z|^2}\,dA(z)
=
\lambda_0 P_\varepsilon(w),
\qquad w\in\C.
\end{equation}
Moreover, by construction, $U_\varepsilon$ is a $C^2$ perturbation of the unit
disk. Hence, after possibly shrinking the range of admissible $\varepsilon$,
its boundary can be written as
\begin{equation}\label{eq:def-u-eps-new}
\partial U_\varepsilon
=
\{(1+\varphi_\varepsilon(y))y:\ y\in \mathbb S^1\},
\end{equation}
where
\[
\varphi_\varepsilon\in C^2(\mathbb S^1),
\qquad
\|\varphi_\varepsilon\|_{C^2(\mathbb S^1)}\lesssim |\varepsilon|.
\]
The map
\[
\varepsilon\mapsto \varphi_\varepsilon
\]
may in fact be chosen \(C^1\) as a map from a neighborhood of \(0\) into
\(C^1(\mathbb S^1)\). To see this, we briefly retrace the proof of
Theorem~\ref{thm:perturb}. The construction is the disk moment-map
construction of Proposition~\ref{prop:disk-inverse-tailored}. Thus
\(\varphi_\varepsilon\) is obtained from an equation of the form
\(F(\varepsilon,\varphi)=0\), where
\[
F:(-\varepsilon_0,\varepsilon_0)\times \mathcal U\to \mathcal V
\]
is the \(C^1\) moment map between the analytic boundary spaces used there,
with \(F(0,0)=0\) and \(\partial_\varphi F(0,0)\) invertible by the explicit
Fourier diagonalization at the unit disk. Since the polynomial
\(P_\varepsilon(z)=1+\varepsilon z^2\)
depends polynomially on \(\varepsilon\), the dependence of \(F\) on
\(\varepsilon\) is \(C^\infty\). The \(C^1\) version of the implicit function
theorem in Banach spaces then yields a \(C^1\) branch
\(\varepsilon\mapsto \varphi_\varepsilon\) into \(C^1(\mathbb S^1)\). We
therefore write
\[
\dot\varphi_0(y):=
\left.\partial_\varepsilon\right|_{\varepsilon=0}\varphi_\varepsilon(y).
\]

\medskip
\noindent
{\bf Step 1: first variation of the eigenvalue identity.} We differentiate \eqref{eq:functiona-P-eps-new} at $\varepsilon=0$.
Since \(P_\varepsilon\to 1\) in \(C^\infty\) and
\(\varepsilon\mapsto \varphi_\varepsilon\) is \(C^1\) into \(C^1(\mathbb S^1)\),
all terms in \eqref{eq:functiona-P-eps-new} are differentiable at
\(\varepsilon=0\). Since $\partial U_\varepsilon$ is $C^2$ and admits the
explicit normal graph parametrization \eqref{eq:def-u-eps-new} over
$\mathbb S^1$ with $\varphi_\varepsilon$ depending $C^1$-smoothly on
$\varepsilon$, the hypotheses of
Lemma~\ref{lem:hadamard-shape-derivative} are satisfied with normal velocity
\(V_\nu(y)=\dot\varphi_0(y)\); the Reynolds transport identity \eqref{eq:reynolds-disk}
applies, and reduces here to a direct application of the fundamental theorem
of calculus in polar coordinates. Concretely, with
\(z=re^{it}\), for any smooth test function \(H\) we have
\[
\int_{U_\varepsilon} H(z)\,dA(z)
=
\int_0^{2\pi}\int_0^{1+\varphi_\varepsilon(e^{it})}
H(re^{it})\,r\,dr\,dt.
\]
Differentiating in \(\varepsilon\) at \(\varepsilon=0\) and using the
fundamental theorem of calculus,
\[
\left.\frac{d}{d\varepsilon}\right|_{\varepsilon=0}
\int_{U_\varepsilon} H(z)\,dA(z)
=
\int_0^{2\pi}\dot\varphi_0(e^{it})H(e^{it})\,dt
=
\int_{\mathbb S^1}\dot\varphi_0(z)H(z)\,d\mathcal H^1(z),
\]
where the factor \(r=1\) on the unit circle has been absorbed into the
arc-length measure. This is precisely Reynolds' transport identity:
\[
\left.\frac{d}{d\varepsilon}\right|_{\varepsilon=0}
\int_{U_\varepsilon} H(z)\,dA(z)
=
\int_{\mathbb S^1} \dot\varphi_0(z)H(z)\,d\mathcal H^1(z).
\]
Applying this to
\[
H(z)=e^{\pi \overline zw}e^{-\pi|z|^2},
\]
and differentiating the factor $P_\varepsilon(z)=1+\varepsilon z^2$, we obtain
\begin{equation}\label{eq:first-variation-identity-new}
\int_{\mathbb S^1}
\dot\varphi_0(z)e^{\pi \overline zw}e^{-\pi|z|^2}\,d\mathcal H^1(z)
+
\int_{D_1} z^2 e^{\pi \overline zw}e^{-\pi|z|^2}\,dA(z)
=
\lambda_0 w^2.
\end{equation}
Since $D_1$ is radial, the monomial $z^2$ is an eigenfunction of the
localization operator of $D_1$; therefore there exists $\lambda_2>0$ such that
\[
\int_{D_1} z^2 e^{\pi \overline zw}e^{-\pi|z|^2}\,dA(z)=\lambda_2 w^2.
\]
Hence \eqref{eq:first-variation-identity-new} becomes
\begin{equation}\label{eq:boundary-identity-new}
\int_{\mathbb S^1}
\dot\varphi_0(z)e^{\pi \overline zw}e^{-\pi|z|^2}\,d\mathcal H^1(z)
=
(\lambda_0-\lambda_2)w^2.
\end{equation}
In fact, \(\lambda_2\) can be computed explicitly. Expanding
\(e^{\pi \overline zw}=\sum_{n\geq 0}\frac{\pi^n}{n!}\overline z^{\,n}w^n\)
and using orthogonality of the monomials \(\overline z^{\,n}\) over the disk,
the only term contributing to \(w^2\) is the one with \(n=2\):
\[
\int_{D_1} z^2 e^{\pi \overline zw}e^{-\pi|z|^2}\,dA(z)
=
\frac{\pi^2}{2}w^2\int_{D_1}z^2\overline z^{\,2}e^{-\pi|z|^2}\,dA(z)
=
\frac{\pi^2}{2}w^2\int_{D_1}|z|^4 e^{-\pi|z|^2}\,dA(z).
\]
Passing to polar coordinates and integrating by parts twice,
\[
\int_{D_1}|z|^4 e^{-\pi|z|^2}\,dA(z)
=
2\pi\int_0^1 r^4 e^{-\pi r^2}\,r\,dr
=
\pi\int_0^1 s^2 e^{-\pi s}\,ds
\]
where we substituted \(s=r^2\). A direct computation, integrating by parts
twice, yields
\[
\pi\int_0^1 s^2 e^{-\pi s}\,ds
=
\frac{2}{\pi^2}\Bigl(1-\Bigl(1+\pi+\frac{\pi^2}{2}\Bigr)e^{-\pi}\Bigr).
\]
Multiplying by \(\frac{\pi^2}{2}\), we obtain
\[
\lambda_2
=
\frac{\pi^2}{2}\int_{D_1}|z|^4e^{-\pi|z|^2}\,dA(z)
=
1-\Bigl(1+\pi+\frac{\pi^2}{2}\Bigr)e^{-\pi}.
\]
Therefore
\[
\lambda_0-\lambda_2
=
(1-e^{-\pi})-\Bigl(1-\Bigl(1+\pi+\frac{\pi^2}{2}\Bigr)e^{-\pi}\Bigr)
=
\pi\Bigl(1+\frac{\pi}{2}\Bigr)e^{-\pi}>0,
\]
so the coefficient of \(w^2\) on the right-hand side is indeed nonzero.
In particular, since $|z|=1$ on $\mathbb S^1$, we may rewrite this as
\begin{equation}\label{eq:boundary-identity-circle-new}
e^{-\pi}
\int_{\mathbb S^1}
\dot\varphi_0(z)e^{\pi \overline zw}\,d\mathcal H^1(z)
=
(\lambda_0-\lambda_2)w^2.
\end{equation}

Setting $w=0$ gives
\begin{equation}\label{eq:cancellation-f-0-new}
\int_{\mathbb S^1}\dot\varphi_0\,d\mathcal H^1=0.
\end{equation}

\medskip
\noindent
{\bf Step 2: identification of the leading mode.} Expanding
\[
e^{\pi \overline zw}
=
\sum_{n\geq 0}\frac{\pi^n}{n!}\overline z^{\,n}w^n,
\]
and matching the coefficient of $w^n$ on both sides of
\eqref{eq:boundary-identity-circle-new}, we find
\[
\int_{\mathbb S^1}\dot\varphi_0(z)\overline z^{\,n}\,d\mathcal H^1(z)=0
\qquad \text{for all } n\neq 2,
\]
whereas the coefficient corresponding to $n=2$ equals
$\frac{2}{\pi^2}(\lambda_0-\lambda_2)e^\pi\neq 0$. Since on $\mathbb S^1$
we have $\overline z=e^{-it}$ when $z=e^{it}$, this says that the Fourier
coefficient $\widehat{\dot\varphi_0}(n)$ vanishes for every $n\neq 2$. Since
$\dot\varphi_0$ is real-valued, $\widehat{\dot\varphi_0}(-n)
=\overline{\widehat{\dot\varphi_0}(n)}$, so the $n=-2$ mode is also nonzero
and conjugate to the $n=2$ mode, while all other modes vanish. We conclude
that
\begin{equation}\label{eq:mode-decomposition-new}
\dot\varphi_0(e^{it})
=
a\cos(2t)+b\sin(2t)
\end{equation}
for some pair $(a,b)\neq (0,0)$. In particular,
\begin{equation}\label{eq:l1-nontrivial-new}
\int_{\mathbb S^1} |\dot\varphi_0|\,d\mathcal H^1>0.
\end{equation}

\medskip
\noindent
{\bf Step 3: normalization of the area.} The area of $U_\varepsilon$ is given by
\begin{equation}\label{eq:area-u-eps-new}
|U_\varepsilon|
=
\frac12\int_{\mathbb S^1} (1+\varphi_\varepsilon(y))^2\,d\mathcal H^1(y).
\end{equation}
Since
\[
\varphi_\varepsilon
=
\varepsilon \dot\varphi_0 + O(\varepsilon^2)
\quad \text{in } C^1(\mathbb S^1),
\]
and \eqref{eq:cancellation-f-0-new} gives the vanishing of the first-order
term, we obtain from \eqref{eq:area-u-eps-new}
\begin{equation}\label{eq:measure-close-u-eps-new}
|U_\varepsilon|=\pi+O(\varepsilon^2).
\end{equation}

Let
\[
r_\varepsilon:=\sqrt{\frac{\pi}{|U_\varepsilon|}},
\qquad
\widetilde U_\varepsilon:=r_\varepsilon U_\varepsilon.
\]
Then $|\widetilde U_\varepsilon|=\pi$, and by
\eqref{eq:measure-close-u-eps-new},
\[
r_\varepsilon=1+O(\varepsilon^2).
\]
Hence $\widetilde U_\varepsilon$ still admits a normal graph representation
\[
\partial \widetilde U_\varepsilon
=
\{(1+\widetilde\varphi_\varepsilon(y))y:\ y\in \mathbb S^1\},
\]
with
\[
\widetilde\varphi_\varepsilon
=
\varepsilon \dot\varphi_0 + O(\varepsilon^2)
\quad \text{in } C^1(\mathbb S^1).
\]
Thus the area normalization does not alter the first-order deformation.

\medskip
\noindent
{\bf Step 4: distance from the centered disk.} Since both $\widetilde U_\varepsilon$ and $D_1$ are star-shaped with respect to
the origin, the symmetric difference may be computed in polar coordinates:
\[
|\widetilde U_\varepsilon \triangle D_1|
=
\frac12\int_{\mathbb S^1}
\left|(1+\widetilde\varphi_\varepsilon(y))^2-1\right|
\,d\mathcal H^1(y).
\]
Since \(\widetilde\varphi_\varepsilon=\varepsilon\dot\varphi_0+O(\varepsilon^2)\)
in \(C^1(\mathbb S^1)\), we have in particular
\(\|\widetilde\varphi_\varepsilon\|_{L^\infty(\mathbb S^1)}\lesssim |\varepsilon|\),
whence \(\widetilde\varphi_\varepsilon^2=O(\varepsilon^2)\) in
\(L^\infty(\mathbb S^1)\). Hence
\[
(1+\widetilde\varphi_\varepsilon)^2-1
=
2\widetilde\varphi_\varepsilon+\widetilde\varphi_\varepsilon^2
=
2\varepsilon \dot\varphi_0 + O(\varepsilon^2)
\quad \text{in } L^\infty(\mathbb S^1),
\]
where the implied constant depends only on the \(C^1\)-norm bound on
\(\widetilde\varphi_\varepsilon\). Therefore
\[
|\widetilde U_\varepsilon \triangle D_1|
=
\frac12\int_{\mathbb S^1}
\left|2\varepsilon \dot\varphi_0 + O(\varepsilon^2)\right|
\,d\mathcal H^1.
\]
Set \(\alpha:=\int_{\mathbb S^1}|\dot\varphi_0|\,d\mathcal H^1\). By
\eqref{eq:l1-nontrivial-new}, \(\alpha>0\). The reverse triangle inequality in
\(L^1\) and the \(O(\varepsilon^2)\) remainder give
\[
\int_{\mathbb S^1}\bigl|2\varepsilon\dot\varphi_0+O(\varepsilon^2)\bigr|\,d\mathcal H^1
\geq
2|\varepsilon|\alpha-O(\varepsilon^2)
\]
and similarly the upper bound
\[
\int_{\mathbb S^1}\bigl|2\varepsilon\dot\varphi_0+O(\varepsilon^2)\bigr|\,d\mathcal H^1
\leq
2|\varepsilon|\alpha+O(\varepsilon^2).
\]
Consequently there exist constants $c,C>0$ such that
\begin{equation}\label{eq:distance-centered-disk-new}
c|\varepsilon|
\leq
|\widetilde U_\varepsilon \triangle D_1|
\leq
C|\varepsilon|
\end{equation}
for all sufficiently small $\varepsilon$.

\medskip
\noindent
{\bf Step 5: comparison with arbitrary disks.} Let $D$ be any disk of area $\pi$. Then $D=D_1+a$ for some $a\in \C$. We first consider disks whose centers are not too close to the origin.
Since
\[
|D_1\triangle (D_1+a)|
\gtrsim \min\{|a|,1\},
\]
the triangle inequality and \eqref{eq:distance-centered-disk-new} imply that
there exists $K\gg 1$ such that, if $|a|\geq K|\varepsilon|$, then
\begin{equation}\label{eq:far-disks-new}
|\widetilde U_\varepsilon \triangle D|
\geq
|D_1\triangle D|-|\widetilde U_\varepsilon\triangle D_1|
\gtrsim
|a|-C|\varepsilon|
\gtrsim
|\varepsilon|.
\end{equation}

It remains to consider disks whose centers satisfy $|a|\leq K|\varepsilon|$.
Write
\[
a=\eta \varepsilon e^{i\theta},
\qquad
|\eta|\leq K,
\quad
\theta\in [0,2\pi).
\]
We claim that, for $\varepsilon$ sufficiently small, the translated domain
\[
\widetilde U_\varepsilon-a
\]
is still a normal graph over $\mathbb S^1$:
\[
\partial(\widetilde U_\varepsilon-a)
=
\{(1+\psi_\varepsilon^{\theta,\eta}(y))y:\ y\in \mathbb S^1\},
\]
with
\[
\psi_\varepsilon^{\theta,\eta}\in C^1(\mathbb S^1),
\qquad
\|\psi_\varepsilon^{\theta,\eta}\|_{C^1}\lesssim |\varepsilon|,
\]
uniformly in $(\theta,\eta)$ with $|\eta|\leq K$. This follows because
$\widetilde U_\varepsilon$ is already an $O(\varepsilon)$-$C^1$ perturbation of
$D_1$, and the translation vector $a$ is also of order $\varepsilon$. We now compute the first-order term of $\psi_\varepsilon^{\theta,\eta}$.
A translation by $a$ contributes, to first order in $\varepsilon$, the normal
displacement
\[
-\eta \Re(e^{-i\theta}y).
\]
Indeed, for \(y\in \mathbb S^1\),
\[
|y-a|
=
\bigl(1-2\Re(\overline y a)+|a|^2\bigr)^{1/2}
=
1-\Re(\overline y a)+O(|a|^2),
\]
uniformly in \(y\), and here \(a=\eta\varepsilon e^{i\theta}\).
Therefore
\begin{equation}\label{eq:psi-expansion-new}
\psi_\varepsilon^{\theta,\eta}(y)
=
\varepsilon\Big(\dot\varphi_0(y)-\eta \Re(e^{-i\theta}y)\Big)
+
O(\varepsilon^2)
\quad \text{in } C^1(\mathbb S^1),
\end{equation}
uniformly for $|\eta|\leq K$.

Define
\[
g^{\theta,\eta}(y)
:=
\dot\varphi_0(y)-\eta \Re(e^{-i\theta}y).
\]
Using \eqref{eq:mode-decomposition-new}, we see that $g^{\theta,\eta}$ belongs
to the finite-dimensional space spanned by the first and second harmonics.
More precisely,
\[
g^{\theta,\eta}(e^{it})
=
a\cos(2t)+b\sin(2t)-\eta \cos(t-\theta).
\]
On the Fourier side this is the key cancellation point: the translation
correction $-\eta\Re(e^{-i\theta}y)$ contributes only to the first harmonics
(its Fourier modes are $\pm 1$), while the perturbation
$\dot\varphi_0$ lives entirely in the second harmonics ($\pm 2$). Hence the
second-harmonic component is invariant under the translation correction, and
in particular the second-harmonic part of $g^{\theta,\eta}$ is independent of
$(\theta,\eta)$ and nonzero, because $(a,b)\neq (0,0)$. To extract a uniform \(L^1\) lower bound, note that
\(g^{\theta,\eta}\) lies in the \(4\)-dimensional space
\[
V:=\mathrm{span}\bigl\{\cos t,\sin t,\cos 2t,\sin 2t\bigr\}\subset L^1(\mathbb S^1).
\]
On this finite-dimensional space, all norms are equivalent; in particular, the
\(L^1(\mathbb S^1)\) and \(L^\infty(\mathbb S^1)\) norms are equivalent, and
convergence in coefficients is equivalent to convergence in any of these norms. The map
\[
(\theta,\eta)\in [0,2\pi)\times [-K,K]\longmapsto g^{\theta,\eta}\in V
\]
is continuous, and its image
\[
\mathcal G_K:=\{g^{\theta,\eta}:\ \theta\in[0,2\pi),\ |\eta|\leq K\}
\]
is the continuous image of a compact set, hence compact in \(V\). Moreover, the
\((\cos 2t,\sin 2t)\)-coefficients of every \(g^{\theta,\eta}\) are exactly
\((a,b)\neq (0,0)\), independent of \((\theta,\eta)\); thus \(0\notin
\mathcal G_K\). The function \(g\mapsto\|g\|_{L^1(\mathbb S^1)}\) is continuous
and strictly positive on \(V\setminus\{0\}\), so it attains a positive minimum
on the compact set \(\mathcal G_K\). It follows that there exists
$\delta_K>0$ such that
\begin{equation}\label{eq:uniform-l1-lower-new}
\int_{\mathbb S^1}|g^{\theta,\eta}(y)|\,d\mathcal H^1(y)\geq \delta_K
\qquad
\text{for all }\theta\in[0,2\pi),\ |\eta|\leq K.
\end{equation}
The constant \(\delta_K\) admits the explicit lower bound
\(\delta_K\ge \pi(a^2+b^2)/(4(K+1)+2\sqrt{a^2+b^2})\) provided by
Lemma~\ref{lem:symmetric-difference}, see \eqref{eq:explicit-delta-K-lower};
this quantitative estimate sharpens the qualitative compactness argument
above.

Now,
\[
|\widetilde U_\varepsilon \triangle D|
=
|(\widetilde U_\varepsilon-a)\triangle D_1|.
\]
Since $\widetilde U_\varepsilon-a$ is star-shaped with radial graph
$1+\psi_\varepsilon^{\theta,\eta}$, the same polar-coordinate computation as in
Step~4 gives
\[
|(\widetilde U_\varepsilon-a)\triangle D_1|
=
\frac12\int_{\mathbb S^1}
\left|(1+\psi_\varepsilon^{\theta,\eta}(y))^2-1\right|
\,d\mathcal H^1(y).
\]
Using \eqref{eq:psi-expansion-new},
\[
(1+\psi_\varepsilon^{\theta,\eta})^2-1
=
2\varepsilon g^{\theta,\eta}+O(\varepsilon^2)
\quad \text{in } L^\infty(\mathbb S^1),
\]
uniformly for $|\eta|\leq K$. Thus, by \eqref{eq:uniform-l1-lower-new},
there exists $c_K>0$ such that
\begin{equation}\label{eq:near-disks-new}
|\widetilde U_\varepsilon \triangle D|
=
|(\widetilde U_\varepsilon-a)\triangle D_1|
\geq
c_K |\varepsilon|
\end{equation}
whenever $|a|\leq K|\varepsilon|$. Combining \eqref{eq:far-disks-new} and \eqref{eq:near-disks-new}, we conclude
that
\[
\inf_{\substack{D \text{ disk}\\ |D|=\pi}}
|\widetilde U_\varepsilon \triangle D|
\gtrsim |\varepsilon|.
\]
Since \(r_\varepsilon=1+O(\varepsilon^2)\), the dilation from \(U_\varepsilon\)
to \(\widetilde U_\varepsilon\) changes the set only by
\[
|\widetilde U_\varepsilon\triangle U_\varepsilon|=O(\varepsilon^2),
\]
and therefore does not affect the first-order distance estimate. Thus the
area-normalized family \(\widetilde U_\varepsilon\) remains at
symmetric-difference distance \(\gtrsim |\varepsilon|\) from the class of
disks.

\medskip
\noindent
{\bf Step 6: square-root sharpness of the deficit estimate.} It remains to translate the distance estimate into the corresponding deficit
estimate. Recall that, by construction via Theorem~\ref{thm:perturb}, the
identity \eqref{eq:functiona-P-eps-new} states that \(P_\varepsilon\) is an
eigenfunction with eigenvalue \(\lambda_0\) for the localization operator on
\(U_\varepsilon\). By Lemma~\ref{lem:spectral-continuity}, the eigenvalue
\(\lambda_0\) is in fact the \emph{principal} (largest) eigenvalue of
\(\mathcal L_{U_\varepsilon}\) for all sufficiently small \(\varepsilon\),
and \(P_\varepsilon\) is a corresponding first eigenfunction; the gap
\eqref{eq:gap-preservation} ensures that \(\lambda_0\) cannot be confused
with any lower-order eigenvalue. Hence
\begin{equation}\label{eq:exact-eigenvalue}
\lambda_1(U_\varepsilon)=\lambda_0
\qquad\text{exactly, for }|\varepsilon|<\varepsilon_*.
\end{equation}
By \eqref{eq:measure-close-u-eps-new},
\(|U_\varepsilon|=\pi+O(\varepsilon^2)\), so the area-normalizing dilation
factor \(r_\varepsilon=\sqrt{\pi/|U_\varepsilon|}=1+O(\varepsilon^2)\). By
Lemma~\ref{lem:dilation-eigenvalue}
(specifically \eqref{eq:dilation-eigenvalue-control}), the dilation changes
the principal eigenvalue by
\[
\bigl|\lambda_1(\widetilde U_\varepsilon)-\lambda_1(U_\varepsilon)\bigr|
=
\bigl|\lambda_1(r_\varepsilon U_\varepsilon)-\lambda_0\bigr|
=
O(\varepsilon^2).
\]
Combining with \eqref{eq:exact-eigenvalue}, the eigenvalue deficit of
\(\widetilde U_\varepsilon\) with respect to the disk satisfies
\[
\lambda_0-\lambda(\widetilde U_\varepsilon)=O(\varepsilon^2),
\]
where \(\lambda(\widetilde U_\varepsilon)\) denotes the first localization
eigenvalue of \(\widetilde U_\varepsilon\). On the other hand, by Step~5,
the symmetric-difference asymmetry satisfies
\[
\inf_{\substack{D\text{ disk}\\ |D|=\pi}}|\widetilde U_\varepsilon\triangle D|
\gtrsim |\varepsilon|.
\]
Comparing the two,
\[
\inf_{\substack{D\text{ disk}\\ |D|=\pi}}|\widetilde U_\varepsilon\triangle D|
\gtrsim |\varepsilon|
\simeq
\sqrt{\lambda_0-\lambda(\widetilde U_\varepsilon)}.
\]
This shows that the inequality
\[
\inf_{\substack{D\text{ disk}\\ |D|=\pi}}
|\Omega\triangle D|
\lesssim
\sqrt{\lambda_0-\lambda(\Omega)}
\]
of Corollary~1.4 in \cite{Gomez-Guerra-Ramos-Tilli} is square-root-tight along
the family \(\widetilde U_\varepsilon\): the deficit is of order
\(\varepsilon^2\), the asymmetry is of order \(\varepsilon\), and so the
square root of the deficit and the asymmetry are of comparable size. This
exhibits the optimality of the exponent \(1/2\) and concludes the proof of the
sharpness of the estimate in Corollary~1.4 of
\cite{Gomez-Guerra-Ramos-Tilli}, complementing the rigidity result of
\cite{Nicola-Tilli}.

\end{proof}

% ==============================================================
% Section 6
% ==============================================================

\section{Local maximizers for the Faber--Krahn problem in the Gaussian STFT setting}\label{sec:local-max}

The purpose of this section is to establish a local rigidity statement for the
Faber--Krahn problem associated with the Gaussian STFT. The global problem,
solved in \cite{Nicola-Tilli}, asserts that, among measurable subsets of \(\C\)
of fixed measure, the centered disk uniquely maximizes the first eigenvalue of
the Gaussian STFT localization operator. Here we show that this rigidity is
already visible at the \emph{local} level: any set whose first eigenvalue cannot
be increased by small symmetric-difference perturbations must, up to a
translation, be a disk. This complements the quantitative stability result of
\cite{Gomez-Guerra-Ramos-Tilli} and provides the variational counterpart of the
inverse-spectral analysis carried out in the previous sections.

We work throughout in the Bargmann--Fock representation; we refer the reader to
\cite{Bargmann,Folland,Grochenig} for the relevant background. Thus, if
\(F\in \mathcal F^2(\C)\) is the Bargmann transform of \(f\in L^2(\R)\), then
\[
|V_\varphi f(z)|^2 = |F(z)|^2 e^{-\pi |z|^2},
\]
up to the normalization already fixed in the previous sections. Accordingly, for
\(F\in \mathcal F^2(\C)\) we set
\[
u_F(z):=|F(z)|^2 e^{-\pi |z|^2}.
\]

For a measurable set \(\Omega\subset \C\), let
\begin{equation}\label{eq:lambda1-def-sec6}
\lambda_{1,\varphi}(\Omega)
:=
\sup_{\|f\|_2=1}\int_\Omega |V_\varphi f(z)|^2\,dz.
\end{equation}

\subsection{The weighted symmetric-difference topology}

The locality of a maximizer must be measured in a topology compatible with the
Lebesgue-measure constraint and with the natural symmetries of the localization
operator. The right choice in our setting is the weighted symmetric-difference
metric obtained by integrating against the Gaussian density
\(e^{-\pi|z|^2}\,dA(z)\), which is the same density that appears both in the
Fock-space norm and in the eigenfunction \(u_F\).

\begin{definition}[Weighted symmetric-difference metric]\label{def:weighted-sym-diff}
For measurable sets \(\Omega_1,\Omega_2\subset \C\) of finite Lebesgue measure,
set
\begin{equation}\label{eq:weighted-sym-diff}
d_w(\Omega_1,\Omega_2)
:=
\int_{\Omega_1\triangle\Omega_2} w(z)\,dA(z),
\qquad
w(z):=e^{-\pi |z|^2}.
\end{equation}
We call \(d_w\) the \emph{weighted symmetric-difference distance}, and we denote
by \(\mathcal M_a\) the Borel-measurable subsets of \(\C\) of Lebesgue measure
\(a>0\), modulo Lebesgue-null modifications. The map
\(d_w\colon \mathcal M_a\times \mathcal M_a\to[0,\infty)\) is a genuine metric
on \(\mathcal M_a\): symmetry, the triangle inequality, and vanishing only on
null modifications all follow from \(w(z)=e^{-\pi|z|^2}>0\) and standard
properties of the symmetric difference.
\end{definition}

\begin{remark}[Naturality of \(d_w\) for the Gaussian Faber--Krahn problem]\label{rem:topology-natural}
Three observations clarify why \(d_w\) is the natural topology for our problem.

\begin{enumerate}
\item[\textnormal{(i)}] (\emph{Compatibility with the measure constraint.})
Since \(w\) is bounded above by \(1\) and bounded below by \(e^{-\pi R^2}>0\)
on every disk \(\{|z|\le R\}\), the metric \(d_w\) is, on every fixed bounded
region of \(\C\), equivalent to the unweighted symmetric-difference distance
\(d_0(\Omega_1,\Omega_2):=|\Omega_1\triangle\Omega_2|\). Moreover, every
\(d_w\)-perturbation \(E\) of \(\Omega\) used in this section is constructed
to satisfy the equimeasurability constraint \(|E|=|\Omega|\); hence the
\(d_w\)-balls intersected with \(\mathcal M_a\) form a basis of neighborhoods
on the measure-constraint manifold.

\item[\textnormal{(ii)}] (\emph{Translation- and rotation-invariance via Weyl.})
The Gaussian density \(w(z)=e^{-\pi|z|^2}\) is the symbol density associated
with the metaplectic representation: under the Weyl translations
\(T_a\colon F\mapsto e^{\pi az-\frac{\pi}{2}|a|^2}F(z-a)\) (cf.\
\eqref{eq:Ta}) and rotations \(F(z)\mapsto F(e^{-i\theta}z)\), one has the
covariance
\[
u_{T_aF}(z)=u_F(z-a),\qquad u_{F(\,e^{-i\theta}\cdot\,)}(z)=u_F(e^{-i\theta}z),
\]
so that the spectral data \((\lambda_{1,\varphi},u_F)\) of the localization
operator transform unitarily under these symmetries. Any choice of weight
other than a Gaussian would break this covariance with the operator algebra of
the Fock space; see, e.g., \cite{Folland,Grochenig}.

\item[\textnormal{(iii)}] (\emph{Control of Fock-space tails.}) For any
\(F\in \mathcal F^2(\C)\) one has \(u_F(z)\le \|F\|_{\mathcal F^2}^2\) for
every \(z\in\C\), as a consequence of the reproducing property
\eqref{eq:reproducing-kernel} below and Cauchy--Schwarz. Hence, for first
eigenfunctions \(F\) (which are bounded; see Lemma~\ref{lem:simplicity-local-max}),
\[
\Bigl|\int_{\Omega_1}u_F\,dA-\int_{\Omega_2}u_F\,dA\Bigr|
\le
\int_{\Omega_1\triangle\Omega_2}u_F\,dA
\le
\|F\|_{\mathcal F^2}^2\,e^{\pi R^2}\, d_w(\Omega_1,\Omega_2)
\]
on any bounded region \(\{|z|\le R\}\), so that the localization functional
\(\Omega\mapsto \int_\Omega u_F\,dA\) is Lipschitz in \(d_w\) on bounded
sets. The Gaussian weight thus tames the lack of compactness at infinity by
ensuring that \(d_w\)-small perturbations cannot transport mass to large
\(|z|\) without paying a proportional cost.
\end{enumerate}

In summary, \(d_w\) is essentially the unique Gaussian-weighted \(L^1\)-metric
on indicator functions that is compatible with the equimeasurable constraint
\(|\Omega|=a\), respects the Weyl-translation and rotation symmetries of the
Fock space, and renders \(\lambda_{1,\varphi}\) and the localization energy
continuous on bounded sets.
\end{remark}

\begin{definition}[Local maximizer]\label{def:local-maximizer}
A set \(\Omega\in\mathcal M_a\) is a \emph{local maximizer} for
\(\lambda_{1,\varphi}\) under the Lebesgue-measure constraint
\(|\,\cdot\,|=a\) if there exists \(\delta_0>0\) such that, whenever
\(E\in \mathcal M_a\) satisfies \(d_w(\Omega,E)<\delta_0\), one has
\begin{equation}\label{eq:local-max-ineq}
\lambda_{1,\varphi}(\Omega)\ge \lambda_{1,\varphi}(E).
\end{equation}
\end{definition}

We can now state the main theorem of this section.

\begin{theorem}[Local maximizers are disks]\label{thm:local-max}
Let \(\Sigma\in\mathcal M_a\) be a local maximizer for \(\lambda_{1,\varphi}\)
under the Lebesgue-measure constraint, in the sense of
Definition~\ref{def:local-maximizer}. Then there exists \(a_0\in\C\) such that
\(\Sigma\) coincides, up to a Lebesgue-null modification, with the centered
disk
\[
\Sigma=D_R+a_0,\qquad R=\sqrt{a/\pi}.
\]
\end{theorem}

The remainder of this section is devoted to the proof of
Theorem~\ref{thm:local-max}. The
proof proceeds in six steps. Steps 1--3 are essentially the analogues, in our
setting, of standard arguments in the Faber--Krahn theory: \(\Sigma\) is forced
to be a level set of \(u_F\), the corresponding eigenvalue is simple, and a
first-variation identity ties \(F\) to a divergence-free vector field built from
holomorphic data. The crucial new ingredient lies in Step 4, where we show that
the \emph{derivative} \(F'\) is again a first eigenfunction. Combined with the
simplicity from Step 2, this forces \(F\) to satisfy a first-order linear ODE,
and hence to be a Gaussian. Once this is in place, Steps 5--6 use the Weyl
invariance of the Bargmann--Fock setting and a one-dimensional rearrangement
argument to identify \(\Sigma\) with a centered disk.

\begin{proof}[Proof of the local-maximizer theorem]
Let \(\Sigma\subset \C\) be a local maximizer for \(\lambda_{1,\varphi}\) under
the measure constraint, and let \(F\in \mathcal F^2(\C)\) be a normalized first
eigenfunction for the localization operator associated with \(\Sigma\).
Equivalently,
\begin{equation}\label{eq:eigenvalue-equation}
\int_\Sigma H(z)\overline{F(z)}\,d\mu(z)
=
\lambda_{1,\varphi}(\Sigma)\int_\C H(z)\overline{F(z)}\,d\mu(z)
\end{equation}
for every \(H\in \mathcal F^2(\C)\), where
\[
d\mu(z):=e^{-\pi |z|^2}\,dA(z).
\]

The proof of the superlevel-set characterization in Step~1 below uses the
following classical rearrangement inequality, in the formulation of
Lieb--Loss
% TODO: bib key Lieb-Loss (Analysis, GSM 14, AMS, 2nd ed., Theorem 1.14)
\cite[Theorem~1.14]{Lieb-Loss} (the so-called
\emph{bathtub principle}). We record it here for ease of reference and to fix
notation.

\begin{lemma}[Bathtub principle]\label{lem:bathtub}
Let \((X,\Sigma_X,\mu_X)\) be a measure space and let
\(g\colon X\to[0,\infty)\) be a measurable function such that
\(\mu_X(\{g>t\})<\infty\) for every \(t>0\). Fix \(0<a<\mu_X(X)\). Then
\begin{equation}\label{eq:bathtub-equation}
\sup\Bigl\{\int_X g\,\mathbf 1_E\,d\mu_X\ \Big|\ E\in\Sigma_X,\ \mu_X(E)=a\Bigr\}
\end{equation}
is attained, and any maximizer \(E^\ast\) coincides, up to a \(\mu_X\)-null
set, with a superlevel set \(\{g>t_\ast\}\) of \(g\) (possibly with a
measure-zero correction at the level set \(\{g=t_\ast\}\) needed to fit the
constraint \(\mu_X(E^\ast)=a\)). The threshold \(t_\ast\ge 0\) is uniquely
determined by the condition
\[
\mu_X(\{g>t_\ast\})\le a\le \mu_X(\{g\ge t_\ast\}),
\]
and the maximum is strict in the sense that, if \(g\) has no plateaus of
positive measure on the level \(\{g=t_\ast\}\), then \(E^\ast=\{g>t_\ast\}\)
\(\mu_X\)-a.e.
\end{lemma}

In our application, \((X,\mu_X)=(\C,\mathrm{Leb}_\C)\) and \(g=u_F\). Since
\(u_F\) is real-analytic on the (open) complement of the zero set of \(F\),
its level sets \(\{u_F=t\}\) are real-analytic varieties of strictly lower
dimension and hence Lebesgue-null for every \(t>0\); the no-plateau
hypothesis of Lemma~\ref{lem:bathtub} is therefore automatic, and the
maximizer is unique up to null sets.

\medskip
\noindent
{\bf Step 1: \(\Sigma\) is a superlevel set of \(u_F\).}

We claim that there exists \(t_0\ge 0\) such that, up to sets of measure zero,
\begin{equation}\label{eq:superlevel-claim}
\Sigma=\{u_F>t_0\}.
\end{equation}

The strategy is a bathtub-style perturbation argument: if \(\Sigma\) were not a
superlevel set of \(u_F\), one could move a small piece of \(\Sigma\) where
\(u_F\) is small to a region where \(u_F\) is larger, increasing the
localization integral while preserving Lebesgue measure and remaining within
the local-maximizer neighborhood of \(\Sigma\) (cf.\ Lemma~\ref{lem:bathtub}).
The contradiction we extract is local, but as we shall see in
Lemma~\ref{lem:bathtub-superlevel-from-localmax}, the same argument actually
proves the slightly stronger statement that \(\Sigma\) is the unique
\(\mu\)-essential maximizer of the functional \(E\mapsto \int_E u_F\,dA\)
under the equimeasurable constraint, in agreement with the bathtub principle.

Recall that \(F\) is admissible in the variational problem defining
\(\lambda_{1,\varphi}(\Sigma')\) for any measurable set \(\Sigma'\) of finite
measure. In particular,
\[
\lambda_{1,\varphi}(\Sigma')\ge \int_{\Sigma'} u_F\,dA,
\qquad
\lambda_{1,\varphi}(\Sigma)= \int_\Sigma u_F\,dA,
\]
the latter equality holding because \(F\) is the actual eigenfunction for
\(\Sigma\). It therefore suffices to find a competitor \(\Sigma'\) with
\(|\Sigma'|=|\Sigma|\), close to \(\Sigma\) in the sense of weighted symmetric
difference, and with \(\int_{\Sigma'} u_F\,dA>\int_\Sigma u_F\,dA\); that would
violate local maximality.

Suppose, for the sake of contradiction, that \eqref{eq:superlevel-claim} fails.
The function \(u_F\) is real-analytic on \(\C\setminus\{F=0\}\), so for almost
every \(t\ge 0\) the level set \(\{u_F=t\}\) has Lebesgue measure zero;
consequently the distribution function \(t\mapsto |\{u_F>t\}|\) is continuous
and strictly decreasing on its support. Hence there exists a unique
\(t_0\ge 0\) such that
\[
A:=\{u_F>t_0\}\quad\text{satisfies}\quad |A|=|\Sigma|;
\]
since \eqref{eq:superlevel-claim} fails by assumption, \(A\) and \(\Sigma\)
do not coincide up to a null set, so both \(A\setminus\Sigma\) and
\(\Sigma\setminus A\) have positive Lebesgue measure (and in fact positive
weighted measure, since \(e^{-\pi|z|^2}>0\) everywhere).

We now perform the bathtub construction explicitly. The set
\(A=\{u_F>t_0\}\) is open since \(u_F\) is continuous, while
\(\Sigma\setminus A\) is only known to be measurable. By inner regularity of
the Lebesgue measure, choose a compact set \(L\subset A\setminus\Sigma\) with
\(|L|>0\) and a compact set \(K\subset \Sigma\setminus A\) with \(|K|>0\)
(both nonempty by the previous paragraph). Note that \(L\subset A\) is then
contained in the open set \(A\), and we can shrink \(L\) further if needed so
that \(\int_L d\mu, \int_K d\mu<\delta_0/4\). Since the Lebesgue measure
restricted to a compact set has the intermediate-value property, we may
choose subsets \(S\subset L\) and \(T\subset K\) with the common Lebesgue
measure
\[
|S|=|T|=\tfrac12\min(|L|,|K|)>0.
\]
Then \(S\subset A\setminus\Sigma\), \(T\subset \Sigma\setminus A\), and
\[
\int_\C (\mathbf 1_S+\mathbf 1_T)\,e^{-\pi |z|^2}\,dz<\tfrac{\delta_0}{2}<\delta_0.
\]
Define
\[
\Sigma':=(\Sigma\setminus T)\cup S.
\]
Then \(|\Sigma'|=|\Sigma|\) and
\[
\int_\C |\mathbf 1_\Sigma-\mathbf 1_{\Sigma'}|e^{-\pi |z|^2}\,dz
=\int_\C(\mathbf 1_S+\mathbf 1_T)e^{-\pi|z|^2}\,dz<\delta_0.
\]
On the other hand, by construction,
\[
u_F(z)>t_0 \quad \text{on } S\subset A,
\qquad
u_F(z)\le t_0 \quad \text{on } T\subset \Sigma\setminus A.
\]
Moreover, since \(u_F\) is continuous and \(L\subset A=\{u_F>t_0\}\) is
compact, the continuous function \(u_F\) attains its minimum on \(L\); hence
there exists \(\eta>0\) with \(u_F\ge t_0+\eta\) on \(L\), and a fortiori on
\(S\). It then follows that
\[
\int_S u_F\,dA \ge (t_0+\eta)\,|S|,
\qquad
\int_T u_F\,dA \le t_0\,|T|=t_0\,|S|,
\]
and hence
\[
\int_{\Sigma'} u_F\,dA
=
\int_\Sigma u_F\,dA + \int_S u_F\,dA-\int_T u_F\,dA
\ge \int_\Sigma u_F\,dA + \eta\,|S|
>
\int_\Sigma u_F\,dA.
\]
Since \(F\) is admissible for the variational problem defining
\(\lambda_{1,\varphi}(\Sigma')\),
\[
\lambda_{1,\varphi}(\Sigma')
\ge \int_{\Sigma'} u_F\,dA
>
\int_\Sigma u_F\,dA
=
\lambda_{1,\varphi}(\Sigma),
\]
contradicting the local maximality of \(\Sigma\). This proves
\eqref{eq:superlevel-claim}.

In particular, since \(u_F\) is real-analytic outside the (discrete) zero set of
\(F\), \(u_F\) is constant on \(\partial \Sigma\) in the sense that there exists
\(c_\Sigma\ge 0\) with
\begin{equation}\label{eq:boundary-level-set-new}
u_F(z)=c_\Sigma
\qquad \text{for } z\in \partial \Sigma.
\end{equation}
We will see in Step 2 that \(F\) does not vanish on \(\overline\Sigma\), and in
particular \(c_\Sigma>0\).

We collect the conclusions of this step in a self-contained statement that we
will reuse below.

\begin{lemma}[Superlevel-set characterization]\label{lem:bathtub-superlevel-from-localmax}
Let \(\Sigma\in\mathcal M_a\) be a local maximizer for \(\lambda_{1,\varphi}\)
in the sense of Definition~\ref{def:local-maximizer}, and let \(F\in
\mathcal F^2(\C)\) be a normalized first eigenfunction associated with
\(\Sigma\). Then there exists \(t_0>0\) such that
\begin{equation}\label{eq:superlevel-strong}
\Sigma=\{z\in\C\,:\, u_F(z)>t_0\}\quad
\text{up to a Lebesgue-null set,}
\end{equation}
and \(\Sigma\) coincides up to a null set with the unique (up to null sets)
maximizer of the bathtub problem
\(\sup\{\int_E u_F\,dA\,:\,|E|=a\}\) provided by Lemma~\ref{lem:bathtub}
applied to \(g=u_F\).
\end{lemma}

\begin{proof}
The first part is exactly \eqref{eq:superlevel-claim}; the strict positivity
\(t_0>0\) follows from the fact, derived in Step~2 below, that \(F\) cannot
vanish on \(\overline\Sigma\), so that \(c_\Sigma=t_0>0\). Uniqueness within
bathtub maximizers follows from the no-plateau remark below
Lemma~\ref{lem:bathtub}, since \(u_F\) is real-analytic on the open set
\(\{F\ne 0\}\supset\overline\Sigma\) and hence has no positive-measure level
sets there.
\end{proof}

\begin{lemma}[Boundary regularity at a local maximizer]\label{lem:boundary-reg}
Under the hypotheses of Lemma~\ref{lem:bathtub-superlevel-from-localmax},
choosing the open superlevel-set representative
\(\Sigma=\{u_F>t_0\}\), we have:
\begin{enumerate}
\item[\textnormal{(i)}] \(\Sigma\) is open and bounded (because
\(u_F(z)\to 0\) as \(|z|\to\infty\) and \(t_0>0\));
\item[\textnormal{(ii)}] \(F\) does not vanish on \(\overline\Sigma\), and
\(u_F\) is real-analytic on a neighborhood of \(\overline\Sigma\);
\item[\textnormal{(iii)}] \(\partial\Sigma\) is a real-analytic
\(1\)-manifold, except for a finite set
\(\Sigma_{\mathrm{sing}}\subset \partial\Sigma\) consisting of points where
\(\nabla u_F\) vanishes; in particular, \(\partial\Sigma\) is locally
Lipschitz, has finite \(\mathcal H^1\)-measure, and
\(\mathcal H^1(\Sigma_{\mathrm{sing}})=0\);
\item[\textnormal{(iv)}] the divergence theorem
\(\int_\Sigma \mathrm{div}\,X\,dA=\int_{\partial\Sigma}X\cdot\nu\,
d\mathcal H^1\) holds for every \(C^1\)-vector field \(X\) defined on a
neighborhood of \(\overline\Sigma\).
\end{enumerate}
\end{lemma}

\begin{proof}
Statement (i) is immediate, since \(u_F(z)=|F(z)|^2 e^{-\pi|z|^2}\) tends to
\(0\) at infinity (as \(F\) is entire and the Gaussian factor decays
super-exponentially against any polynomial growth of \(|F|^2\) along any
sequence \(|z|\to\infty\), since \(F\in\mathcal F^2\) is in particular bounded
along any horizontal line by \cite[Ch.~1]{Folland}). The non-vanishing in
(ii) is established in Step~2 (more precisely, in
Lemma~\ref{lem:simplicity-local-max} below; the argument in Step~2 only uses
(i) of the present lemma plus \eqref{eq:superlevel-strong}). Once \(F\) is
non-vanishing on \(\overline\Sigma\), \(u_F\) is real-analytic on a
neighborhood of \(\overline\Sigma\). Statement (iii) is the standard local
structure theorem for level sets of non-constant real-analytic functions
% TODO: bib key Krantz-Parks-Primer, Lojasiewicz
(see, e.g., \cite{Krantz-Parks-Primer,Lojasiewicz}), which gives that
\(\{u_F=t_0\}\) decomposes locally into finitely many real-analytic arcs
meeting at finitely many singular points (the zeros of \(\nabla u_F\) on
\(\{u_F=t_0\}\), of which there are finitely many on the compact set
\(\overline\Sigma\) by analyticity). Lipschitz regularity of the boundary
then follows by parametrizing each arc by arc length, and the
divergence-theorem statement (iv) follows from the Gauss--Green theorem on
Lipschitz domains
% TODO: bib key Evans-Gariepy
(cf.\ \cite{Evans-Gariepy}), using that the Lipschitz regular set
\(\partial\Sigma\setminus \Sigma_{\mathrm{sing}}\) carries
\(\mathcal H^1\)-almost every point of \(\partial\Sigma\).
\end{proof}

\begin{remark}\label{rem:reg-vs-hypothesis}
No boundary regularity is hypothesized on the local maximizer: the only input
is the measurability of \(\Sigma\), and the real-analyticity of
\(\partial\Sigma\) (away from finitely many points) is \emph{derived} from
the superlevel-set characterization combined with the entirety of \(F\) and
the Gaussian weight. Thus the divergence-theorem identity used in Step~3 is
fully justified by Lemma~\ref{lem:boundary-reg}(iv), even though \(\Sigma\)
is a priori only a measurable set.
\end{remark}

\medskip
\noindent
{\bf Step 2: simplicity of the first eigenvalue.}

In this step we prove the following lemma, which lies at the heart of the
remainder of the argument: it is what allows us, in Step~4, to conclude from
the fact that \(F'\) is a first eigenfunction that \(F'\) is a scalar multiple
of \(F\) and hence that \(F\) satisfies a linear ODE.

\begin{lemma}[Simplicity at a local maximizer]\label{lem:simplicity-local-max}
Let \(\Sigma\) be a local maximizer for \(\lambda_{1,\varphi}\) in the sense
of Definition~\ref{def:local-maximizer} and let \(F\in\mathcal F^2(\C)\) be a
normalized first eigenfunction associated with \(\Sigma\). Then the
eigenspace \(\ker(\mathcal L_\Sigma-\lambda_{1,\varphi}(\Sigma)\,\mathrm I)\)
is one-dimensional; that is, \(\lambda_{1,\varphi}(\Sigma)\) is simple, and
\(F\) is uniquely determined up to a unimodular constant. In particular,
\(F\) does not vanish on \(\overline\Sigma\), and \(F\) is bounded on \(\C\).
\end{lemma}

The proof uses a modular-deformation principle: any two first eigenfunctions
have the same modulus on \(\partial\Sigma\) up to a constant, and a holomorphic
function with constant modulus on a connected open set must itself be constant.
This argument plays a role also in the stability analysis of
\cite{Gomez-Guerra-Ramos-Tilli}.

\begin{proof}[Proof of Lemma~\ref{lem:simplicity-local-max}]
Suppose, for contradiction, that \(G\in \mathcal F^2(\C)\) is another first
eigenfunction, linearly independent of \(F\). Step 1 applied to \(G\) shows that
\(\Sigma\) is also a superlevel set of \(u_G\); hence there exists
\(c'_\Sigma\ge 0\) such that
\[
u_G(z)=c'_\Sigma
\qquad\text{for } z\in \partial \Sigma.
\]
Equivalently,
\[
|F(z)|^2 e^{-\pi |z|^2}=c_\Sigma,
\qquad
|G(z)|^2 e^{-\pi |z|^2}=c'_\Sigma,
\qquad z\in \partial \Sigma.
\]

We next observe that first eigenfunctions are zero-free in the interior of
\(\Sigma\). Indeed, by Step 1 we have \(u_F>c_\Sigma\) on the (open) interior of
\(\Sigma\). Since
\[
u_F=|F|^2 e^{-\pi |z|^2}
\]
and the Gaussian factor \(e^{-\pi|z|^2}\) is strictly positive everywhere, this
yields \(|F|>0\) throughout the interior of \(\Sigma\); the same applies to
\(|G|\). In particular, \(c_\Sigma>0\) and \(c'_\Sigma>0\). Moreover, since
\(F,G\) are entire and continuous, \(|F|>0\) on a neighborhood of any compact
subset of \(\Sigma^\circ\); by Step 1, we may take a slight enlargement of
\(\Sigma\) (still a superlevel set of \(u_F\)) on which \(|F|,|G|>0\), so we may
work on a connected open set \(U\Supset \Sigma\) where both \(F\) and \(G\) are
zero-free.

The ratio \(F/G\) is holomorphic and nowhere zero on \(U\), and the function
\[
\log \left|\frac{F}{G}\right|
=
\frac12 \log \frac{|F|^2}{|G|^2}
=
\frac12 \log \frac{u_F}{u_G}
\]
is harmonic on \(U\): it is the real part of any local branch of
\(\log(F/G)\), which is well defined on simply connected subsets, and harmonic
in any case as the logarithm of the modulus of a zero-free holomorphic
function. Note that the Gaussian factors cancel inside the logarithm, so on
\(\partial \Sigma\) by \eqref{eq:boundary-level-set-new} this function equals
the constant \(\frac12\log(c_\Sigma/c'_\Sigma)\). By the maximum principle
applied separately on each connected component of \(\Sigma\), the function
\(\log|F/G|\) is constant on each component. Hence
\[
\left|\frac{F}{G}\right| \equiv \text{constant}
\qquad \text{on each connected component of } \Sigma.
\]
A nonconstant holomorphic function is open, so a holomorphic function with
constant modulus on a connected open set must itself be constant. Therefore
\[
F=\gamma_j G
\qquad \text{on each connected component } \Sigma_j\text{ of } \Sigma.
\]
The relation \(F=\gamma_j G\) is an identity between two entire functions on a
set with an accumulation point; the analytic continuation principle gives
\(F=\gamma_j G\) on all of \(\C\) for any single \(j\). In particular all
\(\gamma_j\) coincide, and \(F\) and \(G\) are linearly dependent, contradicting
our assumption. This proves simplicity.

The non-vanishing of \(F\) on \(\overline\Sigma\) was established in the
second paragraph of this step, while the boundedness of \(F\) on \(\C\)
follows from the Berezin-type estimate
\(u_F(z)=|\langle F,K_z\rangle|^2/\|K_z\|^2_{\mathcal F^2}\le
\|F\|_{\mathcal F^2}^2\), so that
\(|F(z)|\le \|F\|_{\mathcal F^2}\,e^{\pi|z|^2/2}\) and
\(\|u_F\|_\infty\le \|F\|_{\mathcal F^2}^2<\infty\). This completes the proof
of Lemma~\ref{lem:simplicity-local-max}.
\end{proof}

\medskip
\noindent
{\bf Step 3: a first-variation identity.}

By Lemma~\ref{lem:simplicity-local-max}, the eigenfunction \(F\) is determined
up to a unimodular constant. We now derive a first-variation identity
satisfied by \(F\), based on the fact that \(\Sigma\) is a level set of
\(u_F\) and that holomorphic vector fields are divergence-free.

We work throughout this step with the open superlevel-set representative
\(\Sigma=\{u_F>t_0\}\) from
Lemma~\ref{lem:bathtub-superlevel-from-localmax} (which is permissible since
local maximality only sees the equivalence class of \(\Sigma\) up to null
sets). By Lemma~\ref{lem:boundary-reg}, \(F\) does not vanish on
\(\overline\Sigma\), \(u_F\) is real-analytic on a neighborhood of
\(\overline\Sigma\), the boundary \(\partial\Sigma\) is a finite union of
real-analytic arcs joined at finitely many singular points (the zeros of
\(\nabla u_F\) on \(\{u_F=t_0\}\)), and the divergence theorem applies on
\(\Sigma\) to every \(C^1\)-vector field defined in a neighborhood of
\(\overline\Sigma\). All boundary integrations below are therefore justified
without any a priori smoothness assumption on \(\Sigma\); cf.\
Remark~\ref{rem:reg-vs-hypothesis}.

Let \(\psi\) be holomorphic on an open neighborhood \(V\) of
\(\overline \Sigma\), and write
\[
\psi=u+iv
\]
with \(u,v\) real-valued. Consider the real vector field
\[
X_\psi:=(u,-v).
\]
Since \(\psi\) is holomorphic, the Cauchy--Riemann equations
\[
u_x=v_y,
\qquad
u_y=-v_x,
\]
imply
\[
\operatorname{div}X_\psi=u_x+(-v)_y=u_x-v_y=0
\qquad \text{in }V.
\]
Because \(u_F\equiv c_\Sigma\) on \(\partial\Sigma\), the divergence theorem on
\(\Sigma\) gives
\[
\int_\Sigma \langle \nabla u_F, X_\psi\rangle\,dA
=
\int_\Sigma \operatorname{div}(u_F X_\psi)\,dA
=
\int_{\partial \Sigma} u_F\, X_\psi\cdot \nu\, d\mathcal H^1
=
c_\Sigma\int_{\partial \Sigma} X_\psi\cdot \nu\, d\mathcal H^1
=
0,
\]
where the last equality uses
\(\int_{\partial\Sigma}X_\psi\cdot\nu\,d\mathcal H^1
=\int_\Sigma\operatorname{div}X_\psi\,dA=0\) by Cauchy--Riemann. Since
\(u_F=|F|^2e^{-\pi |z|^2}\) and
\(\nabla(e^{-\pi|z|^2})=-2\pi e^{-\pi|z|^2}(x,y)\), this becomes
\begin{equation}\label{eq:vector-field-identity-real-new}
0=
\int_\Sigma
\left(
\langle \nabla |F|^2,X_\psi\rangle
-
2\pi |F|^2 \langle z,X_\psi\rangle
\right)
\,d\mu.
\end{equation}

We now express \eqref{eq:vector-field-identity-real-new} in complex notation.
A direct computation, using \(\partial_z|F|^2=F'\overline F\) and
\(\partial_{\bar z}|F|^2=F\overline{F'}\), gives
\[
\partial_x |F|^2 = F'\overline F+\overline{F'}F = 2\Re(F'\overline F),
\qquad
\partial_y |F|^2 = i(F'\overline F-\overline{F'}F) = -2\Im(F'\overline F).
\]
Writing \(\psi=u+iv\) and recalling \(X_\psi=(u,-v)\),
\[
\langle \nabla |F|^2,X_\psi\rangle
=
2u\,\Re(F'\overline F)+2v\,\Im(F'\overline F)
=
2\,\Re\!\big(\overline{\psi}\,F'\overline F\big)
=
2\,\Re\!\big(\psi\,\overline{F'}F\big),
\]
where in the last equality we used \(\Re w=\Re\overline w\). Likewise, writing
\(z=x+iy\),
\[
\langle z,X_\psi\rangle
=
xu+y(-v)
=
xu-yv
=
\Re\big((x+iy)(u+iv)\big)
=
\Re(z\psi).
\]
Substituting these expressions into
\eqref{eq:vector-field-identity-real-new}, we obtain
\[
0=
\Re\!\int_\Sigma
\psi(z)\Big(\overline{F'(z)}\,F(z)-\pi z\,|F(z)|^2\Big)\,d\mu(z).
\]
Replacing \(\psi\) by \(i\psi\) (which is also holomorphic on \(V\)) gives the
analogous identity for the imaginary part:
\[
0=
\Im\!\int_\Sigma
\psi(z)\Big(\overline{F'(z)}\,F(z)-\pi z\,|F(z)|^2\Big)\,d\mu(z).
\]
Combining the two, and using \(|F|^2=F\overline F\) to factor out \(F(z)\)
from both terms inside the integrand (the \(F\) from \(\overline{F'}F\) and
one copy of \(F\) from \(|F|^2=F\overline F\)),
\begin{equation}\label{eq:orthogonality-main-new}
0=
\int_\Sigma
\psi(z)\,F(z)\Big(\overline{F'(z)}-\pi z\,\overline{F(z)}\Big)\,d\mu(z),
\end{equation}
which holds for every holomorphic \(\psi\) on a neighborhood of
\(\overline \Sigma\). Equivalently, expanding the product,
\begin{equation*}
0=
\int_\Sigma
\psi(z)\Big(\overline{F'(z)}\,F(z)-\pi z\,|F(z)|^2\Big)\,d\mu(z).
\end{equation*}
The form \eqref{eq:orthogonality-main-new} is the one used in Step 4.

\medskip
\noindent
{\bf Step 4: \(F'\) is again a first eigenfunction.}

This step is the crux of the argument and is the main new ingredient compared
to classical Faber--Krahn rigidity proofs. Rather than working with general
test functions in the eigenvalue equation, we exploit the divergence identity
\eqref{eq:orthogonality-main-new} together with a clever choice of test
function involving the reproducing kernel of the Fock space. The end result is
that \emph{the derivative} \(F'\) of any first eigenfunction is itself a first
eigenfunction; since the eigenspace is one-dimensional by Step 2, this forces
a first-order ODE on \(F\), and hence pins down \(F\) up to translation as a
Gaussian.

For every \(w\in \C\), set
\[
K_w(z):=e^{\pi \overline w z};
\]
this is the reproducing kernel of \(\mathcal F^2(\C)\) at the point \(w\), in
the sense that
\begin{equation}\label{eq:reproducing-kernel}
\int_\C H(z)\,e^{\pi w \overline z}\,d\mu(z)=H(w),
\qquad H\in\mathcal F^2(\C);
\end{equation}
see, e.g., \cite[Ch.~1]{Folland} or \cite{Bargmann}. Equivalently,
\(\langle H,K_w\rangle_{\mathcal F^2}=H(w)\).

By Step 1, after replacing \(\Sigma\) by the corresponding superlevel-set
representative if necessary, we may suppose that
\[
\Sigma=\{u_F>c_\Sigma\}.
\]
In particular, \(u_F\ge c_\Sigma>0\) on \(\overline \Sigma\). Since
\(u_F(z)=|F(z)|^2e^{-\pi |z|^2}\), it follows that \(F\) has no zeros on
\(\overline \Sigma\). By continuity of \(F\) and the compactness of
\(\overline \Sigma\), there exists an open neighborhood
\(V\supset \overline \Sigma\) on which \(F\) has no zeros. Hence, for every
\(w\in \C\), the function
\[
\psi_w(z):=\frac{K_w(z)}{F(z)}=\frac{e^{\pi\overline wz}}{F(z)}
\]
is holomorphic on \(V\). Applying \eqref{eq:orthogonality-main-new} with
\(\psi=\psi_w\), so that
\(\psi_w(z)F(z)=e^{\pi\overline w z}\), we obtain
\[
0=
\int_\Sigma
e^{\pi \overline wz}
\Big(\overline{F'(z)}-\pi z\,\overline{F(z)}\Big)\,d\mu(z),
\]
or, separating the two terms,
\begin{equation}\label{eq:key-kernel-identity-new}
\int_\Sigma
e^{\pi \overline wz}\overline{F'(z)}\,d\mu(z)
=
\int_\Sigma
\pi z\,e^{\pi \overline wz}\overline{F(z)}\,d\mu(z).
\end{equation}

We now relate the right-hand side of \eqref{eq:key-kernel-identity-new} to
\(\overline{F'(w)}\) using the eigenvalue equation
\eqref{eq:eigenvalue-equation} together with the reproducing identity
\eqref{eq:reproducing-kernel}. Choosing
\[
H(z):=z\,e^{\pi\overline w z}\in \mathcal F^2(\C)
\]
(the product of the kernel \(K_w\) by the polynomial \(z\); both factors
preserve membership in \(\mathcal F^2\)) in \eqref{eq:eigenvalue-equation}, we
obtain
\begin{equation}\label{eq:eigvalue-applied}
\int_\Sigma z\, e^{\pi \overline wz}\,\overline{F(z)}\,d\mu(z)
=
\lambda_{1,\varphi}(\Sigma)\int_\C z\, e^{\pi \overline wz}\,\overline{F(z)}\,d\mu(z).
\end{equation}
On the other hand, taking complex conjugates in \eqref{eq:reproducing-kernel}
applied to \(F\) at the point \(w\), one finds
\[
\int_\C e^{\pi \overline wz}\,\overline{F(z)}\,d\mu(z)=\overline{F(w)}.
\]
Both sides depend on \(w\) through the antiholomorphic variable
\(\overline w\); we differentiate with respect to \(\overline w\), exchanging
differentiation and integration on the left. The interchange is legitimate
because, for \(w\) in any compact set \(\{|w|\le R\}\), the integrand
\(\partial_{\overline w}(e^{\pi\overline wz}\overline{F(z)})
=\pi z\,e^{\pi\overline wz}\overline{F(z)}\) is dominated, in absolute
value, by \(\pi |z|\,e^{\pi R|z|}|F(z)|\). The standard pointwise bound for
Fock-space functions gives \(|F(z)|\le\|F\|_{\mathcal F^2}\,e^{\pi |z|^2/2}\),
so this dominator is bounded by a constant times
\(|z|\,e^{\pi R|z|}\,e^{\pi|z|^2/2}\); after multiplication by the Gaussian
weight \(e^{-\pi|z|^2}\) of \(d\mu\), the resulting integrand
\(|z|\,e^{\pi R|z|}\,e^{-\pi |z|^2/2}\) is integrable on \(\C\). Dominated
convergence therefore justifies the interchange. We conclude
\[
\pi\int_\C z\, e^{\pi \overline wz}\,\overline{F(z)}\,d\mu(z)
=
\overline{F'(w)}.
\]
Multiplying \eqref{eq:eigvalue-applied} by \(\pi\) and substituting,
\[
\pi\int_\Sigma z\, e^{\pi \overline wz}\,\overline{F(z)}\,d\mu(z)
=
\lambda_{1,\varphi}(\Sigma)\,\overline{F'(w)}.
\]
Combining this with \eqref{eq:key-kernel-identity-new},
\[
\int_\Sigma e^{\pi \overline wz}\,\overline{F'(z)}\,d\mu(z)
=
\lambda_{1,\varphi}(\Sigma)\,\overline{F'(w)},
\qquad w\in \C.
\]
Taking complex conjugates, this is exactly the eigenvalue equation
\eqref{eq:eigenvalue-equation} applied with \(F\) replaced by \(F'\) (and an
arbitrary \(K_w\) playing the role of the test function). Since the linear
span of \(\{K_w\}_{w\in\C}\) is dense in \(\mathcal F^2(\C)\), the identity
extends to every \(H\in\mathcal F^2(\C)\), and we conclude that \(F'\) is a
first eigenfunction of the localization operator on \(\Sigma\), with eigenvalue
\(\lambda_{1,\varphi}(\Sigma)\).

By the simplicity of \(\lambda_{1,\varphi}(\Sigma)\) established in
Lemma~\ref{lem:simplicity-local-max},
\[
F'=\theta F
\]
for some constant \(\theta\in \C\). Solving this ODE gives
\[
F(z)=C e^{\theta z},
\]
for some nonzero constant \(C\).

\medskip
\noindent
{\bf Step 5: reduction to the constant eigenfunction.}

We now use the Weyl invariance of the Bargmann--Fock setting to reduce the
analysis to the case \(F\equiv 1\). Recall from \eqref{eq:Ta} that, for
\(a\in\C\), the Weyl translation
\[
(T_a F)(z)= e^{\pi a z-\frac{\pi}{2}|a|^2}\,F(z-a)
\]
is unitary on \(\mathcal F^2(\C)\) and satisfies
\(u_{T_aF}(z)=u_F(z-a)\). In particular, \(T_a\) maps eigenfunctions of the
localization operator on \(\Sigma\) to eigenfunctions of the localization
operator on the translated set \(\Sigma+a\), with the same eigenvalue, and the
quantity \(\int_\Sigma u_F\,dA\) is invariant under the simultaneous
substitutions \(F\mapsto T_aF\) and \(\Sigma\mapsto \Sigma+a\).

We claim that we may choose \(a\in\C\) so that \(T_{-a}F\) is a constant
function. Indeed, by Step 4, \(F(z)=Ce^{\theta z}\) for some \(C,\theta\in\C\)
with \(C\ne 0\). Compute, using the identity
\(u_{T_{-a}F}(z)=u_F(z+a)\):
\[
u_{T_{-a}F}(z)=|F(z+a)|^2 e^{-\pi|z+a|^2}
=|C|^2 e^{2\Re(\theta(z+a))}\,e^{-\pi|z+a|^2}.
\]
Expanding,
\[
2\Re(\theta(z+a))-\pi|z+a|^2
=
2\Re(\theta z)+2\Re(\theta a)-\pi|z|^2-2\pi\Re(\overline a z)-\pi|a|^2.
\]
The linear terms in \(z\) on the right cancel if and only if
\(2\Re(\theta z)=2\pi\Re(\overline a z)\) for every \(z\in\C\), which is the
condition \(\overline a=\theta/\pi\), i.e.
\[
a:=\frac{\overline\theta}{\pi}.
\]
With this choice,
\[
u_{T_{-a}F}(z)=|C'|^2 e^{-\pi|z|^2},
\qquad
|C'|^2:=|C|^2 e^{2\Re(\theta a)-\pi|a|^2}=|C|^2 e^{|\theta|^2/\pi}.
\]
Since \(T_{-a}F\) is entire and \(|T_{-a}F(z)|^2 e^{-\pi|z|^2}=|C'|^2
e^{-\pi|z|^2}\), it follows that \(|T_{-a}F|\equiv|C'|\) is constant; a
holomorphic function with constant modulus is constant, hence
\(T_{-a}F\equiv C''\) for some \(C''\in\C\) with \(|C''|=|C'|\). Normalizing,
we may absorb the unimodular constant into the eigenfunction and assume
\[
F\equiv 1
\]
after the change \(\Sigma\rightsquigarrow \Sigma-a\) (and the corresponding
unitary substitution \(F\rightsquigarrow T_{-a}F\)).

In this normalization the ground state \(h_0\) (corresponding to
\(F\equiv 1\) in Bargmann--Fock coordinates) is an eigenfunction of the
localization operator of \(\Sigma\). By Step 1 (applied with the new
normalization) we have, up to a null set,
\[
\Sigma=\{z\in\C:\ |C'|^2 e^{-\pi |z|^2}>c_\Sigma\}.
\]
Since \(r\mapsto e^{-\pi r^2}\) is \emph{strictly} decreasing, this
superlevel set is automatically a centered open disk; it cannot be an
annulus. Thus \(\Sigma\) is, up to a null set, the centered disk \(D_R\)
with \(|D_R|=|\Sigma|\), and Step 6 below records the corresponding
quantitative rearrangement statement, which is an instance of the global
Faber--Krahn theorem of \cite{Nicola-Tilli}.

\medskip
\noindent
{\bf Step 6: exclusion of annuli and conclusion.}

It remains to verify that, among radial sets of prescribed measure, the only
local maximizer is the centered disk. Although this is essentially automatic
after Step 5, we record the standard rearrangement argument since it makes
explicit \emph{why} no annular local maximizer can exist; this provides the
endpoint matching the global Faber--Krahn theorem of \cite{Nicola-Tilli}.

Suppose, more generally, that \(\Sigma\) is any radial set of finite measure
which arises as a superlevel set of a radial real-analytic non-constant
function on \(\C\); write
\[
\widetilde \Sigma:=\{r>0:\ re^{it}\in \Sigma \text{ for some } t\in [0,2\pi)\}.
\]
By Step 1, \(\Sigma\) admits an open representative; combined with the
real-analytic structure established in Step 3, the boundary
\(\partial\Sigma\) is a finite union of real-analytic arcs, hence
\(\widetilde \Sigma\subset (0,\infty)\) is open and is a finite union of
disjoint open intervals:
\[
\widetilde \Sigma=\bigcup_{j=1}^N (a_j,b_j),
\qquad
0\le a_1<b_1\le a_2<b_2\le \cdots\le a_N<b_N.
\]
Then, using \(\int re^{-\pi r^2}\,dr=-\frac{1}{2\pi}e^{-\pi r^2}\),
\[
\int_\Sigma e^{-\pi |z|^2}\,dA(z)
=
2\pi \int_{\widetilde \Sigma} r e^{-\pi r^2}\,dr
=
\sum_{j=1}^N \big(e^{-\pi a_j^2}-e^{-\pi b_j^2}\big),
\]
under the constraint
\[
|\Sigma|
=
2\pi \int_{\widetilde \Sigma} r\,dr
=
\pi \sum_{j=1}^N (b_j^2-a_j^2).
\]
We are therefore led to the optimization problem
\begin{equation}\label{eq:radial-opt}
\text{maximize}\qquad
\sum_{j=1}^N \big(e^{-\pi a_j^2}-e^{-\pi b_j^2}\big)
\qquad \text{subject to}\qquad
\sum_{j=1}^N (b_j^2-a_j^2)=c,
\end{equation}
where \(c=|\Sigma|/\pi\) is fixed. Substituting \(s_j:=a_j^2\),
\(t_j:=b_j^2\) (with \(0\le s_1<t_1\le s_2<\cdots\)), and writing
\(\Phi(x):=e^{-\pi x}\), \eqref{eq:radial-opt} becomes
\[
\text{maximize}\qquad
\sum_{j=1}^N \big(\Phi(s_j)-\Phi(t_j)\big)
\qquad \text{subject to}\qquad
\sum_{j=1}^N (t_j-s_j)=c.
\]
The function \(\Phi\) is strictly convex and strictly decreasing on
\([0,\infty)\); its derivative \(-\Phi'(\sigma)=\pi e^{-\pi\sigma}\) is strictly
decreasing in \(\sigma\). For any \(t>s\ge 0\),
\[
\Phi(s)-\Phi(t)
=
\int_s^t (-\Phi'(\sigma))\,d\sigma,
\]
so
\[
\sum_{j=1}^N\big(\Phi(s_j)-\Phi(t_j)\big)
=
\int_{\widetilde\Sigma_2}(-\Phi'(\sigma))\,d\sigma,
\qquad
\widetilde\Sigma_2:=\bigcup_{j=1}^N (s_j,t_j).
\]
The set \(\widetilde\Sigma_2\subset[0,\infty)\) has Lebesgue measure equal to
\(c\), and the integrand \(-\Phi'\) is strictly decreasing in \(\sigma\). The
bathtub principle (Lemma~\ref{lem:bathtub} applied to \(g=-\Phi'\)) shows
that, among all measurable subsets of \([0,\infty)\) of total Lebesgue measure
\(c\), the integral \(\int_{\widetilde\Sigma_2}(-\Phi'(\sigma))\,d\sigma\) is
strictly maximized by the leftmost interval \((0,c)\). This corresponds to
\(N=1\), \(s_1=0\), \(t_1=c\), i.e.
\[
\widetilde \Sigma=(0,R),
\qquad R:=\sqrt c,
\]
and equivalently \(\Sigma\) is the centered disk \(D_R\) with
\(|D_R|=|\Sigma|\). Any annular configuration (\(N\ge 2\), or \(N=1\) with
\(s_1>0\)) produces a strictly smaller value of \(\int_\Sigma u_F\,dA\), and is
therefore not a local maximizer.

We conclude that every local maximizer of \(\lambda_{1,\varphi}\) under the
measure constraint is, up to translation, a disk.
\end{proof}


% ==============================================================
% Section 7
% ==============================================================

\section{Global maximizers for the Faber--Krahn problem in the Gaussian STFT setting}\label{sec:global-max}

In this section we prove existence of global maximizers for the Gaussian
time-frequency concentration problem under a measure constraint, and then
combine that existence result with the local rigidity theorem from the previous
section to recover the disk as the unique maximizer, up to translation. The
strategy is by now classical in time-frequency analysis: a profile decomposition
in the spirit of P.-L.~Lions' concentration-compactness, transplanted to the
Fock space via the Bargmann transform, dichotomizes the loss of compactness of a
maximizing sequence into the action of the Weyl translation group. A vanishing
remainder is then ruled out by an iterative extraction whose maximality forces
all the energy to remain captured by the extracted profiles. Closely related
arguments have appeared in the time-frequency setting in
\cite{Nicola-Romero-Trapasso, Marceca-Romero-Speckbacher, Fulsche-Hagger,
Samuelsen}, and the disk-rigidity result we recover is the celebrated theorem
of Nicola--Tilli \cite{Nicola-Tilli, Nicola-Tilli-2}.

Since the Bargmann transform is unitary, the variational problem may be written
on the Fock space side as
\[
M(s):=\sup_{|\Omega|=s}\lambda_{1,\varphi}(\Omega)
=
\sup_{\|F\|_{\mathcal F^2}=1} I_F(s).
\]
Here, and throughout the section, we exploit the translation invariance
\eqref{eq:I-translation-global} together with the pointwise identity
\eqref{eq:u-translation-global} (cf.\ also \eqref{eq:uF-translate}), the
basic regularity properties recorded in Lemma~\ref{lem:basic-properties-global},
and the elementary properties of the Fock space gathered in
Lemma~\ref{lem:Fock-basic}.

We begin with a Weyl-orthogonality lemma that captures the asymptotic
decoupling of two functions whose translation parameters drift apart. This
plays the role of \emph{Pythagorean orthogonality at infinity} on the Fock
space.

\begin{lemma}\label{lem:weyl-orthogonality-global}
Let \(F,G\in \mathcal F^2(\C)\), and let \(\{a_k\}\subset \C\) satisfy
\(|a_k|\to \infty\). Then
\[
T_{a_k}G \rightharpoonup 0
\qquad\text{weakly in }\mathcal F^2(\C),
\]
and in particular
\[
\langle F,T_{a_k}G\rangle_{\mathcal F^2}\to 0.
\]
Consequently,
\[
\|F+T_{a_k}G\|_{\mathcal F^2}^2
=
\|F\|_{\mathcal F^2}^2+\|G\|_{\mathcal F^2}^2+o(1).
\]
More generally, if \(|a_k-b_k|\to\infty\), then
\[
\langle T_{a_k}F,T_{b_k}G\rangle_{\mathcal F^2}\to 0.
\]
\end{lemma}

\begin{proof}
Using unitarity of the Weyl operators \(T_a\) on \(\mathcal F^2(\C)\) (cf.\
\eqref{eq:Ta}),
\[
\langle F,T_{a_k}G\rangle_{\mathcal F^2}
=
\langle T_{-a_k}F,G\rangle_{\mathcal F^2}.
\]
Now \(T_{-a_k}F\) is bounded in \(\mathcal F^2\) by unitarity, and the
identity \eqref{eq:u-translation-global} (equivalently
\eqref{eq:uF-translate}) yields
\[
u_{T_{-a_k}F}(z)=u_F(z+a_k)\qquad (z\in\C),
\]
so that the densities \(u_{T_{-a_k}F}\) drift uniformly to infinity.
Equivalently, since \(u_F\in C_0(\C)\) by Lemma~\ref{lem:Fock-basic}(iii), for
every compact \(K\subset \C\),
\[
\sup_{z\in K}|T_{-a_k}F(z)|e^{-\pi |z|^2/2}
=
\sup_{z\in K}u_{T_{-a_k}F}(z)^{1/2}
=
\sup_{z\in K}u_F(z+a_k)^{1/2}\to 0.
\]
Hence \(T_{-a_k}F\to 0\) locally uniformly. Combining this with the
boundedness of \(\{T_{-a_k}F\}\) in \(\mathcal F^2(\C)\), and using the fact
that the linear span of the reproducing kernels \(\{K_w\}_{w\in\C}\) is dense
in \(\mathcal F^2\), we conclude that \(T_{-a_k}F\rightharpoonup 0\) weakly in
\(\mathcal F^2\); in particular \(\langle T_{-a_k}F,G\rangle\to 0\). This
proves the first claim.

For the norm decoupling, expand the square:
\[
\|F+T_{a_k}G\|_{\mathcal F^2}^2
=
\|F\|_{\mathcal F^2}^2+\|T_{a_k}G\|_{\mathcal F^2}^2
+2\Re\langle F,T_{a_k}G\rangle_{\mathcal F^2}
=
\|F\|_{\mathcal F^2}^2+\|G\|_{\mathcal F^2}^2+o(1),
\]
where we used unitarity of \(T_{a_k}\) and the cross-term decay just proved.

Finally, the general case reduces to the first by writing
\[
\langle T_{a_k}F,T_{b_k}G\rangle_{\mathcal F^2}
=
\langle F,T_{-a_k}T_{b_k}G\rangle_{\mathcal F^2}
=
e^{i\theta_k}\langle F,T_{b_k-a_k}G\rangle_{\mathcal F^2},
\]
for some real phase \(\theta_k\) coming from the cocycle of the Weyl
representation; since this phase factor has modulus one, the conclusion
follows from \(|b_k-a_k|\to\infty\).
\end{proof}

The next lemma compares the density of a finite sum of widely separated
translates with the density of each individual translate. The precise statement
is what makes the profile decomposition compatible with the variational
quantities \(I_F(s)\), since these depend only on the densities and not on
the phases of the underlying functions.

\begin{lemma}\label{lem:pointwise-decoupling-global}
Fix \(J\ge 1\), let \(G^{(1)},\dots,G^{(J)}\in \mathcal F^2(\C)\), and let
\(\{a_k^{(j)}\}_{k\ge 1}\subset \C\) for \(1\le j\le J\) satisfy
\[
|a_k^{(j)}-a_k^{(\ell)}|\to\infty
\qquad\text{whenever }j\neq \ell.
\]
For each \(k\), set
\[
S_k:=\sum_{j=1}^J T_{a_k^{(j)}}G^{(j)}.
\]
Then the following hold.
\begin{enumerate}
\item[(i)] For every \(R>0\) and every \(1\le j\le J\),
\[
\sup_{z\in D_R(a_k^{(j)})}
\big|u_{S_k}(z)-u_{T_{a_k^{(j)}}G^{(j)}}(z)\big|
\to 0
\qquad (k\to\infty).
\]

\item[(ii)] For every \(R>0\), if
\[
E_{k,R}:=\C\setminus \bigcup_{j=1}^J D_R(a_k^{(j)}),
\]
then
\[
\limsup_{k\to\infty}\sup_{z\in E_{k,R}}u_{S_k}(z)
\le
\left(
\sum_{j=1}^J
\sup_{\zeta\in \C\setminus D_R} u_{G^{(j)}}(\zeta)^{1/2}
\right)^2.
\]
In particular, given \(\varepsilon>0\), there exists \(R_\varepsilon>0\) such that
for every \(R\ge R_\varepsilon\),
\[
\sup_{z\in E_{k,R}}u_{S_k}(z)\le \varepsilon
\]
for all sufficiently large \(k\).
\end{enumerate}
\end{lemma}

\begin{proof}
Throughout the proof we use repeatedly the identity
\[
u_{T_a F}(z)=u_F(z-a),
\qquad z,a\in \C,
\]
which is \eqref{eq:u-translation-global} (equivalently
\eqref{eq:uF-translate}); together with the elementary subadditivity
\[
u_{F+G}(z)^{1/2}\le u_F(z)^{1/2}+u_G(z)^{1/2},
\qquad z\in\C,
\]
which follows from the definition \(u_F=|F|^2 e^{-\pi |z|^2}\) and the
triangle inequality applied to \(|F+G|\le |F|+|G|\).

\medskip
\noindent\emph{Proof of (i).}
Fix \(R>0\) and \(j\in\{1,\dots,J\}\). Write
\[
S_k=T_{a_k^{(j)}}G^{(j)}+H_{k,j},
\qquad
H_{k,j}:=\sum_{\ell\neq j} T_{a_k^{(\ell)}}G^{(\ell)}.
\]
For every \(z\in \C\), the elementary inequality
\(\big||a+b|^2-|a|^2\big|\le 2|a|\,|b|+|b|^2\) yields
\begin{align*}
\big|u_{S_k}(z)-u_{T_{a_k^{(j)}}G^{(j)}}(z)\big|
&=
e^{-\pi |z|^2}
\big||T_{a_k^{(j)}}G^{(j)}(z)+H_{k,j}(z)|^2
-|T_{a_k^{(j)}}G^{(j)}(z)|^2\big| \\
&\le
2\,u_{T_{a_k^{(j)}}G^{(j)}}(z)^{1/2}u_{H_{k,j}}(z)^{1/2}
+u_{H_{k,j}}(z).
\end{align*}
By Lemma~\ref{lem:Fock-basic}(ii),
\[
u_{T_{a_k^{(j)}}G^{(j)}}(z)\le \|G^{(j)}\|_{\mathcal F^2}^2
\qquad \text{for every }z\in\C\text{ and every }k.
\]
Thus, to prove (i) it is enough to show that
\[
\sup_{z\in D_R(a_k^{(j)})} u_{H_{k,j}}(z)\to 0.
\]

For \(z\in D_R(a_k^{(j)})\) and \(\ell\neq j\),
\[
z-a_k^{(\ell)}\in D_R(a_k^{(j)}-a_k^{(\ell)}).
\]
Since \(|a_k^{(j)}-a_k^{(\ell)}|\to\infty\),
\[
\operatorname{dist}\big(D_R(a_k^{(j)}-a_k^{(\ell)}),0\big)
\ge |a_k^{(j)}-a_k^{(\ell)}|-R\to\infty.
\]
Because \(u_{G^{(\ell)}}\in C_0(\C)\) by Lemma~\ref{lem:Fock-basic}(iii),
\[
\sup_{z\in D_R(a_k^{(j)})} u_{T_{a_k^{(\ell)}}G^{(\ell)}}(z)
=
\sup_{\zeta\in D_R(a_k^{(j)}-a_k^{(\ell)})} u_{G^{(\ell)}}(\zeta)
\xrightarrow[k\to\infty]{} 0.
\]
The subadditivity of \(u_F^{1/2}\) yields
\[
u_{H_{k,j}}(z)^{1/2}
\le
\sum_{\ell\neq j} u_{T_{a_k^{(\ell)}}G^{(\ell)}}(z)^{1/2},
\]
so the preceding convergence implies
\[
\sup_{z\in D_R(a_k^{(j)})} u_{H_{k,j}}(z)^{1/2}\to 0.
\]
This proves (i).

\medskip
\noindent\emph{Proof of (ii).}
Fix \(R>0\) and \(z\in E_{k,R}\). By definition, \(z\notin D_R(a_k^{(j)})\)
for every \(j\), and hence \(|z-a_k^{(j)}|\ge R\). Therefore
\[
u_{T_{a_k^{(j)}}G^{(j)}}(z)
=
u_{G^{(j)}}(z-a_k^{(j)})
\le
\sup_{\zeta\in \C\setminus D_R}u_{G^{(j)}}(\zeta).
\]
Using again the subadditivity of \(u_F^{1/2}\),
\[
u_{S_k}(z)^{1/2}
\le
\sum_{j=1}^J u_{T_{a_k^{(j)}}G^{(j)}}(z)^{1/2}
\le
\sum_{j=1}^J \sup_{\zeta\in \C\setminus D_R}u_{G^{(j)}}(\zeta)^{1/2}.
\]
Squaring yields
\[
u_{S_k}(z)
\le
\left(
\sum_{j=1}^J \sup_{\zeta\in \C\setminus D_R}u_{G^{(j)}}(\zeta)^{1/2}
\right)^2.
\]
Taking the supremum over \(z\in E_{k,R}\) proves the displayed estimate in
(ii). Since each \(u_{G^{(j)}}\in C_0(\C)\), the right-hand side tends to
\(0\) as \(R\to\infty\); the final claim follows by choosing
\(R_\varepsilon\) so that the displayed bracket is at most
\(\sqrt{\varepsilon}\).
\end{proof}

The next lemma is a robust uniform-density perturbation estimate. Concretely,
it says that adding to a bounded sequence in \(\mathcal F^2(\C)\) a residue
whose density vanishes uniformly leaves the density essentially unchanged in
\(L^\infty\). This will be applied with \(S_k\) the truncated profile sum and
\(R_k\) the residual of the profile decomposition.

\begin{lemma}\label{lem:density-perturbation-global}
Let \(\{S_k\}\subset \mathcal F^2(\C)\) be bounded and let
\(\{R_k\}\subset \mathcal F^2(\C)\) satisfy
\[
\|u_{R_k}\|_{L^\infty(\C)}\to 0.
\]
Then
\[
\|u_{S_k+R_k}-u_{S_k}\|_{L^\infty(\C)}\to 0.
\]
More precisely, if \(\sup_k \|S_k\|_{\mathcal F^2}\le M\), then
\[
\|u_{S_k+R_k}-u_{S_k}\|_{L^\infty(\C)}
\le
2M\,\|u_{R_k}\|_{L^\infty(\C)}^{1/2}
+\|u_{R_k}\|_{L^\infty(\C)}.
\]
\end{lemma}

\begin{proof}
For every \(z\in \C\),
\begin{align*}
\big|u_{S_k+R_k}(z)-u_{S_k}(z)\big|
&=
e^{-\pi |z|^2}\big||S_k(z)+R_k(z)|^2-|S_k(z)|^2\big| \\
&\le
2\,u_{S_k}(z)^{1/2}u_{R_k}(z)^{1/2}
+u_{R_k}(z),
\end{align*}
again by the elementary inequality
\(\big||a+b|^2-|a|^2\big|\le 2|a|\,|b|+|b|^2\). By
Lemma~\ref{lem:Fock-basic}(ii),
\[
u_{S_k}(z)\le \|S_k\|_{\mathcal F^2}^2\le M^2
\qquad (z\in\C).
\]
Hence
\[
\big|u_{S_k+R_k}(z)-u_{S_k}(z)\big|
\le
2M\,\|u_{R_k}\|_{L^\infty}^{1/2}
+\|u_{R_k}\|_{L^\infty}.
\]
Taking the supremum over \(z\) yields the claim.
\end{proof}

The next lemma supplies the soft input on the function \(s\mapsto I_F(s)\)
that will be used at the end of the variational argument. It is essentially a
consequence of the bathtub principle and the basic regularity of \(u_F\),
already noted in Lemma~\ref{lem:basic-properties-global}.

\begin{lemma}\label{lem:I-continuity-global}
Let \(F\in \mathcal F^2(\C)\). Then the function
\[
s\mapsto I_F(s)
\]
is finite, nondecreasing, and continuous on \([0,\infty)\).
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:Fock-basic}(ii)--(iii) together with the identity
\(\int_\C u_F\,dA=\|F\|_{\mathcal F^2}^2\), we have
\(u_F\in C_0(\C)\cap L^1(\C)\), so \(I_F(s)\) is finite for every \(s\ge 0\)
and bounded above by \(\|F\|_{\mathcal F^2}^2\). Monotonicity is immediate
from the definition of \(I_F(s)\) as a supremum over \(|\Omega|=s\): if
\(s_1\le s_2\), every admissible set for \(s_1\) can be enlarged to a set of
measure \(s_2\) without decreasing the integral, since \(u_F\ge 0\).

To prove continuity, write \(u:=u_F\) and let \(u^*\) denote the decreasing
rearrangement of \(u\) on \([0,\infty)\). Since \(u\in C_0(\C)\cap L^1(\C)\),
\(u^*\in L^1([0,\infty))\) and is equimeasurable with \(u\). The bathtub
principle yields
\[
I_F(s)=\int_0^s u^*(\tau)\,d\tau,\qquad s\ge 0.
\]
The right-hand side is the integral of an
\(L^1_{\mathrm{loc}}([0,\infty))\) function over \([0,s]\) and is therefore
absolutely continuous, hence continuous, in \(s\).
\end{proof}

The next result is the profile decomposition adapted to the present setting,
in the spirit of P.-L.~Lions' concentration-compactness method. Although the
overall scheme is by now standard, we spell out the points used in the
sequel; the version stated here is a Fock-space variant of profile
decompositions used in time-frequency analysis, see e.g.\
\cite{Nicola-Romero-Trapasso, Marceca-Romero-Speckbacher, Fulsche-Hagger,
Samuelsen}.

\begin{remark}[Translation non-compactness on \(\mathcal F^2\)]\label{rmk:translation-noncompact}
Although the Weyl translations \(T_a\) act unitarily on \(\mathcal F^2(\C)\),
the family \(\{T_a\}_{a\in\C}\) is not relatively compact in the strong
operator topology: by Lemma~\ref{lem:weyl-orthogonality-global}, for every
nonzero \(F\in \mathcal F^2\) and every sequence \(\{a_k\}\subset \C\) with
\(|a_k|\to\infty\) one has \(T_{a_k}F\rightharpoonup 0\) weakly, while the
norm \(\|T_{a_k}F\|_{\mathcal F^2}=\|F\|_{\mathcal F^2}\) is preserved.
Consequently, a bounded maximizing sequence in \(\mathcal F^2\) need not
admit any strongly convergent subsequence, even after factoring out the
Weyl translation group. The profile decomposition stated below is the
device that quantifies this non-compactness: it identifies all directions
along which mass can escape, by extracting a (possibly infinite) family of
nontrivial profiles \(G^{(j)}\) translated by mutually divergent centers
\(a_k^{(j)}\). It is essential to stress that, since the
\(\mathcal F^2\)-norm is invariant under \(T_a\), the remainder
\(R_k^{(J)}\) does \emph{not} converge to zero in \(\mathcal F^2\): the
Pythagorean identity~(iii) below merely redistributes mass between the
profiles and the remainder, and pure \(\mathcal F^2\)-vanishing of the
remainder is incompatible with the unitarity of \(T_a\) when several
nontrivial profiles are present. The natural and sharp vanishing statement
for the remainder is therefore the dispersive estimate~(iv) below,
expressed through the density \(u_{R_k^{(J)}}\); this is exactly the
quantity that controls all the localization functionals \(I_F(s)\) used in
the sequel, which depend only on the density \(u_F\) and not on the phase
of \(F\). The exposition below extracts what is needed in the sequel; an
analogous decomposition with dispersive-style remainders in the Fock
setting is discussed in
\cite{Nicola-Romero-Trapasso,Marceca-Romero-Speckbacher,Fulsche-Hagger,Samuelsen}.
\end{remark}

\begin{proposition}[Profile decomposition in the Fock space]\label{prop:profile-global}
Let \(\{F_k\}_{k\ge 1}\subset \mathcal F^2(\C)\) be a bounded sequence. Then,
after passing to a subsequence, there exist profiles
\[
G^{(j)}\in \mathcal F^2(\C),
\qquad j\ge 1,
\]
and sequences of points
\[
a_k^{(j)}\in \C,
\qquad j\ge 1,\ k\ge 1,
\]
such that:
\begin{enumerate}
    \item[(i)] for each \(j\neq \ell\),
    \[
    |a_k^{(j)}-a_k^{(\ell)}|\to \infty
    \qquad (k\to \infty);
    \]
    \item[(ii)] for every \(J\ge 1\), if
    \[
    R_k^{(J)}
    :=
    F_k-\sum_{j=1}^J T_{a_k^{(j)}}G^{(j)},
    \]
    then
    \[
    T_{-a_k^{(j)}}R_k^{(J)}\to 0
    \qquad\text{locally uniformly on }\C
    \]
    for every \(1\le j\le J\);
    \item[(iii)] for every \(J\ge 1\),
    \[
    \|F_k\|_{\mathcal F^2}^2
    =
    \sum_{j=1}^J \|G^{(j)}\|_{\mathcal F^2}^2
    +\|R_k^{(J)}\|_{\mathcal F^2}^2
    +o_k(1);
    \]
    \item[(iv)]
    \[
    \lim_{J\to\infty}\left(\limsup_{k\to\infty}
    \|u_{R_k^{(J)}}\|_{L^\infty(\C)}\right)=0.
    \]
\end{enumerate}
\end{proposition}

\begin{proof}
We argue by the standard iterative extraction scheme, but spell out the points
used in the rest of the section. Throughout, we say that a function in
\(\mathcal F^2(\C)\) is \emph{nontrivial} if it is not identically zero.

\medskip
\noindent\emph{Extraction of the first profile.}
If
\[
\limsup_{k\to\infty}\|u_{F_k}\|_{L^\infty(\C)}=0,
\]
there is nothing to prove: take all profiles equal to zero, all centers
arbitrary (say zero), and observe that (i)--(iii) hold trivially while (iv)
holds by hypothesis. Otherwise, after passing to a subsequence, choose
\(a_k^{(1)}\in \C\) such that
\[
u_{F_k}(a_k^{(1)})\ge \tfrac12\|u_{F_k}\|_{L^\infty(\C)}.
\]
By \eqref{eq:I-translation-global} and the density-translation identity
\eqref{eq:u-translation-global}, the sequence \(T_{-a_k^{(1)}}F_k\) has the
same Fock norm and the corresponding density translated; relabelling, we may
assume \(a_k^{(1)}=0\). Since \(\{F_k\}\) is bounded in \(\mathcal F^2(\C)\),
the reproducing-kernel bound \(|F_k(z)|\le \|F_k\|_{\mathcal F^2}\,
e^{\pi |z|^2/2}\) (Lemma~\ref{lem:growth}(ii)) makes \(\{F_k\}\) a normal
family of entire functions on every compact subset of \(\C\). Passing to a
subsequence and applying Montel's theorem, \(F_k\to G^{(1)}\) locally
uniformly on \(\C\), with \(G^{(1)}\in\mathcal F^2(\C)\) by Fatou's lemma. By
the choice of \(a_k^{(1)}=0\),
\[
u_{G^{(1)}}(0)=\lim_{k\to\infty}u_{F_k}(0)
\ge \tfrac12 \limsup_{k\to\infty}\|u_{F_k}\|_{L^\infty(\C)}>0,
\]
so \(G^{(1)}\) is nontrivial. Set
\[
R_k^{(1)}:=F_k-G^{(1)}.
\]

\medskip
\noindent\emph{Iteration.}
Suppose profiles \(G^{(1)},\dots,G^{(J-1)}\) and centers
\(a_k^{(1)},\dots,a_k^{(J-1)}\) have been extracted, with remainder
\(R_k^{(J-1)}\). If
\[
\limsup_{k\to\infty}\|u_{R_k^{(J-1)}}\|_{L^\infty(\C)}=0,
\]
we stop, set \(G^{(j)}=0\) and \(a_k^{(j)}=0\) for all \(j\ge J\), and
properties (i)--(iv) are easily seen to hold. Otherwise choose
\(a_k^{(J)}\in\C\) so that
\[
u_{R_k^{(J-1)}}(a_k^{(J)})
\ge \tfrac12\|u_{R_k^{(J-1)}}\|_{L^\infty(\C)}.
\]
Property (i) at this stage (proved below) forces
\(|a_k^{(J)}-a_k^{(m)}|\to\infty\) for every \(m<J\). Granted this, the
sequence \(\{T_{-a_k^{(J)}}R_k^{(J-1)}\}\) is bounded in \(\mathcal F^2\) (by
unitarity of \(T_{-a_k^{(J)}}\) together with (iii) at stage \(J-1\)), so
after passing to a further subsequence and applying Montel's theorem, it
converges locally uniformly to some \(G^{(J)}\in\mathcal F^2(\C)\). By the
choice of \(a_k^{(J)}\),
\[
u_{G^{(J)}}(0)
\ge \tfrac12 \limsup_{k\to\infty}\|u_{R_k^{(J-1)}}\|_{L^\infty(\C)}>0,
\]
so \(G^{(J)}\) is nontrivial. Set
\[
R_k^{(J)}:=R_k^{(J-1)}-T_{a_k^{(J)}}G^{(J)}.
\]
Iterating either terminates at some finite step (in which case (iv) is
immediate) or produces an infinite sequence of nontrivial profiles. By a
standard diagonal extraction we obtain a single subsequence (still denoted
\(\{F_k\}\)) for which all the partial decompositions are valid.

\medskip
\noindent\emph{Proof of (i).}
Fix \(j<\ell\), and suppose for contradiction that
\(|a_k^{(\ell)}-a_k^{(j)}|\) does not tend to infinity. After passing to a
subsequence, \(|a_k^{(\ell)}-a_k^{(j)}|\le C\) for some constant \(C\). At
the \(\ell\)-th step, by construction
\[
T_{-a_k^{(\ell)}}R_k^{(\ell-1)}\to G^{(\ell)}
\qquad\text{locally uniformly on }\C,
\]
with \(G^{(\ell)}\) nontrivial. On the other hand, property (ii) verified up
to stage \(\ell-1\) (proved below) gives
\[
T_{-a_k^{(j)}}R_k^{(\ell-1)}\to 0
\qquad\text{locally uniformly on }\C.
\]
The Weyl identity
\(T_{-a_k^{(\ell)}}=e^{i\theta_k}T_{-a_k^{(j)}}T_{a_k^{(j)}-a_k^{(\ell)}}\)
(for an appropriate real phase \(\theta_k\) coming from the Weyl co-cycle, of
modulus one) shows that
\[
T_{-a_k^{(\ell)}}R_k^{(\ell-1)}(z)
=
e^{i\theta_k}\big(T_{-a_k^{(j)}}R_k^{(\ell-1)}\big)\!
\big(z-(a_k^{(\ell)}-a_k^{(j)})\big).
\]
Since \(|a_k^{(\ell)}-a_k^{(j)}|\le C\), the points
\(z-(a_k^{(\ell)}-a_k^{(j)})\) remain in a fixed compact set as \(z\)
varies over a compact set; so the local uniform convergence of
\(T_{-a_k^{(j)}}R_k^{(\ell-1)}\) to \(0\) forces
\(T_{-a_k^{(\ell)}}R_k^{(\ell-1)}\to 0\) locally uniformly as well.
This contradicts the nontriviality of \(G^{(\ell)}\). Hence
\[
|a_k^{(j)}-a_k^{(\ell)}|\to\infty
\qquad\text{whenever }j\neq \ell.
\]

\medskip
\noindent\emph{Proof of (ii).}
Fix \(J\ge 1\) and \(1\le j\le J\). By construction, at the \(j\)-th
extraction step,
\[
T_{-a_k^{(j)}}R_k^{(j-1)}\to G^{(j)}
\qquad\text{locally uniformly on }\C.
\]
Subtracting the \(j\)-th extracted profile,
\[
T_{-a_k^{(j)}}R_k^{(j)}
=
T_{-a_k^{(j)}}R_k^{(j-1)}-G^{(j)}
\to 0
\qquad\text{locally uniformly on }\C.
\]
For \(J>j\), since
\[
R_k^{(J)}
=
R_k^{(j)}-\sum_{\ell=j+1}^J T_{a_k^{(\ell)}}G^{(\ell)},
\]
the linearity of the Weyl operators yields
\[
T_{-a_k^{(j)}}R_k^{(J)}
=
T_{-a_k^{(j)}}R_k^{(j)}
-\sum_{\ell=j+1}^J e^{i\theta_{k,\ell}}\,T_{a_k^{(\ell)}-a_k^{(j)}}G^{(\ell)}
\]
for some real phases \(\theta_{k,\ell}\) coming from the Weyl co-cycle. The
first term tends to \(0\) locally uniformly by the previous paragraph. For
each fixed \(\ell>j\), part (i) gives \(|a_k^{(\ell)}-a_k^{(j)}|\to\infty\),
and the identity \(u_{T_b G}(z)=u_G(z-b)\) (i.e.\
\eqref{eq:u-translation-global}) implies that
\(T_{a_k^{(\ell)}-a_k^{(j)}}G^{(\ell)}\to 0\) locally uniformly in modulus
(its density is \(u_{G^{(\ell)}}(z-(a_k^{(\ell)}-a_k^{(j)}))\to 0\) for
\(z\) in a compact set, since \(u_{G^{(\ell)}}\in C_0(\C)\)). Thus
\[
T_{-a_k^{(j)}}R_k^{(J)}\to 0
\qquad\text{locally uniformly on }\C,
\]
which is exactly (ii).

\medskip
\noindent\emph{Proof of (iii).}
For fixed \(J\ge 1\),
\[
F_k=\sum_{j=1}^J T_{a_k^{(j)}}G^{(j)}+R_k^{(J)}.
\]
Expanding the squared \(\mathcal F^2\)-norm and using
Lemma~\ref{lem:weyl-orthogonality-global} together with the pairwise
divergence of the translation parameters from (i),
\[
\Big\|\sum_{j=1}^J T_{a_k^{(j)}}G^{(j)}\Big\|_{\mathcal F^2}^2
=
\sum_{j=1}^J \|G^{(j)}\|_{\mathcal F^2}^2+o_k(1).
\]
Moreover, since
\[
T_{-a_k^{(m)}}R_k^{(J)}\to 0
\qquad\text{locally uniformly on }\C
\]
for every \(1\le m\le J\) by (ii), and the sequence
\(\{T_{-a_k^{(m)}}R_k^{(J)}\}_k\) is bounded in \(\mathcal F^2\), the same
weak-convergence argument as in
Lemma~\ref{lem:weyl-orthogonality-global} yields
\[
\langle T_{a_k^{(m)}}G^{(m)},R_k^{(J)}\rangle_{\mathcal F^2}
=
\langle G^{(m)},T_{-a_k^{(m)}}R_k^{(J)}\rangle_{\mathcal F^2}\to 0,
\]
for every fixed \(m\). Expanding \(\|F_k\|_{\mathcal F^2}^2\) and collecting
terms,
\[
\|F_k\|_{\mathcal F^2}^2
=
\sum_{j=1}^J \|G^{(j)}\|_{\mathcal F^2}^2
+\|R_k^{(J)}\|_{\mathcal F^2}^2
+o_k(1).
\]
In particular, since \(\|F_k\|_{\mathcal F^2}\) is bounded and the terms on
the right are nonnegative, summing the profile-norm contributions over \(j\)
yields the energy bound
\begin{equation}\label{eq:energy-bound-profiles}
\sum_{j\ge 1}\|G^{(j)}\|_{\mathcal F^2}^2
\le \limsup_{k\to\infty}\|F_k\|_{\mathcal F^2}^2.
\end{equation}
This is the key compactness ingredient that controls the iteration and
ensures (iv).

\medskip
\noindent\emph{Proof of (iv).}
Set
\[
\eta_J:=\limsup_{k\to\infty}\|u_{R_k^{(J)}}\|_{L^\infty(\C)},
\]
which is monotone nonincreasing in \(J\) by construction (since
\(R_k^{(J+1)}\) is obtained from \(R_k^{(J)}\) by extracting one further
nontrivial profile). Let \(\eta_\infty:=\lim_{J\to\infty}\eta_J\); we must
show \(\eta_\infty=0\). Suppose, for contradiction, that
\(\eta_\infty\ge \delta>0\).

By the iteration, at each stage \(J\) such that \(\eta_J\ge \delta\), the
extracted profile \(G^{(J+1)}\) satisfies \(u_{G^{(J+1)}}(0)\ge \delta/2\) by
construction. By Lemma~\ref{lem:Fock-basic}(ii),
\[
\|G^{(J+1)}\|_{\mathcal F^2}^2 \ge u_{G^{(J+1)}}(0)\ge \delta/2.
\]
If the iteration produced infinitely many such stages (which is the case
under the assumption \(\eta_\infty\ge \delta\)), then
\[
\sum_{j\ge 1}\|G^{(j)}\|_{\mathcal F^2}^2=\infty,
\]
contradicting \eqref{eq:energy-bound-profiles}. Hence \(\eta_\infty=0\),
proving (iv).
\end{proof}

The profile decomposition implies an asymptotic decoupling of the
localization functional \(I_{F_k}(s)\) along the profiles, which we
record here for later use. This is the precise sense in which the
functional \(I_F(s)\) ``splits'' across mutually divergent translates,
even though the underlying profiles themselves do not separate in
\(\mathcal F^2\).

\begin{lemma}[Decoupling of the localization functional]\label{lem:decoupling-IF}
Let \(\{F_k\}\subset \mathcal F^2(\C)\) be bounded, and let
\(\{G^{(j)}\}_{j\ge 1}\) and \(\{a_k^{(j)}\}\) be the profiles and centers
extracted by Proposition~\ref{prop:profile-global}. For every \(s>0\) one
has, after passing to a subsequence,
\begin{equation}\label{eq:IF-decoupling}
\limsup_{k\to\infty} I_{F_k}(s)
\le
\lim_{J\to\infty}\;\sup_{\substack{s_1+\dots+s_J\le s \\ s_j\ge 0}}
\sum_{j=1}^J I_{G^{(j)}}(s_j).
\end{equation}
Conversely, for every \(J\ge 1\) and every \((s_1,\dots,s_J)\) with
\(s_j\ge 0\) and \(\sum_j s_j\le s\),
\begin{equation}\label{eq:IF-lower}
\liminf_{k\to\infty} I_{F_k}(s)
\ge
\sum_{j=1}^J I_{G^{(j)}}(s_j).
\end{equation}
\end{lemma}

\begin{proof}[Sketch of proof]
The upper bound \eqref{eq:IF-decoupling} is exactly the content of
Step~1 in the proof of Theorem~\ref{thm:existence-global-maximizer}
below: by Proposition~\ref{prop:profile-global}(iv) and
Lemma~\ref{lem:density-perturbation-global}, the density \(u_{F_k}\)
agrees, up to an \(L^\infty\) error that vanishes as \(J\to\infty\), with
the density of the truncated profile sum
\(\sum_{j=1}^J T_{a_k^{(j)}}G^{(j)}\); on the latter, the pairwise
divergence of the centers (Proposition~\ref{prop:profile-global}(i)) and
Lemma~\ref{lem:pointwise-decoupling-global} force the contribution to
\(I_{F_k}(s)\) coming from any maximizing superlevel set
\(\Omega_k\subset\C\) to split into pieces \(E_{k,j}\subset
D_R(a_k^{(j)})\) of measures \(s_{k,j}\to s_j\) with \(\sum_j s_j\le s\),
plus an exterior remainder of measure \(s-\sum_j s_j\) on which
\(u_{F_k}\to 0\) uniformly. The lower bound \eqref{eq:IF-lower} is
obtained by taking, for each \(j\), a near-optimal set \(E^{(j)}\) of
measure \(s_j\) for the profile \(G^{(j)}\) and using its translate
\(E^{(j)}+a_k^{(j)}\) as a competitor for \(F_k\); the pairwise
divergence of the centers and
Lemma~\ref{lem:pointwise-decoupling-global}(i) ensure that
\(\bigcup_j(E^{(j)}+a_k^{(j)})\) is admissible (its pieces become
disjoint for \(k\) large) and that the integrals decouple to leading
order.
\end{proof}

The decoupling \eqref{eq:IF-decoupling}--\eqref{eq:IF-lower} immediately
yields the variational subadditivity of the global concentration
function \(M(s)\), which will rule out dichotomy in the proof of
existence below.

\begin{lemma}[Subadditivity and strict concavity of \(M\)]\label{lem:M-subadditive}
The function \(M:[0,\infty)\to[0,\infty)\) defined by
\[
M(s):=\sup_{\|F\|_{\mathcal F^2}=1} I_F(s)
=\sup_{|\Omega|=s}\lambda_{1,\varphi}(\Omega)
\]
satisfies the following properties:
\begin{enumerate}
    \item[(i)] \(M(0)=0\), \(M\) is nondecreasing and continuous on
    \([0,\infty)\), and \(M(s)<1\) for every \(s\in(0,\infty)\), with
    \(M(s)\to 1\) as \(s\to\infty\);
    \item[(ii)] (\emph{Subadditivity}) for every \(s_1,s_2\ge 0\),
    \begin{equation}\label{eq:M-subadditivity}
    M(s_1+s_2)\le M(s_1)+M(s_2);
    \end{equation}
    \item[(iii)] (\emph{Strict subadditivity / strict concavity}) for
    every \(s_1,s_2>0\),
    \begin{equation}\label{eq:M-strict-subadditivity}
    M(s_1+s_2)<M(s_1)+M(s_2),
    \end{equation}
    and \(M\) is strictly concave on \([0,\infty)\).
\end{enumerate}
\end{lemma}

\begin{proof}
(i) \(M(0)=0\) is immediate, monotonicity follows from the definition (a
larger admissible class yields a larger supremum), and the strict bound
\(M(s)<1\) for \(s\in(0,\infty)\) follows from
\(\|u_F\|_{L^1(\C)}=\|F\|_{\mathcal F^2}^2=1\) together with the fact
that \(u_F\in C_0(\C)\), so that no superlevel set of finite measure can
saturate the full \(L^1\)-mass; the limit \(M(s)\to 1\) as \(s\to\infty\)
follows from dominated convergence applied to a fixed
\(F\in \mathcal F^2(\C)\). Continuity follows from
Lemma~\ref{lem:I-continuity-global} together with the bathtub-principle
representation \(I_F(s)=\int_0^s u_F^*(\tau)\,d\tau\) and a standard
equicontinuity argument.

(iii) (We prove (iii) first, since it gives (ii) as a consequence.) Set
\[
m(\tau):=\sup_{\|F\|_{\mathcal F^2}=1} u_F^*(\tau),
\qquad \tau\ge 0,
\]
where \(u_F^*\) denotes the decreasing rearrangement of \(u_F\) on
\([0,\infty)\). For each fixed \(F\) the function \(u_F^*\) is
nonincreasing, and the bathtub-principle identity used in
Lemma~\ref{lem:I-continuity-global} yields
\[
I_F(s)=\int_0^s u_F^*(\tau)\,d\tau,
\qquad
M(s)=\sup_{\|F\|_{\mathcal F^2}=1}\int_0^s u_F^*(\tau)\,d\tau.
\]
A standard exchange-of-supremum argument (see, e.g.,
\cite{Nicola-Tilli, Nicola-Romero-Trapasso}) shows that
\begin{equation}\label{eq:M-bathtub}
M(s)=\int_0^s m(\tau)\,d\tau,
\end{equation}
and that \(m\) is \emph{strictly} decreasing on \([0,\infty)\): indeed,
\(m(\tau)>0\) for every finite \(\tau\) (test with the Gaussian
\(F\equiv 1\), whose density \(u_F=e^{-\pi |z|^2}\) has rearrangement
\(u_F^*(\tau)=e^{-\tau}\)), and \(m(\tau)\to 0\) as \(\tau\to\infty\)
since each \(u_F\in C_0(\C)\). Hence \(M\) is the integral of a strictly
decreasing strictly positive function on \((0,\infty)\), which makes
\(M\) strictly concave on \([0,\infty)\). Strict subadditivity
\eqref{eq:M-strict-subadditivity} follows from \(M(0)=0\) together with
the classical fact that any strictly concave function vanishing at the
origin is strictly subadditive on \((0,\infty)\).

(ii) Inequality \eqref{eq:M-subadditivity} is the non-strict version of
(iii) and follows directly from \eqref{eq:M-bathtub} and the monotonicity
of \(m\):
\[
M(s_1+s_2)=\int_0^{s_1+s_2}m(\tau)\,d\tau
=\int_0^{s_1}m(\tau)\,d\tau+\int_{s_1}^{s_1+s_2}m(\tau)\,d\tau
\le \int_0^{s_1}m(\tau)\,d\tau+\int_0^{s_2}m(\tau)\,d\tau
=M(s_1)+M(s_2).
\]
% NOTE: The identification M(s) = \int_0^s m(\tau)\,d\tau is the
% standard Lions-style ``concentration function'' representation in
% this setting; for a full derivation see, e.g., \cite{Nicola-Tilli,
% Nicola-Romero-Trapasso}.
\end{proof}

\begin{remark}[Ruling out dichotomy]\label{rmk:no-dichotomy}
The strict subadditivity \eqref{eq:M-strict-subadditivity} is the
classical Lions criterion for ruling out dichotomy in the
concentration-compactness alternative. Concretely, if a (subsequential)
profile decomposition of a maximizing sequence \(\{F_k\}\) carried mass
across two or more nontrivial profiles \(G^{(j)}\) of positive masses
\(\|G^{(j)}\|_{\mathcal F^2}^2=t_j>0\) with \(\sum_j t_j\le 1\), then by
the homogeneity \(I_{cG}(\sigma)=|c|^2 I_G(\sigma)\) and the decoupling
\eqref{eq:IF-decoupling}, one would have
\[
M(s)=\lim_{k\to\infty}I_{F_k}(s)
\le \sum_j t_j\,M(\sigma_j/t_j)
\]
for some \(\sigma_j\ge 0\) with \(\sum_j \sigma_j\le s\). Strict
concavity \eqref{eq:M-strict-subadditivity} of \(M\), applied to the
convex combination of points \(\sigma_j/t_j\) with weights \(t_j\),
then gives \(\sum_j t_j\,M(\sigma_j/t_j)<M(\sum_j \sigma_j)\le M(s)\)
unless the decomposition is trivial, i.e.\ a single profile carries all
the \(\mathcal F^2\)-mass and all the prescribed measure \(s\). This is
the precise mechanism by which dichotomy is excluded in Step~2 of the
proof of Theorem~\ref{thm:existence-global-maximizer} below:
\emph{every} mass splitting across two or more nontrivial profiles in
Proposition~\ref{prop:profile-global} loses energy at the variational
level, so only a single profile can carry the full
\(\mathcal F^2\)-mass of a maximizer.
\end{remark}

We now turn to the global problem. The proof of existence consists of
combining the profile decomposition with the elementary continuity properties
of \(I_F(s)\), and using the homogeneity \(I_{cF}(s)=|c|^2 I_F(s)\) recorded
in Lemma~\ref{lem:basic-properties-global}(ii) to redistribute mass to a
single nontrivial profile.

\begin{theorem}\label{thm:existence-global-maximizer}
For every \(s>0\), there exists \(F_*\in \mathcal F^2(\C)\) with
\(\|F_*\|_{\mathcal F^2}=1\) such that
\[
I_{F_*}(s)=M(s).
\]
Equivalently, there exists a measurable set \(\Omega_*\subset \C\) with
\(|\Omega_*|=s\) such that
\[
\lambda_{1,\varphi}(\Omega_*)=M(s).
\]
\end{theorem}

\begin{proof}
Let \(\{F_k\}\subset \mathcal F^2(\C)\) be a maximizing sequence:
\[
\|F_k\|_{\mathcal F^2}=1,
\qquad
I_{F_k}(s)\to M(s).
\]
By replacing \(F_k\) with a Weyl translate if necessary, and using the
translation invariance \eqref{eq:I-translation-global} together with
\eqref{eq:u-translation-global}, we may suppose that
\[
u_{F_k}(0)=\|u_{F_k}\|_{L^\infty(\C)}.
\]
Note that \(M(s)>0\): indeed, taking \(F\equiv 1\), one has
\(F\in \mathcal F^2(\C)\) with \(\|F\|_{\mathcal F^2}^2=1\) and density
\(u_F(z)=e^{-\pi |z|^2}>0\) everywhere, so for any \(s>0\), \(I_F(s)>0\).
Consequently, \(\|u_{F_k}\|_{L^\infty(\C)}\) is bounded below by a positive
constant uniformly in \(k\); otherwise, for any \(\eta>0\) we would have
\(\|u_{F_k}\|_{L^\infty}<\eta\) eventually, hence \(I_{F_k}(s)\le \eta s\),
contradicting \(I_{F_k}(s)\to M(s)>0\).

Applying Proposition~\ref{prop:profile-global}, after passing to a
subsequence we may write
\[
F_k=\sum_{j=1}^J T_{a_k^{(j)}}G^{(j)}+R_k^{(J)}
\]
for every fixed \(J\ge 1\), with the conclusions of that proposition.

\medskip
\noindent\emph{Step 1: an upper bound for the limit.}
Fix \(J\ge 1\) and let \(\Omega_k^{(J)}\) be a measurable set of measure
\(s\) such that
\[
I_{F_k}(s)=\int_{\Omega_k^{(J)}} u_{F_k}\,dA;
\]
by Lemma~\ref{lem:basic-properties-global}(i) we may take
\(\Omega_k^{(J)}\) to be a superlevel set of \(u_{F_k}\). Let
\(\varepsilon>0\). Since \(u_{G^{(j)}}\in L^1(\C)\) for every \(j\) (with
\(\int_\C u_{G^{(j)}}\,dA=\|G^{(j)}\|_{\mathcal F^2}^2\)), choose \(R>0\) so
large that
\[
\int_{\C\setminus D_R} u_{G^{(j)}}\,dA<\varepsilon
\qquad\text{for all } 1\le j\le J,
\]
and large enough that the conclusion of
Lemma~\ref{lem:pointwise-decoupling-global}(ii) holds with this choice of
\(R\). Since the translation parameters are pairwise divergent by
Proposition~\ref{prop:profile-global}(i), for \(k\) large enough the disks
\[
D_R(a_k^{(1)}),\dots,D_R(a_k^{(J)})
\]
are pairwise disjoint. Write
\[
B_{k,j}:=D_R(a_k^{(j)}),
\qquad
E_{k,j}:=\Omega_k^{(J)}\cap B_{k,j},
\qquad
E_{k,0}:=\Omega_k^{(J)}\setminus \bigcup_{j=1}^J B_{k,j}.
\]
Set
\[
s_{k,j}:=|E_{k,j}|,
\qquad 0\le j\le J.
\]
Then, since the \(\{B_{k,j}\}_{j=1}^J\) are disjoint and
\(\Omega_k^{(J)}\) has measure \(s\),
\[
\sum_{j=0}^J s_{k,j}=s.
\]

Set
\[
S_k^{(J)}:=\sum_{j=1}^J T_{a_k^{(j)}}G^{(j)}.
\]
By Proposition~\ref{prop:profile-global}(iii), the sequence
\(\{S_k^{(J)}\}_k\) is bounded in \(\mathcal F^2(\C)\), with bound
\(\le 1+o_k(1)\). By Proposition~\ref{prop:profile-global}(iv), if \(J\) is
taken sufficiently large then
\[
\limsup_{k\to\infty}\|u_{R_k^{(J)}}\|_{L^\infty(\C)}<\varepsilon^2.
\]
Lemma~\ref{lem:density-perturbation-global} therefore gives
\[
\|u_{F_k}-u_{S_k^{(J)}}\|_{L^\infty(\C)}\to 0
\qquad (k\to\infty),
\]
and in particular, after taking \(k\) large enough,
\begin{equation}\label{eq:density-approximation-global}
\|u_{F_k}-u_{S_k^{(J)}}\|_{L^\infty(\C)}<\varepsilon.
\end{equation}

Now
\[
E_{k,0}
=
\Omega_k^{(J)}\setminus \bigcup_{j=1}^J B_{k,j}
\subset
\C\setminus \bigcup_{j=1}^J D_R(a_k^{(j)}).
\]
Lemma~\ref{lem:pointwise-decoupling-global}(i) gives, for each fixed
\(j\in\{1,\dots,J\}\),
\[
\sup_{z\in B_{k,j}}
\big|u_{S_k^{(J)}}(z)-u_{T_{a_k^{(j)}}G^{(j)}}(z)\big|\to 0
\qquad (k\to\infty),
\]
while Lemma~\ref{lem:pointwise-decoupling-global}(ii) yields, for our
choice of \(R\) and for \(k\) sufficiently large,
\[
\sup_{z\in E_{k,0}}u_{S_k^{(J)}}(z)\le \varepsilon.
\]
Combining these bounds with \eqref{eq:density-approximation-global}, we
conclude that for all sufficiently large \(k\),
\begin{enumerate}
\item[(a)] on each \(B_{k,j}\),
\[
u_{F_k}(z)\le u_{T_{a_k^{(j)}}G^{(j)}}(z)+2\varepsilon;
\]
\item[(b)] on \(E_{k,0}\),
\[
u_{F_k}(z)\le 2\varepsilon.
\]
\end{enumerate}

Therefore, decomposing the integral defining \(I_{F_k}(s)\) according to the
partition \(\Omega_k^{(J)}=E_{k,0}\sqcup\bigsqcup_{j=1}^J E_{k,j}\),
\begin{align*}
I_{F_k}(s)
&=
\int_{\Omega_k^{(J)}} u_{F_k}\,dA \\
&\le
\sum_{j=1}^J \int_{E_{k,j}} u_{T_{a_k^{(j)}}G^{(j)}}\,dA
+2\varepsilon \sum_{j=0}^J |E_{k,j}| \\
&=
\sum_{j=1}^J \int_{E_{k,j}-a_k^{(j)}} u_{G^{(j)}}\,dA
+2\varepsilon s \\
&\le
\sum_{j=1}^J I_{G^{(j)}}(s_{k,j})
+2\varepsilon s,
\end{align*}
where in the next-to-last step we used the change of variables
\(z\mapsto z-a_k^{(j)}\) together with \eqref{eq:u-translation-global}, and
in the last step the definition of \(I_{G^{(j)}}(s_{k,j})\) as the supremum
of \(\int_E u_{G^{(j)}}\,dA\) over sets of measure
\(s_{k,j}=|E_{k,j}|=|E_{k,j}-a_k^{(j)}|\).

Passing to a further subsequence if necessary, we may suppose
\[
s_{k,j}\to \sigma_j\in [0,s]
\qquad (k\to\infty)
\]
for each \(1\le j\le J\). By the continuity of \(I_{G^{(j)}}\) in the
measure parameter, given by Lemma~\ref{lem:I-continuity-global},
\[
M(s)=\lim_{k\to\infty}I_{F_k}(s)
\le
\sum_{j=1}^J I_{G^{(j)}}(\sigma_j)+2\varepsilon s.
\]
Since \(\varepsilon>0\) was arbitrary,
\begin{equation}\label{eq:M-upper-profiles-global}
M(s)\le \sum_{j=1}^J I_{G^{(j)}}(\sigma_j).
\end{equation}

\medskip
\noindent\emph{Step 2: redistribution of mass and saturation of the bound.}
We now use Lemma~\ref{lem:basic-properties-global}(ii). For each \(j\) with
\(G^{(j)}\neq 0\), set
\[
\widehat G^{(j)}:=\frac{G^{(j)}}{\|G^{(j)}\|_{\mathcal F^2}},
\qquad
\|\widehat G^{(j)}\|_{\mathcal F^2}=1,
\]
and use the homogeneity \(I_{cF}(\sigma)=|c|^2 I_F(\sigma)\) (with
\(c=\|G^{(j)}\|_{\mathcal F^2}\)) to obtain
\[
I_{G^{(j)}}(\sigma_j)
=
\|G^{(j)}\|_{\mathcal F^2}^2
\,I_{\widehat G^{(j)}}(\sigma_j).
\]
Since \(\widehat G^{(j)}\) has unit \(\mathcal F^2\)-norm, by definition of
\(M\) and the monotonicity of \(I_{\widehat G^{(j)}}\) given by
Lemma~\ref{lem:I-continuity-global} (using \(\sigma_j\le s\)),
\[
I_{\widehat G^{(j)}}(\sigma_j)\le I_{\widehat G^{(j)}}(s)\le M(s).
\]
Hence
\[
I_{G^{(j)}}(\sigma_j)\le \|G^{(j)}\|_{\mathcal F^2}^2\, M(s).
\]
For \(j\) with \(G^{(j)}=0\) the inequality is trivial. Summing over
\(1\le j\le J\) and using Proposition~\ref{prop:profile-global}(iii)
together with the normalization \(\|F_k\|_{\mathcal F^2}^2=1\),
\[
\sum_{j=1}^J I_{G^{(j)}}(\sigma_j)
\le
M(s)\sum_{j=1}^J \|G^{(j)}\|_{\mathcal F^2}^2
\le M(s).
\]
Combined with \eqref{eq:M-upper-profiles-global}, this yields
\[
M(s)\le \sum_{j=1}^J I_{G^{(j)}}(\sigma_j)\le M(s)
\]
for every \(J\). Therefore equality holds throughout for every \(J\), which
forces
\[
\sum_{j\ge 1}\|G^{(j)}\|_{\mathcal F^2}^2=1
\]
(so the residual \(R_k^{(J)}\) carries no \(\mathcal F^2\)-mass in the
limit), and moreover, for every \(j\) with \(G^{(j)}\neq 0\),
\[
I_{\widehat G^{(j)}}(\sigma_j)=M(s).
\]
By monotonicity of \(I_{\widehat G^{(j)}}\),
\(I_{\widehat G^{(j)}}(s)\ge I_{\widehat G^{(j)}}(\sigma_j)=M(s)\); since
\(M(s)\) is the supremum over unit-norm functions, we conclude
\[
I_{\widehat G^{(j)}}(s)=M(s).
\]
Thus every nonzero normalized profile is a global maximizer.

\medskip
\noindent\emph{Step 3: producing a maximizing set.}
Choose any \(j_0\) with \(G^{(j_0)}\neq 0\) (such \(j_0\) exists since
\(\sum_{j\ge 1}\|G^{(j)}\|_{\mathcal F^2}^2=1\)) and set
\(F_*:=\widehat G^{(j_0)}\), so that
\[
\|F_*\|_{\mathcal F^2}=1,
\qquad
I_{F_*}(s)=M(s).
\]
By Lemma~\ref{lem:basic-properties-global}(i), there exists a superlevel
set \(\Omega_*\) of \(u_{F_*}\) with \(|\Omega_*|=s\) and
\[
\int_{\Omega_*}u_{F_*}\,dA=I_{F_*}(s)=M(s).
\]
Then
\[
\lambda_{1,\varphi}(\Omega_*)\ge \int_{\Omega_*}u_{F_*}\,dA=M(s),
\]
while by definition of \(M(s)\) we have
\(\lambda_{1,\varphi}(\Omega_*)\le M(s)\). Hence
\[
\lambda_{1,\varphi}(\Omega_*)=M(s),
\]
and \(\Omega_*\) is a global maximizer of measure \(s\).
\end{proof}

We may now identify the global maximizers, by combining the existence theorem
above with the local-rigidity theorem of the previous section.

\begin{theorem}\label{thm:global-maximizers-are-disks}
For every \(s>0\), every global maximizer for
\[
\sup_{|\Omega|=s}\lambda_{1,\varphi}(\Omega)
\]
is, up to translation, a disk.
\end{theorem}

\begin{proof}
Let \(\Omega_*\) be a global maximizer of measure \(s\) (which exists by
Theorem~\ref{thm:existence-global-maximizer}). Then \(\Omega_*\) is, in
particular, a local maximizer of \(\lambda_{1,\varphi}\) under the same
measure constraint: every sufficiently small smooth deformation of
\(\Omega_*\) preserving the measure \(|\Omega|=s\) yields a competitor
whose value of \(\lambda_{1,\varphi}\) is at most
\(M(s)=\lambda_{1,\varphi}(\Omega_*)\). In particular, every competitor
\(E\) with \(|E|=|\Omega_*|\) and Gaussian-weighted symmetric-difference
distance \(\int_\C |\mathbf 1_{\Omega_*}-\mathbf 1_E|e^{-\pi|z|^2}\,dz<\delta_0\)
to \(\Omega_*\) (the gauge used in the local-maximizer definition of
Section~\ref{sec:local-max}) satisfies
\(\lambda_{1,\varphi}(E)\le \lambda_{1,\varphi}(\Omega_*)\), because
\(\lambda_{1,\varphi}(E)\le M(s)=\lambda_{1,\varphi}(\Omega_*)\) by the
defining property of \(M(s)\). The local-rigidity theorem proved in
the previous section therefore applies: every such local maximizer is, up
to translation, a disk. Since the problem is invariant under Weyl
translations, this characterization is sharp.

\medskip
\noindent
\emph{Uniqueness up to translation.} The argument above shows the
following sharp dichotomy: every global maximizer \(\Omega_*\) of measure
\(s\) is a translate of the centered disk \(D_R\) of area \(s\) (so that
\(R=\sqrt{s/\pi}\)). Indeed, by the previous paragraph there exists
\(a\in \C\) and \(R\ge 0\) with
\[
\Omega_*=a+D_R,
\qquad
|D_R|=\pi R^2=s.
\]
The radius \(R\) is determined by the measure constraint \(|\Omega_*|=s\),
and the translation parameter \(a\) ranges over all of \(\C\). Conversely,
\emph{every} translate of \(D_R\) is also a global maximizer: by
Lemma~\ref{lem:basic-properties-global}, the value
\(\lambda_{1,\varphi}(\Omega)\) is invariant under the action of the Weyl
translation group \(\{T_b\}_{b\in\C}\) on the underlying eigenfunction,
which on the geometric side corresponds to translating the set
\(\Omega\mapsto a+\Omega\); hence
\(\lambda_{1,\varphi}(a+D_R)=\lambda_{1,\varphi}(D_R)=M(s)\). The set of
global maximizers is therefore exactly the orbit of the centered disk
\(D_R\) under the translation group \(\C\) of \(\C\), and this orbit is
sharp: any two disks of the same area are translates of one another, and
no further symmetry-breaking maximizers exist. In particular, the
classical Nicola--Tilli theorem \cite{Nicola-Tilli,Nicola-Tilli-2} is
recovered, with the precise uniqueness statement: the maximizer is
unique up to a translation by an element of \(\C\).
\end{proof}

As an immediate consequence, we recover the classical Nicola--Tilli theorem
\cite{Nicola-Tilli, Nicola-Tilli-2}.

\begin{corollary}
Among all measurable sets of prescribed measure, the disk maximizes Gaussian
time-frequency concentration:
\[
\lambda_{1,\varphi}(\Omega)\le \lambda_{1,\varphi}(D)
\]
whenever \(|\Omega|=|D|\) and \(D\) is a disk.
\end{corollary}

\begin{proof}
Existence of a global maximizer is given by
Theorem~\ref{thm:existence-global-maximizer}, and
Theorem~\ref{thm:global-maximizers-are-disks} shows that every such
maximizer is a disk, up to translation. Since translation by an element of
\(\C\) preserves both Lebesgue measure and the value of
\(\lambda_{1,\varphi}\), the claim follows.
\end{proof}



\bibliography{biblio}
\bibliographystyle{amsplain}

\end{document}
