\subsection{Two perturbative auxiliary results}\label{app:auxiliary-results}

In this appendix we prove two perturbative results used in the proof of
Theorem~\ref{thm:local-perturbative}. The first is a free-boundary stability
statement around a strictly negative obstacle-type solution, in the spirit of
the perturbative one-phase results of Isakov~\cite[Chapter~5]{Isakov} and the
classical free-boundary literature on quadrature domains
\cite{Aharonov-Schiffer-Zalcman,Karp,Gustafsson,Shahgholian,Gustafsson-Shahgholian}.
The second is a local realization theorem for weighted quadrature domains near
a reference domain. Both statements are tailored to the setting of the present
paper.

\subsubsection{A perturbative free-boundary theorem}\label{app:isakov-type}

We begin with the perturbative free-boundary statement used in
Theorem~\ref{thm:perturb}. The point of the formulation below is that the
unknown domain is not obtained by solving a Dirichlet problem on a prescribed
domain. Rather, the domain is chosen so that the Newtonian potential of
\(f\,\mathbf 1_{\Omega}\) has vanishing exterior gradient. This is the
quadrature-domain, or null-quadrature, form of the one-phase problem; for
smooth boundaries it is equivalent to the overdetermined system
\[
-\Delta u=f \quad\text{in }\Omega,\qquad
u=\partial_\nu u=0 \quad\text{on }\partial\Omega,
\qquad
u=0 \quad\text{on }\C\setminus\Omega .
\]
The proof is the local Cauchy-transform version of the perturbative
free-boundary method of Isakov~\cite[Chapter~5]{Isakov}, and is also closely
related to the perturbative quadrature-domain construction of
\cite{Cherednichenko,Gustafsson,Gustafsson-Shahgholian,Shahgholian,Karp}.

Let \(\Omega_0\subset\C\simeq\R^2\) be a bounded simply connected \(C^2\)
domain. For \(\rho>0\) sufficiently small, every \(C^2\) domain \(\Omega\)
which is \(\rho\)-close to \(\Omega_0\) can be written uniquely as a normal
graph over \(\partial\Omega_0\):
\[
\partial\Omega
=
\{x+\varphi(x)\nu(x):x\in\partial\Omega_0\},
\]
where \(\nu\) is the outer unit normal to \(\partial\Omega_0\) and
\(\varphi\in C^2(\partial\Omega_0)\) is small. We denote this domain by
\(\Omega_\varphi\).

\begin{proposition}[Perturbative null-quadrature theorem]\label{prop:isakov-tailored}
Let \(\Omega_0\subset\C\) be a bounded simply connected \(C^2\) domain, let
\(\Omega'\) be an open neighborhood of \(\overline{\Omega_0}\), and let
\(f_0\in C^5(\overline{\Omega'})\) satisfy
\[
f_0>0 \qquad\text{on }\partial\Omega_0 .
\]
Assume that there exists a compactly supported function
\[
u_0\in C^1(\C)\cap C^{2,\alpha}(\overline{\Omega_0})
\qquad\text{for some }\alpha\in(0,1)
\]
such that
\begin{equation}\label{eq:appendix-reference-problem}
-\Delta u_0=f_0\,\mathbf 1_{\Omega_0}
\qquad\text{in }\mathcal D'(\C),
\end{equation}
\[
u_0=0 \quad\text{on }\C\setminus\Omega_0,
\qquad
u_0<0 \quad\text{in }\Omega_0 .
\]
Then there exist \(\varepsilon>0\) and \(\rho>0\) such that the following
holds. Whenever \(f\in C^5(\overline{\Omega'})\) satisfies
\[
\|f-f_0\|_{C^5(\overline{\Omega'})}<\varepsilon,
\]
there are a unique normal graph
\[
\Omega_f=\Omega_{\varphi(f)},\qquad
\varphi(f)\in C^2(\partial\Omega_0),\qquad
\|\varphi(f)\|_{C^2}<\rho,
\]
and a compactly supported function \(u_f\in C^1(\C)\cap
C^{2,\alpha}(\overline{\Omega_f})\) such that
\begin{equation}\label{eq:appendix-perturbed-problem}
-\Delta u_f=f\,\mathbf 1_{\Omega_f}
\qquad\text{in }\mathcal D'(\C),
\end{equation}
\[
u_f=0 \quad\text{on }\C\setminus\Omega_f,
\qquad
u_f<0 \quad\text{in }\Omega_f .
\]
In particular,
\[
u_f=\partial_\nu u_f=0
\qquad\text{on }\partial\Omega_f
\]
in the classical trace sense. Moreover, the map
\[
f\mapsto\varphi(f)
\]
is \(C^1\) from a neighborhood of \(f_0\) in \(C^5(\overline{\Omega'})\) into
\(C^2(\partial\Omega_0)\).
\end{proposition}

\begin{proof}
We give the proof in the form needed in the paper. The argument is an implicit
function theorem for the exterior Cauchy transform of the source
\(f\,\mathbf 1_{\Omega}\).

\medskip
\noindent\emph{Step 1: the exterior Cauchy-transform formulation.}
Choose a bounded \(C^2\) domain \(\Omega_2\) with
\[
\overline{\Omega_0}\subset \Omega_2,\qquad
\overline{\Omega_2}\subset \Omega',
\]
and shrink the normal-graph neighborhood of \(\Omega_0\) so that
\(\overline{\Omega_\varphi}\subset\Omega_2\) for every admissible
\(\varphi\). For such \(\varphi\) and for \(f\) close to \(f_0\), define
\[
\mathcal C(\varphi,f)(z)
:=
\int_{\Omega_\varphi}\frac{f(w)}{z-w}\,dA(w),
\qquad z\in\partial\Omega_2 .
\]
Since \(z\in\partial\Omega_2\) stays a positive distance from
\(\overline{\Omega_\varphi}\), this integral is nonsingular and defines a
\(C^2\) function of \(z\) on \(\partial\Omega_2\).

The reason this is the correct free-boundary equation is the following. Let
\[
N_{\varphi,f}(z)
:=
-\frac1{2\pi}\int_{\Omega_\varphi}\log|z-w|\,f(w)\,dA(w).
\]
Then \(-\Delta N_{\varphi,f}=f\,\mathbf 1_{\Omega_\varphi}\). Moreover,
\(\partial_zN_{\varphi,f}\) is a nonzero constant multiple of
\(\mathcal C(\varphi,f)\) on \(\C\setminus\overline{\Omega_\varphi}\). Hence
\[
\mathcal C(\varphi,f)\equiv0
\quad\text{on }\C\setminus\overline{\Omega_\varphi}
\]
if and only if \(N_{\varphi,f}\) is constant on the exterior component of
\(\C\setminus\overline{\Omega_\varphi}\). After subtracting this constant,
one obtains a compactly supported solution of
\(-\Delta u=f\,\mathbf 1_{\Omega_\varphi}\).

For the reference pair this exterior condition holds. Indeed, from
\eqref{eq:appendix-reference-problem} and \(u_0=0\) on
\(\C\setminus\Omega_0\), the function \(\partial_z u_0\) vanishes on
\(\C\setminus\overline{\Omega_0}\). On the other hand
\[
\partial_{\bar z}(\partial_z u_0)
=\frac14\Delta u_0
=-\frac14 f_0\,\mathbf 1_{\Omega_0}
\]
in distributions. The Cauchy transform of \(f_0\,\mathbf 1_{\Omega_0}\) solves
the same \(\bar\partial\)-equation up to the harmless universal constant and
vanishes at infinity. By uniqueness of compactly supported \(\bar\partial\)
solutions modulo entire functions vanishing at infinity, it follows that
\[
\mathcal C(0,f_0)(z)=0,
\qquad z\in\C\setminus\overline{\Omega_0}.
\]
In particular, \(\mathcal C(0,f_0)=0\) on \(\partial\Omega_2\).

\medskip
\noindent\emph{Step 2: functional-analytic setup.}
Let \(Y\) be the Banach space of traces on \(\partial\Omega_2\) of exterior
Cauchy transforms of \(C^2\) densities on \(\partial\Omega_0\):
\[
Y:=
\left\{
z\mapsto
\int_{\partial\Omega_0}\frac{\sigma(w)}{z-w}\,d\sigma(w)
\Big|_{\partial\Omega_2}
:\ \sigma\in C^2(\partial\Omega_0)
\right\},
\]
equipped with the quotient norm inherited from \(C^2(\partial\Omega_0)\). By
the exterior Cauchy inversion theorem on \(C^2\) curves, this norm is
equivalent to the \(C^2\)-norm of the corresponding exterior holomorphic
function on any fixed annulus between \(\partial\Omega_0\) and
\(\partial\Omega_2\).

For \(\varphi\) sufficiently small, \(\mathcal C(\varphi,f)|_{\partial\Omega_2}\)
belongs to \(Y\). This is the standard exterior balayage property of the
Cauchy transform: any \(C^2\) volume density supported in \(\Omega_2\) has, on
the exterior of \(\Omega_2\), the same Cauchy transform as a unique \(C^2\)
boundary density on \(\partial\Omega_0\). Equivalently, one applies the
exterior Cauchy inversion on \(\partial\Omega_0\) to the holomorphic function
\(\mathcal C(\varphi,f)\) in the unbounded component of
\(\C\setminus\overline{\Omega_2}\).

The map
\[
\mathcal C:
C^2(\partial\Omega_0)\times C^5(\overline{\Omega'})
\longrightarrow Y
\]
is \(C^1\) in a neighborhood of \((0,f_0)\). To see this, write
\(\Omega_\varphi=\Phi_\varphi(\Omega_0)\), where \(\Phi_\varphi\) is a
\(C^2\) diffeomorphism depending \(C^1\)-smoothly on \(\varphi\). Then
\[
\mathcal C(\varphi,f)(z)
=
\int_{\Omega_0}
\frac{f(\Phi_\varphi(w))J_\varphi(w)}{z-\Phi_\varphi(w)}\,dA(w),
\qquad z\in\partial\Omega_2 ,
\]
where \(J_\varphi=|\det D\Phi_\varphi|\). The denominator is uniformly bounded
away from zero for \(z\in\partial\Omega_2\), so differentiation in
\((\varphi,f)\) under the integral sign is justified by dominated convergence
and the standard smooth dependence of the normal graph map.

\medskip
\noindent\emph{Step 3: linearization in the boundary variable.}
Let \(\psi\in C^2(\partial\Omega_0)\) and set \(\varphi_t=t\psi\). The
Hadamard variation formula gives
\begin{equation}\label{eq:appendix-shape-derivative-null}
D_\varphi\mathcal C(0,f_0)[\psi](z)
=
\int_{\partial\Omega_0}
\frac{f_0(w)\psi(w)}{z-w}\,d\sigma(w),
\qquad z\in\partial\Omega_2 .
\end{equation}
Indeed, the first-order change of the area integral is the integral over the
thin normal shell swept by the boundary, with normal velocity \(\psi\) and
boundary density \(f_0\).

We denote the operator in \eqref{eq:appendix-shape-derivative-null} by \(L\).
We claim that
\[
L:C^2(\partial\Omega_0)\longrightarrow Y
\]
is an isomorphism. If \(L\psi=0\) on \(\partial\Omega_2\), then the Cauchy
transform
\[
F(z):=\int_{\partial\Omega_0}
\frac{f_0(w)\psi(w)}{z-w}\,d\sigma(w)
\]
is holomorphic on \(\C\setminus\overline{\Omega_0}\), vanishes at infinity,
and vanishes on the curve \(\partial\Omega_2\). By the identity theorem,
\[
F\equiv0
\qquad\text{on }\C\setminus\overline{\Omega_0}.
\]
Taking non-tangential limits on \(\partial\Omega_0\) and using the
Sokhotski--Plemelj jump relation for \(C^2\) curves, we obtain
\[
f_0\psi=0
\qquad\text{on }\partial\Omega_0 .
\]
Since \(f_0>0\) on \(\partial\Omega_0\), this gives \(\psi=0\), so \(L\) is
injective.

Conversely, let \(h\in Y\), and let \(H\) be its holomorphic extension to
\(\C\setminus\overline{\Omega_0}\), vanishing at infinity. The classical
exterior Cauchy inversion problem on the \(C^2\) curve \(\partial\Omega_0\)
gives a unique density \(\sigma\in C^2(\partial\Omega_0)\) such that
\[
H(z)=\int_{\partial\Omega_0}\frac{\sigma(w)}{z-w}\,d\sigma(w),
\qquad z\in\C\setminus\overline{\Omega_0}.
\]
The density depends continuously on the exterior trace of \(H\) by the
Fredholm theory of the Cauchy singular integral on \(C^2\) curves. Setting
\[
\psi:=\frac{\sigma}{f_0}
\]
is legitimate because \(f_0\) is strictly positive on \(\partial\Omega_0\);
then \(L\psi=h\). Thus \(L\) is onto \(Y\), and the open mapping theorem gives
a bounded inverse.

\medskip
\noindent\emph{Step 4: solving the free-boundary equation.}
We now solve
\[
\mathcal C(\varphi,f)=0
\qquad\text{on }\partial\Omega_2 .
\]
Since \(\mathcal C(0,f_0)=0\) and
\(D_\varphi\mathcal C(0,f_0)=L\) is a Banach-space isomorphism, the implicit
function theorem gives \(\varepsilon>0\), \(\rho>0\), and a unique \(C^1\) map
\[
f\mapsto\varphi(f)\in C^2(\partial\Omega_0),
\qquad
\|\varphi(f)\|_{C^2}<\rho,
\]
defined for \(\|f-f_0\|_{C^5(\overline{\Omega'})}<\varepsilon\), such that
\[
\mathcal C(\varphi(f),f)=0
\qquad\text{on }\partial\Omega_2 .
\]
Let \(\Omega_f:=\Omega_{\varphi(f)}\). Since
\(\overline{\Omega_f}\subset\Omega_2\), the function
\(\mathcal C(\varphi(f),f)\) is holomorphic on
\(\C\setminus\overline{\Omega_f}\), vanishes at infinity, and vanishes on the
curve \(\partial\Omega_2\), which lies in that domain. The identity theorem
therefore yields
\[
\mathcal C(\varphi(f),f)\equiv0
\qquad\text{on }\C\setminus\overline{\Omega_f}.
\]

\medskip
\noindent\emph{Step 5: construction of the compactly supported solution.}
Define
\[
N_f(z):=
-\frac1{2\pi}\int_{\Omega_f}\log|z-w|\,f(w)\,dA(w).
\]
Then \(-\Delta N_f=f\,\mathbf 1_{\Omega_f}\). By Step~4,
\(\partial_zN_f=0\) on \(\C\setminus\overline{\Omega_f}\), hence \(N_f\) is
constant on the exterior component of \(\C\setminus\overline{\Omega_f}\).
Because \(\Omega_f\) is a small deformation of the simply connected domain
\(\Omega_0\), its complement has only this exterior component. Subtracting the
exterior constant, we obtain a compactly supported function \(u_f\) satisfying
\[
-\Delta u_f=f\,\mathbf 1_{\Omega_f}
\qquad\text{in }\mathcal D'(\C),
\qquad
u_f=0\quad\text{on }\C\setminus\Omega_f .
\]
Standard Calderon--Zygmund estimates applied to the bounded compactly
supported source \(f\,\mathbf 1_{\Omega_f}\) give
\(u_f\in W^{2,p}_{\mathrm{loc}}(\C)\) for every finite \(p\), hence
\(u_f\in C^1(\C)\). Interior Schauder estimates give
\(u_f\in C^{2,\alpha}(\overline{\Omega_f})\) up to the boundary from the
interior. Since \(u_f\equiv0\) on the exterior open set and \(u_f\in C^1(\C)\),
we also have
\[
u_f=\partial_\nu u_f=0
\qquad\text{on }\partial\Omega_f .
\]

\medskip
\noindent\emph{Step 6: preservation of the sign.}
It remains only to check that \(u_f<0\) in \(\Omega_f\) after shrinking
\(\varepsilon\). The potentials \(u_f\) depend continuously on \(f\) and
\(\varphi(f)\) in \(C^1\) on compact subsets after pullback to \(\Omega_0\),
and in \(C^2\) in a fixed collar of the boundary from the interior. Hence, on
any compact set
\[
K_\delta:=\{x\in\Omega_0:\operatorname{dist}(x,\partial\Omega_0)\ge\delta\},
\]
the pullbacks \(u_f\circ\Phi_{\varphi(f)}\) converge uniformly to \(u_0\).
Since \(u_0<0\) in \(\Omega_0\), this gives strict negativity on \(K_\delta\)
for \(f\) close to \(f_0\).

Near the boundary the argument uses the second-order nondegeneracy. Because
the zero extension of \(u_0\) is \(C^1\), one has
\[
u_0=\partial_\nu u_0=0
\qquad\text{on }\partial\Omega_0 .
\]
Moreover, since \(u_0|_{\partial\Omega_0}=0\), all tangential derivatives of
the boundary trace vanish; combined with \(\partial_\nu u_0=0\), the identity
\(-\Delta u_0=f_0\) gives
\[
\partial_{\nu\nu}u_0=-f_0
\qquad\text{on }\partial\Omega_0 .
\]
The same identity holds for \(u_f\) on \(\partial\Omega_f\). Since
\(f_0>0\) on \(\partial\Omega_0\) and \(f\) is \(C^5\)-close to \(f_0\), there
is \(c_0>0\) such that
\[
\partial_{\nu\nu}u_f\le -c_0
\qquad\text{on }\partial\Omega_f
\]
for all admissible \(f\). Taylor expansion along inward normal segments then
gives, uniformly for \(x\in\partial\Omega_f\) and \(0<t<t_0\),
\[
u_f(x-t\nu_f(x))\le -\frac{c_0}{4}t^2<0,
\]
after possibly reducing \(t_0\) and \(\varepsilon\). This proves negativity in
a boundary collar, and the compact-region argument gives negativity in the
remaining part of \(\Omega_f\).

The uniqueness of \(\Omega_f\) among sufficiently small \(C^2\) normal graphs
is exactly the local uniqueness furnished by the implicit function theorem in
Step~4. The \(C^1\) dependence of \(f\mapsto\varphi(f)\) is also part of that
theorem.
\end{proof}
