\section{Proof of Theorem \ref{thm:perturb}}\label{sec:perturb-proof}

\subsection{The disk inverse step}\label{subsec:disk-inverse-step}

The proof rests on a local inverse theorem at the Daubechies disk. The result
below is self-contained, but its point of view is inspired by perturbative
inverse-source and quadrature-domain methods: Isakov's local free-boundary
scheme for inverse source problems, Cherednichenko's local inverse logarithmic
potential theorem, and the quadrature-domain framework developed by
Gustafsson, Shahgholian, Karp, and Aharonov--Schiffer--Zalcman. In the present
disk-based setting the required inverse step can be proved directly by
diagonalizing the full moment map in Fourier modes.

Fix \(0<\lambda<1\), and let \(r_\lambda>0\) be determined by
\[
1-e^{-\pi r_\lambda^2}=\lambda .
\]
For a real-valued \(2\pi\)-periodic function \(\varphi\) with
\(\|\varphi\|_{C^0}<r_\lambda/2\), set
\[
U_\varphi
:=
\{re^{i\theta}:0\le r<r_\lambda+\varphi(\theta)\}.
\]
For \(\tau>0\), let \(\mathcal A_\tau^\R\) be the Banach space of real-valued
periodic functions
\[
\varphi(\theta)=\sum_{k\in\Z}\varphi_k e^{ik\theta},
\qquad
\varphi_{-k}=\overline{\varphi_k},
\]
with norm
\[
\|\varphi\|_{\mathcal A_\tau}
:=
\sum_{k\in\Z}|\varphi_k|e^{\tau |k|}<\infty .
\]
This is a Banach algebra, and \(\mathcal A_\tau^\R\hookrightarrow C^m\) for
every fixed \(m\). In particular, small elements of \(\mathcal A_\tau^\R\)
produce real-analytic \(C^2\) Jordan domains.

\begin{proposition}[Disk symmetrized inverse theorem]\label{prop:disk-inverse-tailored}
Let \(N\ge1\), \(0<\lambda<1\), and \(r_\lambda\) be as above. There are
\(\tau>0\), \(\varepsilon>0\), and a \(C^1\) map
\[
b=(b_1,\ldots,b_N)\longmapsto \varphi_b\in\mathcal A_\tau^\R,
\qquad
\varphi_0=0,
\]
defined for \(\max_j|b_j|<\varepsilon\), such that, for
\[
P_b(z):=1+\sum_{j=1}^N b_jz^j,
\qquad
P_b^\#(z):=\overline{P_b(\overline z)},
\qquad
Q_b(w):=P_b^\#(\partial_w/\pi)P_b(w),
\]
and
\[
U_b:=U_{\varphi_b},
\]
one has
\begin{equation}\label{eq:disk-inverse-identity}
\int_{U_b}|P_b(z)|^2e^{-\pi |z|^2}e^{\pi\overline z w}\,dA(z)
=
\lambda Q_b(w),
\qquad w\in\C .
\end{equation}
Moreover,
\[
\|\varphi_b\|_{C^2(\mathbb S^1)}
\le C_{\lambda,N}\max_{1\le j\le N}|b_j|,
\]
and the branch is locally unique among sufficiently small analytic radial
graphs in \(\mathcal A_\tau^\R\).
\end{proposition}

\begin{proof}
We solve the coefficient equations obtained by expanding the entire identity
\eqref{eq:disk-inverse-identity}. Write
\[
Q_b(w)=\sum_{j=0}^N q_j(b)w^j,
\]
and \(q_j(b)=0\) for \(j>N\). The constant coefficient is real:
\[
q_0(b)=1+\sum_{k=1}^N \frac{k!}{\pi^k}|b_k|^2.
\]
Since
\[
e^{\pi\overline z w}
=
\sum_{j=0}^\infty \frac{\pi^j}{j!}\overline z^{\,j}w^j,
\]
the desired identity is equivalent to the infinite system
\begin{equation}\label{eq:disk-moment-system}
\frac{\pi^j}{j!}\int_{U_\varphi}
|P_b(z)|^2\overline z^{\,j}e^{-\pi |z|^2}\,dA(z)
=
\lambda q_j(b),
\qquad j\ge0 .
\end{equation}

We introduce the weighted sequence space adapted to the linearization at the
circle. Put
\[
a_j:=2\pi e^{-\pi r_\lambda^2}r_\lambda^{j+1}\frac{\pi^j}{j!},
\qquad j\ge0,
\]
and let \(\mathcal Y_\tau\) be the space of sequences
\(y=(y_j)_{j\ge0}\), with \(y_0\in\R\), such that
\[
\|y\|_{\mathcal Y_\tau}
:=
\frac{|y_0|}{a_0}
+2\sum_{j=1}^\infty e^{\tau j}\frac{|y_j|}{a_j}
<\infty .
\]
Define
\[
\mathcal F_j(b,\varphi)
:=
\frac{\pi^j}{j!}\int_{U_\varphi}
|P_b(z)|^2\overline z^{\,j}e^{-\pi |z|^2}\,dA(z)
-\lambda q_j(b),
\qquad j\ge0 .
\]
Thus \(\mathcal F(b,\varphi)=0\) is precisely
\eqref{eq:disk-moment-system}. At \(b=0\), \(\varphi=0\), the domain is the
disk \(D_{r_\lambda}\), and radial symmetry gives
\[
\frac{\pi^j}{j!}\int_{D_{r_\lambda}}
\overline z^{\,j}e^{-\pi |z|^2}\,dA(z)
=
\begin{cases}
\lambda, & j=0,\\
0, & j\ge1.
\end{cases}
\]
Hence \(\mathcal F(0,0)=0\).

We next compute the derivative with respect to the boundary graph. Let
\(\psi(\theta)=\sum_{k\in\Z}\psi_k e^{ik\theta}\in\mathcal A_\tau^\R\).
Differentiating the polar-coordinate formula
\[
\int_{U_\varphi}H(z)\,dA(z)
=
\int_0^{2\pi}\int_0^{r_\lambda+\varphi(\theta)}
H(re^{i\theta})r\,dr\,d\theta
\]
at \(\varphi=0\), with
\(H(z)=\overline z^{\,j}e^{-\pi|z|^2}\), gives
\[
D_\varphi\mathcal F_j(0,0)[\psi]
=
\frac{\pi^j}{j!}
\int_0^{2\pi}
\psi(\theta)r_\lambda^{j+1}e^{-ij\theta}e^{-\pi r_\lambda^2}
\,d\theta
=
a_j\psi_j .
\]
Consequently
\[
D_\varphi\mathcal F(0,0)\colon
\mathcal A_\tau^\R\to\mathcal Y_\tau,
\qquad
\psi\mapsto(a_j\psi_j)_{j\ge0},
\]
is an isomorphism. Its inverse is explicit:
if \(y\in\mathcal Y_\tau\), then
\[
\psi_0=\frac{y_0}{a_0},
\qquad
\psi_j=\frac{y_j}{a_j}\quad(j\ge1),
\qquad
\psi_{-j}=\overline{\psi_j}.
\]
The definition of the two norms gives
\(\|\psi\|_{\mathcal A_\tau}=\|y\|_{\mathcal Y_\tau}\).

It remains to justify the use of the Banach-space implicit function theorem.
For \(\|\varphi\|_{\mathcal A_\tau}\) small, the function
\(\theta\mapsto r_\lambda+\varphi(\theta)\) extends holomorphically to the
strip \(|\Im\theta|<\tau\) and stays in a fixed annulus
\(r_\lambda/2<|r|<3r_\lambda/2\). In polar coordinates,
\[
\mathcal F_j(b,\varphi)+\lambda q_j(b)
=
\frac{\pi^j}{j!}\int_0^{2\pi}e^{-ij\theta}
\int_0^{r_\lambda+\varphi(\theta)}
P_b(re^{i\theta})P_b^\#(re^{-i\theta})r^{j+1}e^{-\pi r^2}\,dr\,d\theta .
\]
Expanding the inner integral at \(r_\lambda\) gives an absolutely convergent
power series in \(\varphi\), whose coefficients are analytic functions of
\(\theta\) and polynomial functions of \(b\). Since \(\mathcal A_\tau\) is a
Banach algebra and \(P_b(re^{i\theta})P_b^\#(re^{-i\theta})\) is a finite
trigonometric polynomial of degree at most \(N\), the resulting series and
its first derivatives in \((b,\varphi)\) converge in \(\mathcal Y_\tau\) after
possibly decreasing \(\tau\) and restricting to
\(\|b\|+\|\varphi\|_{\mathcal A_\tau}<\eta\). More explicitly, Cauchy's
estimate on a slightly wider strip gives, for \(0<\tau'<\tau\),
\[
\sum_{j\ge0}e^{\tau' j}\frac1{a_j}
\left|
\frac{\pi^j}{j!}\widehat{R_j}(j)
\right|
\le
C_{\lambda,N,\tau,\tau'}\|R\|_{\mathcal A_\tau},
\]
where \(\widehat{R_j}(j)\) denotes the \(j\)-th Fourier coefficient of the
analytic coefficient appearing in the \(j\)-th moment equation. Applying this
estimate term by term to the Taylor expansion in \(\varphi\) yields
\[
\|\mathcal F(b,\varphi)-\mathcal F(b,\psi)
-D_\varphi\mathcal F(b,\psi)[\varphi-\psi]\|_{\mathcal Y_{\tau'}}
\le
C(\|b\|+\|\varphi\|_{\mathcal A_\tau}
+\|\psi\|_{\mathcal A_\tau})
\|\varphi-\psi\|_{\mathcal A_\tau}^2,
\]
and analogous estimates for differentiation in \(b\). Shrinking the strip
once and then relabelling \(\tau'\) as \(\tau\), this proves that
\[
\mathcal F:
\{(b,\varphi):\|b\|+\|\varphi\|_{\mathcal A_\tau}<\eta\}
\longrightarrow \mathcal Y_\tau
\]
is \(C^1\).

The Banach implicit function theorem now applies at \((0,0)\), because
\(D_\varphi\mathcal F(0,0)\) is an isomorphism. Thus, for \(\|b\|\) small,
there is a unique \(\varphi_b\in\mathcal A_\tau^\R\), small in
\(\mathcal A_\tau\), such that \(\mathcal F(b,\varphi_b)=0\), and
\(b\mapsto\varphi_b\) is \(C^1\). The embedding
\(\mathcal A_\tau\hookrightarrow C^2\) gives the displayed \(C^2\) bound.
Finally, \(\mathcal F(b,\varphi_b)=0\) gives all coefficient identities
\eqref{eq:disk-moment-system}; summing the power series in \(w\) gives
\eqref{eq:disk-inverse-identity} for every \(w\in\C\), since both sides are
entire functions. This proves the proposition.
\end{proof}

\begin{remark}
The proof above is the only place where analyticity of the boundary
parametrization is used. The constructed domains are therefore \(C^\infty\),
hence \(C^2\), which is the regularity needed later. The argument does not
assert a general local quadrature-domain theorem near an arbitrary reference
domain; it proves exactly the disk-based inverse statement used below.
\end{remark}

\begin{proof}[Proof of Theorem \ref{thm:perturb}]
We again use the Bargmann transform. Let
\[
P(z)=1+\sum_{k=1}^N b_k z^k,
\]
where the coefficients $b_k$ are chosen so that the Bargmann transform of
\[
f_0=h_0+\sum_{k=1}^N a_k h_k
\]
is exactly $P$. We also write
\[
P^\#(z):=\overline{P(\overline z)}
=1+\sum_{k=1}^N \overline{b_k}z^k
\]
for the coefficientwise conjugate polynomial. Then the condition that $f_0$ be an eigenfunction of $\mathcal{L}_U$ with eigenvalue $\lambda$ is equivalent to
\begin{equation}\label{eq:eigenfunction-general-new}
\int_U P(z)e^{-\pi|z|^2}e^{\pi \overline z w}\,dA(z)=\lambda P(w),
\qquad w\in \C.
\end{equation}
Set
\[
Q(w):=P^\#(\partial_w/\pi)P(w).
\]
By Proposition~\ref{prop:disk-inverse-tailored}, after decreasing
\(\varepsilon_0(\lambda,N)\) if necessary, there exists a real-analytic radial
graph \(U=U_b\), \(C^2\)-close to the Daubechies disk of radius
\(r_\lambda\), for which
\begin{equation}\label{eq:almost-reduced-new}
\int_U |P(z)|^2e^{-\pi|z|^2}e^{\pi\overline z w}\,dA(z)
=
\lambda Q(w),
\qquad w\in\C .
\end{equation}
We now recover the unsymmetrized identity
\eqref{eq:eigenfunction-general-new}. Define
\[
G(w):=\int_U P(z)e^{-\pi|z|^2}e^{\pi\overline z w}\,dA(z).
\]
The function \(G\) is entire, and differentiating under the integral is
justified by boundedness of \(U\). Since
\[
\Big(\frac{\partial_w}{\pi}\Big)^j e^{\pi\overline z w}
=\overline z^{\,j}e^{\pi\overline z w},
\]
we have
\[
P^\#(\partial_w/\pi)G(w)
=
\int_U |P(z)|^2e^{-\pi|z|^2}e^{\pi\overline z w}\,dA(z)
=
\lambda Q(w)
=
P^\#(\partial_w/\pi)(\lambda P)(w).
\]
Thus \(H:=G-\lambda P\) is an entire solution of
\[
P^\#(\partial_w/\pi)H=0.
\]

Let \(\widetilde P^\#(\zeta):=P^\#(\zeta/\pi)\), and let
\(\zeta_1,\ldots,\zeta_\ell\) be its zeros, with multiplicities
\(m_1,\ldots,m_\ell\). The elementary structure theorem for
constant-coefficient ordinary differential equations gives
\[
H(w)=\sum_{j=1}^\ell R_j(w)e^{\zeta_j w},
\]
where \(\deg R_j<m_j\). On the other hand, if
\(M:=\sup_{z\in U}|z|\), then
\[
|G(w)|\le C(1+|w|)^N e^{\pi M|w|},
\qquad w\in\C,
\]
and therefore \(H\) has exponential type at most \(\pi M\).
Since \(U\) stays in a fixed neighborhood of \(D_{r_\lambda}\), we have
\(M\le C_\lambda\). The zeros of \(P^\#\), and hence of
\(\widetilde P^\#\), escape to infinity as \(b\to0\). Shrinking
\(\varepsilon_0(\lambda,N)\) once more, we may assume
\[
|\zeta_j|>10M,\qquad 1\le j\le \ell .
\]
If some \(R_j\) were nonzero, choose one of maximal \(|\zeta_j|\) for which
\(R_j\not\equiv0\) and relabel it \(\zeta_1\). Since the \(\zeta_j\) are
\emph{distinct} (they are the distinct roots of \(\widetilde P^\#\)),
the Cauchy--Schwarz inequality
\(\Re(\zeta_j\overline{\zeta_1})\le|\zeta_j||\zeta_1|\) is strict whenever
\(\zeta_j\ne\zeta_1\) and \(|\zeta_j|=|\zeta_1|\); when \(|\zeta_j|<|\zeta_1|\)
strictness is automatic. Hence for every \(\zeta_j\ne\zeta_1\),
\[
\Re(\zeta_j\overline{\zeta_1})<|\zeta_1|^2 .
\]
Along \(w=t\overline{\zeta_1}\), \(t\to+\infty\), the term
\(R_1(w)e^{\zeta_1w}\) has modulus \(|R_1(t\overline{\zeta_1})|e^{t|\zeta_1|^2}\),
which grows like a positive power of \(t\) times \(e^{t|\zeta_1|^2}\)
because \(R_1\not\equiv0\); every other term is bounded by a polynomial
in \(t\) times \(e^{t\Re(\zeta_j\overline{\zeta_1})}\), with strictly smaller
exponential rate. Therefore
\[
|H(t\overline{\zeta_1})|\ge c e^{t|\zeta_1|^2}
\]
for all large \(t\). The exponential-type bound gives, for every
\(\delta>0\),
\[
|H(t\overline{\zeta_1})|
\le C_\delta e^{(\pi+\delta)Mt|\zeta_1|}.
\]
Letting \(t\to\infty\) and then \(\delta\downarrow0\) yields
\(|\zeta_1|\le \pi M\), contradicting \(|\zeta_1|>10M\). Hence all
\(R_j\) vanish and \(H\equiv0\), which proves
\eqref{eq:eigenfunction-general-new}.

The Bargmann transform is unitary and intertwines the localization operator
with the integral operator in \eqref{eq:eigenfunction-general-new}. Therefore
the inverse Bargmann transform \(f_0\) of \(P\) satisfies
\[
\mathcal L_U f_0=\lambda f_0 .
\]
This proves the theorem.
\end{proof}


% ==============================================================
% Section 4
% ==============================================================
