\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{mathtools}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Om}{\Omega}
\newcommand{\rstar}{\rho_{*}}
\newcommand{\rdel}{\rho_\delta}
\newcommand{\Hn}{\mathcal H^{n-1}}
\newcommand{\X}{\mathcal X}

\title{Unconditional Velocity-Defect Bound\\
       and the Reduction of Bad-Level Kinetic\\
       to a Homothetic-Trace Question}
\author{}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We prove an unconditional pointwise inequality
\[
   \Bigl(\int_{\partial^*E_\rho}|V_\rho-\bar V_\rho|\,d\Hn\Bigr)^{\!2}
   \;\le\;\Bigl(\frac{P(B_\rho)}{P(E_\rho)}\Bigr)^{\!2}D_H(t(\rho))
   \;\le\;D_H(t(\rho))
\]
for every a.e.\ finite-perimeter torsion level $\rho\in[\rstar,1]$.
The bound holds on \emph{all} levels, not only the Fusco--Julin good
set, and the prefactor $(P(B_\rho)/P(E_\rho))^{2}\le 1$ is itself
small on isoperimetrically-bad levels.  Integrating against
$d\mu=-t'\,d\rho$ and using the level-set deficit identity gives, with
no further hypothesis,
\[
   \int_{\rstar}^{\rdel}\Bigl(\int_{\partial^*E_\rho}|V_\rho-\bar V_\rho|\,d\Hn\Bigr)^{2}d\mu(\rho)
   \;\le\; C(n,\rstar)\,\delta_T(\Om).
\]
The remaining obstruction to closing the bad-level kinetic action
$\int_{B_I}|\dot F_\rho|_\X^{2}d\mu\le C\delta$ is therefore reduced
to the analogous integrated bound for the
\emph{homothetic} term $\int|H_{z_\rho,\rho}-\bar V_\rho|d\Hn$ for
some Borel centre field $z_\rho$ defined on bad levels.  We sketch
two routes for this remaining piece — the centroid space--time
$\Pi$-identity and a direct $L^1$-radial-trace
construction — and identify which inputs they need.
\end{abstract}

\section{Setup}\label{sec:setup}

Adopt the notation of \texttt{WIP\_WeightedMetricTrace.tex}: torsion
function $u=u_\Om$, $-\Delta u=1$, levels $E_\rho=\{u>t(\rho)\}$,
$|E_\rho|=\omega_n\rho^n$, $w(\rho)=-t'(\rho)\ge 0$,
$d\mu=w\,d\rho$, $V_\rho=w/|\nabla u|$,
$\bar V_\rho=P(B_\rho)/P(E_\rho)$, $D_H$ the Cauchy--Schwarz defect
$D_H=\alpha\beta-P^{2}$ with $\alpha=\int 1/|\nabla u|\,d\Hn$,
$\beta=\int|\nabla u|\,d\Hn=|E_\rho|$, $P=P(E_\rho)$,
$P(B_\rho)=n\omega_n\rho^{n-1}$.

For convenience write $P^{*}:=P(B_\rho)$.  The fundamental flux
identity $w\alpha=P^{*}$ (consequence of
$|E_\rho|=\omega_n\rho^n$ and $\alpha=-m'(t(\rho))$,
$w=-t'(\rho)$) is used throughout.

\section{The unconditional velocity-defect bound}\label{sec:main}

\begin{lemma}[Weighted variance of $V$]\label{lem:V-weighted-var}
For a.e.\ $\rho\in[\rstar,1]$ at which $E_\rho$ has finite perimeter,
\begin{equation}\label{eq:V-weighted-id}
   \int_{\partial^{*}E_\rho}\frac{(V_\rho-\bar V_\rho)^{2}}{V_\rho}\,d\Hn
   \;=\;\frac{P^{*}}{P^{2}}\,D_H(t(\rho)).
\end{equation}
\end{lemma}

\begin{proof}
Set $f:=V_\rho=w/|\nabla u|$, $\bar f:=\bar V_\rho=P^{*}/P$.
Expanding $(f-\bar f)^{2}/f=f-2\bar f+\bar f^{2}/f$ and integrating,
\[
   \int(f-\bar f)^{2}/f
   =\int f-2\bar f P+\bar f^{2}\!\int 1/f.
\]
Now $\int f=\int V_\rho=w\alpha=P^{*}$ (flux);
$\int 1/f=\int|\nabla u|/w=\beta/w$;
$\bar f P=P^{*}$ and $\bar f^{2}=P^{*\,2}/P^{2}$.  Hence
\[
   \int(f-\bar f)^{2}/f
   =P^{*}-2P^{*}+\frac{P^{*\,2}}{P^{2}}\cdot\frac{\beta}{w}
   =-P^{*}+\frac{P^{*}}{P^{2}}\cdot\frac{P^{*}\beta}{w}
   =-P^{*}+\frac{P^{*}}{P^{2}}\,\alpha\beta,
\]
where the last equality used $w\alpha=P^{*}$ to write
$P^{*}\beta/w=\alpha\beta$.  Therefore
\[
   \int(f-\bar f)^{2}/f
   =\frac{P^{*}}{P^{2}}\bigl(\alpha\beta-P^{2}\bigr)
   =\frac{P^{*}}{P^{2}}\,D_H.\qedhere
\]
\end{proof}

\begin{theorem}[Unconditional $L^{1}$ velocity-defect bound]
\label{thm:V-defect}
For a.e.\ $\rho\in[\rstar,1]$ at which $E_\rho$ has finite perimeter,
\begin{equation}\label{eq:V-defect}
   \Bigl(\int_{\partial^{*}E_\rho}|V_\rho-\bar V_\rho|\,d\Hn\Bigr)^{\!2}
   \;\le\;\Bigl(\frac{P^{*}}{P}\Bigr)^{\!2}D_H(t(\rho))
   \;\le\;D_H(t(\rho)).
\end{equation}
No isoperimetric smallness or Fusco--Julin good-level assumption is
used.
\end{theorem}

\begin{proof}
By Cauchy--Schwarz in the form
$\bigl(\int|g|\,d\Hn\bigr)^{2}\le\bigl(\int g^{2}/V_\rho\,d\Hn\bigr)\bigl(\int V_\rho\,d\Hn\bigr)$
applied to $g:=V_\rho-\bar V_\rho$ (with the standard
$\sqrt{V_\rho}\cdot\sqrt{1/V_\rho}$-factorisation),
\[
   \Bigl(\int|V_\rho-\bar V_\rho|\Bigr)^{2}
   \le\Bigl(\int\frac{(V_\rho-\bar V_\rho)^{2}}{V_\rho}\Bigr)\!\Bigl(\int V_\rho\Bigr)
   =\frac{P^{*}}{P^{2}}\,D_H\cdot P^{*}
   =\Bigl(\frac{P^{*}}{P}\Bigr)^{\!2}D_H,
\]
using Lemma~\ref{lem:V-weighted-id} and $\int V_\rho=P^{*}$.  The
second inequality of \eqref{eq:V-defect} follows from
$P\ge P^{*}$ (isoperimetric inequality).
\end{proof}

\begin{remark}[Strengthening over \textsc{TrimmedVelocityRepair}]
\label{rem:strengthen}
The estimate \eqref{eq:V-defect} is sharper than the bound proved in
\texttt{WIP\_TrimmedVelocityRepair.tex} in two ways.
\begin{enumerate}
\item It is \emph{unconditional}: the previous argument restricted to
the Fusco--Julin good set $G_I=\{D_I\le\eta_I\}$ via a truncation
$\{f\ge\bar f/2\}$.  No such restriction is needed here.  The
Cauchy--Schwarz $(\int|g|)^{2}\le(\int g^{2}/V)(\int V)$ does not
require a lower bound on $V$: it weights the variance by $V$ itself,
making the integrand integrable wherever $V$ is.
\item The prefactor $(P^{*}/P)^{2}\le 1$ is itself \emph{smaller}
on isoperimetrically bad levels.  Since
$\mathcal I(\rho)=P^{2}-P^{*\,2}=(P-P^{*})(P+P^{*})$, we have
$(P^{*}/P)^{2}=1-\mathcal I/P^{2}$.  In the regime where
$P\gg P^{*}$ on a bad level, the velocity defect is suppressed by
a factor $\le (P^{*}/P)^{2}\le P^{*\,2}/(P^{*\,2}+\mathcal I)$.
\end{enumerate}
\end{remark}

\begin{corollary}[Integrated velocity-defect on all levels]
\label{cor:V-integrated}
\begin{equation}\label{eq:V-integrated}
   \int_{\rstar}^{\rdel}\Bigl(\int_{\partial^{*}E_\rho}|V_\rho-\bar V_\rho|\,d\Hn\Bigr)^{\!2}d\mu(\rho)
   \;\le\;\int_{\rstar}^{\rdel}D_H(t(\rho))\,d\mu(\rho)
   \;\le\;C(n,\rstar)\,\delta_T(\Om).
\end{equation}
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:V-defect} pointwise, then integrate; the second
inequality is the level-set deficit identity of
\texttt{WIP\_LevelSetIdentity.tex}.
\end{proof}

\section{Reduction of the bad-level kinetic problem}\label{sec:reduction}

Combining \eqref{eq:V-defect} with the unconditional metric upper
gradient of \texttt{WIP\_LimsupDeformation.tex},
\[
   |\dot F_\rho|_\X
   \le \rho^{-n}\inf_{a\in\R^{n}}\int_{\partial^{*}E_\rho}
       |V_\rho-H_{z_\rho,\rho}-a\cdot\nu_\rho|\,d\Hn,
\]
specialising to $a=0$, and the triangle inequality
$|V_\rho-H_{z_\rho,\rho}|\le|V_\rho-\bar V_\rho|+|H_{z_\rho,\rho}-\bar V_\rho|$,
we obtain pointwise
\begin{equation}\label{eq:Fdot-decomp-uncon}
   |\dot F_\rho|_\X^{2}
   \;\le\;2\rho^{-2n}\Bigl[D_H(t(\rho))
   +\bigl(\int|H_{z_\rho,\rho}-\bar V_\rho|\,d\Hn\bigr)^{2}\Bigr]
\end{equation}
for any bounded Borel centre field $z_\rho$.  This holds on
\emph{every} a.e.\ finite-perimeter level, with no FJ smallness.

\begin{proposition}[Reduction to homothetic-trace]\label{prop:reduction}
Suppose there is a bounded Borel centre field
$\rho\mapsto z_\rho\in\R^{n}$, $|z_\rho|\le R'$, and a constant
$C_{\rm hom}=C_{\rm hom}(n,R,R',\rstar)>0$ such that
\begin{equation}\label{eq:hom-integrated}
   \int_{\rstar}^{\rdel}\Bigl(\int_{\partial^{*}E_\rho}|H_{z_\rho,\rho}-\bar V_\rho|\,d\Hn\Bigr)^{\!2}d\mu(\rho)
   \;\le\;C_{\rm hom}\,\delta_T(\Om).
\end{equation}
Then
\begin{equation}\label{eq:full-kinetic}
   \int_{\rstar}^{\rdel}|\dot F_\rho|_\X^{2}\,d\mu(\rho)
   \;\le\;C(n,R,R',\rstar)\,\delta_T(\Om).
\end{equation}
In particular both bad-level kinetic hypotheses
\textup{(eq:bad-I-action)} and \textup{(eq:bad-tau-action)} of
\texttt{WIP\_WeightedMetricTrace.tex} are discharged.
\end{proposition}

\begin{proof}
Integrate \eqref{eq:Fdot-decomp-uncon} against $d\mu$ and use
Corollary~\ref{cor:V-integrated} for the first piece,
\eqref{eq:hom-integrated} for the second, and
$\rho^{-2n}\le\rstar^{-2n}$ on $[\rstar,\rdel]$.
The bad-$\tau$ kinetic follows by the standard
$w\ge\tau_0$-on-$G_\tau$ split applied to \eqref{eq:full-kinetic}
inside \texttt{WIP\_WeightedMetricTrace.tex}'s Theorem~3.2 proof, and
the bad-$I$ kinetic is a direct corollary because $B_I$ has
finite $\mu$-measure inside $[\rstar,\rdel]$.
\end{proof}

\section{Status of \eqref{eq:hom-integrated}: two candidate routes}
\label{sec:routes}

The conditional input \eqref{eq:hom-integrated} is the
\emph{only} remaining input needed to make Plan 2 / Route $\delta$
unconditional.  Two routes for proving it are visible.

\subsection{Route I: centroid space--time $\Pi$-identity}

Choose $z_\rho:=\bar z_\rho$, the centroid of $E_\rho$.  The
divergence identity \cite[Eq.~(5.3$'$)]{SpaceTimeIdentity},
\[
   \int_{\partial^{*}E_\rho}|\nu_{E_\rho}-e_{z_\rho}|^{2}d\Hn
   =2\bigl(P(E_\rho)-P(B_\rho)\bigr)+2\Pi(E_\rho,\bar z_\rho),
\]
combined with the radial trace estimate of
\cite[Thm.~2.2]{FJCenterBridge}, gives
\begin{equation}\label{eq:hom-via-Pi}
   \Bigl(\int|H_{\bar z_\rho,\rho}-\bar V_\rho|\,d\Hn\Bigr)^{2}
   \le C(n,R,\rstar)\Bigl[|E_\rho\Delta B_\rho(\bar z_\rho)|^{2}
   +\bigl(\int|\nu-e_{z_\rho}|^{2}d\Hn\bigr)^{2}\Bigr].
\end{equation}
By the pointwise slice-rearrangement inequality
$|E_\rho\Delta B_\rho(\bar z_\rho)|^{2}\le C\,\Pi(E_\rho,\bar z_\rho)$
of \cite[Lem.~4.3]{SpaceTimeIdentity} and the integrated
identity
\[
   \int_{\rstar}^{\rdel}\Pi(E_\rho,\bar z_\rho)\,d\mu
   \le C_\Pi\,\delta_T \qquad (\Pi\text{-int})
\]
of the same block, \emph{plus} an integrated bound on
$\bigl(\int|\nu-e_{z_\rho}|^{2}\bigr)^{2}$ which is open
(naive Cauchy--Schwarz only yields a $\sqrt{\delta_T}$ rate, not
$\delta_T$), one obtains \eqref{eq:hom-integrated}.  The remaining
sub-target inside Route I is therefore
\[
   \int_{\rstar}^{\rdel}\Bigl(\int_{\partial^{*}E_\rho}|\nu-e_{z_\rho}|^{2}\,d\Hn\Bigr)^{\!2}d\mu(\rho)
   \;\le\;C\,\delta_T,
\]
which is currently isolated as a separate open problem.

\subsection{Route II: oriented radial flux on bad levels}

The oriented divergence trace
\cite[Thm.~2.1]{FJCenterBridge} gives, for \emph{any} centre $z$
with $|z|\le R+1$,
\[
   \int_{\partial^{*}E_\rho}\Bigl|\tfrac{|x-z|}{\rho}-1\Bigr|d\Hn
   \le\tfrac{n}{\rstar}|E_\rho\Delta B_\rho(z)|
   +\tfrac{W(R,\rstar)}{2}\int|\nu-e_z|^{2}d\Hn,
\]
unconditionally on the deficit.  If $z$ is chosen as the
\emph{Fraenkel} centre $z_F=z_F(E_\rho)$, then
$|E_\rho\Delta B_\rho(z_F)|^{2}\le C_F\,\mathcal I(\rho)$ holds
unconditionally (Figalli--Maggi--Pratelli).  The squared integrated
$\int|\nu-e_{z_F}|^{2}d\Hn$ at the \emph{Fraenkel} centre is not
$\le C\mathcal I$ in general — that is the input that fails when one
tries to use the Fraenkel centre as a substitute for the FJ centre
on bad levels.  Closing Route II therefore reduces to bounding
$\int\bigl(\int|\nu-e_{z_F}|^{2}\bigr)^{2}d\mu$ separately, with
the same kind of structural difficulty as Route I.

\section{Summary of progress}\label{sec:summary}

\begin{itemize}
\item Theorem~\ref{thm:V-defect} is new: the $L^{1}$-velocity defect
$\int|V-\bar V|d\Hn$ is controlled by $\sqrt{D_H}$ on \emph{every}
finite-perimeter level, with prefactor $P^{*}/P\le 1$.  The previous
\textsc{TrimmedVelocityRepair} bound was good-level only.
\item Corollary~\ref{cor:V-integrated} integrates this against
$d\mu$ unconditionally, giving the half of the kinetic action that
involves $D_H$ directly.
\item Proposition~\ref{prop:reduction} reduces the bad-level kinetic
problem to a single integrated homothetic-trace bound
\eqref{eq:hom-integrated}.
\item Section~\ref{sec:routes} isolates the residual difficulty as
\[
   \int_{\rstar}^{\rdel}\Bigl(\int|\nu-e_{z_\rho}|^{2}d\Hn\Bigr)^{\!2}d\mu(\rho)\;\le\;C\,\delta_T,
\]
for either the centroid centre $z_\rho=\bar z_\rho$ (Route I, via
$\Pi$-int) or the Fraenkel centre $z_\rho=z_F$ (Route II, direct).
This is a clean, decoupled mathematical question and not specific
to Fusco--Julin.
\end{itemize}

\begin{thebibliography}{99}

\bibitem{LevelSetIdentity}
Plan 2 building block \textsc{LevelSetIdentity},
\texttt{WIP\_LevelSetIdentity.tex}.

\bibitem{LimsupDeformation}
Plan 2 Deliverable~A, \textsc{LimsupDeformation},
\texttt{WIP\_LimsupDeformation.tex}.

\bibitem{TrimmedVelocityRepair}
Plan 2 building block \textsc{TrimmedVelocityRepair},
\texttt{WIP\_TrimmedVelocityRepair.tex}.

\bibitem{SpaceTimeIdentity}
Plan 2 auxiliary block \textsc{SpaceTimeIdentity},
\texttt{WIP\_SpaceTimeIdentity.tex}.

\bibitem{FJCenterBridge}
Plan 2 bridge block \textsc{FJCenterBridge},
\texttt{WIP\_FJCenterBridge.tex}.

\bibitem{WeightedMetricTrace}
Plan 2 building block \textsc{WeightedMetricTrace},
\texttt{WIP\_WeightedMetricTrace.tex}.

\end{thebibliography}

\end{document}
